### 2020-08-03 notebooks/Eigenvector_investigation_0528.Rmd
added 2 notebooks

---
itle: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=4,fig.height = 4)
```

```{r}
library(tidyverse)
```

```{r}
eigvecs <- data.table::fread('../data/interim/eigvecs.txt')%>%rownames_to_column('id')%>%mutate(id=as.numeric(id))
eigvals <- data.table::fread('../data/interim/eigvals.txt')
#getwd()

eig_l0 <- eigvecs[,2]#%>%pull()
eig_l1116 <- eigvecs[,1118]#%>%pull()
```

```{r}
ggplot(eigvecs,aes(x=id,y=sort(V1)))+geom_point()+geom_hline(aes(yintercept=0,color='red'))

ggplot(eigvecs,aes(x=id,y=sort(V1117)))+geom_point()+geom_hline(aes(yintercept=0,color='red'))
```

```{r}
summary(eig_l0)
summary(eig_l1116)
```

```{r}
library(igraph)
g_file = read_csv('../data/interim/costanzo_pcc_ALL')
g = graph_from_data_frame(g_file,directed = FALSE)%>%igraph::simplify()
gc = induced_subgraph(g,V(g)[components(g)$membership==1])
# ee = embed_laplacian_matrix(gc,5182)
# L = laplacian_matrix(gc)
enm_df = read_csv('../data/interim/enm_df.csv')
tictoc::tic()
lost.edges <- c()
for(i in 1:(vcount(gc)-1)){#seq_along(V(gc))){
  if (i ==vcount(gc)){
    next
  }
   c1 = induced.subgraph(gc,V(gc)[enm_df$orf_name[eigvecs[,i+1]>0]])
   c2= induced.subgraph(gc,V(gc)[enm_df$orf_name[eigvecs[,i+1]<0]])
   lost.edges <- c(lost.edges, (ecount(gc)-ecount(c1)-ecount(c2)))
  print(i,length(lost.edges))
   }
tictoc::toc()
plot(lost.edges)
```

### 2020-08-03 src/visualize/paper_figures.py

@@ -11,14 +11,15 @@ from src.visualize.visualize import plot_correlation_density, plot_vector, plot_
 from mlxtend.evaluate import permutation_test 
 
 # Random collectivity
-data_path = 'data/interim/pcc_0525/'
+data_path = 'data/interim/pcc_0603/'
 with open(f'{data_path}/rewire_data_er.pickle','rb') as f:
     e_er = pickle.load(f)
 with open(f'{data_path}/pcc.pickle','rb') as f:
     e_pcc = pickle.load(f)
 with open(f'{data_path}/rewire_data_nodegseq.pickle','rb') as f:
     e_nodegseq = pickle.load(f)
-figure_path = e_er[0].figure_path = e_pcc.figure_path = e_nodegseq[0].figure_path = 'reports/figures/pcc_0601/'
+figure_path = e_er[0].figure_path = e_pcc.figure_path = e_nodegseq[0].figure_path = 'reports/figures/pcc_0603/'
+figure_path =e_pcc.figure_path ='reports/figures/pcc_0603/'
 e_pcc.e_list[0].figure_path=figure_path
 e_er[0].plot_collectivity(figure_name = 'coll_er', figure_extension='png')
 e_pcc.plot_collectivity(figure_name = 'coll_pcc', figure_extension='png')
@@ -27,12 +28,14 @@ e_pcc.e_list[0].plot_collectivity(figure_name = 'coll_keepingdegseq', figure_ext
 
 plot_lambda_collectivity(e_pcc.gnm.getEigvals(),e_pcc.coll,figure_path,figure_name ='lambda_coll_real')
 plot_lambda_collectivity(e_er[0].gnm.getEigvals(),e_er[0].coll,figure_path,figure_name ='lambda_coll_er')
+plot_lambda_collectivity(e_nodegseq[0].gnm.getEigvals(),e_nodegseq[0].coll,figure_path,figure_name ='lambda_coll_nodegseq')
 plot_lambda_collectivity(e_pcc.e_list[0].gnm.getEigvals(),e_pcc.e_list[0].coll,figure_path,figure_name ='lambda_coll_keepingdegseq')
 #General plots
 e_pcc.plot_network_spring()
 e_pcc.plot_vector(sorted=True)
 e_pcc.plot_scatter(x='deg',y='eff',figure_name='deg_eff',figure_extension='pdf')
[…]

### 2020-09-15 notebooks/paper_plots_0909.Rmd
Rmd file for paper plots added

---
title: "Paper figures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
with open(f'data/interim/yuri/yuri.pickle','rb') as f:
    e_yuri = pickle.load(f)
with open(f'data/interim/huri/huri.pickle','rb') as f:
    e_huri = pickle.load(f)

pcc_df = e_pcc.df
yuri_df = e_yuri.df
huri_df = e_huri.df
```

```{r}
pcc_df = py$pcc_df
yuri_df = py$yuri_df
huri_df = py$huri_df
library(tidyverse)
library(cowplot)
library(ggpubr)
```

```{r}
p1 = ggplot(pcc_df, aes(x=deg,y=eff))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Effectiveness')+
    stat_cor(method='pearson')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
p2 = ggplot(pcc_df, aes(x=deg,y=sens))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Sensitivity')+
    stat_cor(method='spearman')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
lgn = cowplot::get_legend(p2)

plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn, nrow=1, labels=c('A','B',''))

```

```{r}
pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
yuri_rewire_df = read_csv('data/interim/yuri/rewire_data.csv')
huri_rewire_df = read_csv('data/interim/huri/rewire_data.csv')

rewire_df = pcc_rewire_df%>%mutate(data='pcc')%>%bind_rows(
                                                           yuri_rewire_df%>%mutate(data='yuri'))%>%
        bind_rows(huri_rewire_df%>%mutate(data='huri'))
```

```{r}
network_labels  <- c('Costanzo 2016','Yeast PPI','HuRI')
#p3 = ggplot(rewire_df, aes(x=eff_deg_pearson))+
#    stat_density(geom = "line", trim=TRUE)+
##    geom_histogram(binwidth = 0.001)+
#    geom_vline(xintercept=0.9,color='red')+
#    theme_bw()

combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
    bind_rows(
    data.frame(sens_deg_spearman= c(cor(pcc_df$deg, pcc_df$sens,method='spearman'),cor(yuri_df$deg,yuri_df$sens,method='spearman'),cor(huri_df$deg,huri_df$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df$deg, pcc_df$eff),cor(yuri_df$deg,yuri_df$eff),cor(huri_df$deg,huri_df$eff)), type='real',data=c('pcc','yuri','huri')))%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

p3 = combined_rewire_df%>%
    ggplot(aes(x=data,y=eff_deg_pearson,color=type))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_point(position=position_jitterdodge(dodge.width=0.9), aes(shape=data))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    xlab('')+ylab('Effectiveness degree correlation')+
    theme_bw()+
    theme(axis.text.x=element_blank())
p4 = combined_rewire_df%>%
    ggplot(aes(x=data,y=sens_deg_spearman,color=type))+
#    geom_boxplot()+
#    geom_jitter(aes(color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    geom_point(position=position_jitterdodge(dodge.width=0.9), aes(shape=data))+
    xlab('')+ylab('Sensitivity degree correlation')+
    theme_bw()+
    theme(axis.text.x=element_blank())+
    scale_shape_discrete(labels=network_labels)+
    scale_color_discrete(labels=c('Rewired network', 'Real network'))

lgn34  <- cowplot::get_legend(p4)
    theme(axis.text.x=element_blank())
plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn,
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=2, labels=c('A','B','','C','D',''))
ggsave('tmp.png')
```

```{r deletion}
pcc_deletion = read_csv('data/interim/deletion_analysis_0911/pcc_deletion.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='pcc')
yuri_deletion = read_csv('data/interim/deletion_analysis_0911/yuri_deletion.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='yuri')
huri_deletion = read_csv('data/interim/deletion_analysis_0911/huri_deletion.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='huri')

deletion_df  <- bind_rows(pcc_deletion, yuri_deletion, huri_deletion)%>%mutate(group = fct_relevel(group,c('pcc','yuri','huri')))

facet_labels  <- network_labels
names(facet_labels) <- c("pcc",'yuri','huri')

library(MESS)
auc_data <- deletion_df%>%
    group_by(group, variable_0)%>%
    summarise(auc=MESS::auc(gc_size,range), r = range[min(which(gc_size < 0.05))])%>%
    ungroup()%>%
    mutate(variable_0=fct_reorder(variable_0, auc, min))

auc_plot <- auc_data%>%
    ggplot(aes(x=variable_0,y=r))+
    geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
    geom_line(aes(group=group),color='grey')+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    theme_bw()+
    ylab("AUC")+
    xlab("Deletion parameter")+
    labs(color = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
    scale_colour_brewer(palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='right')

deletion_plot <- deletion_df %>% mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
    ggplot(aes(x=range, y= gc_size, color = variable_0  ))+
#    geom_point(size=1)+
        geom_line()+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('Ratio of deleted nodes')+
    ylab('Giant component ratio')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    theme_bw()+
    theme(legend.position='right')

deletion_lgn <- cowplot::get_legend(auc_plot)
plot_grid(deletion_plot+    theme(legend.position='')
, auc_plot+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.45, 0.45,.1), labels=c('A','B'))
ggsave('tmp.png',width=12)

```

### 2020-09-15 src/data/gi_enm.py
Analysis script for GI data

@@ -1,0 +1,36 @@
+import src
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+import networkx as nx
+import pickle
+from tqdm import tqdm
+from src.enm import *
+from src.utils import *
+from Bio import SeqIO
+
+
+figure_path = 'reports/figures/gi_0827'
+enm = Enm('enm')
+enm.read_network('data/interim/SGA_02_withoverlapping.csv',sep=',')
+enm.gnm_analysis(normalized=False)
+
+enm.figure_path=figure_path
+enm.output_path = 'data/interim/gi_0827/'
+enm.spring_pos()
+
+enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False)
+
+neigbor_btw = []
+neighbor_degree = []
+for i in enm.graph_gc.nodes:
+    neigbor_btw.append(np.average([enm.df.loc[enm.df.orf_name==a,'btw'].values for a in nx.neighbors(enm.graph_gc,i)]))
+    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
+
+enm.df['neighbor_btw'] = neigbor_btw
+enm.df['neighbor_degree'] = neighbor_degree
+
+with open(f"{enm.output_path}/gi.pickle",'wb') as f:
+    pickle.dump(enm,f)
+
+

### 2020-09-15 src/features/pcc_enm.py

@@ -1,62 +1,0 @@
-import src
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from tqdm import tqdm
-from src.enm import *
-from src.utils import *
-
-from Bio import SeqIO
-
-
-figure_path = 'reports/figures/pcc_0603'
-enm = Enm('enm')
-enm.read_network('data/interim/costanzo_pcc_ALL',sep=',')
-enm.gnm_analysis(normalized=True)
-
-enm.figure_path=figure_path
-enm.output_path = 'data/interim/pcc_0603/'
-
-enm.simulate_rewire(output_name='rewire_data',save=True, normalized=True)
-enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=True)
-enm.simulate_rewire(output_name='rewire_data_er', save=True, nodegseq=True,random_network_type='er', normalized=True)
-
-with open(f"{enm.output_path}/pcc.pickle",'wb') as f:
-    pickle.dump(enm,f)
-
-
-## ---- 
-from src.visualize.visualize import plot_lambda_collectivity
-
-plot_lambda_collectivity(enm.gnm.getEigvals(),enm.coll,figure_path)
-
-
-#enm
-enm.fiedler_evaluation()
-
-adj = nx.adjacency_matrix(gc).todense()
-orf_names = self.df.orf_name
-g_ig = igraph.Graph.Adjacency((adj > 0).tolist())
-g_ig.vs['name'] = orf_names
-#g_ig.set_vertec
-gc = self.graph_gc
-eigvecs = self.gnm.getEigvecs()
-figsize = kwargs.pop('figsize',(12,6))
-
-lost_edges = [ ]
-
-for i in tqdm(range(5182)):
-    cl1 = [orf_names[i] for i, j in enumerate(eigvecs[:,i]) if j>0]
-    cl2 = [orf_names[i] for i, j in enumerate(eigvecs[:,i]) if j<0]
-    cg1 = g_ig.induced_subgraph(cl1)
-    cg2 = g_ig.induced_subgraph(cl2)
-#    cg1 = nx.induced_subgraph(gc, cl1)
-#    cg2 = nx.induced_subgraph(gc,cl2)
-    lost_edges.append( len(gc.edges)-(len(cg2.es)+len(cg1.es)))
-
-lost_edges[:10]
-#enm.lost_edges[:10]
[…]

### 2020-09-17 notebooks/paper_plots_0909.Rmd
targeted attack and average neighbor degree analysis plots added

@@
     e_pcc = pickle.load(f)
-with open(f'data/interim/yuri/yuri.pickle','rb') as f:
+with open(f'data/interim/yuri_0916/yuri.pickle','rb') as f:
     e_yuri = pickle.load(f)
-with open(f'data/interim/huri/huri.pickle','rb') as f:
+with open(f'data/interim/huri_0916/huri.pickle','rb') as f:
     e_huri = pickle.load(f)
@@
 pcc_df = e_pcc.df
+pcc_gc = e_pcc.graph_gc
+pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))
 yuri_df = e_yuri.df
@@
 ```{r}
-pcc_df = py$pcc_df
-yuri_df = py$yuri_df
-huri_df = py$huri_df
+pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.))
+yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.))
+huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.))
+
+combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
+    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
 library(tidyverse)
@@
     theme_bw()
-p2 = ggplot(pcc_df, aes(x=deg,y=sens))+
+p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
     geom_point(aes(color=cat_))+
@@
  nrow=2, labels=c('A','B','','C','D',''))
-ggsave('tmp.png')
+ggsave('reports/figures/paper_figures_0916/fig2.png')
 ```
@@
 ,deletion_lgn, nrow=1, rel_widths =c(0.45, 0.45,.1), labels=c('A','B'))
-ggsave('tmp.png',width=12)
+ggsave('reports/figures/paper_figures_0916/fig3.png',width=12)
 
 ```
+
+# Sensor connectivity and neighbor degree
+```{r}
+sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
+    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
+
+#library(ggridges)
+
+#sensor_connectivity_df %>%
+#    filter(type=='random')%>%
+#    ggplot(aes(x=ratio,y=data))+
+##    facet_grid(rows=vars(data))+
+##    geom_histogram(bins=50)
+#    geom_density_ridges()
+#ggsave('tmp.png',width=12)
+
+#p3 = 
+sensor_connectivity_plot <- 
+    ggplot()+
+    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
+                 aes(x=data,y=ratio,color=type))+
+#    geom_jitter()+
+    geom_point(data=sensor_connectivity_df%>%filter(type=='real'),
+            aes(x=data,y=ratio,color=type, group=data))+
+               #position=position_jitter(), aes(shape=data))+
+    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
+    scale_x_discrete(labels=network_labels)+
+  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
+    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
+    theme_bw()
+neighbor_degree_plot <- combined_df%>%
+    ggplot(aes(x=neighbor_degree,y=sens_norm))+
+    facet_grid(rows=vars(data),labeller = labeller(data=facet_labels))+
+    geom_point()+
+    theme_bw()+
+    xlab('Average neighbor degree')+
+    ylab('Sensitivity')
+plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
+ggsave('reports/figures/paper_figures_0916/fig4.png')
+
+```

### 2020-09-24 notebooks/paper_plots_0909.Rmd
Changed AUC y axis label amd converted to bar plot

@@
     ggplot(aes(x=variable_0,y=r))+
-    geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
-    geom_line(aes(group=group),color='grey')+
+    geom_bar(aes(fill=variable_0),stat='identity')+
+ #   geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
+#    geom_line(aes(group=group),color='grey')+
     facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
     theme_bw()+
-    ylab("AUC")+
+    ylab("Cost of fractioning the network (AUC)")+
     xlab("Deletion parameter")+
-    labs(color = "Deletion\nparameter")+
+    labs(fill = "Deletion\nparameter")+
     scale_x_discrete(labels = c(
@@
                                 "Sensitivity"))+
-    scale_colour_brewer(palette = "Set1", labels= c(
+    scale_fill_brewer(palette = "Set1", labels= c(
                                 "Degree",
@@
 , auc_plot+    theme(legend.position='')
-,deletion_lgn, nrow=1, rel_widths =c(0.45, 0.45,.1), labels=c('A','B'))
+,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))
 ggsave('reports/figures/paper_figures_0916/fig3.png',width=12)
@@
 neighbor_degree_plot <- combined_df%>%
-    ggplot(aes(x=neighbor_degree,y=sens_norm))+
-    facet_grid(rows=vars(data),labeller = labeller(data=facet_labels))+
+    ggplot(aes(x=sens_norm,y=neighbor_degree))+
+    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
     geom_point()+
     theme_bw()+
-    xlab('Average neighbor degree')+
-    ylab('Sensitivity')
+    ylab('Average neighbor degree')+
+    xlab('Sensitivity')
 plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
@@
 ```
+
+```{r}
+convert_networkx_to_igraph <- 			# 
+    function
+(
+ 	nx_object,
+    df
+)
+{
+    nx =  reticulate::import("networkx")
+    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
+    ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
+    igraph::set_vertex_attr(ig, "pos", nxqjjj
+    ig
+
+}
+```
+```{r}
+plot_network_spring <- 			# 
+    function
+(
+    gc , df , pos , ... 	
+)
+{
+ pcc_gc_ig = convert_networkx_to_igraph(gc, df)
+
+png('tmp.png')
+plot(pcc_gc_ig, vertex.size=1, vertex.label=NA, layout = pos)
+dev.off()
+
+}
+pcc_gc = py$pcc_gc
+pcc_gc_pos = matrix(unlist(py$pcc_gc_pos),ncol=2,byrow=TRUE)
+plot_network_spring(pcc_gc, pcc_df, pcc_gc_pos)
+```

### 2020-09-26 notebooks/paper_plots_0909.Rmd
separated scatter plots from randomizations

--- 2020-09-15 notebooks/paper_plots_0909.Rmd
@@
 ```{r}
-pcc_df = py$pcc_df
-yuri_df = py$yuri_df
-huri_df = py$huri_df
 library(tidyverse)
@@
 library(ggpubr)
+
+pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
+yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
+huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
+
+combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
+    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
 ```
@@
 ```{r}
-p1 = ggplot(pcc_df, aes(x=deg,y=eff))+
+p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
     geom_point(aes(color=cat_))+
@@
     guides(color=guide_legend(title="Experiment categories"))+
-    theme_bw()
+    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
 lgn = cowplot::get_legend(p2)
-
-plot_grid(p1+theme(legend.position=''),
+fig3 = plot_grid(p1+theme(legend.position=''),
           p2+theme(legend.position=''),
-          lgn, nrow=1, labels=c('A','B',''))
-
+          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
+ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
 ```
@@
 
+facet_labels  <- network_labels
+names(facet_labels) <- c("pcc",'yuri','huri')
+
 combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
@@
 
-p3 = combined_rewire_df%>%
-    ggplot(aes(x=data,y=eff_deg_pearson,color=type))+
+p3 = 
+    ggplot()+
+    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
 #    geom_boxplot()+
 #    geom_jitter()+
-    geom_point(position=position_jitterdodge(dodge.width=0.9), aes(shape=data))+
+    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
+    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
     guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-    xlab('')+ylab('Effectiveness degree correlation')+
+    ylab('Density')+xlab('Effectiveness degree correlation')+
     theme_bw()+
-    theme(axis.text.x=element_blank())
-p4 = combined_rewire_df%>%
-    ggplot(aes(x=data,y=sens_deg_spearman,color=type))+
+    theme(panel.spacing = unit(2, "lines"))+
+    scale_y_continuous(expand = c(0, 0)) 
+p4 = 
+    ggplot()+
+    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
 #    geom_boxplot()+
-#    geom_jitter(aes(color=type))+
+#    geom_jitter()+
+    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
+    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
     guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-    geom_point(position=position_jitterdodge(dodge.width=0.9), aes(shape=data))+
-    xlab('')+ylab('Sensitivity degree correlation')+
+    ylab('Density')+xlab('Sensitivity degree correlation')+
     theme_bw()+
-    theme(axis.text.x=element_blank())+
-    scale_shape_discrete(labels=network_labels)+
-    scale_color_discrete(labels=c('Rewired network', 'Real network'))
-
+    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
+    scale_color_discrete(labels=c('Rewired networks', 'Real networks'))+
+    scale_y_continuous(expand = c(0, 0)) 
 lgn34  <- cowplot::get_legend(p4)
-    theme(axis.text.x=element_blank())
-plot_grid(p1+theme(legend.position=''),
-          p2+theme(legend.position=''),
-          lgn,
+plot_grid(
           p3+theme(legend.position=''),
  p4+theme(legend.position=''), lgn34,
- nrow=2, labels=c('A','B','','C','D',''))
-ggsave('tmp.png')
+ nrow=3, labels=c('A','B','','C','D',''), rel_heights = c(0.45,0.45,0.1))
+ggsave('reports/figures/paper_figures_0916/fig2.png',width=7)
 ```
@@
 
-facet_labels  <- network_labels
-names(facet_labels) <- c("pcc",'yuri','huri')
-
 library(MESS)
@@
 auc_plot <- auc_data%>%
-    ggplot(aes(x=variable_0,y=r))+
-    geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
-    geom_line(aes(group=group),color='grey')+
+    ggplot(aes(x=variable_0,y=auc))+
+    geom_bar(aes(fill=variable_0),stat='identity')+
+ #   geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
+#    geom_line(aes(group=group),color='grey')+
     facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
     theme_bw()+
-    ylab("AUC")+
+    ylab("Robustness")+
     xlab("Deletion parameter")+
-    labs(color = "Deletion\nparameter")+
+    labs(fill = "Deletion\nparameter")+
     scale_x_discrete(labels = c(
@@
 
+#combined_df %>% group_by(data)%>%summarise(deg_btw = cor(deg, btw),
+#                                           deg_eff = cor(deg,eff),
+#                                           deg_sens = cor(deg,sens),
+#                                           deg_eigen = cor(deg, eigenvec_centr),
+#                                           deg_closeness = cor(deg, closeness_centr))
 deletion_plot <- deletion_df %>% mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
@@
     scale_colour_brewer(palette = "Set1")+ 
-    xlab('Ratio of deleted nodes')+
-    ylab('Giant component ratio')+
+    xlab('% Deleted Nodes')+
+    ylab('% Giant Component Size')+
     scale_y_continuous(labels = scales::percent)+
@@
 , auc_plot+    theme(legend.position='')
-,deletion_lgn, nrow=1, rel_widths =c(0.45, 0.45,.1), labels=c('A','B'))
-ggsave('tmp.png',width=12)
+,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))
+ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)
 
 ```
+
+# Sensor connectivity and neighbor degree
+```{r}
+sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
+    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
+
+#library(ggridges)
+
+#sensor_connectivity_df %>%
+#    filter(type=='random')%>%
+#    ggplot(aes(x=ratio,y=data))+
+##    facet_grid(rows=vars(data))+
+##    geom_histogram(bins=50)
+#    geom_density_ridges()
+#ggsave('tmp.png',width=12)
+
+#p3 = 
+sensor_connectivity_plot <- 
+    ggplot()+
+    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
+                 aes(x=data,y=ratio,color=type))+
+#    geom_jitter()+
+    geom_point(data=sensor_connectivity_df%>%filter(type=='real'),
+            aes(x=data,y=ratio,color=type, group=data))+
+               #position=position_jitter(), aes(shape=data))+
+    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
+    scale_x_discrete(labels=network_labels)+
+  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
+    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
+    theme_bw()
+neighbor_degree_plot <- combined_df%>%
+    ggplot(aes(x=sens_norm,y=neighbor_degree))+
+    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
+    geom_point()+
+    theme_bw()+
+    ylab('Average neighbor degree')+
+    xlab('Sensitivity')
+plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
+ggsave('reports/figures/paper_figures_0916/fig5.png')
+
+```
+
+```{r}
+convert_networkx_to_igraph <- 			# 
+    function
+(
+ 	nx_object,
+    df
+)
+{
+    nx =  reticulate::import("networkx")
+    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
+    #ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
+    ig = igraph::set_vertex_attr(ig , name =  'name', value  = (df$orf_name))
+    #igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
+    ig
+}
+```
+```{r}
+plot_network_spring <- 			# 
+    function
+(
+    gc , df , pos , ... 	
+)
+{
+ pcc_gc_ig = convert_networkx_to_igraph(gc, df)
+
+png('tmp.png')
+plot(pcc_gc_ig, vertex.size=1, vertex.label=NA, layout = pos)
+dev.off()
+
+}
+pcc_gc = py$pcc_gc
+pcc_gc_pos = matrix(unlist(py$pcc_gc_pos),ncol=2,byrow=TRUE)
+
+pcc_gc_ig = convert_networkx_to_igraph(pcc_gc, pcc_df)
+
+get_subnetwork  <- function(gc, subset){
+    sub_gc_nodes = igraph::ego(gc, nodes= subset)%>%unlist%>%unique
+
+    sub_gc  <- igraph::induced_subgraph(gc, sub_gc_nodes)
+
+    sub_gc
+}
+
+pcc_sensors = pcc_df %>% filter(sens>quantile(sens,0.99))
+pcc_sensor_sub = get_subnetwork(pcc_gc_ig, pcc_sensors$orf_name)
+#plot_network_spring(pcc_gc, pcc_df, pcc_gc_pos)
+
+png('tmp.png', res=150, height=3, width=3,units='in')
+plot(pcc_sensor_sub, vertex.size = 2 , vertex.color = 'white', vertex.label.color='black',vertex.label.size=8, vertex.label.cex = 0.4, layout=igraph::layout.fruchterman.reingold)
+dev.off()
+```

### 2020-10-05 notebooks/paper_plots_0909.Rmd
auc made inlet

@@
     ungroup()%>%
-    mutate(variable_0=fct_reorder(variable_0, auc, min))
+    mutate(variable_0=fct_reorder(variable_0, auc, min))%>%pivot_wider(-r, names_from=group, values_from=auc)
 
-auc_plot <- auc_data%>%
-    ggplot(aes(x=variable_0,y=auc))+
-    geom_bar(aes(fill=variable_0),stat='identity')+
- #   geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
-#    geom_line(aes(group=group),color='grey')+
-    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
+auc_plot_pcc <- auc_data%>%
+    ggplot(aes(x=variable_0,y=pcc))+
+    geom_bar(aes(fill=variable_0,alpha = (variable_0  )),stat='identity')+
     theme_bw()+
@@
     xlab("Deletion parameter")+
+    scale_alpha_manual(name='Deletion\nparameter', values = c(0.3,0.3,1,0.3,0.3,0.3,1), labels= c(
+                                "Degree",
+                                "Betweenness",
+                                "Effectiveness",
+                                "Closeness",
+                                "Eigencentrality",
+                                "Random",
+                                "Sensitivity"), guide = 'legend')+
     labs(fill = "Deletion\nparameter")+
     scale_x_discrete(labels = c(
+                                "D",
+                                "B",
+                                "Eff",
+                                "C",
+                                "E",
+                                "R",
+                                "S"))+
+    scale_fill_brewer(name = 'Deletion\nparameter', palette = "Set1", guide='legend', labels= c(
                                 "Degree",
@@
                                 "Sensitivity"))+
+   theme(legend.position='bottom', legend.title=element_text(size=18), legend.text=element_text(size=14),legend.spacing.x = unit(1.0, 'cm'),legend.spacing.y = unit(1.0, 'cm'))
+auc_plot_yuri <- auc_data%>%
+    ggplot(aes(x=variable_0,y=yuri))+
+    geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ),stat='identity')+
+    theme_bw()+
+    ylab("Robustness")+
+    xlab("Deletion parameter")+
+    labs(fill = "Deletion\nparameter")+
+    scale_alpha_manual(name = '', values = c(0.3, 1), guide = FALSE)+
+    scale_x_discrete(labels = c(
+                                "D",
+                                "B",
+                                "Eff",
+                                "C",
+                                "E",
+                                "R",
+                                "S"))+
+    scale_fill_brewer(name='', palette = "Set1", labels= c(
+                                "Degree",
+                                "Betweenness",
+                                "Effectiveness",
+                                "Closeness",
+                                "Eigencentrality",
+                                "Random",
+                                "Sensitivity"))+
+   theme(legend.position='right')
+auc_plot_huri<- auc_data%>%
+    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ))+
+    geom_bar(aes(fill=variable_0),stat='identity')+
+    theme_bw()+
+    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
+    ylab("Robustness")+
+    xlab("Deletion parameter")+
+    labs(fill = "Deletion\nparameter")+
+    scale_x_discrete(labels = c(
+                                "D",
+                                "B",
+                                "Eff",
+                                "C",
+                                "E",
+                                "R",
+                                "S"))+
     scale_fill_brewer(palette = "Set1", labels= c(
@@
    theme(legend.position='right')
-
 #combined_df %>% group_by(data)%>%summarise(deg_btw = cor(deg, btw),
@@
 #                                           deg_closeness = cor(deg, closeness_centr))
-deletion_plot <- deletion_df %>% mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
-    ggplot(aes(x=range, y= gc_size, color = variable_0  ))+
+deletion_plot_pcc <-  pcc_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
+    ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ))+
 #    geom_point(size=1)+
-        geom_line()+
-    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
+        geom_line(size=2)+
+#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
     scale_colour_brewer(palette = "Set1")+ 
@@
     theme_bw()+
-    theme(legend.position='right')
+    ggtitle('Costanzo 2016')+
+    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
+    theme(legend.position='bottom',panel.border = element_blank(), axis.line = element_line())
+deletion_plot_yuri <-  yuri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
+ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion')  ))+
+#    geom_point(size=1)+
+        geom_line(size=2)+
+#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
+    scale_colour_brewer(palette = "Set1")+ 
+    xlab('% Deleted Nodes')+
+    ggtitle('Yeast PPI')+
+    ylab('% Giant Component Size')+
+    scale_y_continuous(labels = scales::percent)+
+    scale_x_continuous(labels = scales::percent)+
+    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
+    theme_bw()+
+    theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
+deletion_plot_huri <-  huri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
+ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion')  ))+
+#    geom_point(size=1)+
+        geom_line(size=2)+
+#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
+    scale_colour_brewer(palette = "Set1")+ 
+    xlab('% Deleted Nodes')+
+    ylab('% Giant Component Size')+
+    ggtitle('HuRI')+
+    scale_y_continuous(labels = scales::percent)+
+    scale_x_continuous(labels = scales::percent)+
+    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
+    theme_bw()+
+    theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
+deletion_lgn <- cowplot::get_legend(auc_plot_pcc)
+pcc_with_inset = ggdraw(deletion_plot_pcc+    theme(legend.position=''))+
+  draw_plot(auc_plot_pcc+theme(legend.position=''), .50, .62, .45, .35) +
+  draw_plot_label(
+    c("A", ""),
+    c(0, 0.45),
+    c(1, 0.95),
+    size = 12
+  )
+yuri_with_inset = ggdraw(deletion_plot_yuri+    theme(legend.position=''))+
+  draw_plot(auc_plot_yuri+theme(legend.position=''), .50, .62, .45, .35) +
+  draw_plot_label(
+    c("B", ""),
+    c(0, 0.45),
+    c(1, 0.95),
+    size = 12
+  )
+huri_with_inset = ggdraw(deletion_plot_huri+    theme(legend.position=''))+
+  draw_plot(auc_plot_huri+theme(legend.position=''), .50, .62, .45, .35) +
+  draw_plot_label(
+    c("C", ""),
+    c(0, 0.45),
+    c(1, 0.95),
+    size = 12
+  )
+plot_grid(pcc_with_inset, yuri_with_inset, huri_with_inset, ncol=3)%>%plot_grid(deletion_lgn,nrow=2, rel_heights=c(0.9,.1))
+ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)
 
-deletion_lgn <- cowplot::get_legend(auc_plot)
-plot_grid(deletion_plot+    theme(legend.position='')
-, auc_plot+    theme(legend.position='')
+plot_grid(deletion_plot_pcc+    theme(legend.position='')
+, auc_plot_pcc+    theme(legend.position='')
 ,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))
-ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)
 
@@
 ```
-```{r}
-plot_network_spring <- 			# 
-    function
-(
-    gc , df , pos , ... 	
-)
-{
- pcc_gc_ig = convert_networkx_to_igraph(gc, df)
-
-png('tmp.png')
-plot(pcc_gc_ig, vertex.size=1, vertex.label=NA, layout = pos)
-dev.off()
-
-}
-pcc_gc = py$pcc_gc
-pcc_gc_pos = matrix(unlist(py$pcc_gc_pos),ncol=2,byrow=TRUE)
-
-pcc_gc_ig = convert_networkx_to_igraph(pcc_gc, pcc_df)
-
-get_subnetwork  <- function(gc, subset){
-    sub_gc_nodes = igraph::ego(gc, nodes= subset)%>%unlist%>%unique
-
-    sub_gc  <- igraph::induced_subgraph(gc, sub_gc_nodes)
-
-    sub_gc
-}
-
-pcc_sensors = pcc_df %>% filter(sens>quantile(sens,0.99))
-pcc_sensor_sub = get_subnetwork(pcc_gc_ig, pcc_sensors$orf_name)
-#plot_network_spring(pcc_gc, pcc_df, pcc_gc_pos)
-
-png('tmp.png', res=150, height=3, width=3,units='in')
-plot(pcc_sensor_sub, vertex.size = 2 , vertex.color = 'white', vertex.label.color='black',vertex.label.size=8, vertex.label.cex = 0.4, layout=igraph::layout.fruchterman.reingold)
-dev.off()
-```

### 2020-10-05 notebooks/paper_plots_0909.Rmd
scatter plots of random and real networks created.

@@
 
-pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
-yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
-huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
-
+pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    py$e_pcc$e_list[[1]]$df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'random')
+)%>%mutate(group=fct_relevel(group, c('real','random')))
+yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    py$e_yuri$e_list[[1]]$df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'random')
+)%>%mutate(group=fct_relevel(group, c('real','random')))
+huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    py$e_huri$e_list[[1]]$df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'random')
+)%>%mutate(group=fct_relevel(group, c('real','random')))
 combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
@@
 ```{r}
+pcc_deg_eff = pcc_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=eff_norm))+
+    geom_point()+
+    facet_grid(rows = vars(group), scales='free') +
+    theme_bw()+
+    ylab("Effectiveness")+
+    xlab("Degree")+
+    stat_cor(method='pearson', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+pcc_deg_sens = pcc_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=sens_norm))+
+    geom_point()+
+    facet_grid(rows = vars(group), scales='free') +
+    theme_bw()+
+    ylab("Sensitivity")+
+    xlab("Degree")+
+    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+yuri_deg_eff = yuri_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=eff_norm))+
+    geom_point()+
+    facet_grid(rows = vars(group), scales='free') +
+    theme_bw()+
+    ylab("Effectiveness")+
+    xlab("Degree")+
+    stat_cor(method='pearson', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+yuri_deg_sens = yuri_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=sens_norm))+
+    geom_point()+
+    facet_grid(rows = vars(group), scales='free') +
+    theme_bw()+
+    ylab("Sensitivity")+
+    xlab("Degree")+
+    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+huri_deg_eff = huri_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=eff_norm))+
+    geom_point()+
+    facet_grid(rows = vars(group), scales='free') +
+    theme_bw()+
+    ylab("Effectiveness")+
+    xlab("Degree")+
+    stat_cor(method='pearson', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+huri_deg_sens = huri_df %>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=sens_norm))+
+    geom_point()+
+    facet_grid(rows = vars(group), scales='free') +
+    theme_bw()+
+    ylab("Sensitivity")+
+    xlab("Degree")+
+    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
+                   yuri_deg_eff, yuri_deg_sens,
+                   huri_deg_eff, huri_deg_sens,
+                   ncol=2)
+ggsave('tmp.png',width=10,height=10)
+
 p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
@@
 
-combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
+combined_rewire_df <- rewire_df%>%select(data, eff_deg_spearman,sens_deg_spearman)%>%mutate(type = 'random')%>% 
     bind_rows(
-    data.frame(sens_deg_spearman= c(cor(pcc_df$deg, pcc_df$sens,method='spearman'),cor(yuri_df$deg,yuri_df$sens,method='spearman'),cor(huri_df$deg,huri_df$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df$deg, pcc_df$eff),cor(yuri_df$deg,yuri_df$eff),cor(huri_df$deg,huri_df$eff)), type='real',data=c('pcc','yuri','huri')))%>%
+    data.frame(sens_deg_spearman= c(cor(pcc_df$deg, pcc_df$sens,method='spearman'),cor(yuri_df$deg,yuri_df$sens,method='spearman'),cor(huri_df$deg,huri_df$sens,method='spearman')), eff_deg_spearman= c(cor(pcc_df$deg, pcc_df$eff,method='spearman'),cor(yuri_df$deg,yuri_df$eff,method='spearman'),cor(huri_df$deg,huri_df$eff,method='spearman')), type='real',data=c('pcc','yuri','huri')))%>%
     mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
@@
 #    geom_jitter()+
-    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
-    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
+    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_spearman,color=type, y=..scaled..),linetype = "dashed")+
+    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_spearman,color=type))+
     guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+

### 2020-11-09 notebooks/poster_plots_1023.Rmd
poster plots Rmd added for RSGDream

---
title: "Paper figures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)

pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))
```

```{r}
library(tidyverse)
library(cowplot)
library(ggpubr)

pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
    py$e_pcc$e_list[[1]]$df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'random')
)%>%mutate(group=fct_relevel(group, c('real','random')))
combined_df = pcc_df

random_dfs_list = lapply(list.files('data/interim/pcc_1020/random_dfs', full.names=T), data.table::fread)
random_dfs_list = mapply(c, random_dfs_list, list.files('data/interim/pcc_1020/random_dfs'), SIMPLIFY=F)
random_dfs_100 = data.table::rbindlist(random_dfs_list,fill=T)
colnames(random_dfs_100)[length(colnames(random_dfs_100))] <- 'filename'
```
```{r}
theme_fontsize = theme(axis.text = element_text(size = 14), axis.title = element_text(size = 20), legend.text = element_text(size=16))
```

Random mean calculations
```{r}
random_dfs_means = random_dfs_100%>%
    group_by(filename)%>%
    summarise(mean_eff = mean(eff), mean_sens = mean(sens), mean_btw = mean(btw))%>%
    ungroup()
real_mean_eff = mean(pcc_df$eff[pcc_df$group=='real'])
real_mean_sens = mean(pcc_df$sens[pcc_df$group=='real'])

eff_p = (sum(real_mean_eff<random_dfs_means$mean_eff)+1)/(length(random_dfs_means$mean_eff)+1)

sens_p = (sum(real_mean_sens<random_dfs_means$mean_sens)+1)/(length(random_dfs_means$mean_sens)+1)
```

Degree - Eff - Sens distributions
```{r}
combined_df%>%filter(group=='real')%>%
    ggplot(aes(x=deg, y = ..count../sum(..count..)))+
#    facet_grid(rows=vars(data))+
    geom_histogram(binwidth=1)+
#    xlim(1,NA)+
    ylim(NA, 0.1)

degree_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     combined_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     combined_df%>%filter(group=='random'),aes(x=deg,y=..scaled..,color=group),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())+theme_fontsize
eff_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= combined_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= combined_df%>%filter(group=='random'),
               aes(x=eff_norm ,y=..scaled..,color=group),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())+theme_fontsize+
annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
sensitivity_dens <- 
    ggplot()+
#    facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= combined_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= combined_df%>%filter(group=='random'),
               aes(x=sens_norm ,y=..scaled..,color=group),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())+
theme_fontsize+
annotate("text", x = 0.001, y = 0.9, label=sprintf("p = %#.2f", sens_p), fontface='italic', size=6)
dens_lgn = cowplot::get_legend(sensitivity_dens)
dens_plots = cowplot::plot_grid(degree_dens+theme(legend.position='none'), eff_dens+theme(legend.position='none'), sensitivity_dens+theme(legend.position='none'), ncol=3,labels=c('A','B','C'))
cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
#ggsave('tmp.png')
#ggsave('reports/figures/poster_figures_1023/fig3.png')
#    coord_trans(x = "log10", y = "log1p")
#    scale_x_continuous(trans = "log10")
    #scale_x_log10()
#    geom_histogram(binwidth=1)+
#    xlim(1,NA)+
#    ylim(NA, 0.1)

```

```{r}
real_random_labels = c('Real\nnetwork','Rewired\nnetwork')
names(real_random_labels)  = c('real','random')
pcc_deg_eff = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=eff_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Effectiveness")+
    xlab("Degree")+
    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1,size=6) +
    theme(strip.text.y = element_text(angle = 0))+theme_fontsize+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
pcc_deg_sens = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
    ggplot(aes(x=deg, y=sens_norm))+
    geom_point()+
#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
    theme_bw()+
    ylab("Sensitivity")+
    xlab("Degree")+
    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1,size=6) +
    theme(strip.text.y = element_text(angle = 0))+theme_fontsize+
    scale_y_continuous(labels = scales::label_scientific(digits=1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
                    labels = c('D','E'),
                   ncol=2)
```

```{r}
pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
rewire_df = pcc_rewire_df%>%mutate(data='pcc')
```

```{r}
network_labels  <- c('Costanzo 2016','Yeast PPI','HuRI')
#p3 = ggplot(rewire_df, aes(x=eff_deg_pearson))+
#    stat_density(geom = "line", trim=TRUE)+
##    geom_histogram(binwidth = 0.001)+
#    geom_vline(xintercept=0.9,color='red')+
#    theme_bw()

facet_labels  <- network_labels
names(facet_labels) <- c("pcc",'yuri','huri')

combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
    bind_rows(
    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc')))
p3 = 
    ggplot()+
#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree\ncorrelation')+
    theme_bw()+theme_fontsize+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) +
    annotate("text", label="p = 0.009", x = 0.6, y= 0.9, fontface = 'italic', size=6)
p4 = 
    ggplot()+
#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree\ncorrelation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real network'))+
    scale_y_continuous(expand = c(0, 0)) +theme_fontsize+
    annotate("text", label="p = 0.009", x = -0.6, y= 0.9, fontface='italic',size=6)
lgn34  <- cowplot::get_legend(p4)
distr_plots <- plot_grid(
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), nrow=1, labels=c('F','G'))
plot_grid(dens_plots, deg_scatter_plots, distr_plots, lgn34,
 nrow=4,rel_heights = c(0.4,0.25, 0.25,.1))
ggsave('reports/figures/poster_figures_1023/fig4.png',width=9,height=12)
```

# Sensor connectivity and neighbor degree

```{r}
sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))%>%filter(data=='pcc')

#library(ggridges)

#sensor_connectivity_df %>%
#    filter(type=='random')%>%
#    ggplot(aes(x=ratio,y=data))+
##    facet_grid(rows=vars(data))+
##    geom_histogram(bins=50)
#    geom_density_ridges()
#ggsave('tmp.png',width=12)

#p3 = 
sensor_connectivity_plot <- 
    ggplot()+
#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =sensor_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =sensor_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
    theme_bw()+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
    theme(legend.position='bottom')+
    scale_y_continuous(expand = c(0, 0))

#p3 = 
    ggplot()+
    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
                 aes(x=data,y=ratio,color=type))+
#    geom_jitter()+
    geom_vline(data=sensor_connectivity_df%>%filter(type=='real'),
            aes(x=data,y=ratio,color=type, group=data))+
               #position=position_jitter(), aes(shape=data))+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
#    scale_x_discrete(labels=network_labels)+
  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
    theme_bw()

neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
    mutate(is_sensor = factor(ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE), levels=c(TRUE,FALSE)))%>%
#    mutate(is_sensor = fct_relevel(is_sensor,c(TRUE,FALSE)))%>%
    ggplot(aes(x=is_sensor,y=(neighbor_degree)))+
#    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
#    geom_point()+
    geom_boxplot()+
    theme_bw()+
    ylab('Average neighbor degree')+
    xlab('')+ stat_compare_means()+
    scale_x_discrete(labels=c('Sensor', 'Not Sensor'))
plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
ggsave('reports/figures/poster_figures_1023/fig5.png',width=5)

#combined_df%>%filter(group=='real'&data=='huri')%>%mutate(is_sensor = ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE))%>%
#    coin::independence_test(neighbor_degree~is_sensor, data=.)

```

```{r}
convert_networkx_to_igraph <- 			# 
    function
(
 	nx_object,
    df
)
{
    nx =  reticulate::import("networkx")
    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
    #ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
    ig = igraph::set_vertex_attr(ig , name =  'name', value  = (df$orf_name))
    #igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
    ig
}
```

```{r deletion}
pcc_deletion = read_csv('data/interim/deletion_analysis_0911/pcc_deletion_100.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='pcc')
yuri_deletion = read_csv('data/interim/deletion_analysis_0911/yuri_deletion_100.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='yuri')
huri_deletion = read_csv('data/interim/deletion_analysis_0911/huri_deletion_100.csv')%>%
    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='huri')

deletion_df  <- bind_rows(pcc_deletion, yuri_deletion, huri_deletion)%>%mutate(group = fct_relevel(group,c('pcc','yuri','huri')))

library(MESS)
auc_data <- deletion_df%>%
    group_by(group, variable_0)%>%
    summarise(auc=MESS::auc(gc_size,range), r = range[min(which(gc_size < 0.05))])%>%
    ungroup()%>%
    mutate(variable_0=fct_reorder(variable_0, auc, min))%>%pivot_wider(-r, names_from=group, values_from=auc)

auc_plot_pcc <- auc_data%>%
    ggplot(aes(x=variable_0,y=pcc))+
    geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" )),stat='identity')+
    theme_bw()+
    ylab("Robustness")+
    xlab("Deletion parameter")+
    scale_alpha_manual(name = '', values = c(0.3, 1), guide = FALSE)+
    labs(fill = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "D",
                                "B",
                                "Eff",
                                "C",
                                "E",
                                "R",
                                "DR",
                                "S"))+
    scale_fill_brewer(name = 'Deletion\nparameter', palette = "Set1", guide='legend', labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Degree Reversed",
                                "Sensitivity"
                                ))+
   theme(legend.position='bottom', legend.title=element_text(size=18), legend.text=element_text(size=14),legend.spacing.x = unit(1.0, 'cm'),legend.spacing.y = unit(1.0, 'cm'))
auc_plot_yuri <- auc_data%>%
    ggplot(aes(x=variable_0,y=yuri))+
    geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ),stat='identity')+
    theme_bw()+
    ylab("Robustness")+
    xlab("Deletion parameter")+
    labs(fill = "Deletion\nparameter")+
    scale_alpha_manual(name = '', values = c(0.3, 1), guide = FALSE)+
    scale_x_discrete(labels = c(
                                "D",
                                "B",
                                "Eff",
                                "C",
                                "E",
                                "R", "DR",
                                "S"))+
    scale_fill_brewer(name='', palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity","Degree Reversed"))+
   theme(legend.position='right')
auc_plot_huri<- auc_data%>%
    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" ) ))+
    geom_bar(aes(fill=variable_0),stat='identity')+
    theme_bw()+
    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
    ylab("Robustness")+
    xlab("Deletion parameter")+
    labs(fill = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "D",
                                "B",
                                "Eff",
                                "C",
                                "E",
                                "R",
                                "DR","S"))+
    scale_fill_brewer(palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity","Degree Reversed"))+
   theme(legend.position='right')
#combined_df %>% group_by(data)%>%summarise(deg_btw = cor(deg, btw),
#                                           deg_eff = cor(deg,eff),
#                                           deg_sens = cor(deg,sens),
#                                           deg_eigen = cor(deg, eigenvec_centr),
#                                           deg_closeness = cor(deg, closeness_centr))
deletion_plot_pcc <-  pcc_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
    ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" ) ))+
#    geom_point(size=1)+
        geom_line(size=2)+
#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('% Deleted Nodes')+
    ylab('% Giant Component Size')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    theme_bw()+
    ggtitle('Costanzo 2016')+
    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
    theme(legend.position='bottom',panel.border = element_blank(), axis.line = element_line())
deletion_plot_yuri <-  yuri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" )  ))+
#    geom_point(size=1)+
        geom_line(size=2)+
#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('% Deleted Nodes')+
    ggtitle('Yeast PPI')+
    ylab('% Giant Component Size')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
    theme_bw()+
    theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
deletion_plot_huri <-  huri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion"  ) ))+
#    geom_point(size=1)+
        geom_line(size=2)+
#    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('% Deleted Nodes')+
    ylab('% Giant Component Size')+
    ggtitle('HuRI')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
    theme_bw()+
    theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
deletion_lgn <- cowplot::get_legend(auc_plot_pcc)
pcc_with_inset = ggdraw(deletion_plot_pcc+    theme(legend.position=''))+
  draw_plot(auc_plot_pcc+theme(legend.position=''), .50, .62, .45, .35) +
  draw_plot_label(
    c("A", ""),
    c(0, 0.45),
    c(1, 0.95),
    size = 12
  )
yuri_with_inset = ggdraw(deletion_plot_yuri+    theme(legend.position=''))+
  draw_plot(auc_plot_yuri+theme(legend.position=''), .50, .62, .45, .35) +
  draw_plot_label(
    c("B", ""),
    c(0, 0.45),
    c(1, 0.95),
    size = 12
  )
huri_with_inset = ggdraw(deletion_plot_huri+    theme(legend.position=''))+
  draw_plot(auc_plot_huri+theme(legend.position=''), .50, .62, .45, .35) +
  draw_plot_label(
    c("C", ""),
    c(0, 0.45),
    c(1, 0.95),
    size = 12
  )
plot_grid(pcc_with_inset, yuri_with_inset, huri_with_inset, ncol=3)%>%plot_grid(deletion_lgn,nrow=2, rel_heights=c(0.9,.1))
ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)

plot_grid(deletion_plot_pcc+    theme(legend.position='')
, auc_plot_pcc+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))

```

### 2020-11-11 notebooks/paper_plots_0909.Rmd
paper plots include a combined plot of density distributions.

--- 2020-10-05 notebooks/paper_plots_0909.Rmd
@@
 
-pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
-yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
-huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
-
+pcc_df_random  = data.table::rbindlist(lapply(py$e_pcc$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
+yuri_df_random  = data.table::rbindlist(lapply(py$e_yuri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
+huri_df_random  = data.table::rbindlist(lapply(py$e_huri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
+pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    pcc_df_random%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(py$pcc_df),eff_norm = eff/nrow(py$pcc_df), group = 'random')
+)%>%mutate(group=fct_relevel(group, c('real','random')))
+yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    yuri_df_random%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(py$yuri_df),eff_norm = eff/nrow(py$yuri_df), group = 'random')
+)%>%mutate(group=fct_relevel(group, c('real','random')))
+huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    huri_df_random%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(py$huri_df),eff_norm = eff/nrow(py$huri_df), group = 'random')
+)%>%mutate(group=fct_relevel(group, c('real','random')))
 combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
@@
 
+Degree - Eff - Sens distributions
 ```{r}
-p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
-    geom_point(aes(color=cat_))+
+combined_df%>%filter(group=='real')%>%
+    ggplot(aes(x=deg, y = ..count../sum(..count..)))+
+    facet_grid(rows=vars(data))+
+    geom_histogram(binwidth=1)+
+#    xlim(1,NA)+
+    ylim(NA, 0.1)
+
+pcc_degree_dens <- 
+    ggplot()+
+    #facet_grid(rows=vars(data))+
+    #geom_density()+
+    geom_line(data=     pcc_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data=     pcc_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
+    theme_bw()+
     xlab('Degree')+
-    ylab('Effectiveness')+
-    stat_cor(method='pearson')   +
-    guides(color=guide_legend(title="Experiment categories"))+
-    theme_bw()
-p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
-    geom_point(aes(color=cat_))+
+    ylab('Density')+
+    coord_trans(x = "log10")+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) +
+theme(panel.grid.minor = element_blank())#+theme_fontsize
+pcc_eff_dens <- 
+    ggplot()+
+    #facet_grid(rows=vars(data))+
+#    geom_density()+
+    geom_line(data= pcc_df%>%filter(group=='real'),
+               aes(x=eff_norm ,y=..scaled.., color=group),
+               stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data= pcc_df%>%filter(group=='random'),
+               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
+               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
+    #geom_histogram(binwidth=0.0001)+
+    theme_bw()+
+    ylab('Density')+
+    xlab('Effectiveness')+
+    coord_trans(x = "log10")+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) +
+theme(panel.grid.minor = element_blank())#+theme_fontsize+
+#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
+pcc_sensitivity_dens <- 
+    ggplot()+
+    #facet_grid(rows=vars(data), scales='free_y')+
+#    geom_density()+
+    geom_line(data= pcc_df%>%filter(group=='real'),
+               aes(x=sens_norm,y=..scaled.. , color=group),
+               stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data= pcc_df%>%filter(group=='random'),
+               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
+               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
+    #geom_histogram(binwidth=0.0001)+
+    theme_bw()+
+    xlab('Sensitivity')+
+    ylab('Density')+
+    coord_trans(x = "log10")+
+    scale_color_discrete(labels=c('Rewired networks','Real network'))+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ )+ 
+# scale_y_continuous(
+#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
+#theme_fontsize+
+#annotate("text", x = 0.001, y = 0.9, label=sprintf("p = %#.2f", sens_p), fontface='italic', size=6)
+title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network", fontface='bold')
+pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
+                                pcc_eff_dens+theme(legend.position='none'), 
+                                pcc_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
+pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
+
+yuri_degree_dens <- 
+    ggplot()+
+    #facet_grid(rows=vars(data))+
+    #geom_density()+
+    geom_line(data=     yuri_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data=     yuri_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
+    theme_bw()+
     xlab('Degree')+
-    ylab('Sensitivity')+
-    stat_cor(method='spearman')   +
-    guides(color=guide_legend(title="Experiment categories"))+
-    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
-lgn = cowplot::get_legend(p2)
-fig3 = plot_grid(p1+theme(legend.position=''),
-          p2+theme(legend.position=''),
-          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
-ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
+    ylab('Density')+
+    coord_trans(x = "log10")+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) +
+theme(panel.grid.minor = element_blank())#+theme_fontsize
+yuri_eff_dens <- 
+    ggplot()+
+    #facet_grid(rows=vars(data))+
+#    geom_density()+
+    geom_line(data= yuri_df%>%filter(group=='real'),
+               aes(x=eff_norm ,y=..scaled.., color=group),
+               stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data= yuri_df%>%filter(group=='random'),
+               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
+               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
+    #geom_histogram(binwidth=0.0001)+
+    theme_bw()+
+    ylab('Density')+
+    xlab('Effectiveness')+
+    coord_trans(x = "log10")+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) +
+theme(panel.grid.minor = element_blank())#+theme_fontsize+
+#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
+yuri_sensitivity_dens <- 
+    ggplot()+
+    #facet_grid(rows=vars(data), scales='free_y')+
+#    geom_density()+
+    geom_line(data= yuri_df%>%filter(group=='real'),
+               aes(x=sens_norm,y=..scaled.. , color=group),
+               stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data= yuri_df%>%filter(group=='random'),
+               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
+               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
+    #geom_histogram(binwidth=0.0001)+
+    theme_bw()+
+    xlab('Sensitivity')+
+    ylab('Density')+
+    coord_trans(x = "log10")+
+    scale_color_discrete(labels=c('Rewired networks','Real network'))+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ )+ 
+# scale_y_continuous(
+#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
+title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
+yuri_dens_comb = cowplot::plot_grid(yuri_degree_dens+theme(legend.position='none'), 
+                                yuri_eff_dens+theme(legend.position='none'), 
+                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
+yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
+
+huri_degree_dens <- 
+    ggplot()+
+    #facet_grid(rows=vars(data))+
+    #geom_density()+
+    geom_line(data=     huri_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data=     huri_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
+    theme_bw()+
+    xlab('Degree')+
+    ylab('Density')+
+    coord_trans(x = "log10")+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) +
+theme(panel.grid.minor = element_blank())#+theme_fontsize
+huri_eff_dens <- 
+    ggplot()+
+    #facet_grid(rows=vars(data))+
+#    geom_density()+
+    geom_line(data= huri_df%>%filter(group=='real'),
+               aes(x=eff_norm ,y=..scaled.., color=group),
+               stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data= huri_df%>%filter(group=='random'),
+               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
+               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
+    #geom_histogram(binwidth=0.0001)+
+    theme_bw()+
+    ylab('Density')+
+    xlab('Effectiveness')+
+    coord_trans(x = "log10")+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) +
+theme(panel.grid.minor = element_blank())#+theme_fontsize+
+#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
+huri_sensitivity_dens <- 
+    ggplot()+
+#$    facet_grid(rows=vars(data), scales='free_y')+
+#    geom_density()+
+    geom_line(data= huri_df%>%filter(group=='real'),
+               aes(x=sens_norm,y=..scaled.. , color=group),
+               stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data= huri_df%>%filter(group=='random'),
+               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
+               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
+    #geom_histogram(binwidth=0.0001)+
+    theme_bw()+
+    xlab('Sensitivity')+
+    ylab('Density')+
+    coord_trans(x = "log10")+
+    scale_color_discrete(labels=c('Rewired networks','Real network'))+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ )+ 
+# scale_y_continuous(
+#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
+title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
+huri_dens_comb = cowplot::plot_grid(huri_degree_dens+theme(legend.position='none'), 
+                                huri_eff_dens+theme(legend.position='none'), 
+                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
+huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
+dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
+dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
+                                yuri_dens_comb_title,
+                                huri_dens_comb_title,nrow=3)
+cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
+ggsave('reports/figures/paper_figures_0916/fig1.png')
+
+#degree_dens <- 
+#    ggplot(combined_df%>%filter(group=='real'), aes(x=deg))+
+#    ggplot(combined_df%>%filter(group=='random'), aes(x=deg, y=..scaled.., fill=.id))+
+#    facet_grid(rows=vars(data))+
+#    #geom_density()+
+#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
+#    theme_bw()+
+#    xlab('Degree')+
+#    coord_trans(x = "log10", y = "log1p")+
+#scale_x_continuous(
+#   breaks = scales::trans_breaks("log10", function(x) 10^x),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+# scale_y_continuous(
+#   breaks = scales::trans_breaks("log10", function(x) 10^(x)),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+#theme(panel.grid.minor = element_blank())
+#eff_dens <- 
+#    combined_df%>%filter(group=='real')%>%
+#    ggplot(aes(x=eff_norm ))+
+#    facet_grid(rows=vars(data), scales='free_y')+
+##    geom_density()+
+#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
+#    #geom_histogram(binwidth=0.0001)+
+#    theme_bw()+
+#    xlab('Effectivity')+
+#    coord_trans(x = "log10", y = "log1p")+
+#scale_x_continuous(
+#   breaks = scales::trans_breaks("log10", function(x) 10^x),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+# scale_y_continuous(
+#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+#theme(panel.grid.minor = element_blank())
+#sensitivity_dens <- 
+#    combined_df%>%filter(group=='real')%>%
+#    ggplot(aes(x=sens_norm))+
+#    facet_grid(rows=vars(data))+
+#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
+#   # geom_density()+
+#    theme_bw()+
+#    xlab('Sensitivity')+
+#    coord_trans(x = "log10", y = "log1p")+
+#   # annotation_logticks()+
+#scale_x_continuous(
+#   breaks = scales::trans_breaks("log10", function(x) 10^x),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+# scale_y_continuous(
+#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
+#   labels = scales::trans_format("log10", scales::math_format(10^.x))
+# ) +
+#theme(panel.grid.minor = element_blank())
+#cowplot::plot_grid(degree_dens, eff_dens, sensitivity_dens, ncol=3,labels=c('A','B','C'))
+#ggsave('tmp.png')
+
+#    coord_trans(x = "log10", y = "log1p")
+#    scale_x_continuous(trans = "log10")
+    #scale_x_log10()
+#    geom_histogram(binwidth=1)+
+#    xlim(1,NA)+
+#    ylim(NA, 0.1)
+ggsave('tmp.png')
+
+```
+
+```{r}
+real_random_labels = c('Real\nnetwork','Rewired\nnetwork')
+names(real_random_labels)  = c('real','random')
+pcc_deg_eff = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=eff_norm))+
+    geom_point()+
+#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
+    theme_bw()+
+    ylab("Effectiveness")+
+    xlab("Degree")+
+    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+pcc_deg_sens = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=sens_norm))+
+    geom_point()+
+#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
+    theme_bw()+
+    ylab("Sensitivity")+
+    xlab("Degree")+
+    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+yuri_deg_eff = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=eff_norm))+
+    geom_point()+
+#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
+    theme_bw()+
+    ylab("Effectiveness")+
+    xlab("Degree")+
+    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+yuri_deg_sens = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=sens_norm))+
+    geom_point()+
+#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
+    theme_bw()+
+    ylab("Sensitivity")+
+    xlab("Degree")+
+    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+huri_deg_eff = huri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=eff_norm))+
+    geom_point()+
+#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
+    theme_bw()+
+    ylab("Effectiveness")+
+    xlab("Degree")+
+    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+huri_deg_sens = huri_df %>%filter(group=='real')%>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=sens_norm))+
+    geom_point()+
+#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) )+
+    theme_bw()+
+    ylab("Sensitivity")+
+    xlab("Degree")+
+    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
+                   yuri_deg_eff, yuri_deg_sens,
+                   huri_deg_eff, huri_deg_sens, labels = c('A','','B','','C',''),
+                   ncol=2)
+ggsave('tmp.png',plot=deg_scatter_plots, width=10,height=10)
+
+#p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
+#    geom_point(aes(color=cat_))+
+#    xlab('Degree')+
+#    ylab('Effectiveness')+
+#    stat_cor(method='pearson')   +
+#    guides(color=guide_legend(title="Experiment categories"))+
+#    theme_bw()
+#p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
+#    geom_point(aes(color=cat_))+
+#    xlab('Degree')+
+#    ylab('Sensitivity')+
+#    stat_cor(method='spearman')   +
+#    guides(color=guide_legend(title="Experiment categories"))+
+#    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
+#lgn = cowplot::get_legend(p2)
+#fig3 = plot_grid(p1+theme(legend.position=''),
+#          p2+theme(legend.position=''),
+#          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
+#ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
 ```
@@
     bind_rows(
-    data.frame(sens_deg_spearman= c(cor(pcc_df$deg, pcc_df$sens,method='spearman'),cor(yuri_df$deg,yuri_df$sens,method='spearman'),cor(huri_df$deg,huri_df$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df$deg, pcc_df$eff),cor(yuri_df$deg,yuri_df$eff),cor(huri_df$deg,huri_df$eff)), type='real',data=c('pcc','yuri','huri')))%>%
+    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$sens,method='spearman'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$eff,method='pearson'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc','yuri','huri')))%>%
     mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
@@
     theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
-    scale_color_discrete(labels=c('Rewired networks', 'Real networks'))+
+    scale_color_discrete(labels=c('Rewired networks', 'Real network'))+
     scale_y_continuous(expand = c(0, 0)) 
 lgn34  <- cowplot::get_legend(p4)
-plot_grid(
+distr_plots <- plot_grid(
           p3+theme(legend.position=''),
  p4+theme(legend.position=''), lgn34,
- nrow=3, labels=c('A','B','','C','D',''), rel_heights = c(0.45,0.45,0.1))
-ggsave('reports/figures/paper_figures_0916/fig2.png',width=7)
+ nrow=3, labels=c('D','E','','F','G',''), rel_heights = c(0.45,0.45,0.1))
+#ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
+
+plot_grid(deg_scatter_plots, distr_plots, nrow=2,rel_heights = c(0.6,0.4))
+ggsave('reports/figures/paper_figures_0916/fig2.png',width=8,height=9)
 ```
@@
 ```{r deletion}
-pcc_deletion = read_csv('data/interim/deletion_analysis_0911/pcc_deletion.csv')%>%
+pcc_deletion = read_csv('data/interim/deletion_analysis_0911/pcc_deletion_100.csv')%>%
     pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
     mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='pcc')
-yuri_deletion = read_csv('data/interim/deletion_analysis_0911/yuri_deletion.csv')%>%
+yuri_deletion = read_csv('data/interim/deletion_analysis_0911/yuri_deletion_100.csv')%>%
     pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
     mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='yuri')
-huri_deletion = read_csv('data/interim/deletion_analysis_0911/huri_deletion.csv')%>%
+huri_deletion = read_csv('data/interim/deletion_analysis_0911/huri_deletion_100.csv')%>%
     pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
@@
     ggplot(aes(x=variable_0,y=pcc))+
-    geom_bar(aes(fill=variable_0,alpha = (variable_0  )),stat='identity')+
+    geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" )),stat='identity')+
     theme_bw()+
@@
     xlab("Deletion parameter")+
-    scale_alpha_manual(name='Deletion\nparameter', values = c(0.3,0.3,1,0.3,0.3,0.3,1), labels= c(
-                                "Degree",
-                                "Betweenness",
-                                "Effectiveness",
-                                "Closeness",
-                                "Eigencentrality",
-                                "Random",
-                                "Sensitivity"), guide = 'legend')+
+    scale_alpha_manual(name = '', values = c(0.3, 1), guide = FALSE)+
     labs(fill = "Deletion\nparameter")+
@@
                                 "R",
+                                "DR",
                                 "S"))+
@@
                                 "Random",
-                                "Sensitivity"))+
+                                "Degree Reversed",
+                                "Sensitivity"
+                                ))+
    theme(legend.position='bottom', legend.title=element_text(size=18), legend.text=element_text(size=14),legend.spacing.x = unit(1.0, 'cm'),legend.spacing.y = unit(1.0, 'cm'))
@@
                                 "E",
-                                "R",
+                                "R", "DR",
                                 "S"))+
@@
                                 "Random",
-                                "Sensitivity"))+
+                                "Sensitivity","Degree Reversed"))+
    theme(legend.position='right')
 auc_plot_huri<- auc_data%>%
-    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ))+
+    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" ) ))+
     geom_bar(aes(fill=variable_0),stat='identity')+
@@
                                 "R",
-                                "S"))+
+                                "DR","S"))+
     scale_fill_brewer(palette = "Set1", labels= c(
@@
                                 "Random",
-                                "Sensitivity"))+
+                                "Sensitivity","Degree Reversed"))+
    theme(legend.position='right')
@@
 deletion_plot_pcc <-  pcc_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
-    ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ))+
+    ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" ) ))+
 #    geom_point(size=1)+
@@
 deletion_plot_yuri <-  yuri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
-ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion')  ))+
+ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" )  ))+
 #    geom_point(size=1)+
@@
 deletion_plot_huri <-  huri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
-ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion')  ))+
+ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion"  ) ))+
 #    geom_point(size=1)+
@@
 # Sensor connectivity and neighbor degree
+
 ```{r}
@@
     ggplot()+
+    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
+#    geom_boxplot()+
+#    geom_jitter()+
+    geom_density(data =sensor_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
+    geom_vline(data =sensor_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
+    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
+    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
+    theme_bw()+
+    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
+    theme(legend.position='bottom')+
+    scale_y_continuous(expand = c(0, 0))
+
+#p3 = 
+    ggplot()+
     geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
@@
 #    geom_jitter()+
-    geom_point(data=sensor_connectivity_df%>%filter(type=='real'),
+    geom_vline(data=sensor_connectivity_df%>%filter(type=='real'),
             aes(x=data,y=ratio,color=type, group=data))+
@@
     theme_bw()
-neighbor_degree_plot <- combined_df%>%
-    ggplot(aes(x=sens_norm,y=neighbor_degree))+
+
+neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
+    mutate(is_sensor = factor(ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE), levels=c(TRUE,FALSE)))%>%
+#    mutate(is_sensor = fct_relevel(is_sensor,c(TRUE,FALSE)))%>%
+    ggplot(aes(x=is_sensor,y=log(neighbor_degree)))+
     facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
-    geom_point()+
+#    geom_point()+
+    geom_boxplot()+
     theme_bw()+
-    ylab('Average neighbor degree')+
-    xlab('Sensitivity')
+    ylab('Log(Average neighbor degree)')+
+    xlab('')+ stat_compare_means()+
+    scale_x_discrete(labels=c('aensor', 'Not Sensor'))
 plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
 ggsave('reports/figures/paper_figures_0916/fig5.png')
+
+#combined_df%>%filter(group=='real'&data=='huri')%>%mutate(is_sensor = ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE))%>%
+#    coin::independence_test(neighbor_degree~is_sensor, data=.)
 

### 2020-11-26 notebooks/paper_plots_0909.Rmd
added go colored effector sensor plots to paper plots

@@
 setwd('../')
+source('src/R/plot_density_prs.R')
 ```
@@
 pcc_degree_dens <- 
-    ggplot()+
-    #facet_grid(rows=vars(data))+
-    #geom_density()+
-    geom_line(data=     pcc_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data=     pcc_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
-    theme_bw()+
-    xlab('Degree')+
-    ylab('Density')+
-    coord_trans(x = "log10")+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- ) +
-theme(panel.grid.minor = element_blank())#+theme_fontsize
+    plot_density_prs(pcc_df, deg, xlab='Degree')
 pcc_eff_dens <- 
-    ggplot()+
-    #facet_grid(rows=vars(data))+
-#    geom_density()+
-    geom_line(data= pcc_df%>%filter(group=='real'),
-               aes(x=eff_norm ,y=..scaled.., color=group),
-               stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data= pcc_df%>%filter(group=='random'),
-               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
-               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
-    #geom_histogram(binwidth=0.0001)+
-    theme_bw()+
-    ylab('Density')+
-    xlab('Effectiveness')+
-    coord_trans(x = "log10")+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- ) +
-theme(panel.grid.minor = element_blank())#+theme_fontsize+
+    plot_density_prs(pcc_df, eff_norm, xlab='Effectiveness')
 #annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
 pcc_sensitivity_dens <- 
-    ggplot()+
-    #facet_grid(rows=vars(data), scales='free_y')+
-#    geom_density()+
-    geom_line(data= pcc_df%>%filter(group=='real'),
-               aes(x=sens_norm,y=..scaled.. , color=group),
-               stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data= pcc_df%>%filter(group=='random'),
-               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
-               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
-    #geom_histogram(binwidth=0.0001)+
-    theme_bw()+
-    xlab('Sensitivity')+
-    ylab('Density')+
-    coord_trans(x = "log10")+
-    scale_color_discrete(labels=c('Rewired networks','Real network'))+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- )+ 
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
-#theme_fontsize+
-#annotate("text", x = 0.001, y = 0.9, label=sprintf("p = %#.2f", sens_p), fontface='italic', size=6)
+    plot_density_prs(pcc_df, sens_norm, xlab='Sensitivity')
 title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network", fontface='bold')
@@
 pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-
 yuri_degree_dens <- 
-    ggplot()+
-    #facet_grid(rows=vars(data))+
-    #geom_density()+
-    geom_line(data=     yuri_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data=     yuri_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
-    theme_bw()+
-    xlab('Degree')+
-    ylab('Density')+
-    coord_trans(x = "log10")+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- ) +
-theme(panel.grid.minor = element_blank())#+theme_fontsize
+    plot_density_prs(yuri_df, deg, xlab='Degree')
 yuri_eff_dens <- 
-    ggplot()+
-    #facet_grid(rows=vars(data))+
-#    geom_density()+
-    geom_line(data= yuri_df%>%filter(group=='real'),
-               aes(x=eff_norm ,y=..scaled.., color=group),
-               stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data= yuri_df%>%filter(group=='random'),
-               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
-               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
-    #geom_histogram(binwidth=0.0001)+
-    theme_bw()+
-    ylab('Density')+
-    xlab('Effectiveness')+
-    coord_trans(x = "log10")+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- ) +
-theme(panel.grid.minor = element_blank())#+theme_fontsize+
-#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
+    plot_density_prs(yuri_df, eff_norm, xlab='Effectiveness')
 yuri_sensitivity_dens <- 
-    ggplot()+
-    #facet_grid(rows=vars(data), scales='free_y')+
-#    geom_density()+
-    geom_line(data= yuri_df%>%filter(group=='real'),
-               aes(x=sens_norm,y=..scaled.. , color=group),
-               stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data= yuri_df%>%filter(group=='random'),
-               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
-               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
-    #geom_histogram(binwidth=0.0001)+
-    theme_bw()+
-    xlab('Sensitivity')+
-    ylab('Density')+
-    coord_trans(x = "log10")+
-    scale_color_discrete(labels=c('Rewired networks','Real network'))+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- )+ 
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
+    plot_density_prs(yuri_df, sens_norm, xlab='Sensitivity')
 title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
@@
 yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-
 huri_degree_dens <- 
-    ggplot()+
-    #facet_grid(rows=vars(data))+
-    #geom_density()+
-    geom_line(data=     huri_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data=     huri_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
-    theme_bw()+
-    xlab('Degree')+
-    ylab('Density')+
-    coord_trans(x = "log10")+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- ) +
-theme(panel.grid.minor = element_blank())#+theme_fontsize
+    plot_density_prs(huri_df, deg, xlab='Degree')
 huri_eff_dens <- 
-    ggplot()+
-    #facet_grid(rows=vars(data))+
-#    geom_density()+
-    geom_line(data= huri_df%>%filter(group=='real'),
-               aes(x=eff_norm ,y=..scaled.., color=group),
-               stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data= huri_df%>%filter(group=='random'),
-               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
-               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
-    #geom_histogram(binwidth=0.0001)+
-    theme_bw()+
-    ylab('Density')+
-    xlab('Effectiveness')+
-    coord_trans(x = "log10")+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- ) +
-theme(panel.grid.minor = element_blank())#+theme_fontsize+
-#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
+    plot_density_prs(huri_df, eff_norm, xlab='Effectiveness')
 huri_sensitivity_dens <- 
-    ggplot()+
-#$    facet_grid(rows=vars(data), scales='free_y')+
-#    geom_density()+
-    geom_line(data= huri_df%>%filter(group=='real'),
-               aes(x=sens_norm,y=..scaled.. , color=group),
-               stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data= huri_df%>%filter(group=='random'),
-               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
-               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
-    #geom_histogram(binwidth=0.0001)+
-    theme_bw()+
-    xlab('Sensitivity')+
-    ylab('Density')+
-    coord_trans(x = "log10")+
-    scale_color_discrete(labels=c('Rewired networks','Real network'))+
-scale_x_continuous(
-   breaks = scales::trans_breaks("log10", function(x) 10^x),
-   labels = scales::trans_format("log10", scales::math_format(10^.x))
- )+ 
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
+    plot_density_prs(huri_df, sens_norm, xlab='Sensitivity')
 title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
@@
 ```
+```{r}
+library(RColorBrewer)
+col = brewer.pal(n=9, name='Set1')
+sensor_colors =col[1:6] #brewer.pal(n = 6, name = "Set1")
+effector_colors = col[7:9]#brewer.pal(n=3, name= "Set1_r")
+```
+
+```{python}
+sensor_colors = r.sensor_colors
+effector_colors = r.effector_colors
+sensors_pcc = e_pcc.df.loc[e_pcc.df.sens>np.quantile(e_pcc.df.sens,0.99)]
+#sensor_sub_pcc = get_subnetwork(e_pcc.graph_gc, sensors_pcc.orf_name.values)
+#is_sensor = dict(zip(sensor_sub_pcc.nodes, [True if i in sensors_pcc.orf_name.values else False  for i in sensor_sub_pcc.nodes]))
+#nx.set_node_attributes(sensor_sub_pcc, is_sensor, 'is_sensor')
+sensor_go_terms_separate = [
+    'iron ion\ntransport',
+    'phenylalanine\ntransport',
+    None, 
+    None,
+    None,
+    None,
+    'tricarboxylic\nacid cycle', 
+    'hexose metabolic\nprocess',
+    'protein folding',
+    'mitochondria-nucleus\nsignaling pathway/TCA',
+    None,
+    None,
+    None,
+    None,
+    None,
+    None,
+    None,
+]
+sensor_connected_components = sorted([sorted(list(i)) for i in nx.connected_components(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name))], key=lambda x: x[0])
+sensor_go_terms= {}
+for i in range(len(sensor_go_terms_separate)):
+    for j in sensor_connected_components[i]:
+        sensor_go_terms[j] = sensor_go_terms_separate[i]
+sensors_pcc = sensors_pcc.merge(pd.DataFrame.from_dict(sensor_go_terms,orient='index',columns=['go_group']),right_index=True,left_on='orf_name')
+
+effector_pcc = e_pcc.df.loc[e_pcc.df.eff>np.quantile(e_pcc.df.eff,0.99)]
+#effector_sub_pcc = get_subnetwork(e_pcc.graph_gc, effector_pcc.orf_name.values)
+#is_effector = dict(zip(effector_sub_pcc.nodes, [True if i in effector_pcc.orf_name.values else False  for i in effector_sub_pcc.nodes]))
+#nx.set_node_attributes(effector_sub_pcc, is_effector, 'is_effector')
+effectors_connected_comp = sorted([sorted(list(i)) for i in nx.connected_components(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()))], key=lambda x:x[0])
+effector_pcc.loc[:, 'go_group'] = ['mito' if i in effectors_connected_comp[0] else 'golgi' if i in effectors_connected_comp[1] else 'chromatin' for i in effector_pcc.orf_name]
+effector_order = effector_pcc.groupby('go_group').eff.median().sort_values().index.tolist()
+sensor_order = sensors_pcc.groupby('go_group').sens.median().sort_values().index.tolist()
+```
+
+```{python}
+from matplotlib.lines import Line2D
+pos = e_pcc.graph_gc.nodes('pos')
+fig, ax = plt.subplots(figsize=(12,12))
+legend_elements = [    ]
+e_pcc.plot_network_spring(ax=ax,
+                          node_size=1,
+                          node_color='black',
+ #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
+                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
+                         edge_color='black')
+#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
+nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=sensors_pcc.orf_name.values, node_size=200, pos=pos,
+                          node_color='black',
+                          node_shape='^',edgecolors='black',
+                          linewidths=1)
+for itr, i in enumerate(sensor_order):
+    #print(i, effector_colors[itr])
+
+    orf_names_to_plot = sensors_pcc.loc[sensors_pcc.go_group==i, 'orf_name'].tolist()
+    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
+                          node_color=sensor_colors[itr],
+                          node_shape='^',edgecolors='black',
+                          linewidths=1)
+    legend_elements.append(
+        Line2D([0], [0], marker='^', color='black', label=f'Sensors ({i})',
+                              markerfacecolor=sensor_colors[itr], markersize=12, linestyle="None")
+    )
+nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=effector_pcc.orf_name.values, node_size=100, pos=pos,
+                      node_color='black',
+                      node_shape='o')
+for itr, i in enumerate(effector_order):
+    orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
+    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
+                          node_color=effector_colors[itr],
+                          node_shape='o',edgecolors='black',
+                          linewidths=1)
+    if i == 'mito':
+        lbl = 'Respiratory complex assembly'
+    elif i == 'golgi':
+        lbl = "Golgi vesicle transport"
+    else:
+        lbl = 'Chromosome segragation'
+    legend_elements.append(
+            Line2D([0], [0], marker='o', color='black', label=f'Effectors ({lbl})',
+                                  markerfacecolor=effector_colors[itr], markersize=12, linestyle="None")
+        )
+nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='red', alpha=0.5)
+ax.set_facecolor('white')
+legend_elements.extend(
+    [Line2D([0], [0], marker='o', color='black', label='Genes',
+                              markerfacecolor='black', markersize=4, linestyle="None"),
+#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
+#                               markerfacecolor='black', markersize=10, linestyle="None"),
+#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
+#                               markerfacecolor='black', markersize=10, linestyle="None"),
+                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
+                              markerfacecolor='black', markersize=0, linestyle="-"),
+                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
+                              markerfacecolor='#018571', markersize=0, linestyle="-"),
+                   Line2D([0], [0], marker='o', color='blue', label= 'Effector-Effector edges',
+                              markerfacecolor='#a6611a', markersize=0, linestyle="-")]
+)
+lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
+
+nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
+plt.savefig('tmp_nw.png',bbox_inches='tight')
+```
+
+```{r}
+effector_pcc = py$effector_pcc
+sensors_pcc = py$sensors_pcc%>%mutate(go_group = (as.character(go_group)), go_group=ifelse(go_group=='NULL', NA, go_group))
+#library(tidyverse)
+eff_deg_comp<-ggplot(effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff)), aes(x= go_group, y=deg,fill=go_group))+
+    geom_boxplot()+
+    scale_fill_manual(values=effector_colors,
+                      labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
+    xlab('')+
+    ylab('Degree')+
+    theme_bw()+
+    theme(axis.text.x=element_blank(),legend.title=element_blank(),legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'in'))
+eff_eff_comp<-ggplot(effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff))%>%
+                      mutate(eff_norm =eff / 5183), aes(x= go_group, y=eff_norm,fill=go_group))+
+    geom_boxplot()+
+    #scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
+    xlab('')+
+    scale_fill_manual(values=effector_colors)+
+    ylab('Effectiveness')+
+    theme_bw()+
+    theme(axis.text.x=element_blank(),legend.title=element_blank())
+
+sens_deg_comp<-ggplot(sensors_pcc%>%drop_na()%>%mutate(go_group=fct_reorder(go_group, sens)), aes(x= go_group, y=deg,fill=go_group))+
+    geom_boxplot()+
+#    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
+    xlab('')+
+    ylab('Degree')+
+    scale_fill_manual(values=sensor_colors)+
+    theme_bw()+
+    theme(axis.text.x=element_blank(),legend.title=element_blank(),
+          legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'cm'))
+sens_sens_comp<-ggplot(sensors_pcc%>%drop_na()%>%mutate(go_group=fct_reorder(go_group, sens))%>%
+                      mutate(sens_norm = sens / 5183), aes(x= go_group, y=sens_norm,fill=go_group))+
+    geom_boxplot()+
+#    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
+    xlab('')+
+    ylab('Sensitivity')+
+    scale_fill_manual(values=sensor_colors)+
+    theme_bw()+
+    theme(axis.text.x=element_blank(),legend.title=element_blank())
+
+img <- 'tmp_nw.png' %>%
+  magick::image_read() #%>%
+  #magick::image_resize("570x380")
+
+nw_img = cowplot::ggdraw()+
+    cowplot::draw_image(img, width=1)
+go_plots = cowplot::plot_grid(eff_deg_comp+theme(legend.position='none'),
+                   eff_eff_comp+theme(legend.position='none'),
+                   cowplot::get_legend(eff_deg_comp),
+                   sens_deg_comp+theme(legend.position='none'),
+                   sens_sens_comp+theme(legend.position='none'),
+                   cowplot::get_legend(sens_deg_comp),ncol=3, labels=c('B','C','','D','E',''))
+
+combined = cowplot::plot_grid(nw_img, go_plots,nrow=2,rel_heights=c(0.4,0.6), labels=c('A',''))
+ggsave('reports/figures/paper_figures_0916/fig6.png',plot=combined,width=7,height=12)
+```

### 2020-11-30 notebooks/paper_plots_0909.Rmd
Added significance to eff/sens group comparisons

@@
 library(ggpubr)
+library(ggsignif)
 
@@
 #library(tidyverse)
+effector_pcc$go_group = as.factor(effector_pcc$go_group)
+
+#res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
+#res.aov
+effector_eff_pval = FSA::dunnTest(eff~go_group, effector_pcc)
+effector_eff_pval$res[effector_eff_pval$res$P.adj<0.1,]
+effector_deg_pval = FSA::dunnTest(deg~go_group, effector_pcc)
+effector_deg_pval$res[effector_deg_pval$res$P.adj<0.1,]
+
 eff_deg_comp<-ggplot(effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff)), aes(x= go_group, y=deg,fill=go_group))+
-    geom_boxplot()+
+    geom_boxplot(outlier.shape=NA)+
     scale_fill_manual(values=effector_colors,
@@
     theme_bw()+
-    theme(axis.text.x=element_blank(),legend.title=element_blank(),legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'in'))
+    geom_signif(comparisons=list(c('golgi','chromatin'), c('golgi','mito'),c('mito','chromatin')),
+                annotation=c('**','***','ns'),
+                y_position=c(110,115,120))+
+    theme(axis.text.x=element_blank(),legend.title=element_blank(),legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'in'))+
 eff_eff_comp<-ggplot(effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff))%>%
@@
     xlab('')+
+    ggpubr::stat_compare_means(method='kruskal.test')+
     scale_fill_manual(values=effector_colors)+
@@
     theme(axis.text.x=element_blank(),legend.title=element_blank())
+ggsave('tmp.png', plot=eff_deg_comp)
 
@@
     scale_fill_manual(values=sensor_colors)+
+    ggpubr::stat_compare_means(method='kruskal.test',label.x.npc=.3)+
     theme_bw()+
@@
           legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'cm'))
+sensors_pcc$go_group = as.factor(sensors_pcc$go_group)
+sensors_sens_pval = FSA::dunnTest(sens~go_group, sensors_pcc)
+sensors_sens_pval$res[sensors_sens_pval$res$P.adj<0.1,]
+
 sens_sens_comp<-ggplot(sensors_pcc%>%drop_na()%>%mutate(go_group=fct_reorder(go_group, sens))%>%
@@
     geom_boxplot()+
+    geom_signif(
+        comparisons = list(c("hexose metabolic\nprocess", 'phenylalanine\ntransport'),c("tricarboxylic\nacid cycle", 'phenylalanine\ntransport'),
+                            c('phenylalanine\ntransport', 'protein folding')),
+        annotation = c('**','**', '*'),y_position=c(0.007,0.0075, 0.008)
+                )+
 #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
@@
     cowplot::draw_image(img, width=1)
-go_plots = cowplot::plot_grid(eff_deg_comp+theme(legend.position='none'),
-                   eff_eff_comp+theme(legend.position='none'),
-                   cowplot::get_legend(eff_deg_comp),
+go_plots = cowplot::plot_grid(
                    sens_deg_comp+theme(legend.position='none'),
                    sens_sens_comp+theme(legend.position='none'),
-                   cowplot::get_legend(sens_deg_comp),ncol=3, labels=c('B','C','','D','E',''))
-
+                   cowplot::get_legend(sens_deg_comp),eff_deg_comp+theme(legend.position='none'),
+                   eff_eff_comp+theme(legend.position='none'),
+                   cowplot::get_legend(eff_deg_comp),ncol=3, labels=c('B','C','','D','E',''))
 combined = cowplot::plot_grid(nw_img, go_plots,nrow=2,rel_heights=c(0.4,0.6), labels=c('A',''))
-ggsave('reports/figures/paper_figures_0916/fig6.png',plot=combined,width=7,height=12)
+ggsave('reports/figures/paper_figures_0916/fig6.png',plot=combined,width=9,height=12)
 ```

### 2020-12-05 src/data/gi.py
genetic interaction network clear data and run pipeline on 2 thresholds

@@ -1,0 +1,11 @@
+import pandas as pd
+
+gi = pd.read_csv('~/pgsNetwork/analysis/data/derived_data/SGA_data_combined.csv',sep='\t')
+gi_strong = gi.loc[(gi['Genetic interaction score (ε)']< -.08) & (gi['P-value']<0.05)]
+gi_strong['gene1'] = gi_strong['Query allele name']
+gi_strong['gene2'] = gi_strong['Array allele name']
+
+gi_verystrong =gi_strong.loc[(gi['Genetic interaction score (ε)']< -.2) & (gi['P-value']<0.05)]
+ 
+gi_strong.to_csv('data/interim/gi/gi_.08.csv')
+gi_verystrong.to_csv('data/interim/gi/gi_.2.csv')

### 2020-12-05 src/data/gi_enm.py

@@ -1,36 +1,0 @@
-import src
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from tqdm import tqdm
-from src.enm import *
-from src.utils import *
-from Bio import SeqIO
-
-
-figure_path = 'reports/figures/gi_0827'
-enm = Enm('enm')
-enm.read_network('data/interim/SGA_02_withoverlapping.csv',sep=',')
-enm.gnm_analysis(normalized=False)
-
-enm.figure_path=figure_path
-enm.output_path = 'data/interim/gi_0827/'
-enm.spring_pos()
-
-enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False)
-
-neigbor_btw = []
-neighbor_degree = []
-for i in enm.graph_gc.nodes:
-    neigbor_btw.append(np.average([enm.df.loc[enm.df.orf_name==a,'btw'].values for a in nx.neighbors(enm.graph_gc,i)]))
-    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
-
-enm.df['neighbor_btw'] = neigbor_btw
-enm.df['neighbor_degree'] = neighbor_degree
-
-with open(f"{enm.output_path}/gi.pickle",'wb') as f:
-    pickle.dump(enm,f)
-
-

### 2020-12-05 src/features/gi_enm.py

@@ -1,0 +1,72 @@
+import src
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+import networkx as nx
+import pickle
+from tqdm import tqdm
+from src.enm import *
+from src.utils import *
+
+
+
+#figure_path = 'reports/figures/pcc_0603'
+enm = Enm('enm')
+enm.read_network('data/interim/gi/gi_.08.csv')
+enm.gnm_analysis(normalized=False)
+
+#enm.figure_path=figure_path
+enm.output_path = 'data/interim/gi_1201/'
+os.mkdir(enm.output_path)
+enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
+enm.spring_pos()
+
+os.mkdir(f"{enm.output_path}/random_dfs")
+enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=10)
+random_dfs = [enm.e_list[i].df.to_csv(f'data/interim/gi_1201/random_dfs/rand_{i}.csv') for i in range(10)]
+#enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=10)
+#enm.simulate_rewire(output_name='rewire_data_er', save=True, nodegseq=True,random_network_type='er', normalized=False)
+
+neigbor_btw = []
+neighbor_degree = []
+for i in enm.graph_gc.nodes:
+    neigbor_btw.append(np.average([enm.df.loc[enm.df.orf_name==a,'btw'].values for a in nx.neighbors(enm.graph_gc,i)]))
+    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
+
+enm.df['neighbor_btw'] = neigbor_btw
+enm.df['neighbor_degree'] = neighbor_degree
+
+with open(f"{enm.output_path}/gi_100.pickle",'wb') as f:
+    pickle.dump(enm,f, protocol=4)
+
+
+##### very strong#####
+
+enm_02 = Enm('enm_02')
+enm_02.read_network('data/interim/gi/gi_.2.csv')
+enm_02.gnm_analysis(normalized=False)
+
+#enm.figure_path=figure_path
+enm_02.output_path = 'data/interim/gi_1205_0.2/'
+os.mkdir(enm_02.output_path)
[…]

### 2020-12-05 src/enm.py
added prs weighted path finding

@@ -36,6 +36,7 @@ class Enm():
         self.coll=None
         self.coll_index_sorted = None
         self.prs_mat = None
+        self.prs_mat_df  = None
         self.L = None
 
     def print_name(self):
@@ -132,6 +133,7 @@ class Enm():
         except Exception as e:
             raise AttributeError('GNM is not calculated yet. Call get_gnm() first')
         self.prs_mat = prs_mat
+        self.prs_mat_df = pd.DataFrame(prs_mat,columns=self.nodes, index=self.nodes)
 
     def create_df(self):
         """Create an overall dataframe to store network related and GNM related values
@@ -218,6 +220,29 @@ class Enm():
         #db_connection = sql.create_engine(db_connection_str)
         #db_df = pd.read_sql('SELECT * FROM SUMMARY_2012', con=db_connection)
         #combined_df = pd.merge(combined_df, db_df, left_on='Systematic gene name', right_on='orf_name')
+    def set_perturb_profile(self,source, get_col=True):
+        if get_col:
+            gene_perturb_profile = self.prs_mat_df.loc[source,:]
+        else:
+            gene_perturb_profile = self.prs_mat_df.loc[:,source] 
+        nx.set_node_attributes(self.graph_gc, gene_perturb_profile.to_dict(), name='perturb_profile')
+
+    def get_prs_weighted_path(self, source, target=None, weight='weight', node_weight=None):
+        """
+            calculate shortest path using the PRS matrix values caused by perturbations on source node
+            This uses an adjusted version of networkx dijkstra functions to incorporate node_weight parameter
+            networkx source code should be under /home/oma21/networkx
+        """
+        if nx.get_edge_attributes(self.graph_gc,'weight') == {}:
+            nx.set_edge_attributes(self.graph_gc,0,'weight')
+        if node_weight is None:
+            node_weight = (1/self.prs_mat_df.loc[source,:]).to_dict()
+        if target is not None:
+            distances = nx.single_source_dijkstra(self.graph_gc, source=source,target=target, weight=weight, node_weight=node_weight)
+        else:
+            distances = nx.single_source_dijkstra(self.graph_gc, source=source, weight=weight, node_weight=node_weight)
+        return distances
+
     def get_node_distances(self):
[…]

### 2020-12-05 src/utils.py

@@ -39,6 +39,37 @@ def create_goea(gaf = '../data/raw/ontology/sgd.gaf', obo_fname = '../data/raw/o
 
     return goeaobj, geneid2name#, objanno, ns2assoc, ns2assoc_excl
 
+def create_goea_human(gene2go = '../data/raw/ontology/gene2go', obo_fname = '../data/raw/ontology/go-basic.obo', background='../data/interim/huri_gc_bg.tsv',**kwargs):
+    
+    #background='../data/raw/ontology/sgd_costanzogenes'
+    obodag = GODag(obo_fname)
+    from goatools.anno.genetogo_reader import Gene2GoReader
+
+# Read NCBI's gene2go. Store annotations in a list of namedtuples
+    objanno = Gene2GoReader(gene2go, taxids=[9606])
+#    ns2assoc = objanno.get_ns2assc()
+
+    ns2assoc_excl = objanno.get_ns2assc( ev_exclude = {'HGI' , 'IGI'})
+
+    bg = pd.read_csv(background, header=None)
+    bg_list = list(bg.iloc[:, 0])  # .to_list()
+    
+    import mygene
+    mg = mygene.MyGeneInfo()
+    out = mg.querymany(bg_list,scopes='ensemblgene', fields = 'unigene,entrezgene,uniprot', species=9606, as_dataframe=True)
+
+    geneids = [int(i) for i in out.loc[bg_list,'entrezgene'].dropna().values.tolist()]
+    geneid2name = pd.Series(out['entrezgene'].dropna().index.tolist(),index=[int(i) for i in out.loc[:,'entrezgene'].dropna().values]).to_dict()
+    goeaobj = GOEnrichmentStudyNS(
+        geneids,  # List of mouse protein-coding genes
+        ns2assoc_excl,  # geneid/GO associations
+        obodag,  # Ontologies
+        propagate_counts=False,
+        alpha=0.05,  # default significance cut-off
+        methods=['fdr_bh'], prt=None)
+
+    return goeaobj, geneid2name#, objanno, ns2assoc, ns2assoc_excl
+
 def go_findenrichment( query, outname=None, species='yeast',**kwargs):
     goeaobj, geneid2name = create_goea(**kwargs)
     query_gene_ids = [key for key,value in geneid2name.items() if value in query]#sgd_info[sgd_info.iloc[:,3].isin(query)].iloc[:,0].values.tolist()
[…]

### 2020-12-05 notebooks/paper_plots_0909.Rmd
added gi analysis to plots

@@
     e_huri = pickle.load(f)
+with open(f'data/interim/gi_1201/gi_100.pickle','rb') as f:
+    e_gi = pickle.load(f)
 
 pcc_df = e_pcc.df
+gi_df = e_gi.df
 pcc_gc = e_pcc.graph_gc
@@
 huri_df_random  = data.table::rbindlist(lapply(py$e_huri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
+gi_df_random  = data.table::rbindlist(lapply(py$e_gi$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
 pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
@@
 )%>%mutate(group=fct_relevel(group, c('real','random')))
-combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
-    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
+gi_df = py$gi_df%>%mutate(data='gi')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    gi_df_random%>%mutate(data='gi')%>%mutate(sens_norm = sens/nrow(py$gi_df),eff_norm = eff/nrow(py$gi_df), group = 'random')
+)%>%mutate(group=fct_relevel(group, c('real','random')))
+combined_df = bind_rows(pcc_df, yuri_df,huri_df,gi_df)%>%
+    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))
 ```
@@
 ```{r}
-combined_df%>%filter(group=='real')%>%
-    ggplot(aes(x=deg, y = ..count../sum(..count..)))+
-    facet_grid(rows=vars(data))+
-    geom_histogram(binwidth=1)+
-#    xlim(1,NA)+
-    ylim(NA, 0.1)
+#combined_df%>%filter(group=='real')%>%
+#    ggplot(aes(x=deg, y = ..count../sum(..count..)))+
+#    facet_grid(rows=vars(data))+
+#    geom_histogram(binwidth=1)+
+##    xlim(1,NA)+
+#    ylim(NA, 0.1)
 
@@
 pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
+gi_degree_dens <- 
+    plot_density_prs(gi_df, deg, xlab='Degree')
+gi_eff_dens <- 
+    plot_density_prs(gi_df, eff_norm, xlab='Effectiveness')
+#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
+gi_sensitivity_dens <- 
+    plot_density_prs(gi_df, sens_norm, xlab='Sensitivity')
+title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network GI", fontface='bold')
+gi_dens_comb = cowplot::plot_grid(gi_degree_dens+theme(legend.position='none'), 
+                                gi_eff_dens+theme(legend.position='none'), 
+                                gi_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
+gi_dens_comb_title = cowplot::plot_grid(title, gi_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
 yuri_degree_dens <- 
@@
 dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
+                                gi_dens_comb_title,
                                 yuri_dens_comb_title,
-                                huri_dens_comb_title,nrow=3)
+                                huri_dens_comb_title,nrow=4)
 cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
-ggsave('reports/figures/paper_figures_0916/fig1.png')
+ggsave('reports/figures/paper_figures_1204_withgi/fig1.png')
 
@@
     scale_y_continuous(labels = scales::label_scientific(digits=1))
+gi_deg_eff = gi_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=eff_norm))+
+    geom_point()+
+#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
+    theme_bw()+
+    ylab("Effectiveness")+
+    xlab("Degree")+
+    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
+gi_deg_sens = gi_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+    ggplot(aes(x=deg, y=sens_norm))+
+    geom_point()+
+#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
+    theme_bw()+
+    ylab("Sensitivity")+
+    xlab("Degree")+
+    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
+    theme(strip.text.y = element_text(angle = 0))+
+    scale_y_continuous(labels = scales::label_scientific(digits=1))
 yuri_deg_eff = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
@@
 deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
+                                        gi_deg_eff, gi_deg_sens,
                    yuri_deg_eff, yuri_deg_sens,
@@
                    ncol=2)
-ggsave('tmp.png',plot=deg_scatter_plots, width=10,height=10)
+ggsave('reports/figures/paper_figures_1204_withgi/fig2.png',plot=deg_scatter_plots, width=10,height=10)
 
@@
 pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
+gi_rewire_df = read_csv('data/interim/gi_1201/rewire_data.csv')
 yuri_rewire_df = read_csv('data/interim/yuri/rewire_data.csv')
@@
                                                            yuri_rewire_df%>%mutate(data='yuri'))%>%
-        bind_rows(huri_rewire_df%>%mutate(data='huri'))
+        bind_rows(huri_rewire_df%>%mutate(data='huri'))%>%bind_rows(gi_rewire_df%>%mutate(data='gi'))
 ```
@@
 ```{r}
-network_labels  <- c('Costanzo 2016','Yeast PPI','HuRI')
+network_labels  <- c('Costanzo 2016','Costanzo GI','Yeast PPI','HuRI')
 #p3 = ggplot(rewire_df, aes(x=eff_deg_pearson))+
@@
 facet_labels  <- network_labels
-names(facet_labels) <- c("pcc",'yuri','huri')
+names(facet_labels) <- c("pcc",'gi','yuri','huri')
 
@@
     bind_rows(
-    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$sens,method='spearman'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$eff,method='pearson'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc','yuri','huri')))%>%
-    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
+    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman'),cor(gi_df[gi_df$group=='real',]$deg, gi_df[gi_df$group=='real',]$sens,method='spearman'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$sens,method='spearman'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$sens,method='spearman')),
+               eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson'),cor(gi_df[gi_df$group=='real',]$deg, gi_df[gi_df$group=='real',]$eff,method='pearson'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$eff,method='pearson'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc','gi','yuri','huri')))%>%
+    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))
 
@@
 plot_grid(deg_scatter_plots, distr_plots, nrow=2,rel_heights = c(0.6,0.4))
-ggsave('reports/figures/paper_figures_0916/fig2.png',width=8,height=9)
+ggsave('reports/figures/paper_figures_1204_withgi/fig3.png',width=8,height=9)
 ```

### 2020-12-05 src/data/pcc.py
fixed normalized laplacian calculation by default

@@ -16,12 +16,13 @@ enm.read_network('data/interim/costanzo_pcc_ALL',sep=',')
 enm.gnm_analysis(normalized=False)
 
 #enm.figure_path=figure_path
-enm.output_path = 'data/interim/pcc_0909/'
+enm.output_path = 'data/interim/pcc_1020/'
 enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
 enm.spring_pos()
 
 enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=100)
-enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=100)
+random_dfs = [enm.e_list[i].df.to_csv(f'data/interim/pcc_1020/random_dfs/rand_{i}.csv') for i in range(100)]
+#enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=10)
 #enm.simulate_rewire(output_name='rewire_data_er', save=True, nodegseq=True,random_network_type='er', normalized=False)
 
 neigbor_btw = []

### 2020-12-05 src/features/huri_enm.py

@@ -11,22 +11,32 @@ from Bio import SeqIO
 figure_path = 'reports/figures/huri_0722'
 huri = Enm('huri')
 huri.read_network('data/interim/huri/huri_cleared.csv')
-huri.gnm_analysis()
+huri.gnm_analysis(normalized=False)
 
 huri.figure_path=figure_path
-huri.output_path = 'data/interim/huri/'
+huri.output_path = 'data/interim/huri_0916/'
 #huri.plot_collectivity()
-
-huri.plot_network_spring()
+huri.spring_pos()
+#huri.plot_network_spring()
 #huri.plot_vector(sorted=True)
 #huri.plot_scatter(x='deg',y='eff',figure_name='deg_eff',figure_extension='pdf')
 #huri.plot_scatter(x='deg',y='sens',figure_name='deg_sens',figure_extension='pdf')
 
-huri.simulate_rewire(output_name='rewire_data',save=True)
-huri.rewire_df
-huri.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
-huri.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')
+huri.simulate_rewire(output_name='rewire_data',save=True,normalized=False)
+#huri.rewire_df
+#huri.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
+#huri.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')
 nx.set_node_attributes(huri.graph_gc,dict(zip(list(huri.graph_gc.nodes),list(huri.graph_gc.nodes))),'orf_name')
+
+neigbor_btw = []
+neighbor_degree = []
+for i in huri.graph_gc.nodes:
+    neigbor_btw.append(np.average([huri.df.loc[huri.df.orf_name==a,'btw'].values for a in nx.neighbors(huri.graph_gc,i)]))
+    neighbor_degree.append(np.average([huri.df.loc[huri.df.orf_name==a,'deg'].values for a in nx.neighbors(huri.graph_gc,i)]))
+
+huri.df['neighbor_btw'] = neigbor_btw
+huri.df['neighbor_degree'] = neighbor_degree
+
 
 with open(f"{huri.output_path}/huri.pickle",'wb') as f:
     pickle.dump(huri,f, protocol=4)

### 2020-12-05 src/features/yuri_enm.py

@@ -11,26 +11,36 @@ from Bio import SeqIO
 figure_path = 'reports/figures/yuri_0519'
 yuri = Enm('yuri')
 yuri.read_network('data/interim/yuri/yuri_combined.csv')
-yuri.gnm_analysis()
+yuri.gnm_analysis(normalized=False)
 
 yuri.figure_path=figure_path
-yuri.output_path = 'data/interim/yuri/'
-yuri.plot_collectivity()
-
-yuri.plot_network_spring()
-yuri.plot_vector(sorted=True)
-yuri.plot_scatter(x='deg',y='eff',figure_name='deg_eff',figure_extension='pdf')
-yuri.plot_scatter(x='deg',y='sens',figure_name='deg_sens',figure_extension='pdf')
-
-yuri.simulate_rewire(output_name='rewire_data',save=True)
-yuri.rewire_df
-yuri.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
-yuri.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')
+yuri.output_path = 'data/interim/yuri_0916/'
+#yuri.plot_collectivity()
+yuri.spring_pos()
+#yuri.plot_network_spring()
+#yuri.plot_vector(sorted=True)
+#yuri.plot_scatter(x='deg',y='eff',figure_name='deg_eff',figure_extension='pdf')
+#yuri.plot_scatter(x='deg',y='sens',figure_name='deg_sens',figure_extension='pdf')
+#
+yuri.simulate_rewire(output_name='rewire_data',save=True,normalized=False)
+##yuri.rewire_df
+#yuri.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
+#yuri.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')
 nx.set_node_attributes(yuri.graph_gc,dict(zip(list(yuri.graph_gc.nodes),list(yuri.graph_gc.nodes))),'orf_name')
+
+neigbor_btw = []
+neighbor_degree = []
+for i in yuri.graph_gc.nodes:
+    neigbor_btw.append(np.average([yuri.df.loc[yuri.df.orf_name==a,'btw'].values for a in nx.neighbors(yuri.graph_gc,i)]))
[…]

### 2020-12-21 src/utils.py
added jaccard similarity calculations for HURI psn network

@@ -199,7 +199,7 @@ def sample_nodes_with_degree(gnm_df , nodes_df ):
 def get_in_to_out_edge_ratio(G, nodes_df):
     btw_edges = len(nx.induced_subgraph(G,nodes_df.orf_name).edges)
     flat_list_ego = np.unique([item for sublist in [list(nx.ego_graph(G,i,radius=1).nodes) for i in nodes_df.orf_name.values] for item in sublist])
-    total_edges = len(nx.induced_subgraph(G,flat_list_ego).edges)
+    total_edges = len(nx.induced_subgraph(G,flat_list_ego).edges)- len(nx.induced_subgraph(G,np.setdiff1d(flat_list_ego,nodes_df.orf_name)).edges)
     #rat = len([i for i in flat_list_ego if i in sensors['orf_name'].values ])/len([i for i in flat_list_ego if i not in sensors['orf_name'].values ])
     rat = btw_edges/total_edges #len([i for i in flat_list_ego if i in nodes_df['orf_name'].values ])/len(flat_list_ego)
     return rat
@@ -230,4 +230,11 @@ def get_maximal_subsets(sets):
             maximal_subsets.append(s)
 
     return maximal_subsets
- 
+
+def jaccard_index(G, a,b):
+    a_neigh = [i for i in nx.neighbors(G, a)]
+    b_neigh = [i for i in nx.neighbors(G, b)]
+    union = np.union1d(a_neigh,b_neigh)
+    intersect = np.intersect1d(a_neigh,b_neigh)
+    jaccard = len(intersect)/len(union)
+    return jaccard

### 2020-12-21 src/features/gi_enm.py
new data and slight changes in previous calculations regarding file creations

@@ -48,11 +48,11 @@ enm_02.gnm_analysis(normalized=False)
 
 #enm.figure_path=figure_path
 enm_02.output_path = 'data/interim/gi_1205_0.2/'
-os.mkdir(enm_02.output_path)
+#os.mkdir(enm_02.output_path)
 enm_02.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
 enm_02.spring_pos()
 
-os.mkdir(f"{enm_02.output_path}/random_dfs")
+#os.mkdir(f"{enm_02.output_path}/random_dfs")
 enm_02.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=10)
 random_dfs = [enm_02.e_list[i].df.to_csv(f'{enm_02.output_path}/random_dfs/rand_{i}.csv') for i in range(10)]
 #enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=10)

### 2020-12-21 src/features/gi_go.py

@@ -1,0 +1,69 @@
+import src
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+import networkx as nx
+import pickle
+from src.enm import *
+from src.utils import *
+
+with open('data/interim/gi_1205_0.2/gi_100.pickle','rb') as f:
+    e_gi = pickle.load(f)
+
+#e_gi.df.orf_name.to_csv('data/interim/huri_gc_bg.tsv','\t', index=False, header=False)
+
+#strain_ids = pd.read_csv('data/interim/strain_ids_with_experiment_count_all.csv')
+
+#combined_df = pd.merge(e_gi.df, strain_ids,left_on='orf_name',right_on='Allele Gene name')
+
+goea, geneid2name = create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/costanzo_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')
+sensors_gi = e_gi.df.loc[e_gi.df.sens> np.quantile(e_gi.df.sens,0.99)]
+effectors_gi = e_gi.df.loc[e_gi.df.eff> np.quantile(e_gi.df.eff,0.99)]
+degs_gi = e_gi.df.loc[e_gi.df.deg> np.quantile(e_gi.df.deg,0.99)]
+
+query_deg = e_gi.df.loc[e_gi.df.orf_name.isin(degs_gi.orf_name),'Systematic gene name'].unique()
+query_gene_ids = [key for key,value in geneid2name.items() if value in query_deg]
+goea_res_all = goea.run_study(query_gene_ids)
+goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.05]
+go_df_deg = goea_to_pandas(goea_res_sig, geneid2name)
+
+query_sens = e_gi.df.loc[e_gi.df.orf_name.isin(sensors_gi.orf_name),'Systematic gene name'].unique()
+query_gene_ids = [key for key,value in geneid2name.items() if value in query_sens]
+goea_res_all = goea.run_study(query_gene_ids)
+goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.05]
+go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
+
[…]

### 2020-12-21 src/features/huri_enm.py

@@ -14,7 +14,9 @@ huri.read_network('data/interim/huri/huri_cleared.csv')
 huri.gnm_analysis(normalized=False)
 
 huri.figure_path=figure_path
-huri.output_path = 'data/interim/huri_0916/'
+huri.output_path = 'data/interim/huri_1205/'
+if os.path.exists(huri.output_path)==False:
+    os.mkdir(huri.output_path)
 #huri.plot_collectivity()
 huri.spring_pos()
 #huri.plot_network_spring()
@@ -22,7 +24,10 @@ huri.spring_pos()
 #huri.plot_scatter(x='deg',y='eff',figure_name='deg_eff',figure_extension='pdf')
 #huri.plot_scatter(x='deg',y='sens',figure_name='deg_sens',figure_extension='pdf')
 
-huri.simulate_rewire(output_name='rewire_data',save=True,normalized=False)
+huri.simulate_rewire(output_name='rewire_data',save=True,normalized=False, simnum=10)
+if os.path.exists(f"{huri.output_path}/random_dfs")==False:
+    os.mkdir(f"{huri.output_path}/random_dfs")
+random_dfs = [huri.e_list[i].df.to_csv(f'{huri.output_path}/random_dfs/rand_{i}.csv') for i in range(10)]
 #huri.rewire_df
 #huri.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
 #huri.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')

### 2020-12-21 src/features/nsdp.py

@@ -1,0 +1,43 @@
+import src
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+import networkx as nx
+import pickle
+from tqdm import tqdm
+from src.enm import *
+from src.utils import *
+
+
+
+#figure_path = 'reports/figures/pcc_0603'
+enm = Enm('enm')
+enm.read_network('data/raw/NPdP.csv')
+enm.gnm_analysis(normalized=False)
+
+#enm.figure_path=figure_path
+enm.output_path = 'data/interim/npdp_1211/'
+if os.path.exists(enm.output_path)==False:
+    os.mkdir(enm.output_path)
+#enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
+enm.spring_pos()
+if os.path.exists(f"{enm.output_path}/random_dfs")==False:
+    os.mkdir(f"{enm.output_path}/random_dfs")
+enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=10)
+random_dfs = [enm.e_list[i].df.to_csv(f'{enm.output_path}/random_dfs/rand_{i}.csv') for i in range(10)]
+#enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=10)
+#enm.simulate_rewire(output_name='rewire_data_er', save=True, nodegseq=True,random_network_type='er', normalized=False)
+
+neigbor_btw = []
+neighbor_degree = []
+for i in enm.graph_gc.nodes:
+    neigbor_btw.append(np.average([enm.df.loc[enm.df.orf_name==a,'btw'].values for a in nx.neighbors(enm.graph_gc,i)]))
+    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
+
+enm.df['neighbor_btw'] = neigbor_btw
+enm.df['neighbor_degree'] = neighbor_degree
+
+with open(f"{enm.output_path}/npdp.pickle",'wb') as f:
+    pickle.dump(enm,f, protocol=4)
+
+

### 2020-12-21 src/features/pcc_go.py

@@ -20,13 +20,26 @@ goea, geneid2name = create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='da
 sensors_pcc = e_pcc.df.loc[e_pcc.df.sens> np.quantile(e_pcc.df.sens,0.99)]
 effectors_pcc = e_pcc.df.loc[e_pcc.df.eff> np.quantile(e_pcc.df.eff,0.99)]
 degs_pcc = e_pcc.df.loc[e_pcc.df.deg> np.quantile(e_pcc.df.deg,0.99)]
+query = e_pcc.df.loc[e_pcc.df.orf_name.isin(sensors_pcc.orf_name),'Systematic gene name'].unique()
+query_gene_ids = [key for key,value in geneid2name.items() if value in query]
+goea_res_all = goea.run_study(query_gene_ids)
+goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.1]
+go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
+goea.wr_tsv('data/interim/pcc_0909/pcc_sensor_go.tsv', goea_res_sig)
+
+query = e_pcc.df.loc[e_pcc.df.orf_name.isin(effectors_pcc.orf_name),'Systematic gene name'].unique()
+query_gene_ids = [key for key,value in geneid2name.items() if value in query]
+goea_res_all = goea.run_study(query_gene_ids)
+goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.1]
+go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
+goea.wr_tsv('data/interim/pcc_0909/pcc_effector_go.tsv', goea_res_sig)
+
 query = e_pcc.df.loc[e_pcc.df.orf_name.isin(degs_pcc.orf_name),'Systematic gene name'].unique()
 query_gene_ids = [key for key,value in geneid2name.items() if value in query]
 goea_res_all = goea.run_study(query_gene_ids)
-goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.05]
+goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.1]
 go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
-
-goea.wr_tsv('data/interim/pcc_0909/pcc_sensor_go.tsv', goea_res_sig)
[…]

### 2020-12-21 src/features/sensor_connectivity.py

@@ -54,3 +54,30 @@ pd.concat(
 ).to_csv('data/interim/sensor_connectivity_1205/sensor_connectivity_df.csv')
 
 
+#pcc_random_ratio_list = get_random_in_to_out_ratio(pcc_df, pcc_df.loc[pcc_df.eff>np.quantile(pcc_df.eff,0.99)], e_pcc.graph_gc)
+#pcc_ratio = get_in_to_out_edge_ratio(e_pcc.graph_gc, pcc_df.loc[pcc_df.eff>np.quantile(pcc_df.eff,0.99)])
+#
+#gi_random_ratio_list = get_random_in_to_out_ratio(gi_df, gi_df.loc[gi_df.eff>np.quantile(gi_df.eff,0.99)], e_gi.graph_gc)
+#gi_random_ratio_list = [i+np.finfo(float).eps for i in gi_random_ratio_list]
+#gi_ratio = get_in_to_out_edge_ratio(e_gi.graph_gc, gi_df.loc[gi_df.eff>np.quantile(gi_df.eff,0.99)])
+#
+#huri_random_ratio_list = get_random_in_to_out_ratio(huri_df, huri_df.loc[huri_df.eff>np.quantile(huri_df.eff,0.99)], e_huri.graph_gc)
+#huri_ratio = get_in_to_out_edge_ratio(e_huri.graph_gc, huri_df.loc[huri_df.eff>np.quantile(huri_df.eff,0.99)])
+#
+#yuri_random_ratio_list = get_random_in_to_out_ratio(yuri_df, yuri_df.loc[yuri_df.eff>np.quantile(yuri_df.eff,0.99)], e_yuri.graph_gc)
+#yuri_ratio = get_in_to_out_edge_ratio(e_yuri.graph_gc, yuri_df.loc[yuri_df.eff>np.quantile(yuri_df.eff,0.99)])
+#
+#pd.concat(
+#[
+#    pd.DataFrame([[('pcc'),pcc_ratio, ('real')]], columns=['data','ratio','type']),
+#    pd.DataFrame(list(zip(itr.repeat('pcc'),pcc_random_ratio_list, itr.repeat('random'))), columns=['data','ratio','type']),
+#    pd.DataFrame([[('gi'),gi_ratio, ('real')]], columns=['data','ratio','type']),
+#    pd.DataFrame(list(zip(itr.repeat('gi'),gi_random_ratio_list, itr.repeat('random'))), columns=['data','ratio','type']),
[…]

### 2020-12-21 src/features/yuri_enm.py

@@ -14,7 +14,9 @@ yuri.read_network('data/interim/yuri/yuri_combined.csv')
 yuri.gnm_analysis(normalized=False)
 
 yuri.figure_path=figure_path
-yuri.output_path = 'data/interim/yuri_0916/'
+yuri.output_path = 'data/interim/yuri_1205/'
+if os.path.exists(yuri.output_path)==False:
+    os.mkdir(yuri.output_path)
 #yuri.plot_collectivity()
 yuri.spring_pos()
 #yuri.plot_network_spring()
@@ -22,7 +24,7 @@ yuri.spring_pos()
 #yuri.plot_scatter(x='deg',y='eff',figure_name='deg_eff',figure_extension='pdf')
 #yuri.plot_scatter(x='deg',y='sens',figure_name='deg_sens',figure_extension='pdf')
 #
-yuri.simulate_rewire(output_name='rewire_data',save=True,normalized=False)
+yuri.simulate_rewire(output_name='rewire_data',save=True,normalized=False,simnum=10)
 ##yuri.rewire_df
 #yuri.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
 #yuri.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')

### 2020-12-21 notebooks/10-enm_rnaseq-0825.Rmd
notebooks with all analyses i have until Dec 21st 2020

---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.5.2
  kernelspec:
    display_name: R
    language: R
    name: ir
---

<!-- #region toc=true -->
<h1>Table of Contents<span class="tocSkip"></span></h1>
<div class="toc"><ul class="toc-item"></ul></div>
<!-- #endregion -->

```{r}
library(tidyverse)
library(edgeR)
library(tximport)
library(GenomicFeatures)
```

```{r}
ann  <-  '~/data/genome/gtf/Saccharomyces_cerevisiae.R64-1-1.46.gtf'
table_  <- data.table::fread('~/data/PRJNA475469/SraRunTable_PRJNA475469.txt')
samples <- table_ %>%
                dplyr::select(`Run`,`kinase_inhibitor`,
                       `media`, stress, Genotype)%>%
                #unite('condition', `Factor Value[genotype]`,`Factor Value[environmental stress]`)%>%
                distinct()#
```

```{r}
files <- file.path('~/data/rnaseq/PRJNA475469/quants',(samples$Run),'quant.sf')
names(files) <- samples$Run
```

```{r jupyter={'outputs_hidden': True}}
txdb <- makeTxDbFromEnsembl("Saccharomyces cerevisiae",
                                    server="useastdb.ensembl.org")
k <- keys(txdb, keytype = "TXNAME")
tx2gene <- AnnotationDbi::select(txdb, k, "GENEID", "TXNAME")
txi.salmon <- tximport(files,type='salmon',tx2gene=tx2gene)

ypd_wt <-  samples%>%filter(Genotype=='WT')%>%mutate(stress=ifelse(media=='SDC','SD',ifelse(stress=='None','YPD',stress)))
ypd_wt_runids <-ypd_wt%>%dplyr::select(Run)%>%pull()
```

```{r}
counts_mat<- txi.salmon$counts[,ypd_wt_runids]
y <- DGEList(counts=counts_mat)
y <- calcNormFactors(y,method='TMM')
tmm <- cpm(y)
```

```{r}
samples
```

```{r}

```

```{r}
ypd_sdc_runids <- samples%>%filter(kinase_inhibitor=='None'&(stress=='None'|stress=='Glucose_Dropout')&media=='YPD'&Genotype=='WT')%>%dplyr::select(Run)%>%pull()
ypd_sdc_runids
```

```{r}

counts_mat<- txi.salmon$counts[,ypd_sdc_runids]
y <- DGEList(counts=counts_mat)
y <- calcNormFactors(y,method='TMM')
tmm <- cpm(y)

condition <- factor(samples%>%dplyr::filter(Run%in%ypd_sdc_runids)%>%dplyr::select(stress)%>%pull())
condition<-relevel(condition,ref='None')
design <- model.matrix(~condition)
rownames(design) <- colnames(y)
y <- estimateDisp(y,design,robust=T)
y$common.dispersion

```

```{r}
fit <- glmFit(y,design)
lrt_ds <- glmLRT(fit,coef=2)
FDR <- p.adjust(lrt_ds$table$PValue, method="BH")
tb <- lrt_ds$table
tb['FDR']  <- FDR

#tb[lst_of_genes,]
```

```{r}
enm_df <- data.table::fread('../data/interim/0824_df_withlinkcom.csv')
```

```{r jupyter={'outputs_hidden': True}}
enm_df
```

```{r}
strain_ids <- data.table::fread('../data/interim/strain_ids_with_experiment_count_all.csv')
```

```{r}
enm_rnaseq = enm_df %>% 
inner_join(strain_ids,c('orf_name'='Allele Gene name'))%>%
inner_join(tb%>%rownames_to_column('orf_name'),c('Systematic gene name.y'='orf_name'))
```

```{r}
enm_rnaseq %>%ggplot(aes(x=eff,y=(logFC),col=FDR < 0.01))+
    geom_point()+
    geom_hline(yintercept=1)+
    geom_hline(yintercept=-1)
```

```{r}

```

### 2020-12-21 notebooks/paper_plots_0909.Rmd
notebooks with all analyses i have until Dec 21st 2020

@@
     e_pcc = pickle.load(f)
-with open(f'data/interim/yuri_0916/yuri.pickle','rb') as f:
+with open(f'data/interim/yuri_1205/yuri.pickle','rb') as f:
     e_yuri = pickle.load(f)
-with open(f'data/interim/huri_0916/huri.pickle','rb') as f:
+with open(f'data/interim/huri_1205/huri.pickle','rb') as f:
     e_huri = pickle.load(f)
-with open(f'data/interim/gi_1201/gi_100.pickle','rb') as f:
+with open(f'data/interim/gi_1205_0.2/gi_100.pickle','rb') as f:
     e_gi = pickle.load(f)
@@
     plot_density_prs(pcc_df, sens_norm, xlab='Sensitivity')
-title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network", fontface='bold')
+title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
 pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
@@
     plot_density_prs(gi_df, sens_norm, xlab='Sensitivity')
-title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network GI", fontface='bold')
+title <- cowplot::ggdraw() + cowplot::draw_label("Yeast Genetic Interaction", fontface='bold')
 gi_dens_comb = cowplot::plot_grid(gi_degree_dens+theme(legend.position='none'), 
                                 gi_eff_dens+theme(legend.position='none'), 
-                                gi_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
+                                gi_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
 gi_dens_comb_title = cowplot::plot_grid(title, gi_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
@@
                                 yuri_eff_dens+theme(legend.position='none'), 
-                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
+                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
 yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
@@
                                 huri_eff_dens+theme(legend.position='none'), 
-                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
+                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('J','K','L'),ncol=3)
 huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
@@
 cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
-ggsave('reports/figures/paper_figures_1204_withgi/fig1.png')
+ggsave('reports/figures/paper_figures_1204_withgi/fig1.png', width=8,height=12)
 
@@
 #    ylim(NA, 0.1)
-ggsave('tmp.png')
+#ggsave('tmp.png')
 
@@
                    yuri_deg_eff, yuri_deg_sens,
-                   huri_deg_eff, huri_deg_sens, labels = c('A','','B','','C',''),
+                   huri_deg_eff, huri_deg_sens, labels = c('A','','B','','C','','D',''),
                    ncol=2)
@@
 pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
-gi_rewire_df = read_csv('data/interim/gi_1201/rewire_data.csv')
-yuri_rewire_df = read_csv('data/interim/yuri/rewire_data.csv')
-huri_rewire_df = read_csv('data/interim/huri/rewire_data.csv')
+gi_rewire_df = read_csv('data/interim/gi_1205_0.2/rewire_data.csv')
+yuri_rewire_df = read_csv('data/interim/yuri_1205/rewire_data.csv')
+huri_rewire_df = read_csv('data/interim/huri_1205/rewire_data.csv')
 
@@
 ```{r}
-network_labels  <- c('Costanzo 2016','Costanzo GI','Yeast PPI','HuRI')
+network_labels  <- c('Yeast GI Profile Similarity','Yeast Genetic Interaction','Yeast PPI','HuRI')
 #p3 = ggplot(rewire_df, aes(x=eff_deg_pearson))+
@@
  p4+theme(legend.position=''), lgn34,
- nrow=3, labels=c('D','E','','F','G',''), rel_heights = c(0.45,0.45,0.1))
+ nrow=3, labels=c('E','F',''), rel_heights = c(0.45,0.45,0.1))
 #ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
-
 plot_grid(deg_scatter_plots, distr_plots, nrow=2,rel_heights = c(0.6,0.4))
-ggsave('reports/figures/paper_figures_1204_withgi/fig3.png',width=8,height=9)
+ggsave('reports/figures/paper_figures_1204_withgi/fig3.png',width=10,height=12)
 ```
@@
 ```{r}
-sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
-    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
 
@@
 
+sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/sensor_connectivity_df.csv')%>%
+    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))
 #p3 = 
@@
     scale_y_continuous(expand = c(0, 0)) 
-
-#p3 = 
-    ggplot()+
-    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
-                 aes(x=data,y=ratio,color=type))+
-#    geom_jitter()+
-    geom_vline(data=sensor_connectivity_df%>%filter(type=='real'),
-            aes(x=data,y=ratio,color=type, group=data))+
-               #position=position_jitter(), aes(shape=data))+
-    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
-    scale_x_discrete(labels=network_labels)+
-  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
-    theme_bw()
-
+##p3 = 
+#    ggplot()+
+#    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
+#                 aes(x=data,y=ratio,color=type))+
+##    geom_jitter()+
+#    geom_vline(data=sensor_connectivity_df%>%filter(type=='real'),
+#            aes(x=data,y=ratio,color=type, group=data))+
+#               #position=position_jitter(), aes(shape=data))+
+#    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
+#    scale_x_discrete(labels=network_labels)+
+#  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
+#    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
+#    theme_bw()
 neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
@@
 plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
-ggsave('reports/figures/paper_figures_0916/fig5.png')
+ggsave('reports/figures/paper_figures_1204_withgi/fig5.png')
 

### 2020-12-21 notebooks/paper_plots_1211.Rmd
notebooks with all analyses i have until Dec 21st 2020

--- 2020-12-05 notebooks/paper_plots_0909.Rmd
@@
 import pandas as pd
-import plotnine as p9
 import pickle 
@@
     e_pcc = pickle.load(f)
-with open(f'data/interim/yuri_0916/yuri.pickle','rb') as f:
-    e_yuri = pickle.load(f)
-with open(f'data/interim/huri_0916/huri.pickle','rb') as f:
-    e_huri = pickle.load(f)
-with open(f'data/interim/gi_1201/gi_100.pickle','rb') as f:
-    e_gi = pickle.load(f)
+with open(f'data/interim/psn_1201/psn.pickle','rb') as f:
+    e_psn = pickle.load(f)
+with open(f'data/interim/npdp_1211/npdp.pickle','rb') as f:
+    e_nsdp = pickle.load(f)
+#with open(f'data/interim/nsdp_1205/nsdp.pickle','rb') as f:
+#    e_nsdp = pickle.load(f)
+#with open(f'data/interim/psn_1205/psn.pickle','rb') as f:
+#    e_psn = pickle.load(f)
+#with open(f'data/interim/gi_1205_0.2/gi_100.pickle','rb') as f:
+#    e_gi = pickle.load(f)
 
 pcc_df = e_pcc.df
-gi_df = e_gi.df
+psn_df = e_psn.df
 pcc_gc = e_pcc.graph_gc
 pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))
-yuri_df = e_yuri.df
-huri_df = e_huri.df
+nsdp_df = e_nsdp.df
+#psn_df = e_psn.df
 ```
@@
 pcc_df_random  = data.table::rbindlist(lapply(py$e_pcc$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
-yuri_df_random  = data.table::rbindlist(lapply(py$e_yuri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
-huri_df_random  = data.table::rbindlist(lapply(py$e_huri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
-gi_df_random  = data.table::rbindlist(lapply(py$e_gi$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
+nsdp_df_random  = data.table::rbindlist(lapply(py$e_nsdp$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
+psn_df_random  = data.table::rbindlist(lapply(py$e_psn$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
 pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
@@
 )%>%mutate(group=fct_relevel(group, c('real','random')))
-yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
-    yuri_df_random%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(py$yuri_df),eff_norm = eff/nrow(py$yuri_df), group = 'random')
+nsdp_df = py$nsdp_df%>%mutate(data='nsdp')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    nsdp_df_random%>%mutate(data='nsdp')%>%mutate(sens_norm = sens/nrow(py$nsdp_df),eff_norm = eff/nrow(py$nsdp_df), group = 'random')
 )%>%mutate(group=fct_relevel(group, c('real','random')))
-huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
-    huri_df_random%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(py$huri_df),eff_norm = eff/nrow(py$huri_df), group = 'random')
+psn_df = py$psn_df%>%mutate(data='psn')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
+    psn_df_random%>%mutate(data='psn')%>%mutate(sens_norm = sens/nrow(py$psn_df),eff_norm = eff/nrow(py$psn_df), group = 'random')
 )%>%mutate(group=fct_relevel(group, c('real','random')))
-gi_df = py$gi_df%>%mutate(data='gi')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
-    gi_df_random%>%mutate(data='gi')%>%mutate(sens_norm = sens/nrow(py$gi_df),eff_norm = eff/nrow(py$gi_df), group = 'random')
-)%>%mutate(group=fct_relevel(group, c('real','random')))
-combined_df = bind_rows(pcc_df, yuri_df,huri_df,gi_df)%>%
-    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))
+combined_df = bind_rows(pcc_df, nsdp_df,psn_df)%>%
+    mutate(data= fct_relevel(data, c('pcc','nsdp','psn')))
 ```
@@
 pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-gi_degree_dens <- 
-    plot_density_prs(gi_df, deg, xlab='Degree')
-gi_eff_dens <- 
-    plot_density_prs(gi_df, eff_norm, xlab='Effectiveness')
 #annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
-gi_sensitivity_dens <- 
-    plot_density_prs(gi_df, sens_norm, xlab='Sensitivity')
-title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network GI", fontface='bold')
-gi_dens_comb = cowplot::plot_grid(gi_degree_dens+theme(legend.position='none'), 
-                                gi_eff_dens+theme(legend.position='none'), 
-                                gi_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
-gi_dens_comb_title = cowplot::plot_grid(title, gi_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-yuri_degree_dens <- 
-    plot_density_prs(yuri_df, deg, xlab='Degree')
-yuri_eff_dens <- 
-    plot_density_prs(yuri_df, eff_norm, xlab='Effectiveness')
-yuri_sensitivity_dens <- 
-    plot_density_prs(yuri_df, sens_norm, xlab='Sensitivity')
-title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
-yuri_dens_comb = cowplot::plot_grid(yuri_degree_dens+theme(legend.position='none'), 
-                                yuri_eff_dens+theme(legend.position='none'), 
-                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
-yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-huri_degree_dens <- 
-    plot_density_prs(huri_df, deg, xlab='Degree')
-huri_eff_dens <- 
-    plot_density_prs(huri_df, eff_norm, xlab='Effectiveness')
-huri_sensitivity_dens <- 
-    plot_density_prs(huri_df, sens_norm, xlab='Sensitivity')
-title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
-huri_dens_comb = cowplot::plot_grid(huri_degree_dens+theme(legend.position='none'), 
-                                huri_eff_dens+theme(legend.position='none'), 
-                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
-huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
+nsdp_degree_dens <- 
+    plot_density_prs(nsdp_df, deg, xlab='Degree')
+nsdp_eff_dens <- 
+    plot_density_prs(nsdp_df, eff_norm, xlab='Effectiveness')
+nsdp_sensitivity_dens <- 
+    plot_density_prs(nsdp_df, sens_norm, xlab='Sensitivity')
+title <- cowplot::ggdraw() + cowplot::draw_label("Yeast coexpression network", fontface='bold')
+nsdp_dens_comb = cowplot::plot_grid(nsdp_degree_dens+theme(legend.position='none'), 
+                                nsdp_eff_dens+theme(legend.position='none'), 
+                                nsdp_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
+nsdp_dens_comb_title = cowplot::plot_grid(title, nsdp_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
+psn_degree_dens <- 
+    plot_density_prs(psn_df, deg, xlab='Degree')
+psn_eff_dens <- 
+    plot_density_prs(psn_df, eff_norm, xlab='Effectiveness')
+psn_sensitivity_dens <- 
+    plot_density_prs(psn_df, sens_norm, xlab='Sensitivity')
+title <- cowplot::ggdraw() + cowplot::draw_label("HuRI Profile similarity", fontface='bold')
+psn_dens_comb = cowplot::plot_grid(psn_degree_dens+theme(legend.position='none'), 
+                                psn_eff_dens+theme(legend.position='none'), 
+                                psn_sensitivity_dens+theme(legend.position='none'), labels=c('J','K','L'),ncol=3)
+psn_dens_comb_title = cowplot::plot_grid(title, psn_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
 dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
 dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
-                                gi_dens_comb_title,
-                                yuri_dens_comb_title,
-                                huri_dens_comb_title,nrow=4)
+                                nsdp_dens_comb_title,
+                                psn_dens_comb_title,nrow=3)
 cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
-ggsave('reports/figures/paper_figures_1204_withgi/fig1.png')
-
-#degree_dens <- 
-#    ggplot(combined_df%>%filter(group=='real'), aes(x=deg))+
-#    ggplot(combined_df%>%filter(group=='random'), aes(x=deg, y=..scaled.., fill=.id))+
-#    facet_grid(rows=vars(data))+
-#    #geom_density()+
-#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
-#    theme_bw()+
-#    xlab('Degree')+
-#    coord_trans(x = "log10", y = "log1p")+
-#scale_x_continuous(
-#   breaks = scales::trans_breaks("log10", function(x) 10^x),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log10", function(x) 10^(x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-#theme(panel.grid.minor = element_blank())
-#eff_dens <- 
-#    combined_df%>%filter(group=='real')%>%
-#    ggplot(aes(x=eff_norm ))+
-#    facet_grid(rows=vars(data), scales='free_y')+
-##    geom_density()+
-#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
-#    #geom_histogram(binwidth=0.0001)+
-#    theme_bw()+
-#    xlab('Effectivity')+
-#    coord_trans(x = "log10", y = "log1p")+
-#scale_x_continuous(
-#   breaks = scales::trans_breaks("log10", function(x) 10^x),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-#theme(panel.grid.minor = element_blank())
-#sensitivity_dens <- 
-#    combined_df%>%filter(group=='real')%>%
-#    ggplot(aes(x=sens_norm))+
-#    facet_grid(rows=vars(data))+
-#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
-#   # geom_density()+
-#    theme_bw()+
-#    xlab('Sensitivity')+
-#    coord_trans(x = "log10", y = "log1p")+
-#   # annotation_logticks()+
-#scale_x_continuous(
-#   breaks = scales::trans_breaks("log10", function(x) 10^x),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-#theme(panel.grid.minor = element_blank())
-#cowplot::plot_grid(degree_dens, eff_dens, sensitivity_dens, ncol=3,labels=c('A','B','C'))
-#ggsave('tmp.png')
-
-#    coord_trans(x = "log10", y = "log1p")
-#    scale_x_continuous(trans = "log10")
-    #scale_x_log10()
-#    geom_histogram(binwidth=1)+
-#    xlim(1,NA)+
-#    ylim(NA, 0.1)
-ggsave('tmp.png')
+ggsave('reports/figures/paper_figures_1211_withcoex/fig1.png', width=8,height=12)
 
@@
     scale_y_continuous(labels = scales::label_scientific(digits=1))
-gi_deg_eff = gi_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+nsdp_deg_eff = nsdp_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
     ggplot(aes(x=deg, y=eff_norm))+
@@
     scale_y_continuous(labels = scales::label_scientific(digits=1))
-gi_deg_sens = gi_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+nsdp_deg_sens = nsdp_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
     ggplot(aes(x=deg, y=sens_norm))+
@@
     scale_y_continuous(labels = scales::label_scientific(digits=1))
-yuri_deg_eff = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+psn_deg_eff = psn_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
     ggplot(aes(x=deg, y=eff_norm))+
@@
     scale_y_continuous(labels = scales::label_scientific(digits=1))
-yuri_deg_sens = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
-    ggplot(aes(x=deg, y=sens_norm))+
-    geom_point()+
-#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
-    theme_bw()+
-    ylab("Sensitivity")+
-    xlab("Degree")+
-    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
-    theme(strip.text.y = element_text(angle = 0))+
-    scale_y_continuous(labels = scales::label_scientific(digits=1))
-huri_deg_eff = huri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
-    ggplot(aes(x=deg, y=eff_norm))+
-    geom_point()+
-#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
-    theme_bw()+
-    ylab("Effectiveness")+
-    xlab("Degree")+
-    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
-    theme(strip.text.y = element_text(angle = 0))+
-    scale_y_continuous(labels = scales::label_scientific(digits=1))
-huri_deg_sens = huri_df %>%filter(group=='real')%>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+psn_deg_sens = psn_df %>%filter(group=='real')%>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
     ggplot(aes(x=deg, y=sens_norm))+
@@
 deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
-                                        gi_deg_eff, gi_deg_sens,
-                   yuri_deg_eff, yuri_deg_sens,
-                   huri_deg_eff, huri_deg_sens, labels = c('A','','B','','C',''),
+                   nsdp_deg_eff, nsdp_deg_sens,
+                   psn_deg_eff, psn_deg_sens, labels = c('A','','B','','C','','D',''),
                    ncol=2)
-ggsave('reports/figures/paper_figures_1204_withgi/fig2.png',plot=deg_scatter_plots, width=10,height=10)
+ggsave('reports/figures/paper_figures_1211_withcoex/fig2.png',plot=deg_scatter_plots, width=10,height=10)
 
-#p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
-#    geom_point(aes(color=cat_))+
-#    xlab('Degree')+
-#    ylab('Effectiveness')+
-#    stat_cor(method='pearson')   +
-#    guides(color=guide_legend(title="Experiment categories"))+
-#    theme_bw()
-#p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
-#    geom_point(aes(color=cat_))+
-#    xlab('Degree')+
-#    ylab('Sensitivity')+
-#    stat_cor(method='spearman')   +
-#    guides(color=guide_legend(title="Experiment categories"))+
-#    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
-#lgn = cowplot::get_legend(p2)
-#fig3 = plot_grid(p1+theme(legend.position=''),
-#          p2+theme(legend.position=''),
-#          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
-#ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
 ```
@@
 pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
-gi_rewire_df = read_csv('data/interim/gi_1201/rewire_data.csv')
-yuri_rewire_df = read_csv('data/interim/yuri/rewire_data.csv')
-huri_rewire_df = read_csv('data/interim/huri/rewire_data.csv')
+nsdp_rewire_df = read_csv('data/interim/npdp_1211/rewire_data.csv')
+psn_rewire_df = read_csv('data/interim/psn_1201/rewire_data.csv')
 
 rewire_df = pcc_rewire_df%>%mutate(data='pcc')%>%bind_rows(
-                                                           yuri_rewire_df%>%mutate(data='yuri'))%>%
-        bind_rows(huri_rewire_df%>%mutate(data='huri'))%>%bind_rows(gi_rewire_df%>%mutate(data='gi'))
+                                                           nsdp_rewire_df%>%mutate(data='nsdp'))%>%
+        bind_rows(psn_rewire_df%>%mutate(data='psn'))
 ```
@@
 ```{r}
-network_labels  <- c('Costanzo 2016','Costanzo GI','Yeast PPI','HuRI')
+network_labels  <- c('Yeast GI Profile Similarity','Yeast Coex','HuRI')
 #p3 = ggplot(rewire_df, aes(x=eff_deg_pearson))+
@@
 facet_labels  <- network_labels
-names(facet_labels) <- c("pcc",'gi','yuri','huri')
+names(facet_labels) <- c("pcc",'nsdp','psn')
 
@@
     bind_rows(
-    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman'),cor(gi_df[gi_df$group=='real',]$deg, gi_df[gi_df$group=='real',]$sens,method='spearman'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$sens,method='spearman'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$sens,method='spearman')),
-               eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson'),cor(gi_df[gi_df$group=='real',]$deg, gi_df[gi_df$group=='real',]$eff,method='pearson'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$eff,method='pearson'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc','gi','yuri','huri')))%>%
-    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))
+    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman'),cor(nsdp_df[nsdp_df$group=='real',]$deg,nsdp_df[nsdp_df$group=='real',]$sens,method='spearman'),cor(psn_df[psn_df$group=='real',]$deg,psn_df[psn_df$group=='real',]$sens,method='spearman')),
+               eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson'),cor(nsdp_df[nsdp_df$group=='real',]$deg,nsdp_df[nsdp_df$group=='real',]$eff,method='pearson'),cor(psn_df[psn_df$group=='real',]$deg,psn_df[psn_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc','nsdp','psn')))%>%
+    mutate(data= fct_relevel(data, c('pcc','nsdp','psn')))
 
@@
  p4+theme(legend.position=''), lgn34,
- nrow=3, labels=c('D','E','','F','G',''), rel_heights = c(0.45,0.45,0.1))
+ nrow=3, labels=c('E','F',''), rel_heights = c(0.45,0.45,0.1))
 #ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
-
 plot_grid(deg_scatter_plots, distr_plots, nrow=2,rel_heights = c(0.6,0.4))
-ggsave('reports/figures/paper_figures_1204_withgi/fig3.png',width=8,height=9)
+ggsave('reports/figures/paper_figures_1211_withcoex/fig3.png',width=10,height=12)
 ```
@@
     mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='pcc')
-yuri_deletion = read_csv('data/interim/deletion_analysis_0911/yuri_deletion_100.csv')%>%
+nsdp_deletion = read_csv('data/interim/deletion_analysis_0911/nsdp_deletion_100.csv')%>%
     pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
-    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='yuri')
-huri_deletion = read_csv('data/interim/deletion_analysis_0911/huri_deletion_100.csv')%>%
+    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='nsdp')
+psn_deletion = read_csv('data/interim/deletion_analysis_0911/psn_deletion_100.csv')%>%
     pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
-    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='huri')
+    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='psn')
 
-deletion_df  <- bind_rows(pcc_deletion, yuri_deletion, huri_deletion)%>%mutate(group = fct_relevel(group,c('pcc','yuri','huri')))
+deletion_df  <- bind_rows(pcc_deletion, nsdp_deletion, psn_deletion)%>%mutate(group = fct_relevel(group,c('pcc','nsdp','psn')))
 
@@
    theme(legend.position='bottom', legend.title=element_text(size=18), legend.text=element_text(size=14),legend.spacing.x = unit(1.0, 'cm'),legend.spacing.y = unit(1.0, 'cm'))
-auc_plot_yuri <- auc_data%>%
-    ggplot(aes(x=variable_0,y=yuri))+
+auc_plot_nsdp <- auc_data%>%
+    ggplot(aes(x=variable_0,y=nsdp))+
     geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ),stat='identity')+
@@
    theme(legend.position='right')
-auc_plot_huri<- auc_data%>%
-    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" ) ))+
+auc_plot_psn<- auc_data%>%
+    ggplot(aes(x=variable_0,y=psn, alpha = (variable_0 == "eff_sorted_deletion" ) ))+
     geom_bar(aes(fill=variable_0),stat='identity')+
@@
     theme(legend.position='bottom',panel.border = element_blank(), axis.line = element_line())
-deletion_plot_yuri <-  yuri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
+deletion_plot_nsdp <-  nsdp_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
 ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" )  ))+
@@
     theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
-deletion_plot_huri <-  huri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
+deletion_plot_psn <-  psn_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
 ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion"  ) ))+
@@
   )
-yuri_with_inset = ggdraw(deletion_plot_yuri+    theme(legend.position=''))+
-  draw_plot(auc_plot_yuri+theme(legend.position=''), .50, .62, .45, .35) +
+nsdp_with_inset = ggdraw(deletion_plot_nsdp+    theme(legend.position=''))+
+  draw_plot(auc_plot_nsdp+theme(legend.position=''), .50, .62, .45, .35) +
   draw_plot_label(
@@
   )
-huri_with_inset = ggdraw(deletion_plot_huri+    theme(legend.position=''))+
-  draw_plot(auc_plot_huri+theme(legend.position=''), .50, .62, .45, .35) +
+psn_with_inset = ggdraw(deletion_plot_psn+    theme(legend.position=''))+
+  draw_plot(auc_plot_psn+theme(legend.position=''), .50, .62, .45, .35) +
   draw_plot_label(
@@
   )
-plot_grid(pcc_with_inset, yuri_with_inset, huri_with_inset, ncol=3)%>%plot_grid(deletion_lgn,nrow=2, rel_heights=c(0.9,.1))
+plot_grid(pcc_with_inset, nsdp_with_inset, psn_with_inset, ncol=3)%>%plot_grid(deletion_lgn,nrow=2, rel_heights=c(0.9,.1))
 ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)
@@
 
+sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/sensor_connectivity_df.csv')%>%
+    mutate(data= fct_relevel(data, c('pcc','gi','nsdp','psn')))
 #p3 = 
@@
 plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
-ggsave('reports/figures/paper_figures_0916/fig5.png')
+ggsave('reports/figures/paper_figures_1204_withgi/fig5.png')
 
-#combined_df%>%filter(group=='real'&data=='huri')%>%mutate(is_sensor = ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE))%>%
+#combined_df%>%filter(group=='real'&data=='psn')%>%mutate(is_sensor = ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE))%>%
 #    coin::independence_test(neighbor_degree~is_sensor, data=.)

### 2020-12-21 notebooks/paper_plots_1213_pcc_only.Rmd
notebooks with all analyses i have until Dec 21st 2020

--- 2020-11-30 notebooks/paper_plots_0909.Rmd
@@
     e_pcc = pickle.load(f)
-with open(f'data/interim/yuri_0916/yuri.pickle','rb') as f:
-    e_yuri = pickle.load(f)
-with open(f'data/interim/huri_0916/huri.pickle','rb') as f:
-    e_huri = pickle.load(f)
-
 pcc_df = e_pcc.df
@@
 pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))
-yuri_df = e_yuri.df
-huri_df = e_huri.df
 ```
@@
 pcc_df_random  = data.table::rbindlist(lapply(py$e_pcc$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
-yuri_df_random  = data.table::rbindlist(lapply(py$e_yuri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
-huri_df_random  = data.table::rbindlist(lapply(py$e_huri$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
 pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
@@
 )%>%mutate(group=fct_relevel(group, c('real','random')))
-yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
-    yuri_df_random%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(py$yuri_df),eff_norm = eff/nrow(py$yuri_df), group = 'random')
-)%>%mutate(group=fct_relevel(group, c('real','random')))
-huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
-    huri_df_random%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(py$huri_df),eff_norm = eff/nrow(py$huri_df), group = 'random')
-)%>%mutate(group=fct_relevel(group, c('real','random')))
-combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
-    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
+combined_df =pcc_df
 ```
@@
 ```{r}
-combined_df%>%filter(group=='real')%>%
-    ggplot(aes(x=deg, y = ..count../sum(..count..)))+
-    facet_grid(rows=vars(data))+
-    geom_histogram(binwidth=1)+
-#    xlim(1,NA)+
-    ylim(NA, 0.1)
 
@@
 pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-yuri_degree_dens <- 
-    plot_density_prs(yuri_df, deg, xlab='Degree')
-yuri_eff_dens <- 
-    plot_density_prs(yuri_df, eff_norm, xlab='Effectiveness')
-yuri_sensitivity_dens <- 
-    plot_density_prs(yuri_df, sens_norm, xlab='Sensitivity')
-title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
-yuri_dens_comb = cowplot::plot_grid(yuri_degree_dens+theme(legend.position='none'), 
-                                yuri_eff_dens+theme(legend.position='none'), 
-                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
-yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-huri_degree_dens <- 
-    plot_density_prs(huri_df, deg, xlab='Degree')
-huri_eff_dens <- 
-    plot_density_prs(huri_df, eff_norm, xlab='Effectiveness')
-huri_sensitivity_dens <- 
-    plot_density_prs(huri_df, sens_norm, xlab='Sensitivity')
-title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
-huri_dens_comb = cowplot::plot_grid(huri_degree_dens+theme(legend.position='none'), 
-                                huri_eff_dens+theme(legend.position='none'), 
-                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
-huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
 dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
-dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
-                                yuri_dens_comb_title,
-                                huri_dens_comb_title,nrow=3)
+dens_plots = cowplot::plot_grid(pcc_dens_comb_title,nrow=1)
 cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
-ggsave('reports/figures/paper_figures_0916/fig1.png')
-
-#degree_dens <- 
-#    ggplot(combined_df%>%filter(group=='real'), aes(x=deg))+
-#    ggplot(combined_df%>%filter(group=='random'), aes(x=deg, y=..scaled.., fill=.id))+
-#    facet_grid(rows=vars(data))+
-#    #geom_density()+
-#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
-#    theme_bw()+
-#    xlab('Degree')+
-#    coord_trans(x = "log10", y = "log1p")+
-#scale_x_continuous(
-#   breaks = scales::trans_breaks("log10", function(x) 10^x),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log10", function(x) 10^(x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-#theme(panel.grid.minor = element_blank())
-#eff_dens <- 
-#    combined_df%>%filter(group=='real')%>%
-#    ggplot(aes(x=eff_norm ))+
-#    facet_grid(rows=vars(data), scales='free_y')+
-##    geom_density()+
-#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
-#    #geom_histogram(binwidth=0.0001)+
-#    theme_bw()+
-#    xlab('Effectivity')+
-#    coord_trans(x = "log10", y = "log1p")+
-#scale_x_continuous(
-#   breaks = scales::trans_breaks("log10", function(x) 10^x),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-#theme(panel.grid.minor = element_blank())
-#sensitivity_dens <- 
-#    combined_df%>%filter(group=='real')%>%
-#    ggplot(aes(x=sens_norm))+
-#    facet_grid(rows=vars(data))+
-#    geom_point(stat = 'density')+#, binwidth = 0.1) + 
-#   # geom_density()+
-#    theme_bw()+
-#    xlab('Sensitivity')+
-#    coord_trans(x = "log10", y = "log1p")+
-#   # annotation_logticks()+
-#scale_x_continuous(
-#   breaks = scales::trans_breaks("log10", function(x) 10^x),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-# scale_y_continuous(
-#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
-#   labels = scales::trans_format("log10", scales::math_format(10^.x))
-# ) +
-#theme(panel.grid.minor = element_blank())
-#cowplot::plot_grid(degree_dens, eff_dens, sensitivity_dens, ncol=3,labels=c('A','B','C'))
-#ggsave('tmp.png')
-
-#    coord_trans(x = "log10", y = "log1p")
-#    scale_x_continuous(trans = "log10")
-    #scale_x_log10()
-#    geom_histogram(binwidth=1)+
-#    xlim(1,NA)+
-#    ylim(NA, 0.1)
-ggsave('tmp.png')
+ggsave('reports/figures/paper_figures_1213_pcc_only/fig1.png', width=4,height=4)
 
@@
     scale_y_continuous(labels = scales::label_scientific(digits=1))
-yuri_deg_eff = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
-    ggplot(aes(x=deg, y=eff_norm))+
-    geom_point()+
-#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
-    theme_bw()+
-    ylab("Effectiveness")+
-    xlab("Degree")+
-    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
-    theme(strip.text.y = element_text(angle = 0))+
-    scale_y_continuous(labels = scales::label_scientific(digits=1))
-yuri_deg_sens = yuri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
-    ggplot(aes(x=deg, y=sens_norm))+
-    geom_point()+
-#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
-    theme_bw()+
-    ylab("Sensitivity")+
-    xlab("Degree")+
-    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
-    theme(strip.text.y = element_text(angle = 0))+
-    scale_y_continuous(labels = scales::label_scientific(digits=1))
-huri_deg_eff = huri_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
-    ggplot(aes(x=deg, y=eff_norm))+
-    geom_point()+
-#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
-    theme_bw()+
-    ylab("Effectiveness")+
-    xlab("Degree")+
-    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
-    theme(strip.text.y = element_text(angle = 0))+
-    scale_y_continuous(labels = scales::label_scientific(digits=1))
-huri_deg_sens = huri_df %>%filter(group=='real')%>% #pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
-    ggplot(aes(x=deg, y=sens_norm))+
-    geom_point()+
-#    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) )+
-    theme_bw()+
-    ylab("Sensitivity")+
-    xlab("Degree")+
-    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
-    theme(strip.text.y = element_text(angle = 0))+
-    scale_y_continuous(labels = scales::label_scientific(digits=1))
 deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
-                   yuri_deg_eff, yuri_deg_sens,
-                   huri_deg_eff, huri_deg_sens, labels = c('A','','B','','C',''),
+                    labels = c('D','E'),
                    ncol=2)
-ggsave('tmp.png',plot=deg_scatter_plots, width=10,height=10)
-
-#p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
-#    geom_point(aes(color=cat_))+
-#    xlab('Degree')+
-#    ylab('Effectiveness')+
-#    stat_cor(method='pearson')   +
-#    guides(color=guide_legend(title="Experiment categories"))+
-#    theme_bw()
-#p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
-#    geom_point(aes(color=cat_))+
-#    xlab('Degree')+
-#    ylab('Sensitivity')+
-#    stat_cor(method='spearman')   +
-#    guides(color=guide_legend(title="Experiment categories"))+
-#    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
-#lgn = cowplot::get_legend(p2)
-#fig3 = plot_grid(p1+theme(legend.position=''),
-#          p2+theme(legend.position=''),
-#          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
-#ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
+ggsave('reports/figures/paper_figures_1213_pcc_only/fig2.png',plot=deg_scatter_plots, width=10,height=10)
 ```
@@
 pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
-yuri_rewire_df = read_csv('data/interim/yuri/rewire_data.csv')
-huri_rewire_df = read_csv('data/interim/huri/rewire_data.csv')
-
-rewire_df = pcc_rewire_df%>%mutate(data='pcc')%>%bind_rows(
-                                                           yuri_rewire_df%>%mutate(data='yuri'))%>%
-        bind_rows(huri_rewire_df%>%mutate(data='huri'))
-```
-
-```{r}
-network_labels  <- c('Costanzo 2016','Yeast PPI','HuRI')
-#p3 = ggplot(rewire_df, aes(x=eff_deg_pearson))+
-#    stat_density(geom = "line", trim=TRUE)+
-##    geom_histogram(binwidth = 0.001)+
-#    geom_vline(xintercept=0.9,color='red')+
-#    theme_bw()
-
+rewire_df = pcc_rewire_df%>%mutate(data='pcc')
+network_labels  <- c('Yeast GI Profile Similarity')
 facet_labels  <- network_labels
-names(facet_labels) <- c("pcc",'yuri','huri')
-
+names(facet_labels) <- c("pcc")
 combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
     bind_rows(
-    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$sens,method='spearman'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$sens,method='spearman')), eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson'),cor(yuri_df[yuri_df$group=='real',]$deg,yuri_df[yuri_df$group=='real',]$eff,method='pearson'),cor(huri_df[huri_df$group=='real',]$deg,huri_df[huri_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc','yuri','huri')))%>%
-    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
+    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman')), 
+               eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc')))%>%
+    mutate(data= fct_relevel(data, c('pcc')))
 
@@
     ggplot()+
-    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
+#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
 #    geom_boxplot()+
@@
           p3+theme(legend.position=''),
- p4+theme(legend.position=''), lgn34,
- nrow=3, labels=c('D','E','','F','G',''), rel_heights = c(0.45,0.45,0.1))
+ p4+theme(legend.position=''),labels=c('F','G'),nrow=1 )
+distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
+ nrow=2,rel_heights = c(0.9,0.1))
 #ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
-
-plot_grid(deg_scatter_plots, distr_plots, nrow=2,rel_heights = c(0.6,0.4))
-ggsave('reports/figures/paper_figures_0916/fig2.png',width=8,height=9)
+plot_grid(dens_plots, deg_scatter_plots, distr_plots_withlgn, nrow=3,rel_heights = c(0.4,0.3,.3))
+ggsave('reports/figures/paper_figures_1213_pcc_only/fig3.png',width=10,height=12)
 ```
@@
 ```{r}
-sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
-    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
-
-#library(ggridges)
-
-#sensor_connectivity_df %>%
-#    filter(type=='random')%>%
-#    ggplot(aes(x=ratio,y=data))+
-##    facet_grid(rows=vars(data))+
-##    geom_histogram(bins=50)
-#    geom_density_ridges()
-#ggsave('tmp.png',width=12)
-
-#p3 = 
+sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/sensor_connectivity_df.csv')%>%
+    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))%>%filter(data=='pcc')
+#effector_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/effector_connectivity_df.csv')%>%
+#    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))%>%filter(data=='pcc')
+#effector_connectivity_plot <- 
+#    ggplot()+
+##    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
+##    geom_boxplot()+
+##    geom_jitter()+
+#    geom_density(data =effector_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
+#    geom_vline(data =effector_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
+#    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
+#    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
+#    theme_bw()+
+#    scale_color_discrete(labels=c('Random sampled set', 'Effectors'))+
+#    theme(legend.position='bottom')+
+#    scale_y_continuous(expand = c(0, 0)) 
+eff_neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
+    mutate(is_effector = factor(ifelse(eff_norm>quantile(eff_norm,0.99),TRUE,FALSE), levels=c(TRUE,FALSE)))%>%
+#    mutate(is_effector = fct_relevel(is_effector,c(TRUE,FALSE)))%>%
+    ggplot(aes(x=is_effector,y=log(neighbor_degree)))+
+#    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
+#    geom_point()+
+    geom_boxplot()+
+    theme_bw()+
+    ylab('Log(Average neighbor degree)')+
+    xlab('')+ stat_compare_means()+
+    scale_x_discrete(labels=c('Effector', 'Not Effector'))
 sensor_connectivity_plot <- 
     ggplot()+
-    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
+#    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
 #    geom_boxplot()+
@@
     guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
+    ylab('Density')+xlab('Ratio of between group edges\nto outgroup edges')+
     theme_bw()+
@@
     scale_y_continuous(expand = c(0, 0)) 
-
-#p3 = 
-    ggplot()+
-    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
-                 aes(x=data,y=ratio,color=type))+
-#    geom_jitter()+
-    geom_vline(data=sensor_connectivity_df%>%filter(type=='real'),
-            aes(x=data,y=ratio,color=type, group=data))+
-               #position=position_jitter(), aes(shape=data))+
-    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
-    scale_x_discrete(labels=network_labels)+
-  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
-    theme_bw()
-
 neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
@@
     ggplot(aes(x=is_sensor,y=log(neighbor_degree)))+
-    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
+#    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
 #    geom_point()+
@@
     xlab('')+ stat_compare_means()+
-    scale_x_discrete(labels=c('aensor', 'Not Sensor'))
-plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
-ggsave('reports/figures/paper_figures_0916/fig5.png')
+    scale_x_discrete(labels=c('Sensor', 'Not Sensor'))
+sensor_conn_lgn = get_legend(sensor_connectivity_plot+theme(legend.position='right'))
+plot_grid(neighbor_degree_plot,
+          sensor_connectivity_plot+theme(legend.position='none'), #effector_connectivity_plot,
+    eff_neighbor_degree_plot, sensor_conn_lgn,
+          nrow=2 , 
+          labels=c('A','B','C',''))#%>%
+#    plot_grid(, labels=c('','C'),nrow=2, rel_widths=c(2,1))
+ggsave('reports/figures/paper_figures_1213_pcc_only/fig5.pdf',width=6,height=6)
 

### 2020-12-21 notebooks/poster_plots_1023.Rmd
notebooks with all analyses i have until Dec 21st 2020

@@
 colnames(random_dfs_100)[length(colnames(random_dfs_100))] <- 'filename'
+random_dfs_100<- random_dfs_100%>%mutate(eff_norm = eff/nrow(pcc_df), sens_norm=sens/nrow(pcc_df))
 ```
@@
     geom_line(data=     combined_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data=     combined_df%>%filter(group=='random'),aes(x=deg,y=..scaled..,color=group),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
+    geom_line(data=     random_dfs_100%>%dplyr::mutate(group='random'),aes(x=deg,y=..scaled..,fill=filename),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
     theme_bw()+
@@
                stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data= combined_df%>%filter(group=='random'),
-               aes(x=eff_norm ,y=..scaled..,color=group),
+    geom_line(data= random_dfs_100%>%mutate(group='random'),
+               aes(x=eff_norm ,y=..scaled..,fill=filename),
                stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
@@
                stat = 'density')+#, binwidth = 0.1) + 
-    geom_line(data= combined_df%>%filter(group=='random'),
-               aes(x=sens_norm ,y=..scaled..,color=group),
+    geom_line(data= random_dfs_100%>%dplyr::mutate(group='random'),
+               aes(x=sens_norm,y=..scaled..,fill=filename),
                stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
@@
 cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
-#ggsave('tmp.png')
+ggsave('tmp.png')
 #ggsave('reports/figures/poster_figures_1023/fig3.png')

### 2020-12-21 notebooks/03-PRS_costanzo_07132020.py

@@ -1,0 +1,355 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:percent
+#     text_representation:
+#       extension: .py
+#       format_name: percent
+#       format_version: '1.3'
+#       jupytext_version: 1.5.2
+#   kernelspec:
+#     display_name: Python (enm)
+#     language: python
+#     name: enm
+# ---
+
+# %% [markdown] toc=true
+# <h1>Table of Contents<span class="tocSkip"></span></h1>
+# <div class="toc"><ul class="toc-item"><li><span><a href="#Compare-neighbor-betweenness" data-toc-modified-id="Compare-neighbor-betweenness-1"><span class="toc-item-num">1&nbsp;&nbsp;</span>Compare neighbor betweenness</a></span></li><li><span><a href="#Check-high-effectivenes-nodes-for-a-given-degree-to-understand-the-topology" data-toc-modified-id="Check-high-effectivenes-nodes-for-a-given-degree-to-understand-the-topology-2"><span class="toc-item-num">2&nbsp;&nbsp;</span>Check high effectivenes nodes for a given degree to understand the topology</a></span><ul class="toc-item"><li><ul class="toc-item"><li><ul class="toc-item"><li><span><a href="#Sensor:-sps18-and-neighbors" data-toc-modified-id="Sensor:-sps18-and-neighbors-2.0.0.1"><span class="toc-item-num">2.0.0.1&nbsp;&nbsp;</span>Sensor: sps18 and neighbors</a></span></li><li><span><a href="#Sensor:-sps18-and-neighbors" data-toc-modified-id="Sensor:-sps18-and-neighbors-2.0.0.2"><span class="toc-item-num">2.0.0.2&nbsp;&nbsp;</span>Sensor: sps18 and neighbors</a></span></li></ul></li></ul></li></ul></li><li><span><a href="#Work-on-random-generated-graph" data-toc-modified-id="Work-on-random-generated-graph-3"><span class="toc-item-num">3&nbsp;&nbsp;</span>Work on random generat
[…]

### 2020-12-21 src/R/plot_density_prs.R

@@ -1,0 +1,36 @@
+
+plot_density_prs <- 			# 
+    function
+(
+ 	df , x , xlab= 'Effectiveness', ylab='Density', coord_trans='log10', linesize = 1
+)
+{
+dens_plot <- 
+    ggplot()+
+    #facet_grid(rows=vars(data))+
+#    geom_density()+
+    geom_line(data= df%>%filter(group=='real'),
+               aes(x={{x}} ,y=..scaled.., color=group),
+               stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data= df%>%filter(group=='random'),
+               aes(x={{x}} ,y=..scaled..,fill=random_id, color=group),
+               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
+#    geom_errorbar(data= df%>%filter(group=='real'), stat = "vline", xintercept = "mean",
+#  width=0.8,aes(x = eff_norm , xmax=..x..,xmin=..x..))+
+    geom_vline(data= df%>%filter(group=='real'),aes(xintercept = mean({{x}}), color=group),size=linesize, linetype='dotted')+
+    geom_vline(data= df%>%filter(group=='random'),aes(xintercept = mean({{x}}), color=group, group=random_id), size=linesize, linetype='dotted')+
+    #geom_histogram(binwidth=0.0001)+
+    theme_bw()+
+    ylab(ylab)+
+    xlab(xlab)+
+    coord_trans(x = coord_trans)+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) +
+    scale_color_discrete(labels=c('Rewired networks','Real network'))+
+theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())#+theme_fontsize+
+dens_plot
+}
+#tmp  <- plot_density_prs(pcc_df, eff_norm)
+#ggsave('tmp.png', plot=tmp)

### 2021-02-02 notebooks/paper_plots_0909.Rmd
added inset legends and corrected segregation

@@
     else:
-        lbl = 'Chromosome segragation'
+        lbl = 'Chromosome segregation'
     legend_elements.append(

### 2021-02-02 notebooks/paper_plots_1213_pcc_only.Rmd
added inset legends and corrected segregation

@@
 
-pcc_degree_dens <- 
-    plot_density_prs(pcc_df, deg, xlab='Degree')
 pcc_eff_dens <- 
     plot_density_prs(pcc_df, eff_norm, xlab='Effectiveness')
+dens_lgn = cowplot::get_legend(pcc_eff_dens+theme(legend.position='right'))
+pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab='Degree')+theme(legend.position='none'))+
+        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
+pcc_eff_dens <- 
+    cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab='Effectiveness')+theme(legend.position='none')+
+    coord_trans(x = "log10", xlim=c(NA,10e-2))+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) )+
+        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
 #annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
 pcc_sensitivity_dens <- 
-    plot_density_prs(pcc_df, sens_norm, xlab='Sensitivity')
+    cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab='Sensitivity')+theme(legend.position='none'))+
+        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
 title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
-pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
-                                pcc_eff_dens+theme(legend.position='none'), 
-                                pcc_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
+pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens,#+theme(legend.position='none'), 
+                                pcc_eff_dens,#+theme(legend.position='none'), 
+                                pcc_sensitivity_dens,#+theme(legend.position='none'),
+                                labels=c('A','B','C'),ncol=3)
 pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
+#dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
 dens_plots = cowplot::plot_grid(pcc_dens_comb_title,nrow=1)
-cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
-ggsave('reports/figures/paper_figures_1213_pcc_only/fig1.png', width=4,height=4)
+#cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
+ggsave('reports/figures/paper_figures_0202_pcc_only/fig1.png', plot=dens_plots,width=4,height=4)
 
@@
                    ncol=2)
-ggsave('reports/figures/paper_figures_1213_pcc_only/fig2.png',plot=deg_scatter_plots, width=10,height=10)
+ggsave('reports/figures/paper_figures_0202_pcc_only/fig2.png',plot=deg_scatter_plots, width=10,height=10)
 ```
@@
 distr_plots <- plot_grid(
-          p3+theme(legend.position=''),
- p4+theme(legend.position=''),labels=c('F','G'),nrow=1 )
-distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
- nrow=2,rel_heights = c(0.9,0.1))
+          ggdraw(p3+theme(legend.position=''))+
+        cowplot::draw_plot(dens_lgn, .45,.45,.5,.5),
+ggdraw( p4+theme(legend.position=''))+
+        cowplot::draw_plot(dens_lgn, .45,.45,.5,.5),labels=c('F','G'),nrow=1 )
+#distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
+# nrow=2,rel_heights = c(0.9,0.1))
 #ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
-plot_grid(dens_plots, deg_scatter_plots, distr_plots_withlgn, nrow=3,rel_heights = c(0.4,0.3,.3))
-ggsave('reports/figures/paper_figures_1213_pcc_only/fig3.png',width=10,height=12)
+plot_grid(dens_plots, deg_scatter_plots, distr_plots, nrow=3,rel_heights = c(0.4,0.3,.3))
+ggsave('reports/figures/paper_figures_0202_pcc_only/fig3.png',width=10,height=12)
 ```
@@
 #    plot_grid(, labels=c('','C'),nrow=2, rel_widths=c(2,1))
-ggsave('reports/figures/paper_figures_1213_pcc_only/fig5.pdf',width=6,height=6)
+ggsave('reports/figures/paper_figures_0202_pcc_only/fig5.pdf',width=6,height=6)
 

### 2021-02-02 src/R/plot_density_prs.R

@@ -28,7 +28,7 @@ scale_x_continuous(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
-    scale_color_discrete(labels=c('Rewired networks','Real network'))+
+    scale_color_discrete(labels=c('Rewired\nnetworks','Real\nnetwork'))+
 theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())#+theme_fontsize+
 dens_plot
 }

### 2021-02-03 notebooks/paper_plots_1213_pcc_only.Rmd
changed labels and added margin

@@
 ```{r}
-real_random_labels = c('Real\nnetwork','Rewired\nnetwork')
+real_random_labels = c('Genetic\nnetwork','Random\nnetwork')
 names(real_random_labels)  = c('real','random')
@@
     theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
-    scale_color_discrete(labels=c('Rewired networks', 'Real network'))+
+    scale_color_discrete(labels=c('Random networks', 'Genetic network'))+
     scale_y_continuous(expand = c(0, 0)) 

### 2021-02-03 src/R/plot_density_prs.R

@@ -28,8 +28,8 @@ scale_x_continuous(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
-    scale_color_discrete(labels=c('Rewired\nnetworks','Real\nnetwork'))+
-theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())#+theme_fontsize+
+    scale_color_discrete(labels=c('Random\nnetworks','Genetic\nnetwork'))+
+theme(legend.text = element_text(margin = margin(b = 10)), panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())#+theme_fontsize+
 dens_plot
 }
 #tmp  <- plot_density_prs(pcc_df, eff_norm)

### 2021-02-18 notebooks/17-PRS_dendrogram_cluster_investigation-020921.Rmd
clustering and go analysis functions were written

---
title: "PRS dendrogram clusters"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
source('src/R/get.subclusters.dendrogram.R')
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
#source('src/R/plot_density_prs.R')
library(RColorBrewer)
col = brewer.pal(n=9,name='Set1')
sensor_colors = col[1:6]
effector_colors = col[7:9]
```

# Read data
Read data in python, from pickle file saved earlier.
```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm
from src.utils import *
import scipy.cluster.hierarchy as sch

with open(f'data/interim/pcc_021521_withclustering//pcc_10.pickle','rb') as f:
    e_pcc = pickle.load(f)
pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))

sensors_pcc = e_pcc.sensors_df#e_pcc.df.loc[e_pcc.df.sens>np.quantile(e_pcc.df.sens,0.99)]
effector_pcc = e_pcc.effectors_df
sensor_sub_pcc = get_subnetwork(e_pcc.graph_gc, sensors_pcc.orf_name.values)
effector_sub_pcc = get_subnetwork(e_pcc.graph_gc, effector_pcc.orf_name.values)
effector_order = effector_pcc.groupby('go_group').eff.median().sort_values().index.tolist()
sensor_order = sensors_pcc.groupby('go_group').sens.median().sort_values().index.tolist()
effector_colors_dict = dict(zip(effector_order,r.effector_colors))
sensor_colors_dict = dict(zip(sensor_order,r.sensor_colors))
#sensor_colors_dict['none']=sensor_colors_dict[None]
#del sensor_colors_dict[None]
```

Use scipy distance calculation and pass the square form of the distance matrix to R.
This is done because R's `dist` function is significantly slower than scipy.

```{python}
prs_mat = e_pcc.prs_mat
quantile_threshold =  0.95
method = 'ward'
metric = 'seuclidean'
q99 = np.quantile(prs_mat, quantile_threshold)
prs_mat_cl = copy.deepcopy(prs_mat)
prs_mat_cl[prs_mat_cl > q99] = q99
prs_mat_cl_orig = prs_mat_cl
# , optimal_ordering=True)
#row_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl), method=method)
# ,optimal_ordering=True)
#col_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl.T), method=method)

row_dist_orig = sch.distance.pdist((prs_mat),metric = metric)
col_dist_orig = sch.distance.pdist((prs_mat.T),metric = metric)
row_dist_orig_sqr = sch.distance.squareform(row_dist_orig)
col_dist_orig_sqr = sch.distance.squareform(col_dist_orig)

row_dist = sch.distance.pdist(prs_mat_cl,metric = metric)
col_dist = sch.distance.pdist(prs_mat_cl.T,metric = metric)

row_dist_sqr = sch.distance.squareform(row_dist)
col_dist_sqr = sch.distance.squareform(col_dist)

```
# Plot heatmap
Using the clustering with `euclidian` distance and `ward` linkage, plot the heatmap with row and column colors are the GO term annotations found from effector and sensor analysis

```{r}
library(tidyverse)
library(ComplexHeatmap)
cluster_method = 'ward.D2'
dist_row = as.dist(py$row_dist_sqr)
hclust_row = hclust(dist_row, cluster_method)
dist_col = as.dist(py$col_dist_sqr)
hclust_col = hclust(dist_col, cluster_method)

go_color_map = unlist(append(py$effector_colors_dict,py$sensor_colors_dict))
go_color_map['none'] = 'white'
clrs = map(py$eff_sens_go_list, ~ifelse(is.null(.x), 'none',.x))%>%unlist()

rowColors = rowAnnotation(rowColors=clrs,
                          col=list(rowColors = go_color_map ),
                          #width=unit(100,'mm'),
                          simple_anno_size=unit(3,'cm'),
                          show_annotation_name=FALSE,
                          show_legend=FALSE)
colColors = columnAnnotation(colColors=clrs,
                          col=list(colColors = go_color_map ),
                          simple_anno_size=unit(3,'cm'),
                          #annotation_height=unit(20,'mm'),
                          show_annotation_name=FALSE,
                          show_legend=FALSE)
rowAnnot = HeatmapAnnotation(Effectiveness=anno_lines(rowSums(py$prs_mat)),
                            which='row',
                            name='Effectiveness', 
                            gp = gpar(col='blue'),
                            annotation_name_side = 'top',
                            annotation_name_rot= 0,
                            border=FALSE,
                          show_legend=FALSE
)
colAnnot = HeatmapAnnotation(Sensitivity=anno_lines(colSums(py$prs_mat)), 
                             which='col', 
                             name='Sensitivity',
                            gp = gpar(col='blue'),
                            annotation_name_side = 'left',
                            annotation_name_rot=0,
                            border=FALSE,
                          show_legend=FALSE
)
pdf('tmp_heatmap.pdf')
Heatmap(py$prs_mat_cl, 
        cluster_rows = as.dendrogram(hclust_row),
        cluster_columns=as.dendrogram(hclust_col),
        col=RColorBrewer::brewer.pal(9,'YlGnBu'),
        row_dend_width = unit(20,'mm'),
        column_dend_height = unit(20,'mm'),
        right_annotation=rowAnnot,
        left_annotation = rowColors,
        bottom_annotation=colAnnot,
        top_annotation=colColors,
        show_heatmap_legend=TRUE
)
dev.off()

```

Use dendrogram clusters to assign effectors and sensors to subclusters.
Use goatools to find enriched GO terms within each subcluster

```{r}
effector_pcc = py$effector_pcc
sensors_pcc = py$sensors_pcc

dend_row  <- as.dendrogram(hclust_row)
dend_col  <- as.dendrogram(hclust_col)
effector_pcc <- get.subclusters.dendrogram(dend_row, effector_pcc)
sensors_pcc <- get.subclusters.dendrogram(dend_col, sensors_pcc)

# Import goatools functions from src/utils.py
utils <- import('src.utils')
create_goa = utils$create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/costanzo_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')
goea = create_goa[[1]]
geneid2name = create_goa[[2]]
#utils$query_goatools(sensors_pcc,goea,geneid2name)
eff_go_terms <- list()
sens_go_terms <- list()
for(i in 1:4){
    print(i)
    subcluster <- effector_pcc%>%filter(clusters==i)
    query <- utils$query_goatools(subcluster,goea,geneid2name)
    eff_go_terms[i] = query[1,4]
}
effector_pcc <- unlist(eff_go_terms)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%rename(cluster_go_term='.')%>%right_join(effector_pcc,by=c('rowname'='clusters'))
for(i in 1:4){
    print(i)
    subcluster <- sensors_pcc%>%filter(clusters==i)
    query <- utils$query_goatools(subcluster,goea,geneid2name)
    sens_go_terms[i] = query[1,4]
}
sensors_pcc <- unlist(sens_go_terms)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%rename(cluster_go_term='.')%>%right_join(sensors_pcc,by=c('rowname'='clusters'))

#py$e_pcc$df%>%left_join(effector_pcc)%>%ggplot(aes(x=deg,y=eff,color=cluster_go_term))+geom_point()+
#    xlim(0,NA)+ylim(0,NA)+theme(legend.position='none')
#ggsave('tmp.png')
#py$e_pcc$df%>%left_join(sensors_pcc)%>%ggplot(aes(x=deg,y=sens,color=cluster_go_term))+geom_point()+
#    xlim(0,NA)+ylim(0,NA)+theme(legend.position='none')
#ggsave('tmp.png')

```

Save Enm object with dendrogram `cluster_go_term` assignments

```{python}
e_pcc.sensors_df = r.sensors_pcc
e_pcc.effectors_df = r.effector_pcc

with open(f"{e_pcc.output_path}/pcc_10_r.pickle",'wb') as f:
    pickle.dump(e_pcc,f, protocol=4)

```

Save subcluster dendrogram plots

```{r}
library(dendextend)
png('reports/figures/dendrogram021721/row_dendrogram_colored.png',width=800,height=800)
dend_row[[2]] %>% 
    set("branches_k_color", k = 4) %>% 
    set("labels", NA) %>%    # change labelsk
    plot(xlab="", sub="")
dev.off()
png('reports/figures/dendrogram021721/col_dendrogram_colored.png',width=800,height=800)
dend_col[[1]] %>% 
    set("branches_k_color", k = 4) %>% 
    set("labels", NA) %>%    # change labelsk
    plot(xlab="", sub="")
dev.off()
```

# Seriation analysis

```{r}
library(seriation)
library(tictoc)

tic()
row_order_seriation <- seriate(dist_row, method = 'OLO_ward')
col_order_seriation <- seriate(dist_col, method = 'OLO_ward')
toc()

pdf('tmp_heatmap.pdf')
Heatmap(py$prs_mat_cl_orig, 
        row_order= get_order(row_order_seriation),
        column_order = get_order(col_order_seriation),
        col=RColorBrewer::brewer.pal(9,'YlGnBu'),
#        row_dend_width = unit(20,'mm'),
#        column_dend_height = unit(20,'mm'),
        right_annotation=rowAnnot,
        left_annotation = rowColors,
        bottom_annotation=colAnnot,
        top_annotation=colColors,
        show_heatmap_legend=TRUE
)
dev.off()

tic()
prs_order = seriate(py$prs_mat_cl_orig, method='BEA_TSP')
toc()

pdf('tmp_heatmap.pdf')
Heatmap(py$prs_mat_cl_orig, 
        row_order= get_order(prs_order,1),
        column_order = get_order(prs_order,2),
        col=RColorBrewer::brewer.pal(9,'YlGnBu'),
#        row_dend_width = unit(20,'mm'),
#        column_dend_height = unit(20,'mm'),
        right_annotation=rowAnnot,
        left_annotation = rowColors,
        bottom_annotation=colAnnot,
        top_annotation=colColors,
        show_heatmap_legend=TRUE
)
dev.off()

hclust_col_reordered <- reorder(hclust_col,dist_col)
hclust_row_reordered <- reorder(hclust_row,dist_row)

pdf('tmp_heatmap.pdf',width=6,height=6)
Heatmap((py$prs_mat_cl),
        cluster_rows = as.dendrogram(hclust_row_reordered),
        cluster_columns=as.dendrogram(hclust_col_reordered),
        col=RColorBrewer::brewer.pal(9,'YlGnBu'),
        show_row_dend=FALSE,
        show_column_dend=FALSE,
        row_dend_width = unit(1,'in'),
        column_dend_height = unit(1,'in'),
        right_annotation=rowAnnot,
        left_annotation = rowColors,
        bottom_annotation=colAnnot,
        top_annotation=colColors,
        show_heatmap_legend=TRUE
)
dev.off()
```

### 2021-02-18 src/R/get.subclusters.dendrogram.R

@@ -1,0 +1,24 @@
+#' given a dendrogram, take the smallest child and cut it into 4 subclusters.
+#' Assign the resulting cluster numbers to genes, using given dataframe
+#' 
+#' @param hcl hclust object, to calculate dendrogram
+#' @param df the dataframe to map clusters back to genes. rownames of the dataframe needs to include the dendrogram labels
+#' @param k number of clusters for dendrogram cut, optional. default = 4 
+#' @return The dataframe joined with cluster assignments for some or all genes, depending on the input df 
+get.subclusters.dendrogram <- 			# 
+    function
+(
+ hcl,df, k=4	
+)
+{
+    library(dendextend)
+    dend  <- as.dendrogram(hcl)
+    if(nleaves(dend[[1]])<nleaves(dend[[2]])){
+      sub_dend <- dend[[1]]
+    }else{
+      sub_dend <- dend[[2]]
+    }
+    sub_clusters <- sub_dend %>% cutree(k=k)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname)-1)%>%select(clusters='.', rowname)
+    df_with_clusters <- df%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%left_join(sub_clusters)
+    df_with_clusters
+}

### 2021-02-18 src/R/plot_density_prs.R

@@ -14,7 +14,7 @@ dens_plot <-
                aes(x={{x}} ,y=..scaled.., color=group),
                stat = 'density')+#, binwidth = 0.1) + 
     geom_line(data= df%>%filter(group=='random'),
-               aes(x={{x}} ,y=..scaled..,fill=random_id, color=group),
+               aes(x={{x}} ,y=..scaled..,fill=random_id, color=group),linetype='dashed',
                stat = 'density' ,show.legend=F)+#, binwidth = 0.1) + 
 #    geom_errorbar(data= df%>%filter(group=='real'), stat = "vline", xintercept = "mean",
 #  width=0.8,aes(x = eff_norm , xmax=..x..,xmin=..x..))+
@@ -32,7 +32,7 @@ scale_x_continuous(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
-    scale_color_discrete(labels=c('Random\nnetworks','Genetic\nnetwork'))+
+    scale_color_discrete(labels=c('Rewired\nnetworks','PSN'))+
 theme(legend.text = element_text(margin = margin(b = 10)), panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())#+theme_fontsize+
 dens_plot
 }

### 2021-02-18 src/data/pcc.py

@@ -1,5 +1,4 @@
-import src
-import matplotlib.pyplot as plt
+#import src
 import pandas as pd
 import numpy as np
 import networkx as nx
@@ -7,7 +6,7 @@ import pickle
 from tqdm import tqdm
 from src.enm import *
 from src.utils import *
-
+import matplotlib.pyplot as plt
 
 
 #figure_path = 'reports/figures/pcc_0603'
@@ -16,15 +15,22 @@ enm.read_network('data/interim/costanzo_pcc_ALL',sep=',')
 enm.gnm_analysis(normalized=False)
 
 #enm.figure_path=figure_path
-enm.output_path = 'data/interim/pcc_1020/'
+enm.output_path = 'data/interim/pcc_021521_withclustering/'
 enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
 enm.spring_pos()
+print('clustering')
+enm.get_sensor_effector(use_threshold=False)
 
-enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=100)
-random_dfs = [enm.e_list[i].df.to_csv(f'data/interim/pcc_1020/random_dfs/rand_{i}.csv') for i in range(100)]
+print('go analysis')
+goea, geneid2name = create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', 
+                                background='data/interim/costanzo_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')
+enm.analyze_components_biology(goea, geneid2name, True)
+enm.analyze_components_biology(goea, geneid2name, False)
+print('rewiring')
+enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=10)
+random_dfs = [enm.e_list[i].df.to_csv(f'{enm.output_path}/random_dfs/rand_{i}.csv') for i in range(10)]
 #enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=10)
 #enm.simulate_rewire(output_name='rewire_data_er', save=True, nodegseq=True,random_network_type='er', normalized=False)
-
 neigbor_btw = []
 neighbor_degree = []
 for i in enm.graph_gc.nodes:
@@ -34,7 +40,7 @@ for i in enm.graph_gc.nodes:
[…]

### 2021-02-18 src/enm.py

@@ -5,11 +5,13 @@ import pandas as pd
 import prody
 import numpy as np
 import igraph
+import scipy.cluster.hierarchy as sch
+import copy
 from tqdm import tqdm
 
 from .visualize.visualize import plot_collectivity,plot_correlation_density,plot_network_spring,plot_scatter,plot_vector,heatmap_annotated, plot_fiedler_data
 #from .utilities import *
-from .utils import jaccard_index
+from .utils import jaccard_index, query_goatools
 
 
 class Enm():
@@ -38,7 +40,9 @@ class Enm():
         self.coll_index_sorted = None
         self.prs_mat = None
         self.prs_mat_df  = None
+        self.prs_mat_cl = None
         self.L = None
+        self.go_groups = {}
 
     def print_name(self):
         """This prints name variable
@@ -141,7 +145,7 @@ class Enm():
         """
         df = pd.DataFrame()
         df['orf_name'] = self.nodes
-        df['deg'] = self.degree
+        df['deg'] = np.diag(self.L)
         eff_orig = np.sum(self.prs_mat, axis=1)
         sens_orig = np.sum(self.prs_mat, axis=0)
         eigvecs_df = pd.DataFrame(self.gnm.getEigvecs(
@@ -229,6 +233,88 @@ class Enm():
         #db_connection = sql.create_engine(db_connection_str)
         #db_df = pd.read_sql('SELECT * FROM SUMMARY_2012', con=db_connection)
         #combined_df = pd.merge(combined_df, db_df, left_on='Systematic gene name', right_on='orf_name')
+
+    def get_sensor_effector(self, use_threshold=True, quantile_threshold=0.99):
+        """create sensor and effector sub dataframes using PRS matrix clusters or effectiveness sensitivity thresholds
+
+        :param use_threshold: if true, the nodes with effectiveness/sensitivity above quantile threshold will be taken as effectors and sensors, defaults to True
+        :type use_threshold: bool, optional
+        :param quantile_threshold: any effectiveness/sensitivity value above this quantile will be important, defaults to 0.99
+        :type quantile_threshold: float, optional
+        """
+        if self.df is None:
+            self.gnm_analysis()
+        if use_threshold:
+            sensors_df = self.df.loc[self.df.sens>np.quantile(self.df.sens,quantile_threshold)]
+            effectors_df = self.df.loc[self.df.eff>np.quantile(self.df.eff,quantile_threshold)]
+        else:
+            if self.prs_mat_cl is None:
+                self.cluster_matrix(self.prs_mat)
[…]

### 2021-02-18 src/utils.py

@@ -71,6 +71,16 @@ def create_goea_human(gene2go = '../data/raw/ontology/gene2go', obo_fname = '../
     return goeaobj, geneid2name#, objanno, ns2assoc, ns2assoc_excl
 
 def go_findenrichment( query, outname=None, species='yeast',**kwargs):
+    """Get a query dataframe with set of orfs and return significant go results by first creating goa analysis object and running enrichment analysis
+    use this function instead of `query_goatools` to create goatools object and write results to file directly
+
+    :param query: dataframe for query genes
+    :type query: pandas dataframe
+    :param outname: tsv filename to write results, if None the results will be written to stdio, defaults to None
+    :type outname: str, optional
+    :param species: which species is under question. depreceated, defaults to 'yeast'
+    :type species: str, optional
+    """
     goeaobj, geneid2name = create_goea(**kwargs)
     query_gene_ids = [key for key,value in geneid2name.items() if value in query]#sgd_info[sgd_info.iloc[:,3].isin(query)].iloc[:,0].values.tolist()
 
@@ -97,6 +107,25 @@ def goea_to_pandas(goea_results_sig, geneid2name):
         orf_names.append([geneid2name[_id] for _id in i])
     go_df_n.study_items = orf_names
     return go_df_n 
+
+
+def query_goatools(query, goea,geneid2name):
+    """get query dataframe and goa files and return enrichments
+
+    :param query: query gene dataframe
+    :type query: pandas dataframe
+    :param goea: goa object that will be used to run gene ontology analysis using GOAtools
+    :type goea: goatools.goea.go_enrichment_ns.GOEnrichmentStudyNS
+    :param geneid2name: dictionary to map geneids to gene names. needed to convert systematic names to intended names
+    :type geneid2name: dict
+    :return: enrichment dataframe 
+    :rtype: pandas dataframe
+    """
+    query_gene_ids = [key for key,value in geneid2name.items() if value in query.loc[:,'Systematic gene name'].unique()]
+    goea_res_all = goea.run_study(query_gene_ids)
+    goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.1]
+    go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
+    return go_df_sensor
 
 def network_chance_deletion(list_of_nodes,Gc,out_dict):
     random_hinges = list_of_nodes#df_.sort_values('deg',ascending=False).iloc[0:i,0].tolist()

### 2021-02-18 src/visualize/visualize.py

@@ -1,11 +1,9 @@
-import copy
 import networkx as nx
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.lines import Line2D
 import seaborn as sns
 import scipy.cluster.hierarchy as sch
-from scipy.spatial import distance
 from scipy.stats import pearsonr, spearmanr, gaussian_kde
 figsize = (5, 5)
 #matplotlib.rcParams['pdf.fonttype'] = 42
@@ -267,99 +265,106 @@ def plot_correlation_density(df, rewire_df, x, y, figure_path, **kwargs):
     fig.savefig(f"{figure_path}/{figure_name}.{kwargs.pop('figure_extension','png')}", transparent=False,bbox_extra_artists=(lgd,),bbox_inches='tight')
     return ax
 
-
-def heatmap_annotated(prs_mat, figure_path,show_normalized = True, cluster_normalized = True, row_colors = None, col_colors=None, **kwargs):
-
-    # sch.set_link_color_palette(['b'])
-    
-    # Dendrogram that comes to the left
+def heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path, row_linkage, col_linkage, row_colors = None, col_colors=None, save_figure=False, **kwargs):
+    from seaborn.matrix import ClusterGrid
+    from seaborn import heatmap
     fig = plt.figure(figsize=kwargs.pop('figsize', (8, 8)))
     # Add an axes at position rect [left, bottom, width, height]
-    quantile_threshold = kwargs.pop('quantile_threshold', 0.95)
-    method = kwargs.pop('method', 'ward')
-    q99 = np.quantile(prs_mat, quantile_threshold)
-    prs_mat_cl = copy.deepcopy(prs_mat)
-    prs_mat_cl[prs_mat_cl > q99] = q99
-    # , optimal_ordering=True)
-    if cluster_normalized:
-        row_linkage = sch.linkage(distance.pdist(prs_mat_cl), method=method)
-        col_linkage = sch.linkage(distance.pdist(prs_mat_cl.T), method=method)
-    else:
-        row_linkage = sch.linkage(distance.pdist(prs_mat), method=method)
-        col_linkage = sch.linkage(distance.pdist(prs_mat.T), method=method)
[…]

### 2021-02-18 notebooks/paper_plots_0216_pcc_only_clustered.Rmd
changed plotting Rmds

---
title: "Paper figures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
setwd("../")
source("src/R/plot_density_prs.R")
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc_old = pickle.load(f)
with open(f'data/interim/pcc_021521_withclustering/pcc_10_r.pickle','rb') as f:
    e_pcc = pickle.load(f)
pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))
```

```{r}
library(tidyverse)
library(cowplot)
library(ggpubr)
library(ggsignif)
library(glue)
figure_folder = 'reports/figures/paper_figures_0216_pcc_only/'
pcc_df_random <- data.table::rbindlist(lapply(py$e_pcc$e_list, function(x) x$df), fill = T, idcol = "random_id") %>% mutate(random_id = as.factor(random_id))
pcc_df <- py$pcc_df %>%
  mutate(data = "pcc") %>%
  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real") %>%
  bind_rows(
    pcc_df_random %>% mutate(data = "pcc") %>% mutate(sens_norm = sens / nrow(py$pcc_df), eff_norm = eff / nrow(py$pcc_df), group = "random")
  ) %>%
  mutate(group = fct_relevel(group, c("real", "random")))
combined_df <- pcc_df
```

Degree - Eff - Sens distributions
```{r}

pcc_eff_dens <-
  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness")
dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
pcc_eff_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
    coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
    scale_x_continuous(
      breaks = scales::trans_breaks("log10", function(x) 10^x),
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    )) #+
#   cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity") + theme(legend.position = "none")) #+
#        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
pcc_dens_comb <- cowplot::plot_grid(pcc_eff_dens + theme(legend.position = "none"),
  pcc_sensitivity_dens + theme(legend.position = "none"),
  #+theme(legend.position='none'),
  labels = c("F", "G"), ncol = 2
)
# pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
# dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
dens_plots <- pcc_dens_comb # cowplot::plot_grid(pcc_dens_comb_title,nrow=1)
# cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
# ggsave('reports/figures/paper_figures_0202_pcc_only/fig1.png', plot=pcc_dens_comb,width=4,height=4)
```

```{r}
real_random_labels <- c("PSN", "Rewired\nnetwork")
names(real_random_labels) <- c("real", "random")
pcc_deg_eff <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = eff_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Effectiveness") +
  xlab("Degree") +
  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
pcc_deg_sens <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = sens_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Sensitivity") +
  xlab("Degree") +
  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
  labels = c("A", "B"),
  ncol = 2
)
ggsave(glue("{figure_folder}/fig2.png"), plot = deg_scatter_plots, width = 10, height = 10)
```

```{r}
pcc_rewire_df <- read_csv("data/interim/pcc_021521_withclustering//rewire_data.csv")
rewire_df <- pcc_rewire_df %>% mutate(data = "pcc")
network_labels <- c("Yeast GI Profile Similarity")
facet_labels <- network_labels
names(facet_labels) <- c("pcc")
combined_rewire_df <- rewire_df %>%
  select(data, eff_deg_pearson, sens_deg_spearman) %>%
  mutate(type = "random") %>%
  bind_rows(
    data.frame(
      sens_deg_spearman = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$sens, method = "spearman")),
      eff_deg_pearson = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$eff, method = "pearson")), type = "real", data = c("pcc")
    )
  ) %>%
  mutate(data = fct_relevel(data, c("pcc")))

p3 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = eff_deg_pearson, color = type, y = ..scaled..), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = eff_deg_pearson, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Effectiveness degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines")) +
  scale_y_continuous(expand = c(0, 0))
p4 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = sens_deg_spearman, y = ..scaled.., color = type), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = sens_deg_spearman, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Sensitivity degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines"), legend.position = "bottom") +
  scale_color_discrete(labels = c("Random networks", "Genetic network")) +
  scale_y_continuous(expand = c(0, 0))
lgn34 <- cowplot::get_legend(p4)
distr_plots <- plot_grid(pcc_degree_dens + theme(legend.position = ""),
  ggdraw(p3 + theme(legend.position = "")),
  ggdraw(p4 + theme(legend.position = "")),
  labels = c("C", "D", "E"), nrow = 1
)
# distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
# nrow=2,rel_heights = c(0.9,0.1))
# ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
plot_grid(deg_scatter_plots, distr_plots, dens_plots, nrow = 3, rel_heights = c(0.3, 0.4, .3))
ggsave(glue("{figure_folder}fig3.pdf"), width = 10, height = 12)
```

# Sensor connectivity and neighbor degree

```{r}
sensor_connectivity_df <- read_csv("data/interim/sensor_connectivity_1205/sensor_connectivity_df.csv") %>%
  mutate(data = fct_relevel(data, c("pcc", "gi", "yuri", "huri"))) %>%
  filter(data == "pcc")
# effector_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/effector_connectivity_df.csv')%>%
#    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))%>%filter(data=='pcc')
# effector_connectivity_plot <-
#    ggplot()+
##    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
##    geom_boxplot()+
##    geom_jitter()+
#    geom_density(data =effector_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
#    geom_vline(data =effector_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
#    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
#    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
#    theme_bw()+
#    scale_color_discrete(labels=c('Random sampled set', 'Effectors'))+
#    theme(legend.position='bottom')+
#    scale_y_continuous(expand = c(0, 0))
eff_neighbor_degree_plot <- combined_df %>%
  filter(group == "real") %>%
  group_by(data) %>%
  mutate(is_effector = factor(ifelse(eff_norm > quantile(eff_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
  #    mutate(is_effector = fct_relevel(is_effector,c(TRUE,FALSE)))%>%
  ggplot(aes(x = is_effector, y = log(neighbor_degree))) +
  #    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
  #    geom_point()+
  geom_boxplot() +
  theme_bw() +
  ylab("Log(Average neighbor degree)") +
  xlab("") +
  stat_compare_means() +
  scale_x_discrete(labels = c("Effector", "Not Effector"))
sensor_connectivity_plot <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = sensor_connectivity_df %>% filter(type != "real"), aes(x = ratio, color = type, y = ..scaled..), linetype = "dashed") +
  geom_vline(data = sensor_connectivity_df %>% filter(type == "real"), aes(xintercept = ratio, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Ratio of between group edges\nto outgroup edges") +
  theme_bw() +
  scale_color_discrete(labels = c("Random sampled set", "Sensors")) +
  theme(legend.position = "bottom") +
  scale_y_continuous(expand = c(0, 0))
neighbor_degree_plot <- combined_df %>%
  filter(group == "real") %>%
  group_by(data) %>%
  mutate(is_sensor = factor(ifelse(sens_norm > quantile(sens_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
  #    mutate(is_sensor = fct_relevel(is_sensor,c(TRUE,FALSE)))%>%
  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
  #    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
  #    geom_point()+
  geom_boxplot() +
  theme_bw() +
  ylab("Log(Average neighbor degree)") +
  xlab("") +
  stat_compare_means() +
  scale_x_discrete(labels = c("Sensor", "Not Sensor"))
sensor_conn_lgn <- get_legend(sensor_connectivity_plot + theme(legend.position = "right"))
plot_grid(neighbor_degree_plot,
  sensor_connectivity_plot + theme(legend.position = "none"), # effector_connectivity_plot,
  eff_neighbor_degree_plot, sensor_conn_lgn,
  nrow = 2,
  labels = c("A", "B", "C", "")
) # %>%
#    plot_grid(, labels=c('','C'),nrow=2, rel_widths=c(2,1))
ggsave(glue("{figure_folder}fig5.pdf"), width = 6, height = 6)

# combined_df%>%filter(group=='real'&data=='huri')%>%mutate(is_sensor = ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE))%>%
#    coin::independence_test(neighbor_degree~is_sensor, data=.)
```

```{r}
library(RColorBrewer)
col <- colorRampPalette(brewer.pal(n = 9, name = "Set1"))(12)
sensor_colors <- col[1:8] # brewer.pal(n = 6, name = "Set1")
effector_colors <- col[9:12] # brewer.pal(n=3, name= "Set1_r")
```

```{python}
sensor_colors = r.sensor_colors
effector_colors = r.effector_colors
sensors_pcc = e_pcc.sensors_df
sensors_pcc['go_group'] = sensors_pcc['cluster_go_term']
effector_pcc = e_pcc.effectors_df
effector_pcc['go_group'] = effector_pcc['cluster_go_term']
effector_order = effector_pcc.groupby('go_group').eff.median().sort_values().index.tolist()
sensor_order = sensors_pcc.groupby('go_group').sens.median().sort_values().index.tolist()
```

```{python}
from matplotlib.lines import Line2D
pos = e_pcc_old.graph_gc.nodes('pos')
fig, ax = plt.subplots(figsize=(12,12))
legend_elements = [    ]
e_pcc.plot_network_spring(ax=ax,
                          node_size=1,
                          node_color='black',
 #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
                         edge_color='black')
#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=sensors_pcc.orf_name.values, node_size=200, pos=pos,
                          node_color='black',
                          node_shape='^',edgecolors='black',
                          linewidths=1)
for itr, i in enumerate(sensor_order):
    #print(i, effector_colors[itr])

    orf_names_to_plot = sensors_pcc.loc[sensors_pcc.go_group==i, 'orf_name'].tolist()
#    print(orf_names_to_plot)
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=sensor_colors[itr],
                          node_shape='^',edgecolors='black',
                          linewidths=1)
    legend_elements.append(
        Line2D([0], [0], marker='^', color='black', label=f'Sensors ({i})',
                              markerfacecolor=sensor_colors[itr], markersize=12, linestyle="None")
    )
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=effector_pcc.orf_name.values, node_size=100, pos=pos,
                      node_color='black',
                      node_shape='o')
for itr, i in enumerate(effector_order):
    orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=effector_colors[itr],
                          node_shape='o',edgecolors='black',
                          linewidths=1)
    if i == 'mito':
        lbl = 'Respiratory complex assembly'
    elif i == 'golgi':
        lbl = "Golgi vesicle transport"
    else:
        lbl = 'Chromosome segregation'
    legend_elements.append(
            Line2D([0], [0], marker='o', color='black', label=f'Effectors ({i})',
                                  markerfacecolor=effector_colors[itr], markersize=12, linestyle="None")
        )
nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='red', alpha=0.5)
ax.set_facecolor('white')
legend_elements.extend(
    [Line2D([0], [0], marker='o', color='black', label='Genes',
                              markerfacecolor='black', markersize=4, linestyle="None"),
#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
                              markerfacecolor='black', markersize=0, linestyle="-"),
                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
                              markerfacecolor='#018571', markersize=0, linestyle="-"),
                   Line2D([0], [0], marker='o', color='blue', label= 'Effector-Effector edges',
                              markerfacecolor='#a6611a', markersize=0, linestyle="-")]
)
lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))

nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
plt.savefig('tmp_nw.png',bbox_inches='tight')

```

```{r}
effector_pcc <- py$effector_pcc
sensors_pcc <- py$sensors_pcc %>% mutate(go_group = (as.character(go_group)), go_group = ifelse(go_group == "NaN", NA, go_group))%>%drop_na()
# library(tidyverse)
effector_pcc$go_group <- as.factor(effector_pcc$go_group)

# res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
# res.aov
effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
effector_eff_pval$res[effector_eff_pval$res$P.adj < 0.1, ]
effector_deg_pval <- FSA::dunnTest(deg ~ go_group, effector_pcc)
effector_deg_pval$res[effector_deg_pval$res$P.adj < 0.1, ]

eff_deg_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(
    values = effector_colors,
#    labels = c("Chromosome\nSegragetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")
  ) +
  xlab("") +
  ylab("Degree") +
  theme_bw() +
  geom_signif(
    comparisons = list(c("golgi", "chromatin"), c("golgi", "mito"), c("mito", "chromatin")),
    annotation = c("**", "***", "ns"),
    y_position = c(110, 115, 120)
  ) +
  theme(axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
  geom_boxplot() +
  # scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ggpubr::stat_compare_means(method = "kruskal.test") +
  scale_fill_manual(values = effector_colors) +
  ylab("Effectiveness") +
  theme_bw() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())
ggsave("tmp.png", plot = eff_eff_comp)

sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot() +
  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = sensor_colors) +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
    axis.text.x = element_blank(), legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  ) # , legend.spacing.y = unit(2,'cm'))
sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]

sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
  geom_boxplot() +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
#  geom_signif(
#    comparisons = list(
#      c("hexose metabolic\nprocess", "phenylalanine\ntransport"), c("tricarboxylic\nacid cycle", "phenylalanine\ntransport"),
#      c("phenylalanine\ntransport", "protein folding")
#    ),
#    annotation = c("**", "**", "*"), y_position = c(0.007, 0.0075, 0.008)
#  ) +
  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ylab("Sensitivity") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())

img <- "tmp_nw.png" %>%
  magick::image_read() # %>%
# magick::image_resize("570x380")

nw_img <- cowplot::ggdraw() +
  cowplot::draw_image(img, width = 1)
go_plots <- cowplot::plot_grid(
  sens_deg_comp + theme(legend.position = "none"),
  sens_sens_comp + theme(legend.position = "none"),
  cowplot::get_legend(sens_deg_comp), eff_deg_comp + theme(legend.position = "none"),
  eff_eff_comp + theme(legend.position = "none"),
  cowplot::get_legend(eff_deg_comp),
  ncol = 3, labels = c("B", "C", "", "D", "E", "")
)
combined <- cowplot::plot_grid(nw_img, go_plots, nrow = 2, rel_heights = c(0.4, 0.6), labels = c("A", ""))
ggsave(glue("{figure_folder}/fig6.png"), plot = combined, width = 9, height = 12)

```

### 2021-02-18 tests/test_enm.py

@@ -7,7 +7,25 @@ import matplotlib.pyplot as plt
 @pytest.fixture
 def enm():
     """ Returns empty Enm object with name Empty"""
-    return Enm('Empty')
+    enm =  Enm('Empty')
+
+    L = np.array([[ 5,  0,  0,  0,  0, -1, -1, -1, -1, -1],
+        [ 0,  5,  0,  0,  0, -1, -1, -1, -1, -1],
+        [ 0,  0,  3,  0,  0, -1, -1,  0,  0, -1],
+        [ 0,  0,  0,  1,  0, -1,  0,  0,  0,  0],
+        [ 0,  0,  0,  0,  4, -1, -1, -1,  0, -1],
+        [-1, -1, -1, -1, -1,  8, -1, -1, -1,  0],
+        [-1, -1, -1,  0, -1, -1,  7, -1, -1,  0],
+        [-1, -1,  0,  0, -1, -1, -1,  6, -1,  0],
+        [-1, -1,  0,  0,  0, -1, -1, -1,  6, -1],
+        [-1, -1, -1,  0, -1,  0,  0,  0, -1,  5]])
+    enm.L=L
+#L = D-A
+#A = D-L
+    adj = np.diag(np.diag(L)) - L
+    enm.G = nx.from_numpy_array(adj)
+    enm.giant_component()
+    return enm
 
 
 # def test_read_network(enm):
@@ -20,36 +38,13 @@ def enm():
 from unittest.mock import Mock
 #from .. import my_module
 def test_gnm(enm):
-    L = np.array([[ 5,  0,  0,  0,  0, -1, -1, -1, -1, -1],
-        [ 0,  5,  0,  0,  0, -1, -1, -1, -1, -1],
-        [ 0,  0,  3,  0,  0, -1, -1,  0,  0, -1],
-        [ 0,  0,  0,  1,  0, -1,  0,  0,  0,  0],
-        [ 0,  0,  0,  0,  4, -1, -1, -1,  0, -1],
-        [-1, -1, -1, -1, -1,  8, -1, -1, -1,  0],
-        [-1, -1, -1,  0, -1, -1,  7, -1, -1,  0],
-        [-1, -1,  0,  0, -1, -1, -1,  6, -1,  0],
-        [-1, -1,  0,  0,  0, -1, -1, -1,  6, -1],
-        [-1, -1, -1,  0, -1,  0,  0,  0, -1,  5]])
-    enm.L=L
[…]

### 2021-02-22 notebooks/17-PRS_dendrogram_cluster_investigation-020921.Rmd
fixed effector/sensor coloring of clusters

@@
 library(reticulate)
-source('src/R/get.subclusters.dendrogram.R')
 #use_python("/home/oma21/miniconda3/envs/enm/bin/python")
@@
 #source('src/R/plot_density_prs.R')
+source('src/R/get.subclusters.dendrogram.R')
 library(RColorBrewer)
-col = brewer.pal(n=9,name='Set1')
-sensor_colors = col[1:6]
-effector_colors = col[7:9]
+col = colorRampPalette(brewer.pal(n=9,name='Set1'))(10)
+sensor_colors = col[1:8]
+effector_colors = col[9:10]
 ```
@@
 effector_sub_pcc = get_subnetwork(e_pcc.graph_gc, effector_pcc.orf_name.values)
-effector_order = effector_pcc.groupby('go_group').eff.median().sort_values().index.tolist()
-sensor_order = sensors_pcc.groupby('go_group').sens.median().sort_values().index.tolist()
+effector_order = effector_pcc.groupby('go_term').eff.median().sort_values().index.tolist()
+sensor_order = sensors_pcc.groupby('go_term').sens.median().sort_values().index.tolist()
 effector_colors_dict = dict(zip(effector_order,r.effector_colors))
@@
 # Plot heatmap
-Using the clustering with `euclidian` distance and `ward` linkage, plot the heatmap with row and column colors are the GO term annotations found from effector and sensor analysis
+Using the clustering with `seuclidian` distance and `ward` linkage, plot the heatmap with row and column colors are the GO term annotations found from effector and sensor analysis
 
@@
 go_color_map['none'] = 'white'
-clrs = map(py$eff_sens_go_list, ~ifelse(is.null(.x), 'none',.x))%>%unlist()
+clrs = go_color_map# map(py$eff_sens_go_list, ~ifelse(is.null(.x), 'none',.x))%>%unlist()
 
-rowColors = rowAnnotation(rowColors=clrs,
+rowColors = rowAnnotation(rowColors=py$e_pcc$df%>%left_join(py$effector_pcc)%>%select(go_term)%>%pull%>%map(~ifelse(is.na(.x), 'none',.x))%>%unlist(),
                           col=list(rowColors = go_color_map ),
@@
                           show_legend=FALSE)
-colColors = columnAnnotation(colColors=clrs,
+colColors = columnAnnotation(colColors=py$e_pcc$df%>%left_join(py$sensors_pcc)%>%select(go_term)%>%pull%>%map(~ifelse(is.null(.x), 'none',
+                                                                                                                      ifelse(is.nan(.x),'none',.x)))%>%unlist(),
                           col=list(colColors = go_color_map ),

### 2021-02-22 src/features/pcc_go_v1.py

@@ -1,13 +1,0 @@
-#enm.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
-#enm.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')
-#nx.set_node_attributes(enm.graph_gc,dict(zip(list(enm.graph_gc.nodes),list(enm.graph_gc.nodes))),'orf_name')
-
-## GO Analysis for sensors
-#go_df = pd.read_csv('data/interim/go_results/4.tsv','\t')
-sensors = enm.df.loc[enm.df.loc[:,'sens'] > np.quantile(enm.df.loc[:,'sens'],0.99)].orf_name.values
-strain_ids = pd.read_csv('data/interim/strain_ids_with_experiment_count_all.csv')
-sensors_orf_name = strain_ids.loc[strain_ids['Allele Gene name'].isin(sensors)]['Systematic gene name'].unique()
-go_path = 'data/raw/ontology/'
-#goeaobj, geneid2name = create_goea()
-goeaobj, goea_results_sig,geneid2name, go_df= go_findenrichment(query = sensors_orf_name, obo_fname=f'{go_path}/goslim_generic.obo', gaf = f'{go_path}/sgd.gaf',background=f'{go_path}/sgd_costanzogenes',sgd_info_tab=f'{go_path}/SGD_features.tab')
-#enm.plot_network_spring(plot_go=True,go_df_list=[go_df],level_list=[0.2])

### 2021-04-05 notebooks/17-PRS_dendrogram_cluster_investigation-020921.Rmd
unstashed some CSHL plotting edits

@@
 library(RColorBrewer)
-col = colorRampPalette(brewer.pal(n=9,name='Set1'))(10)
-sensor_colors = col[1:8]
-effector_colors = col[9:10]
+col =brewer.pal(n=8,name='Set1')
+sensor_colors = col[1:4]
+effector_colors = col[5:8]
 ```
@@
     query <- utils$query_goatools(subcluster,goea,geneid2name)
+    print(head(query))
     eff_go_terms[i] = query[1,4]
 }
-effector_pcc <- unlist(eff_go_terms)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%rename(cluster_go_term='.')%>%right_join(effector_pcc,by=c('rowname'='clusters'))
+effector_pcc <- as.character(eff_go_terms)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%rename(cluster_go_term='.')%>%right_join(effector_pcc,by=c('rowname'='clusters'))%>%rename(clusters=rowname)
+
 for(i in 1:4){
@@
     query <- utils$query_goatools(subcluster,goea,geneid2name)
+    print(query)
     sens_go_terms[i] = query[1,4]
 }
-sensors_pcc <- unlist(sens_go_terms)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%rename(cluster_go_term='.')%>%right_join(sensors_pcc,by=c('rowname'='clusters'))
+sensors_pcc <- as.character(sens_go_terms)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%rename(cluster_go_term='.')%>%right_join(sensors_pcc,by=c('rowname'='clusters'))%>%rename(clusters=rowname)
 

### 2021-04-05 notebooks/paper_plots_0216_pcc_only_clustered.Rmd
unstashed some CSHL plotting edits

@@
 source("src/R/plot_density_prs.R")
+source("src/R/get.subclusters.dendrogram.R")
 ```
@@
 library(RColorBrewer)
-col <- colorRampPalette(brewer.pal(n = 9, name = "Set1"))(12)
-sensor_colors <- col[1:8] # brewer.pal(n = 6, name = "Set1")
-effector_colors <- col[9:12] # brewer.pal(n=3, name= "Set1_r")
+col <- brewer.pal(n = 8, name = "Set1")
+sensor_colors <- col[1:4] # brewer.pal(n = 6, name = "Set1")
+effector_colors <- col[5:8] # brewer.pal(n=3, name= "Set1_r")
 ```
@@
 sensors_pcc['go_group'] = sensors_pcc['cluster_go_term']
+sensors_pcc['go_group'] = ['None'  if pd.isna(i) else i for i in sensors_pcc['go_group'].tolist()]
 effector_pcc = e_pcc.effectors_df
 effector_pcc['go_group'] = effector_pcc['cluster_go_term']
-effector_order = effector_pcc.groupby('go_group').eff.median().sort_values().index.tolist()
-sensor_order = sensors_pcc.groupby('go_group').sens.median().sort_values().index.tolist()
+effector_order = effector_pcc.groupby('go_group').clusters.median().sort_values().index.tolist()
+sensor_order = sensors_pcc.groupby('go_group').clusters.median().sort_values().index.tolist()
+#sensor_order.append(None)
 ```
@@
 ```
+
+```{python}
+import copy
+import scipy.cluster.hierarchy as sch
+prs_mat = e_pcc.prs_mat
+quantile_threshold =  0.95
+method = 'ward'
+metric = 'seuclidean'
+q99 = np.quantile(prs_mat, quantile_threshold)
+prs_mat_cl = copy.deepcopy(prs_mat)
+prs_mat_cl[prs_mat_cl > q99] = q99
+prs_mat_cl_orig = prs_mat_cl
+# , optimal_ordering=True)
+#row_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl), method=method)
+# ,optimal_ordering=True)
+#col_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl.T), method=method)
+
+row_dist_orig = sch.distance.pdist((prs_mat),metric = metric)
+col_dist_orig = sch.distance.pdist((prs_mat.T),metric = metric)
+row_dist_orig_sqr = sch.distance.squareform(row_dist_orig)
+col_dist_orig_sqr = sch.distance.squareform(col_dist_orig)
+
+row_dist = sch.distance.pdist(prs_mat_cl,metric = metric)
+col_dist = sch.distance.pdist(prs_mat_cl.T,metric = metric)
+
+row_dist_sqr = sch.distance.squareform(row_dist)
+col_dist_sqr = sch.distance.squareform(col_dist)
+
+```
+
+```{r}
+cluster_method = 'ward.D2'
+dist_row = as.dist(py$row_dist_sqr)
+hclust_row = hclust(dist_row, cluster_method)
+dist_col = as.dist(py$col_dist_sqr)
+hclust_col = hclust(dist_col, cluster_method)
+dend_row  <- as.dendrogram(hclust_row)
+dend_col  <- as.dendrogram(hclust_col)
+#effector_pcc <- get.subclusters.dendrogram(dend_row, effector_pcc)
+#sensors_pcc <- get.subclusters.dendrogram(dend_col, sensors_pcc%>%select(-rowname))
+library(dendextend)
+#png('reports/figures/dendrogram021721/row_dendrogram_colored.png',width=800,height=800)
+dend_row_plot <- dend_row[[2]] %>% 
+    set("branches_k_color", k = 4,value = effector_colors[c(4,2,3,1)]) %>% 
+    set("labels", NA) %>%    # change labelsk
+    as.ggdend()%>%
+    ggplot()#    plot(xlab="", sub="")}
+#dev.off()
+#png('reports/figures/dendrogram021721/col_dendrogram_colored.png',width=800,height=800)
+dend_col_plot <-     dend_col[[1]] %>% 
+    set("branches_k_color", k = 4,value = sensor_colors[c(3,2,4,1)]) %>% 
+    set("labels", NA) %>%    # change labelsk
+    as.ggdend()%>%
+    ggplot()#    plot(xlab="", sub="")}
+#dev.off()
+```
+
+```{python}
+from matplotlib.lines import Line2D
+pos = e_pcc_old.graph_gc.nodes('pos')
+fig, ax = plt.subplots(figsize=(12,12))
+legend_elements = [    ]
+e_pcc.plot_network_spring(ax=ax,
+                          node_size=1,
+                          node_color='black',
+ #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
+                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
+                         edge_color='black')
+#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
+nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=sensors_pcc.orf_name.values, node_size=200, pos=pos,
+                          node_color='black',
+                          node_shape='^',edgecolors='black',
+                          linewidths=1)
+for itr, i in enumerate(sensor_order):
+    orf_names_to_plot = sensors_pcc.loc[sensors_pcc.go_group==i, 'orf_name'].tolist()
+    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
+                          node_color=sensor_colors[itr],
+                          node_shape='^',edgecolors='black',
+                          linewidths=1)
+    legend_elements.append(
+        Line2D([0], [0], marker='^', color='black', label=f'Sensors ({i})',
+                              markerfacecolor=sensor_colors[itr], markersize=12, linestyle="None")
+    )
+nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='red', alpha=0.5)
+ax.set_facecolor('white')
+legend_elements.extend(
+    [Line2D([0], [0], marker='o', color='black', label='Genes',
+                              markerfacecolor='black', markersize=4, linestyle="None"),
+#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
+#                               markerfacecolor='black', markersize=10, linestyle="None"),
+#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
+#                               markerfacecolor='black', markersize=10, linestyle="None"),
+                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
+                              markerfacecolor='black', markersize=0, linestyle="-"),
+                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
+                              markerfacecolor='#018571', markersize=0, linestyle="-")]
+)
+lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
+plt.savefig(f'{r.figure_folder}tmp_nw_sens.png',bbox_inches='tight')
+
+```
+
+```{python}
+from matplotlib.lines import Line2D
+pos = e_pcc_old.graph_gc.nodes('pos')
+fig, ax = plt.subplots(figsize=(12,12))
+legend_elements = [    ]
+e_pcc.plot_network_spring(ax=ax,
+                          node_size=1,
+                          node_color='black',
+ #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
+                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
+                         edge_color='black')
+#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
+nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=effector_pcc.orf_name.values, node_size=100, pos=pos,
+                      node_color='black',
+                      node_shape='o')
+for itr, i in enumerate(effector_order):
+    orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
+    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
+                          node_color=effector_colors[itr],
+                          node_shape='o',edgecolors='black',
+                          linewidths=1)
+    legend_elements.append(
+            Line2D([0], [0], marker='o', color='black', label=f'Effectors ({i})',
+                                  markerfacecolor=effector_colors[itr], markersize=12, linestyle="None")
+        )
+ax.set_facecolor('white')
+legend_elements.extend(
+    [Line2D([0], [0], marker='o', color='black', label='Genes',
+                              markerfacecolor='black', markersize=4, linestyle="None"),
+#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
+#                               markerfacecolor='black', markersize=10, linestyle="None"),
+#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
+#                               markerfacecolor='black', markersize=10, linestyle="None"),
+                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
+                              markerfacecolor='black', markersize=0, linestyle="-"),
+                   Line2D([0], [0], marker='o', color='blue', label= 'Effector-Effector edges',
+                              markerfacecolor='#a6611a', markersize=0, linestyle="-")]
+)
+lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
+
+nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
+plt.savefig(f'{r.figure_folder}tmp_nw_eff.png',bbox_inches='tight')
+
+from src.visualize.visualize import heatmap_annotated
+#import src
+#import importlib
+importlib.reload(src.visualize.visualize)
+heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path=r.figure_folder, row_linkage=e_pcc.row_linkage, col_linkage=e_pcc.col_linkage, save_figure=True)#,
+#                 row_colors=colors, col_colors=colors)
+
+```
+
+```{r}
+library(coin)
+df <- py$e_pcc$df%>%mutate(eff_group = as.factor(ifelse(orf_name%in%effector_pcc$orf_name,'eff','other')),
+                    sens_group = factor(ifelse(orf_name%in%sensors_pcc$orf_name,'sens','other'),levels=c('sens','other')),
+                    eff_norm = eff / nrow(.),
+                    sens_norm = sens/ nrow(.))
+pval_eff = pvalue(independence_test(eff~eff_group,df))
+pval_sens = pvalue(independence_test(sens~sens_group,df))
+
+eff_group_box <- df%>%ggplot(aes(x=eff_group,y=eff_norm))+
+    geom_boxplot()+
+  geom_signif(comparisons = list(c("eff", "other")), 
+              map_signif_level=TRUE, y_position = 0.006)+
+    xlab('')+
+    ylab('Effectiveness')+
+    scale_x_discrete(labels=c('Effectors','Others'))+
+    theme_bw()
+sens_group_box <- df%>%ggplot(aes(x=sens_group,y=sens_norm))+
+    geom_boxplot()+
+  geom_signif(comparisons = list(c("sens", "other")), 
+              map_signif_level=TRUE, y_position = 0.0075)+
+    xlab('')+
+    ylab('Sensitivity')+
+    scale_x_discrete(labels=c('Sensors','Others'))+
+    theme_bw()+ylim(0,0.008)
+#ggsave('tmp.png',sens_group_box)
+heatmap_img <- glue('{figure_folder}prs_heatmap.png')%>%
+    magick::image_read()
+heatmap_img <- cowplot::ggdraw()+
+    cowplot::draw_image(heatmap_img, width = 1)
+eff_nw_img <- glue('{figure_folder}tmp_nw_eff.png') %>%
+  magick::image_read() # %>%
+eff_nw_img <- cowplot::ggdraw() +
+  cowplot::draw_image(eff_nw_img, width = 1)
+sens_nw_img <- glue('{figure_folder}tmp_nw_sens.png') %>%
+  magick::image_read() # %>%
+sens_nw_img <- cowplot::ggdraw() +
+  cowplot::draw_image(sens_nw_img, width = 1)
+cowplot::plot_grid(plot_grid(heatmap_img, plot_grid(sens_group_box, eff_group_box+ylim(0,0.007), nrow=2,labels=c('B','C')), nrow=1, rel_widths = c(0.7,0.3),labels=c('A','')),
+                   plot_grid(dend_col_plot, sens_nw_img, nrow=1, rel_widths=c(0.2,.8), labels=c('D','E')),
+                   plot_grid(dend_row_plot, eff_nw_img, nrow=1, rel_widths=c(0.2,.8), labels=c('F','G')), nrow=3, rel_heights=c(.5,.25,.25))
+ggsave(glue('{figure_folder}fig1.pdf'),height=10,width=8)
+
+```

### 2021-04-05 notebooks/paper_plots_1213_pcc_only.Rmd
unstashed some CSHL plotting edits

--- 2020-12-21 notebooks/paper_plots_1213_pcc_only.Rmd
@@
 library(reticulate)
-#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
-use_condaenv('enm')
-setwd('../')
-source('src/R/plot_density_prs.R')
+# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
+use_condaenv("enm")
+setwd("../")
+source("src/R/plot_density_prs.R")
 ```
@@
 
-pcc_df_random  = data.table::rbindlist(lapply(py$e_pcc$e_list, function(x) x$df),fill=T,idcol='random_id')%>%mutate(random_id = as.factor(random_id))
-pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.), group = 'real')%>%bind_rows(
-    pcc_df_random%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(py$pcc_df),eff_norm = eff/nrow(py$pcc_df), group = 'random')
-)%>%mutate(group=fct_relevel(group, c('real','random')))
-combined_df =pcc_df
+pcc_df_random <- data.table::rbindlist(lapply(py$e_pcc$e_list, function(x) x$df), fill = T, idcol = "random_id") %>% mutate(random_id = as.factor(random_id))
+pcc_df <- py$pcc_df %>%
+  mutate(data = "pcc") %>%
+  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real") %>%
+  bind_rows(
+    pcc_df_random %>% mutate(data = "pcc") %>% mutate(sens_norm = sens / nrow(py$pcc_df), eff_norm = eff / nrow(py$pcc_df), group = "random")
+  ) %>%
+  mutate(group = fct_relevel(group, c("real", "random")))
+combined_df <- pcc_df
 ```
@@
 
-pcc_degree_dens <- 
-    plot_density_prs(pcc_df, deg, xlab='Degree')
 pcc_eff_dens <-
-    plot_density_prs(pcc_df, eff_norm, xlab='Effectiveness')
-#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
+  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness")
+dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
+pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
+#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
+pcc_eff_dens <-
+  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
+    coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
+    scale_x_continuous(
+      breaks = scales::trans_breaks("log10", function(x) 10^x),
+      labels = scales::trans_format("log10", scales::math_format(10^.x))
+    )) #+
+#   cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
+# annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
 pcc_sensitivity_dens <-
-    plot_density_prs(pcc_df, sens_norm, xlab='Sensitivity')
-title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
-pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
-                                pcc_eff_dens+theme(legend.position='none'), 
-                                pcc_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
-pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
-dens_plots = cowplot::plot_grid(pcc_dens_comb_title,nrow=1)
-cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
-ggsave('reports/figures/paper_figures_1213_pcc_only/fig1.png', width=4,height=4)
-
+  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity") + theme(legend.position = "none")) #+
+#        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
+# title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
+pcc_dens_comb <- cowplot::plot_grid(pcc_eff_dens + theme(legend.position = "none"),
+  pcc_sensitivity_dens + theme(legend.position = "none"),
+  #+theme(legend.position='none'),
+  labels = c("F", "G"), ncol = 2
+)
+# pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
+# dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
+dens_plots <- pcc_dens_comb # cowplot::plot_grid(pcc_dens_comb_title,nrow=1)
+# cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
+# ggsave('reports/figures/paper_figures_0202_pcc_only/fig1.png', plot=pcc_dens_comb,width=4,height=4)
 ```
@@
 ```{r}
-real_random_labels = c('Real\nnetwork','Rewired\nnetwork')
-names(real_random_labels)  = c('real','random')
-pcc_deg_eff = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
-    ggplot(aes(x=deg, y=eff_norm))+
-    geom_point()+
+real_random_labels <- c("PSN", "Rewired\nnetwork")
+names(real_random_labels) <- c("real", "random")
+pcc_deg_eff <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+  ggplot(aes(x = deg, y = eff_norm)) +
+  geom_point() +
   #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
-    theme_bw()+
-    ylab("Effectiveness")+
-    xlab("Degree")+
-    stat_cor(method='pearson', cor.coef.name='R', label.x.npc=0.1) +
-    theme(strip.text.y = element_text(angle = 0))+
-    scale_y_continuous(labels = scales::label_scientific(digits=1))
-pcc_deg_sens = pcc_df %>% filter(group=='real')%>%#pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
-    ggplot(aes(x=deg, y=sens_norm))+
-    geom_point()+
+  theme_bw() +
+  ylab("Effectiveness") +
+  xlab("Degree") +
+  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1) +
+  theme(strip.text.y = element_text(angle = 0)) +
+  scale_y_continuous(labels = scales::label_scientific(digits = 1))
+pcc_deg_sens <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
+  ggplot(aes(x = deg, y = sens_norm)) +
+  geom_point() +
   #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
-    theme_bw()+
-    ylab("Sensitivity")+
-    xlab("Degree")+
-    stat_cor(method='spearman', cor.coef.name='rho', label.x.npc=0.1) +
-    theme(strip.text.y = element_text(angle = 0))+
-    scale_y_continuous(labels = scales::label_scientific(digits=1))
+  theme_bw() +
+  ylab("Sensitivity") +
+  xlab("Degree") +
+  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1) +
+  theme(strip.text.y = element_text(angle = 0)) +
+  scale_y_continuous(labels = scales::label_scientific(digits = 1))
 deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
-                    labels = c('D','E'),
-                   ncol=2)
-ggsave('reports/figures/paper_figures_1213_pcc_only/fig2.png',plot=deg_scatter_plots, width=10,height=10)
+  labels = c("A", "B"),
+  ncol = 2
+)
+ggsave("reports/figures/paper_figures_0202_pcc_only/fig2.png", plot = deg_scatter_plots, width = 10, height = 10)
 ```
@@
 ```{r}
-pcc_rewire_df = read_csv('data/interim/pcc_0909/rewire_data.csv')
-rewire_df = pcc_rewire_df%>%mutate(data='pcc')
-network_labels  <- c('Yeast GI Profile Similarity')
+pcc_rewire_df <- read_csv("data/interim/pcc_0909/rewire_data.csv")
+rewire_df <- pcc_rewire_df %>% mutate(data = "pcc")
+network_labels <- c("Yeast GI Profile Similarity")
 facet_labels <- network_labels
 names(facet_labels) <- c("pcc")
-combined_rewire_df <- rewire_df%>%select(data, eff_deg_pearson,sens_deg_spearman)%>%mutate(type = 'random')%>% 
+combined_rewire_df <- rewire_df %>%
+  select(data, eff_deg_pearson, sens_deg_spearman) %>%
+  mutate(type = "random") %>%
   bind_rows(
-    data.frame(sens_deg_spearman= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$sens,method='spearman')), 
-               eff_deg_pearson= c(cor(pcc_df[pcc_df$group=='real',]$deg, pcc_df[pcc_df$group=='real',]$eff,method='pearson')), type='real',data=c('pcc')))%>%
-    mutate(data= fct_relevel(data, c('pcc')))
+    data.frame(
+      sens_deg_spearman = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$sens, method = "spearman")),
+      eff_deg_pearson = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$eff, method = "pearson")), type = "real", data = c("pcc")
+    )
+  ) %>%
+  mutate(data = fct_relevel(data, c("pcc")))
 
-p3 = 
-    ggplot()+
+p3 <-
+  ggplot() +
   #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
@@
   #    geom_jitter()+
-    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
-    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
-    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-    ylab('Density')+xlab('Effectiveness degree correlation')+
-    theme_bw()+
-    theme(panel.spacing = unit(2, "lines"))+
+  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = eff_deg_pearson, color = type, y = ..scaled..), linetype = "dashed") +
+  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = eff_deg_pearson, color = type)) +
+  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
+  ylab("Density") +
+  xlab("Effectiveness degree correlation") +
+  theme_bw() +
+  theme(panel.spacing = unit(2, "lines")) +
   scale_y_continuous(expand = c(0, 0))
-p4 = 
-    ggplot()+
+p4 <-
+  ggplot() +
   #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
@@
   #    geom_jitter()+
-    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
-    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
-    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-    ylab('Density')+xlab('Sensitivity degree correlation')+
-    theme_bw()+
-    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
-    scale_color_discrete(labels=c('Rewired networks', 'Real network'))+
+  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = sens_deg_spearman, y = ..scaled.., color = type), linetype = "dashed") +
+  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = sens_deg_spearman, color = type)) +
+  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
+  ylab("Density") +
+  xlab("Sensitivity degree correlation") +
+  theme_bw() +
+  theme(panel.spacing = unit(2, "lines"), legend.position = "bottom") +
+  scale_color_discrete(labels = c("Random networks", "Genetic network")) +
   scale_y_continuous(expand = c(0, 0))
 lgn34 <- cowplot::get_legend(p4)
-distr_plots <- plot_grid(
-          p3+theme(legend.position=''),
- p4+theme(legend.position=''),labels=c('F','G'),nrow=1 )
-distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
- nrow=2,rel_heights = c(0.9,0.1))
-#ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
-plot_grid(dens_plots, deg_scatter_plots, distr_plots_withlgn, nrow=3,rel_heights = c(0.4,0.3,.3))
-ggsave('reports/figures/paper_figures_1213_pcc_only/fig3.png',width=10,height=12)
+distr_plots <- plot_grid(pcc_degree_dens + theme(legend.position = ""),
+  ggdraw(p3 + theme(legend.position = "")),
+  ggdraw(p4 + theme(legend.position = "")),
+  labels = c("C", "D", "E"), nrow = 1
+)
+# distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
+# nrow=2,rel_heights = c(0.9,0.1))
+# ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
+plot_grid(deg_scatter_plots, distr_plots, dens_plots, nrow = 3, rel_heights = c(0.3, 0.4, .3))
+ggsave("reports/figures/paper_figures_0202_pcc_only/fig3.pdf", width = 10, height = 12)
 ```
@@
 ```{r deletion}
-pcc_deletion = read_csv('data/interim/deletion_analysis_0911/pcc_deletion_100.csv')%>%
-    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
-    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='pcc')
-yuri_deletion = read_csv('data/interim/deletion_analysis_0911/yuri_deletion_100.csv')%>%
-    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
-    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='yuri')
-huri_deletion = read_csv('data/interim/deletion_analysis_0911/huri_deletion_100.csv')%>%
-    pivot_wider(id_cols=c('range','variable_0'),names_from='variable_1',values_from='value')%>%
-    mutate(range = range/max(range), gc_size = gc_size/max(gc_size), group='huri')
+pcc_deletion <- read_csv("data/interim/deletion_analysis_0911/pcc_deletion_100.csv") %>%
+  pivot_wider(id_cols = c("range", "variable_0"), names_from = "variable_1", values_from = "value") %>%
+  mutate(range = range / max(range), gc_size = gc_size / max(gc_size), group = "pcc")
+yuri_deletion <- read_csv("data/interim/deletion_analysis_0911/yuri_deletion_100.csv") %>%
+  pivot_wider(id_cols = c("range", "variable_0"), names_from = "variable_1", values_from = "value") %>%
+  mutate(range = range / max(range), gc_size = gc_size / max(gc_size), group = "yuri")
+huri_deletion <- read_csv("data/interim/deletion_analysis_0911/huri_deletion_100.csv") %>%
+  pivot_wider(id_cols = c("range", "variable_0"), names_from = "variable_1", values_from = "value") %>%
+  mutate(range = range / max(range), gc_size = gc_size / max(gc_size), group = "huri")
 
-deletion_df  <- bind_rows(pcc_deletion, yuri_deletion, huri_deletion)%>%mutate(group = fct_relevel(group,c('pcc','yuri','huri')))
+deletion_df <- bind_rows(pcc_deletion, yuri_deletion, huri_deletion) %>% mutate(group = fct_relevel(group, c("pcc", "yuri", "huri")))
 
 library(MESS)
-auc_data <- deletion_df%>%
-    group_by(group, variable_0)%>%
-    summarise(auc=MESS::auc(gc_size,range), r = range[min(which(gc_size < 0.05))])%>%
-    ungroup()%>%
-    mutate(variable_0=fct_reorder(variable_0, auc, min))%>%pivot_wider(-r, names_from=group, values_from=auc)
+auc_data <- deletion_df %>%
+  group_by(group, variable_0) %>%
+  summarise(auc = MESS::auc(gc_size, range), r = range[min(which(gc_size < 0.05))]) %>%
+  ungroup() %>%
+  mutate(variable_0 = fct_reorder(variable_0, auc, min)) %>%
+  pivot_wider(-r, names_from = group, values_from = auc)
 
-auc_plot_pcc <- auc_data%>%
-    ggplot(aes(x=variable_0,y=pcc))+
-    geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" )),stat='identity')+
-    theme_bw()+
-    ylab("Robustness")+
-    xlab("Deletion parameter")+
-    scale_alpha_manual(name = '', values = c(0.3, 1), guide = FALSE)+
-    labs(fill = "Deletion\nparameter")+
+auc_plot_pcc <- auc_data %>%
+  ggplot(aes(x = variable_0, y = pcc)) +
+  geom_bar(aes(fill = variable_0, alpha = (variable_0 == "eff_sorted_deletion")), stat = "identity") +
+  theme_bw() +
+  ylab("Robustness") +
+  xlab("Deletion parameter") +
+  scale_alpha_manual(name = "", values = c(0.3, 1), guide = FALSE) +
+  labs(fill = "Deletion\nparameter") +
   scale_x_discrete(labels = c(
@@
     "DR",
-                                "S"))+
-    scale_fill_brewer(name = 'Deletion\nparameter', palette = "Set1", guide='legend', labels= c(
+    "S"
+  )) +
+  scale_fill_brewer(name = "Deletion\nparameter", palette = "Set1", guide = "legend", labels = c(
     "Degree",
@@
     "Sensitivity"
-                                ))+
-   theme(legend.position='bottom', legend.title=element_text(size=18), legend.text=element_text(size=14),legend.spacing.x = unit(1.0, 'cm'),legend.spacing.y = unit(1.0, 'cm'))
-auc_plot_yuri <- auc_data%>%
-    ggplot(aes(x=variable_0,y=yuri))+
-    geom_bar(aes(fill=variable_0,alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == 'sens_sorted_deletion') ),stat='identity')+
-    theme_bw()+
-    ylab("Robustness")+
-    xlab("Deletion parameter")+
-    labs(fill = "Deletion\nparameter")+
-    scale_alpha_manual(name = '', values = c(0.3, 1), guide = FALSE)+
+  )) +
+  theme(legend.position = "bottom", legend.title = element_text(size = 18), legend.text = element_text(size = 14), legend.spacing.x = unit(1.0, "cm"), legend.spacing.y = unit(1.0, "cm"))
+auc_plot_yuri <- auc_data %>%
+  ggplot(aes(x = variable_0, y = yuri)) +
+  geom_bar(aes(fill = variable_0, alpha = (variable_0 == "eff_sorted_deletion" | variable_0 == "sens_sorted_deletion")), stat = "identity") +
+  theme_bw() +
+  ylab("Robustness") +
+  xlab("Deletion parameter") +
+  labs(fill = "Deletion\nparameter") +
+  scale_alpha_manual(name = "", values = c(0.3, 1), guide = FALSE) +
   scale_x_discrete(labels = c(
@@
     "R", "DR",
-                                "S"))+
-    scale_fill_brewer(name='', palette = "Set1", labels= c(
+    "S"
+  )) +
+  scale_fill_brewer(name = "", palette = "Set1", labels = c(
     "Degree",
@@
     "Random",
-                                "Sensitivity","Degree Reversed"))+
-   theme(legend.position='right')
-auc_plot_huri<- auc_data%>%
-    ggplot(aes(x=variable_0,y=huri, alpha = (variable_0 == "eff_sorted_deletion" ) ))+
-    geom_bar(aes(fill=variable_0),stat='identity')+
-    theme_bw()+
-    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
-    ylab("Robustness")+
-    xlab("Deletion parameter")+
-    labs(fill = "Deletion\nparameter")+
+    "Sensitivity", "Degree Reversed"
+  )) +
+  theme(legend.position = "right")
+auc_plot_huri <- auc_data %>%
+  ggplot(aes(x = variable_0, y = huri, alpha = (variable_0 == "eff_sorted_deletion"))) +
+  geom_bar(aes(fill = variable_0), stat = "identity") +
+  theme_bw() +
+  scale_alpha_manual(values = c(0.3, 1), guide = FALSE) +
+  ylab("Robustness") +
+  xlab("Deletion parameter") +
+  labs(fill = "Deletion\nparameter") +
   scale_x_discrete(labels = c(
@@
     "R",
-                                "DR","S"))+
-    scale_fill_brewer(palette = "Set1", labels= c(
+    "DR", "S"
+  )) +
+  scale_fill_brewer(palette = "Set1", labels = c(
     "Degree",
@@
     "Random",
-                                "Sensitivity","Degree Reversed"))+
-   theme(legend.position='right')
-#combined_df %>% group_by(data)%>%summarise(deg_btw = cor(deg, btw),
+    "Sensitivity", "Degree Reversed"
+  )) +
+  theme(legend.position = "right")
+# combined_df %>% group_by(data)%>%summarise(deg_btw = cor(deg, btw),
 #                                           deg_eff = cor(deg,eff),
@@
 #                                           deg_closeness = cor(deg, closeness_centr))
-deletion_plot_pcc <-  pcc_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
-    ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion" ) ))+
+deletion_plot_pcc <- pcc_deletion %>%
+  mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0))) %>%
+  ggplot(aes(x = range, y = gc_size, color = variable_0, alpha = (variable_0 == "eff_sorted_deletion"))) +
   #    geom_point(size=1)+
-        geom_line(size=2)+
+  geom_line(size = 2) +
   #    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
-    scale_colour_brewer(palette = "Set1")+ 
-    xlab('% Deleted Nodes')+
-    ylab('% Giant Component Size')+
-    scale_y_continuous(labels = scales::percent)+
-    scale_x_continuous(labels = scales::percent)+
-    theme_bw()+
-    ggtitle('Costanzo 2016')+
-    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
-    theme(legend.position='bottom',panel.border = element_blank(), axis.line = element_line())
-deletion_plot_yuri <-  yuri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
-ggplot(aes(x=range, y= gc_size, color = variable_0 ,alpha = (variable_0 == "eff_sorted_deletion" )  ))+
+  scale_colour_brewer(palette = "Set1") +
+  xlab("% Deleted Nodes") +
+  ylab("% Giant Component Size") +
+  scale_y_continuous(labels = scales::percent) +
+  scale_x_continuous(labels = scales::percent) +
+  theme_bw() +
+  ggtitle("Costanzo 2016") +
+  scale_alpha_manual(values = c(0.3, 1), guide = FALSE) +
+  theme(legend.position = "bottom", panel.border = element_blank(), axis.line = element_line())
+deletion_plot_yuri <- yuri_deletion %>%
+  mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0))) %>%
+  ggplot(aes(x = range, y = gc_size, color = variable_0, alpha = (variable_0 == "eff_sorted_deletion"))) +
   #    geom_point(size=1)+
-        geom_line(size=2)+
+  geom_line(size = 2) +
   #    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
-    scale_colour_brewer(palette = "Set1")+ 
-    xlab('% Deleted Nodes')+
-    ggtitle('Yeast PPI')+
-    ylab('% Giant Component Size')+
-    scale_y_continuous(labels = scales::percent)+
-    scale_x_continuous(labels = scales::percent)+
-    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
-    theme_bw()+
-    theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
-deletion_plot_huri <-  huri_deletion%>%   mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
-ggplot(aes(x=range, y= gc_size, color = variable_0 , alpha = (variable_0 == "eff_sorted_deletion"  ) ))+
+  scale_colour_brewer(palette = "Set1") +
+  xlab("% Deleted Nodes") +
+  ggtitle("Yeast PPI") +
+  ylab("% Giant Component Size") +
+  scale_y_continuous(labels = scales::percent) +
+  scale_x_continuous(labels = scales::percent) +
+  scale_alpha_manual(values = c(0.3, 1), guide = FALSE) +
+  theme_bw() +
+  theme(legend.position = "right", panel.border = element_blank(), axis.line = element_line())
+deletion_plot_huri <- huri_deletion %>%
+  mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0))) %>%
+  ggplot(aes(x = range, y = gc_size, color = variable_0, alpha = (variable_0 == "eff_sorted_deletion"))) +
   #    geom_point(size=1)+
-        geom_line(size=2)+
+  geom_line(size = 2) +
   #    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
-    scale_colour_brewer(palette = "Set1")+ 
-    xlab('% Deleted Nodes')+
-    ylab('% Giant Component Size')+
-    ggtitle('HuRI')+
-    scale_y_continuous(labels = scales::percent)+
-    scale_x_continuous(labels = scales::percent)+
-    scale_alpha_manual(values = c(0.3, 1), guide = FALSE)+
-    theme_bw()+
-    theme(legend.position='right',panel.border = element_blank(), axis.line = element_line())
+  scale_colour_brewer(palette = "Set1") +
+  xlab("% Deleted Nodes") +
+  ylab("% Giant Component Size") +
+  ggtitle("HuRI") +
+  scale_y_continuous(labels = scales::percent) +
+  scale_x_continuous(labels = scales::percent) +
+  scale_alpha_manual(values = c(0.3, 1), guide = FALSE) +
+  theme_bw() +
+  theme(legend.position = "right", panel.border = element_blank(), axis.line = element_line())
 deletion_lgn <- cowplot::get_legend(auc_plot_pcc)
-pcc_with_inset = ggdraw(deletion_plot_pcc+    theme(legend.position=''))+
-  draw_plot(auc_plot_pcc+theme(legend.position=''), .50, .62, .45, .35) +
+pcc_with_inset <- ggdraw(deletion_plot_pcc + theme(legend.position = "")) +
+  draw_plot(auc_plot_pcc + theme(legend.position = ""), .50, .62, .45, .35) +
   draw_plot_label(
@@
   )
-yuri_with_inset = ggdraw(deletion_plot_yuri+    theme(legend.position=''))+
-  draw_plot(auc_plot_yuri+theme(legend.position=''), .50, .62, .45, .35) +
+yuri_with_inset <- ggdraw(deletion_plot_yuri + theme(legend.position = "")) +
+  draw_plot(auc_plot_yuri + theme(legend.position = ""), .50, .62, .45, .35) +
   draw_plot_label(
@@
   )
-huri_with_inset = ggdraw(deletion_plot_huri+    theme(legend.position=''))+
-  draw_plot(auc_plot_huri+theme(legend.position=''), .50, .62, .45, .35) +
+huri_with_inset <- ggdraw(deletion_plot_huri + theme(legend.position = "")) +
+  draw_plot(auc_plot_huri + theme(legend.position = ""), .50, .62, .45, .35) +
   draw_plot_label(
@@
   )
-plot_grid(pcc_with_inset, yuri_with_inset, huri_with_inset, ncol=3)%>%plot_grid(deletion_lgn,nrow=2, rel_heights=c(0.9,.1))
-ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)
+plot_grid(pcc_with_inset, yuri_with_inset, huri_with_inset, ncol = 3) %>% plot_grid(deletion_lgn, nrow = 2, rel_heights = c(0.9, .1))
+ggsave("reports/figures/paper_figures_0916/fig4.png", width = 12)
 
-plot_grid(deletion_plot_pcc+    theme(legend.position='')
-, auc_plot_pcc+    theme(legend.position='')
-,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))
-
+plot_grid(deletion_plot_pcc + theme(legend.position = ""),
+  auc_plot_pcc + theme(legend.position = ""),
+  deletion_lgn,
+  nrow = 1, rel_widths = c(0.4, 0.5, .1), labels = c("A", "B")
+)
 ```
@@
 ```{r}
-sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/sensor_connectivity_df.csv')%>%
-    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))%>%filter(data=='pcc')
-#effector_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/effector_connectivity_df.csv')%>%
+sensor_connectivity_df <- read_csv("data/interim/sensor_connectivity_1205/sensor_connectivity_df.csv") %>%
+  mutate(data = fct_relevel(data, c("pcc", "gi", "yuri", "huri"))) %>%
+  filter(data == "pcc")
+# effector_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/effector_connectivity_df.csv')%>%
 #    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))%>%filter(data=='pcc')
-#effector_connectivity_plot <- 
+# effector_connectivity_plot <-
 #    ggplot()+
@@
 #    scale_y_continuous(expand = c(0, 0))
-eff_neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
-    mutate(is_effector = factor(ifelse(eff_norm>quantile(eff_norm,0.99),TRUE,FALSE), levels=c(TRUE,FALSE)))%>%
+eff_neighbor_degree_plot <- combined_df %>%
+  filter(group == "real") %>%
+  group_by(data) %>%
+  mutate(is_effector = factor(ifelse(eff_norm > quantile(eff_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
   #    mutate(is_effector = fct_relevel(is_effector,c(TRUE,FALSE)))%>%
-    ggplot(aes(x=is_effector,y=log(neighbor_degree)))+
+  ggplot(aes(x = is_effector, y = log(neighbor_degree))) +
   #    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
   #    geom_point()+
-    geom_boxplot()+
-    theme_bw()+
-    ylab('Log(Average neighbor degree)')+
-    xlab('')+ stat_compare_means()+
-    scale_x_discrete(labels=c('Effector', 'Not Effector'))
+  geom_boxplot() +
+  theme_bw() +
+  ylab("Log(Average neighbor degree)") +
+  xlab("") +
+  stat_compare_means() +
+  scale_x_discrete(labels = c("Effector", "Not Effector"))
 sensor_connectivity_plot <-
-    ggplot()+
+  ggplot() +
   #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
@@
   #    geom_jitter()+
-    geom_density(data =sensor_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
-    geom_vline(data =sensor_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
-    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-    ylab('Density')+xlab('Ratio of between group edges\nto outgroup edges')+
-    theme_bw()+
-    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
-    theme(legend.position='bottom')+
+  geom_density(data = sensor_connectivity_df %>% filter(type != "real"), aes(x = ratio, color = type, y = ..scaled..), linetype = "dashed") +
+  geom_vline(data = sensor_connectivity_df %>% filter(type == "real"), aes(xintercept = ratio, color = type)) +
+  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
+  ylab("Density") +
+  xlab("Ratio of between group edges\nto outgroup edges") +
+  theme_bw() +
+  scale_color_discrete(labels = c("Random sampled set", "Sensors")) +
+  theme(legend.position = "bottom") +
   scale_y_continuous(expand = c(0, 0))
-neighbor_degree_plot <- combined_df%>%filter(group=='real')%>%group_by(data)%>%
-    mutate(is_sensor = factor(ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE), levels=c(TRUE,FALSE)))%>%
+neighbor_degree_plot <- combined_df %>%
+  filter(group == "real") %>%
+  group_by(data) %>%
+  mutate(is_sensor = factor(ifelse(sens_norm > quantile(sens_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
   #    mutate(is_sensor = fct_relevel(is_sensor,c(TRUE,FALSE)))%>%
-    ggplot(aes(x=is_sensor,y=log(neighbor_degree)))+
+  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
   #    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
   #    geom_point()+
-    geom_boxplot()+
-    theme_bw()+
-    ylab('Log(Average neighbor degree)')+
-    xlab('')+ stat_compare_means()+
-    scale_x_discrete(labels=c('Sensor', 'Not Sensor'))
-sensor_conn_lgn = get_legend(sensor_connectivity_plot+theme(legend.position='right'))
+  geom_boxplot() +
+  theme_bw() +
+  ylab("Log(Average neighbor degree)") +
+  xlab("") +
+  stat_compare_means() +
+  scale_x_discrete(labels = c("Sensor", "Not Sensor"))
+sensor_conn_lgn <- get_legend(sensor_connectivity_plot + theme(legend.position = "right"))
 plot_grid(neighbor_degree_plot,
-          sensor_connectivity_plot+theme(legend.position='none'), #effector_connectivity_plot,
+  sensor_connectivity_plot + theme(legend.position = "none"), # effector_connectivity_plot,
   eff_neighbor_degree_plot, sensor_conn_lgn,
-          nrow=2 , 
-          labels=c('A','B','C',''))#%>%
+  nrow = 2,
+  labels = c("A", "B", "C", "")
+) # %>%
 #    plot_grid(, labels=c('','C'),nrow=2, rel_widths=c(2,1))
-ggsave('reports/figures/paper_figures_1213_pcc_only/fig5.pdf',width=6,height=6)
+ggsave("reports/figures/paper_figures_0202_pcc_only/fig5.pdf", width = 6, height = 6)
 
-#combined_df%>%filter(group=='real'&data=='huri')%>%mutate(is_sensor = ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE))%>%
+# combined_df%>%filter(group=='real'&data=='huri')%>%mutate(is_sensor = ifelse(sens_norm>quantile(sens_norm,0.99),TRUE,FALSE))%>%
 #    coin::independence_test(neighbor_degree~is_sensor, data=.)
-
 ```
@@
    nx_object,
-    df
-)
-{
-    nx =  reticulate::import("networkx")
-    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
-    #ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
-    ig = igraph::set_vertex_attr(ig , name =  'name', value  = (df$orf_name))
-    #igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
+   df) {
+    nx <- reticulate::import("networkx")
+    ig <- igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = "undirected")
+    # ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
+    ig <- igraph::set_vertex_attr(ig, name = "name", value = (df$orf_name))
+    # igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
     ig
@@
 library(RColorBrewer)
-col = brewer.pal(n=9, name='Set1')
-sensor_colors =col[1:6] #brewer.pal(n = 6, name = "Set1")
-effector_colors = col[7:9]#brewer.pal(n=3, name= "Set1_r")
+col <- brewer.pal(n = 9, name = "Set1")
+sensor_colors <- col[1:6] # brewer.pal(n = 6, name = "Set1")
+effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
 ```
@@
                           linewidths=1)
+legend_elements.append(
+    Line2D([0], [0], marker='^', color='black', label=f'Sensors (No GO enrichment)',
+                          markerfacecolor=sensor_colors[0], markersize=12, linestyle="None")
+)
 for itr, i in enumerate(sensor_order):
@@
         Line2D([0], [0], marker='^', color='black', label=f'Sensors ({i})',
-                              markerfacecolor=sensor_colors[itr], markersize=12, linestyle="None")
-    )
-nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=effector_pcc.orf_name.values, node_size=100, pos=pos,
-                      node_color='black',
-                      node_shape='o')
-for itr, i in enumerate(effector_order):
-    orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
-    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
-                          node_color=effector_colors[itr],
-                          node_shape='o',edgecolors='black',
-                          linewidths=1)
-    if i == 'mito':
-        lbl = 'Respiratory complex assembly'
-    elif i == 'golgi':
-        lbl = "Golgi vesicle transport"
-    else:
-        lbl = 'Chromosome segragation'
-    legend_elements.append(
-            Line2D([0], [0], marker='o', color='black', label=f'Effectors ({lbl})',
-                                  markerfacecolor=effector_colors[itr], markersize=12, linestyle="None")
+                              markerfacecolor=sensor_colors[itr], markersize=16, linestyle="None")
     )
@@
                    Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
-                              markerfacecolor='#018571', markersize=0, linestyle="-"),
+                              markerfacecolor='#018571', markersize=0, linestyle="-")
+])
+lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
+plt.savefig('reports/figures/CSHL_plots_022621/tmp_nwsens.png',bbox_inches='tight')
+#plt.savefig('tmp_nw.png',bbox_inches='tight')
+```
+
+```{python}
+from matplotlib.lines import Line2D
+pos = e_pcc.graph_gc.nodes('pos')
+fig, ax = plt.subplots(figsize=(12,12))
+legend_elements = [    ]
+e_pcc.plot_network_spring(ax=ax,
+                          node_size=1,
+                          node_color='black',
+ #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
+                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
+                         edge_color='black')
+#        Line2D([0], [0], marker='^', color='black', label=f'Sensors ({i})',
+nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=effector_pcc.orf_name.values, node_size=100, pos=pos,
+                      node_color='black',
+                      node_shape='o')
+for itr, i in enumerate(effector_order):
+    orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
+    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=400, pos=pos,
+                          node_color=effector_colors[itr],
+                          node_shape='o',edgecolors='black',
+                          linewidths=1)
+    if i == 'mito':
+        lbl = 'Respiratory complex assembly'
+    elif i == 'golgi':
+        lbl = "Golgi vesicle transport"
+    else:
+        lbl = 'Chromosome segregation'
+    legend_elements.append(
+            Line2D([0], [0], marker='o', color='black', label=f'Effectors ({lbl})',
+                                  markerfacecolor=effector_colors[itr], markersize=16, linestyle="None")
+        )
+nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
+ax.set_facecolor('white')
+legend_elements.extend(
+    [Line2D([0], [0], marker='o', color='black', label='Genes',
+                              markerfacecolor='black', markersize=4, linestyle="None"),
+#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
+#                               markerfacecolor='black', markersize=10, linestyle="None"),
+#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
+#                               markerfacecolor='black', markersize=10, linestyle="None"),
+                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
+                              markerfacecolor='black', markersize=0, linestyle="-"),
+#                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
+#                              markerfacecolor='#018571', markersize=0, linestyle="-")
                    Line2D([0], [0], marker='o', color='blue', label= 'Effector-Effector edges',
-                              markerfacecolor='#a6611a', markersize=0, linestyle="-")]
-)
+                              markerfacecolor='#a6611a', markersize=0, linestyle="-")
+])
 lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
@@
 ```{r}
-effector_pcc = py$effector_pcc
-sensors_pcc = py$sensors_pcc%>%mutate(go_group = (as.character(go_group)), go_group=ifelse(go_group=='NULL', NA, go_group))
-#library(tidyverse)
-effector_pcc$go_group = as.factor(effector_pcc$go_group)
+effector_pcc <- py$effector_pcc
+sensors_pcc <- py$sensors_pcc %>% mutate(go_group = (as.character(go_group)), go_group = ifelse(go_group == "NULL", NA, go_group))
+# library(tidyverse)
+effector_pcc$go_group <- as.factor(effector_pcc$go_group)
 
-#res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
-#res.aov
-effector_eff_pval = FSA::dunnTest(eff~go_group, effector_pcc)
-effector_eff_pval$res[effector_eff_pval$res$P.adj<0.1,]
-effector_deg_pval = FSA::dunnTest(deg~go_group, effector_pcc)
-effector_deg_pval$res[effector_deg_pval$res$P.adj<0.1,]
+# res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
+# res.aov
+effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
+effector_eff_pval$res[effector_eff_pval$res$P.adj < 0.1, ]
+effector_deg_pval <- FSA::dunnTest(deg ~ go_group, effector_pcc)
+effector_deg_pval$res[effector_deg_pval$res$P.adj < 0.1, ]
 
-eff_deg_comp<-ggplot(effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff)), aes(x= go_group, y=deg,fill=go_group))+
-    geom_boxplot(outlier.shape=NA)+
-    scale_fill_manual(values=effector_colors,
-                      labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
-    xlab('')+
-    ylab('Degree')+
-    theme_bw()+
-    geom_signif(comparisons=list(c('golgi','chromatin'), c('golgi','mito'),c('mito','chromatin')),
-                annotation=c('**','***','ns'),
-                y_position=c(110,115,120))+
-    theme(axis.text.x=element_blank(),legend.title=element_blank(),legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'in'))+
-eff_eff_comp<-ggplot(effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff))%>%
-                      mutate(eff_norm =eff / 5183), aes(x= go_group, y=eff_norm,fill=go_group))+
-    geom_boxplot()+
-    #scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
-    xlab('')+
-    ggpubr::stat_compare_means(method='kruskal.test')+
-    scale_fill_manual(values=effector_colors)+
-    ylab('Effectiveness')+
-    theme_bw()+
-    theme(axis.text.x=element_blank(),legend.title=element_blank())
-ggsave('tmp.png', plot=eff_deg_comp)
+eff_deg_comp <- ggplot(effector_pcc %>% right_join(py$e_pcc$df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_reorder(go_group, eff),go_group=fct_relevel(go_group,'Others',after=Inf)),
+                       aes(x = go_group, y = deg, fill = go_group)) +
+  geom_boxplot(outlier.shape = NA) +
+  scale_fill_manual(
+    values = c(effector_colors,'black'),
+    labels = c("Chromosome\nSegragetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
+  ) +
+  xlab("") +
+  ylab("Degree") +
+  theme_bw() +
+  geom_signif(
+    comparisons = list(c("golgi", "chromatin"), c("golgi", "mito"), c("mito", "chromatin")),
+    annotation = c("**", "***", "ns"),
+    y_position = c(115, 120, 130)
+  ) +
+  theme(axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
+ggsave("reports/figures/CSHL_plots_022621/tmp_eff_deg_nolegend.png", plot = eff_deg_comp+theme(legend.position='none'),width=4,height=4)
 
-sens_deg_comp<-ggplot(sensors_pcc%>%drop_na()%>%mutate(go_group=fct_reorder(go_group, sens)), aes(x= go_group, y=deg,fill=go_group))+
-    geom_boxplot()+
+eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
+  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
+  geom_boxplot() +
   # scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
-    xlab('')+
-    ylab('Degree')+
-    scale_fill_manual(values=sensor_colors)+
-    ggpubr::stat_compare_means(method='kruskal.test',label.x.npc=.3)+
-    theme_bw()+
-    theme(axis.text.x=element_blank(),legend.title=element_blank(),
-          legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'cm'))
-sensors_pcc$go_group = as.factor(sensors_pcc$go_group)
-sensors_sens_pval = FSA::dunnTest(sens~go_group, sensors_pcc)
-sensors_sens_pval$res[sensors_sens_pval$res$P.adj<0.1,]
+  xlab("") +
+  ggpubr::stat_compare_means(method = "kruskal.test") +
+  scale_fill_manual(values = effector_colors) +
+  ylab("Effectiveness") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(), legend.title = element_blank())
+ggsave("reports/figures/CSHL_plots_022621/tmp_eff_eff.png", plot = eff_eff_comp+theme(legend.position='none'),width=4,height=4)
 
-sens_sens_comp<-ggplot(sensors_pcc%>%drop_na()%>%mutate(go_group=fct_reorder(go_group, sens))%>%
-                      mutate(sens_norm = sens / 5183), aes(x= go_group, y=sens_norm,fill=go_group))+
-    geom_boxplot()+
+sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(py$e_pcc$df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
+  geom_boxplot(
+    outlier.shape=NA) +
+  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
+  xlab("") +
+  ylab("Degree") +
+  scale_fill_manual(values = c(sensor_colors[1:6],'black')) +
+  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
+  theme_bw() +
+  theme(
+    axis.text.x = element_blank(), legend.title = element_blank(),
+    legend.text = element_text(margin = margin(t = 10, b = 10))
+  )+scale_y_log10()
+  ggsave('reports/figures/CSHL_plots_022621/sens_deg_withlegend.png', plot=sens_deg_comp,width=4,height=4)
+
+sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
+sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
+sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]
+
+sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
+  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
+  geom_boxplot() +
   geom_signif(
-        comparisons = list(c("hexose metabolic\nprocess", 'phenylalanine\ntransport'),c("tricarboxylic\nacid cycle", 'phenylalanine\ntransport'),
-                            c('phenylalanine\ntransport', 'protein folding')),
-        annotation = c('**','**', '*'),y_position=c(0.007,0.0075, 0.008)
-                )+
+    comparisons = list(
+      c("hexose metabolic\nprocess", "phenylalanine\ntransport"), c("tricarboxylic\nacid cycle", "phenylalanine\ntransport"),
+      c("phenylalanine\ntransport", "protein folding")
+    ),
+    annotation = c("**", "**", "*"), y_position = c(0.007, 0.0075, 0.008)
+  ) +
   #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
-    xlab('')+
-    ylab('Sensitivity')+
-    scale_fill_manual(values=sensor_colors)+
-    theme_bw()+
-    theme(axis.text.x=element_blank(),legend.title=element_blank())
+  xlab("") +
+  ylab("Sensitivity") +
+  scale_fill_manual(values = sensor_colors) +
+  theme_bw() +
+  theme(axis.text.x = element_blank(), legend.title = element_blank())
 
-img <- 'tmp_nw.png' %>%
-  magick::image_read() #%>%
-  #magick::image_resize("570x380")
+img <- "tmp_nw.png" %>%
+  magick::image_read() # %>%
+# magick::image_resize("570x380")
 
-nw_img = cowplot::ggdraw()+
-    cowplot::draw_image(img, width=1)
-go_plots = cowplot::plot_grid(
-                   sens_deg_comp+theme(legend.position='none'),
-                   sens_sens_comp+theme(legend.position='none'),
-                   cowplot::get_legend(sens_deg_comp),eff_deg_comp+theme(legend.position='none'),
-                   eff_eff_comp+theme(legend.position='none'),
-                   cowplot::get_legend(eff_deg_comp),ncol=3, labels=c('B','C','','D','E',''))
-combined = cowplot::plot_grid(nw_img, go_plots,nrow=2,rel_heights=c(0.4,0.6), labels=c('A',''))
-ggsave('reports/figures/paper_figures_0916/fig6.png',plot=combined,width=9,height=12)
+nw_img <- cowplot::ggdraw() +
+  cowplot::draw_image(img, width = 1)
+go_plots <- cowplot::plot_grid(
+  sens_deg_comp + theme(legend.position = "none"),
+  sens_sens_comp + theme(legend.position = "none"),
+  cowplot::get_legend(sens_deg_comp), eff_deg_comp + theme(legend.position = "none"),
+  eff_eff_comp + theme(legend.position = "none"),
+  cowplot::get_legend(eff_deg_comp),
+  ncol = 3, labels = c("B", "C", "", "D", "E", "")
+)
+combined <- cowplot::plot_grid(nw_img, go_plots, nrow = 2, rel_heights = c(0.4, 0.6), labels = c("A", ""))
+ggsave('reports/figures/CSHL_plots_022621/sens_deg.png', plot=sens_deg_comp+theme(legend.position='none'),width=4,height=4)
+ggsave('reports/figures/CSHL_plots_022621/sens_sens.png', plot=sens_sens_comp+theme(legend.position='none'),width=4,height=4)
+ggsave("reports/figures/paper_figures_0202_pcc_only/fig6.png", plot = combined, width = 9, height = 12)
 ```

### 2021-04-05 src/enm.py

@@ -366,11 +366,15 @@ class Enm():
         mat_cl = copy.deepcopy(mat)
         mat_cl[mat_cl > q99] = q99
         if cluster_normalized:
-            row_linkage = sch.linkage(sch.distance.pdist(mat_cl, metric=distance_metric), method=method,optimal_ordering=optimal_ordering)
-            col_linkage = sch.linkage(sch.distance.pdist(mat_cl.T, metric=distance_metric), method=method,optimal_ordering=optimal_ordering)
+            row_dist = sch.distance.pdist(mat_cl, metric=distance_metric)
+            col_dist = sch.distance.pdist(mat_cl.T, metric=distance_metric)
+            row_linkage = sch.linkage(row_dist, method=method,optimal_ordering=optimal_ordering)
+            col_linkage = sch.linkage(col_dist, method=method,optimal_ordering=optimal_ordering)
         else:
-            row_linkage = sch.linkage(sch.distance.pdist(mat, metric=distance_metric), method=method,optimal_ordering=optimal_ordering)
-            col_linkage = sch.linkage(sch.distance.pdist(mat.T, metric=distance_metric), method=method,optimal_ordering=optimal_ordering)
+            row_dist = sch.distance.pdist(mat, metric=distance_metric)
+            col_dist = sch.distance.pdist(mat.T, metric=distance_metric)
+            row_linkage = sch.linkage(row_dist, method=method,optimal_ordering=optimal_ordering)
+            col_linkage = sch.linkage(col_dist, method=method,optimal_ordering=optimal_ordering)
 
         root_row, tree_list_row = sch.to_tree(row_linkage, True)
         root_col, tree_list_col = sch.to_tree(col_linkage, True)
@@ -378,6 +382,8 @@ class Enm():
         # ,optimal_ordering=True)
         self.row_linkage = row_linkage
         self.col_linkage = col_linkage
+        self.row_dist = row_dist
+        self.col_dist = col_dist
         self.mat_cl = mat_cl
         self.root_row = root_row
         self.root_col = root_col

### 2021-04-05 src/visualize/visualize.py

@@ -360,12 +360,14 @@ def heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path, row_linkage, col_li
     #plt.axis('off')
     ax_heatmap.set_xticks([])
     ax_heatmap.set_yticks([])
-    plt.colorbar(im, ax=ax_colorbar)
+    cbar = plt.colorbar(im, ax=ax_colorbar)
     
+    cbar.ax.get_yaxis().set_ticks_position('left')
+    cbar.ax.get_yaxis().set_label_position('left')
     # plt.show()
     outname = f"{figure_path}/{kwargs.pop('figure_name','prs_heatmap')}.{kwargs.pop('figure_extension','png')}"
     if save_figure:
-        plt.savefig(outname)
+        plt.savefig(outname,bbox_inches='tight')
 
         # plt.figure()
         # plt.plot(range(len(col_data)),col_data,'-')

### 2021-04-05 notebooks/paper_plots_1213_pcc_only.Rmd
text size changes for fig5

@@
 source("src/R/plot_density_prs.R")
+figure_path = 'reports/figures/0404_paperfigure_sensors/'
 ```
@@
 library(tidyverse)
+library(glue)
 library(cowplot)
@@
 
+# Network plot only sensors
 ```{python}
@@
 lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
-plt.savefig('reports/figures/CSHL_plots_022621/tmp_nwsens.png',bbox_inches='tight')
+figure_path = r.figure_path
+plt.savefig(f'{figure_path}//tmp_nwsens.png',bbox_inches='tight')
 #plt.savefig('tmp_nw.png',bbox_inches='tight')
@@
     values = c(effector_colors,'black'),
-    labels = c("Chromosome\nSegragetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
+    labels = c("Chromosome\nSegregetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
   ) +
@@
   ) +
-  theme(axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
-ggsave("reports/figures/CSHL_plots_022621/tmp_eff_deg_nolegend.png", plot = eff_deg_comp+theme(legend.position='none'),width=4,height=4)
+  theme(
+       axis.text.y=element_text(size=10),
+        axis.title.y=element_text(size=14), axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
+ggsave(glue('{figure_path}//tmp_eff_deg_nolegend.png'), plot = eff_deg_comp+theme(legend.position='none'),width=4,height=4)
+ggsave(glue('{figure_path}//tmp_eff_deg_withlegend.png'), plot = eff_deg_comp,width=6,height=4)
 
@@
   geom_boxplot() +
-  # scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
+  # scale_x_discrete(labels=c('Chromosome\nSegregetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
   xlab("") +
@@
   theme_bw() +
-  theme(axis.text.x = element_blank(), legend.title = element_blank())
-ggsave("reports/figures/CSHL_plots_022621/tmp_eff_eff.png", plot = eff_eff_comp+theme(legend.position='none'),width=4,height=4)
+  theme(
+        axis.text.y=element_text(size=10),
+        axis.title.y=element_text(size=14),axis.text.x = element_blank(), legend.title = element_blank())
+ggsave(glue('{figure_path}//tmp_eff_eff.png'), plot = eff_eff_comp+theme(legend.position='none'),width=4,height=4)
 
@@
     outlier.shape=NA) +
-  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
+  #    scale_x_discrete(labels=c('Chromosome\nSegregetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
   xlab("") +
@@
   theme(
+        axis.title.y=element_text(size=14),
+        axis.text.y=element_text(size=10),
     axis.text.x = element_blank(), legend.title = element_blank(),
@@
   )+scale_y_log10()
-  ggsave('reports/figures/CSHL_plots_022621/sens_deg_withlegend.png', plot=sens_deg_comp,width=4,height=4)
+  ggsave(glue('{figure_path}//sens_deg_withlegend.png'), plot=sens_deg_comp+theme(legend.position='bottom'),width=6,height=4)
+ggsave(glue('{figure_path}//sens_deg.png'), plot=sens_deg_comp+theme(legend.position='none'),width=4,height=4)
 
@@
   ) +
-  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
+  #    scale_x_discrete(labels=c('Chromosome\nSegregetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
   xlab("") +
@@
   theme_bw() +
-  theme(axis.text.x = element_blank(), legend.title = element_blank())
+  theme(
+        axis.title.y=element_text(size=14),
+        axis.text.y=element_text(size=10),
+        axis.text.x = element_blank(), legend.title = element_blank())
+ggsave(glue('{figure_path}//sens_sens.png'), plot=sens_sens_comp+theme(legend.position='none'),width=4,height=4)
 
@@
 combined <- cowplot::plot_grid(nw_img, go_plots, nrow = 2, rel_heights = c(0.4, 0.6), labels = c("A", ""))
-ggsave('reports/figures/CSHL_plots_022621/sens_deg.png', plot=sens_deg_comp+theme(legend.position='none'),width=4,height=4)
-ggsave('reports/figures/CSHL_plots_022621/sens_sens.png', plot=sens_sens_comp+theme(legend.position='none'),width=4,height=4)
-ggsave("reports/figures/paper_figures_0202_pcc_only/fig6.png", plot = combined, width = 9, height = 12)
+ggsave(glue('{figure_path}//sens_deg.png'), plot=sens_deg_comp+theme(legend.position='none'),width=4,height=4)
+ggsave(glue('{figure_path}//sens_sens.png'), plot=sens_sens_comp+theme(legend.position='none'),width=4,height=4)
+#ggsave("reports/figures/paper_figures_0202_pcc_only/fig6.png", plot = combined, width = 9, height = 12)
 ```

### 2021-05-11 notebooks/CSHL_plots_022621.Rmd
more paper figures

---
title: "Paper figures"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
setwd("../")
source("src/R/plot_density_prs.R")
source("src/R/get.subclusters.dendrogram.R")
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc_old = pickle.load(f)
with open(f'data/interim/pcc_021521_withclustering/pcc_10_r.pickle','rb') as f:
    e_pcc = pickle.load(f)
pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))
```

```{r}
library(tidyverse)
library(cowplot)
library(ggpubr)
library(ggsignif)
library(glue)
figure_folder = 'reports/figures/CSHL_plots_022621/'
pcc_df_random <- data.table::rbindlist(lapply(py$e_pcc$e_list, function(x) x$df), fill = T, idcol = "random_id") %>% mutate(random_id = as.factor(random_id))
pcc_df <- py$pcc_df %>%
  mutate(data = "pcc") %>%
  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real") %>%
  bind_rows(
    pcc_df_random %>% mutate(data = "pcc") %>% mutate(sens_norm = sens / nrow(py$pcc_df), eff_norm = eff / nrow(py$pcc_df), group = "random")
  ) %>%
  mutate(group = fct_relevel(group, c("real", "random")))
combined_df <- pcc_df
```

Degree - Eff - Sens distributions
```{r}

pcc_eff_dens <-
  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness")
dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
pcc_eff_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
    coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
    scale_x_continuous(
      breaks = scales::trans_breaks("log10", function(x) 10^x),
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    )) #+
#   cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity") + theme(legend.position = "none")) #+
#        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
pcc_dens_comb <- cowplot::plot_grid(pcc_eff_dens + theme(legend.position = "none"),
  pcc_sensitivity_dens + theme(legend.position = "none"),
  #+theme(legend.position='none'),
  ncol = 2
)
# pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
# dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
dens_plots <- pcc_dens_comb # cowplot::plot_grid(pcc_dens_comb_title,nrow=1)
# cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
ggsave(glue('{figure_folder}/dens_comb.png', plot=pcc_dens_comb,width=8,height=8)
```

```{r}
real_random_labels <- c("PSN", "Rewired\nnetwork")
names(real_random_labels) <- c("real", "random")
pcc_deg_eff <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = eff_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Effectiveness") +
  xlab("Degree") +
  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
pcc_deg_sens <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = sens_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Sensitivity") +
  xlab("Degree") +
  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
#  labels = c("A", "B"),
  ncol = 2
)
ggsave(glue("{figure_folder}/fig2.png"), plot = deg_scatter_plots, width = 10, height = 5)
```

```{r}
pcc_rewire_df <- read_csv("data/interim/pcc_021521_withclustering//rewire_data.csv")
rewire_df <- pcc_rewire_df %>% mutate(data = "pcc")
network_labels <- c("Yeast GI Profile Similarity")
facet_labels <- network_labels
names(facet_labels) <- c("pcc")
combined_rewire_df <- rewire_df %>%
  select(data, eff_deg_pearson, sens_deg_spearman) %>%
  mutate(type = "random") %>%
  bind_rows(
    data.frame(
      sens_deg_spearman = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$sens, method = "spearman")),
      eff_deg_pearson = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$eff, method = "pearson")), type = "real", data = c("pcc")
    )
  ) %>%
  mutate(data = fct_relevel(data, c("pcc")))

p3 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = eff_deg_pearson, color = type, y = ..scaled..), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = eff_deg_pearson, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Effectiveness degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines")) +
  scale_y_continuous(expand = c(0, 0))
p4 <-
  ggplot() +
      facet_grid(cols = vars(name), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_boxplot(data = combined_rewire_df %>% filter(type != "real")%>%select(data, sens_deg_spearman,eff_deg_pearson)%>%pivot_longer(-data), 
               aes(y = value, x = name, color = name)) +
#  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = sens_deg_spearman, y = ..scaled.., color = type), linetype = "dashed") +
  geom_point(data = combined_rewire_df %>% filter(type == "real")%>%select(data, sens_deg_spearman,eff_deg_pearson)%>%pivot_longer(-data), 
             aes(x=name,y=value,color=name)) +
#  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
#  ylab("Density") +
#  xlab("Sensitivity degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines"), legend.position = "bottom") 
#  scale_color_discrete(labels = c("Random networks", "Genetic network")) +
#  scale_y_continuous(expand = c(0, 0))
lgn34 <- cowplot::get_legend(p4)
distr_plots <- plot_grid(pcc_degree_dens + theme(legend.position = ""),
  ggdraw(p3 + theme(legend.position = "")),
  ggdraw(p4 + theme(legend.position = "")),
#  labels = c("C", "D", "E"), 
  nrow = 3
)
# distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
# nrow=2,rel_heights = c(0.9,0.1))
# ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
ggsave(glue("{figure_folder}/distr_plots.pdf"), plot= p4, width = 4, height = 10)

#plot_grid(deg_scatter_plots, distr_plots, dens_plots, nrow = 3, rel_heights = c(0.3, 0.4, .3))
#ggsave(glue("{figure_folder}fig3.pdf"), width = 10, height = 12)
```

```{r}
library(RColorBrewer)
col <- brewer.pal(n = 8, name = "Set1")
sensor_colors <- c(
'#dadaeb',
'#bcbddc',
'#9e9ac8',
'#807dba',
'#6a51a3',
'#4a1486'
)#col[1:4] # brewer.pal(n = 6, name = "Set1")
effector_colors <- c('#bae4b3',
'#74c476',
'#238b45')#col[5:8] # brewer.pal(n=3, name= "Set1_r")
```

```{python}
sensor_colors = r.sensor_colors
effector_colors = r.effector_colors
sensors_pcc = e_pcc_old.sensors_df
sensors_pcc['go_group'] = sensors_pcc['cluster_go_term']
sensors_pcc['go_group'] = ['None'  if pd.isna(i) else i for i in sensors_pcc['go_group'].tolist()]
effector_pcc = e_pcc.effectors_df
effector_pcc['go_group'] = effector_pcc['cluster_go_term']
effector_order = effector_pcc.groupby('go_group').clusters.median().sort_values().index.tolist()
sensor_order = sensors_pcc.groupby('go_group').clusters.median().sort_values().index.tolist()
#sensor_order.append(None)
```
# Dendrogram cluster network plots
```{python}
import copy
import scipy.cluster.hierarchy as sch
prs_mat = e_pcc.prs_mat
quantile_threshold =  0.95
method = 'ward'
metric = 'seuclidean'
q99 = np.quantile(prs_mat, quantile_threshold)
prs_mat_cl = copy.deepcopy(prs_mat)
prs_mat_cl[prs_mat_cl > q99] = q99
prs_mat_cl_orig = prs_mat_cl
# , optimal_ordering=True)
#row_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl), method=method)
# ,optimal_ordering=True)
#col_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl.T), method=method)

row_dist_orig = sch.distance.pdist((prs_mat),metric = metric)
col_dist_orig = sch.distance.pdist((prs_mat.T),metric = metric)
row_dist_orig_sqr = sch.distance.squareform(row_dist_orig)
col_dist_orig_sqr = sch.distance.squareform(col_dist_orig)

row_dist = sch.distance.pdist(prs_mat_cl,metric = metric)
col_dist = sch.distance.pdist(prs_mat_cl.T,metric = metric)

row_dist_sqr = sch.distance.squareform(row_dist)
col_dist_sqr = sch.distance.squareform(col_dist)

```

```{r}
cluster_method = 'ward.D2'
dist_row = as.dist(py$row_dist_sqr)
hclust_row = hclust(dist_row, cluster_method)
dist_col = as.dist(py$col_dist_sqr)
hclust_col = hclust(dist_col, cluster_method)
dend_row  <- as.dendrogram(hclust_row)
dend_col  <- as.dendrogram(hclust_col)
#effector_pcc <- get.subclusters.dendrogram(dend_row, effector_pcc)
#sensors_pcc <- get.subclusters.dendrogram(dend_col, sensors_pcc%>%select(-rowname))
library(dendextend)
png(glue('{figure_folder}/row_dendrogram_colored.png'),width=400,height=400)
dend_row_plot <- dend_row[[2]] %>% 
    set("branches_k_color", k = 4,value = effector_colors[c(4,2,3,1)]) %>% 
    set("labels", NA) %>%    # change labelsk
    as.ggdend()%>%
    ggplot()+
    coord_flip()#    plot(xlab="", sub="")}
dend_row_plot
dev.off()
png(glue('{figure_folder}/col_dendrogram_colored.png'),width=400,height=400)
dend_col_plot <-     dend_col[[1]] %>% 
    set("branches_k_color", k = 4,value = sensor_colors[c(3,2,4,1)]) %>% 
    set("labels", NA) %>%    # change labelsk
    as.ggdend()%>%
    ggplot()
dend_col_plot
dev.off()
```

```{python}
from matplotlib.lines import Line2D
pos = e_pcc_old.graph_gc.nodes('pos')
fig, ax = plt.subplots(figsize=(12,12))
legend_elements = [    ]
e_pcc.plot_network_spring(ax=ax,
                          node_size=1,
                          node_color='black',
 #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
                         edge_color='black')
#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=sensors_pcc.orf_name.values, node_size=200, pos=pos,
                          node_color='black',
                          node_shape='^',edgecolors='black',
                          linewidths=1)
for itr, i in enumerate(sensor_order):
    orf_names_to_plot = sensors_pcc.loc[sensors_pcc.go_group==i, 'orf_name'].tolist()
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=sensor_colors[itr],
                          node_shape='^',edgecolors='black',
                          linewidths=1)
    legend_elements.append(
        Line2D([0], [0], marker='^', color='black', label=f'Column cluster ({itr+1})',
                              markerfacecolor=sensor_colors[itr], markersize=12, linestyle="None")
    )
#nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='red', alpha=0.5)
ax.set_facecolor('white')
legend_elements.extend(
    [Line2D([0], [0], marker='o', color='black', label='Genes',
                              markerfacecolor='black', markersize=4, linestyle="None"),
#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
                              markerfacecolor='black', markersize=0, linestyle="-")]
#                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
#                              markerfacecolor='#018571', markersize=0, linestyle="-")]
)
lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))
plt.savefig(f'{r.figure_folder}tmp_nw_sens.png',bbox_inches='tight')

```

```{python}
from matplotlib.lines import Line2D
pos = e_pcc_old.graph_gc.nodes('pos')
fig, ax = plt.subplots(figsize=(12,12))
legend_elements = [    ]
e_pcc.plot_network_spring(ax=ax,
                          node_size=1,
                          node_color='black',
 #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
                         edge_color='black')
#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=effector_pcc.orf_name.values, node_size=100, pos=pos,
                      node_color='black',
                      node_shape='o')
for itr, i in enumerate(effector_order):
    orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=effector_colors[itr],
                          node_shape='o',edgecolors='black',
                          linewidths=1)
    legend_elements.append(
            Line2D([0], [0], marker='o', color='black', label=f'Row cluster ({itr+1})',
                                  markerfacecolor=effector_colors[itr], markersize=12, linestyle="None")
        )
ax.set_facecolor('white')
legend_elements.extend(
    [Line2D([0], [0], marker='o', color='black', label='Genes',
                              markerfacecolor='black', markersize=4, linestyle="None"),
#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
                              markerfacecolor='black', markersize=0, linestyle="-")]
#                   Line2D([0], [0], marker='o', color='blue', label= 'Effector-Effector edges',
 #                             markerfacecolor='#a6611a', markersize=0, linestyle="-")]
)
lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))

#nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
plt.savefig(f'{r.figure_folder}tmp_nw_eff.png',bbox_inches='tight')

from src.visualize.visualize import heatmap_annotated
#import src
#import importlib
#importlib.reload(src.visualize.visualize)
heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path=r.figure_folder, row_linkage=e_pcc.row_linkage, col_linkage=e_pcc.col_linkage, save_figure=True)#,
#                 row_colors=colors, col_colors=colors)

```

```{r}
library(coin)
df <- py$e_pcc$df%>%mutate(eff_group = as.factor(ifelse(orf_name%in%effector_pcc$orf_name,'eff','other')),
                    sens_group = factor(ifelse(orf_name%in%sensors_pcc$orf_name,'sens','other'),levels=c('sens','other')),
                    eff_norm = eff / nrow(.),
                    sens_norm = sens/ nrow(.))
pval_eff = pvalue(independence_test(eff~eff_group,df))
pval_sens = pvalue(independence_test(sens~sens_group,df))

eff_group_box <- df%>%ggplot(aes(x=eff_group,y=eff_norm))+
    geom_boxplot()+
  geom_signif(comparisons = list(c("eff", "other")), 
              map_signif_level=TRUE, y_position = 0.006)+
    xlab('')+
    ylab('Effectiveness')+
    scale_x_discrete(labels=c('Effectors','Others'))+
    theme_bw()
sens_group_box <- df%>%ggplot(aes(x=sens_group,y=sens_norm))+
    geom_boxplot()+
  geom_signif(comparisons = list(c("sens", "other")), 
              map_signif_level=TRUE, y_position = 0.0075)+
    xlab('')+
    ylab('Sensitivity')+
    scale_x_discrete(labels=c('Sensors','Others'))+
    theme_bw()+ylim(0,0.008)
#ggsave('tmp.png',sens_group_box)
heatmap_img <- glue('{figure_folder}prs_heatmap.png')%>%
    magick::image_read()
heatmap_img <- cowplot::ggdraw()+
    cowplot::draw_image(heatmap_img, width = 1)
eff_nw_img <- glue('{figure_folder}tmp_nw_eff.png') %>%
  magick::image_read() # %>%
eff_nw_img <- cowplot::ggdraw() +
  cowplot::draw_image(eff_nw_img, width = 1)
sens_nw_img <- glue('{figure_folder}tmp_nw_sens.png') %>%
  magick::image_read() # %>%
sens_nw_img <- cowplot::ggdraw() +
  cowplot::draw_image(sens_nw_img, width = 1)
cowplot::plot_grid(plot_grid(heatmap_img, plot_grid(sens_group_box, eff_group_box+ylim(0,0.007), nrow=2,labels=c('B','C')), nrow=1, rel_widths = c(0.7,0.3),labels=c('A','')),
                   plot_grid(dend_col_plot, sens_nw_img, nrow=1, rel_widths=c(0.2,.8), labels=c('D','E')),
                   plot_grid(dend_row_plot, eff_nw_img, nrow=1, rel_widths=c(0.2,.8), labels=c('F','G')), nrow=3, rel_heights=c(.5,.25,.25))
ggsave(glue('{figure_folder}fig1.pdf'),height=10,width=8)

```

# Go term network plots
```{python}
from matplotlib.lines import Line2D
pos = e_pcc_old.graph_gc.nodes('pos')
fig, ax = plt.subplots(figsize=(12,12))
legend_elements = [    ]
e_pcc.plot_network_spring(ax=ax,
                          node_size=1,
                          node_color='black',
 #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
                         edge_color='black')
#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=sensors_pcc.orf_name.values, node_size=200, pos=pos,
                          node_color='black',
                          node_shape='^',edgecolors='black',
                          linewidths=1)
for itr, i in enumerate(sensor_order):
    #print(i, effector_colors[itr])

    orf_names_to_plot = sensors_pcc.loc[sensors_pcc.go_group==i, 'orf_name'].tolist()
#    print(orf_names_to_plot)
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=sensor_colors[itr],
                          node_shape='^',edgecolors='black',
                          linewidths=1)
    legend_elements.append(
        Line2D([0], [0], marker='^', color='black', label=f'Column Cluster ({i})',
                              markerfacecolor=sensor_colors[itr], markersize=12, linestyle="None")
    )
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=effector_pcc.orf_name.values, node_size=100, pos=pos,
                      node_color='black',
                      node_shape='o')
for itr, i in enumerate(effector_order):
    orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=effector_colors[itr],
                          node_shape='o',edgecolors='black',
                          linewidths=1)
    if i == 'mito':
        lbl = 'Respiratory complex assembly'
    elif i == 'golgi':
        lbl = "Golgi vesicle transport"
    else:
        lbl = 'Chromosome segregation'
    legend_elements.append(
            Line2D([0], [0], marker='o', color='black', label=f'Effectors ({i})',
                                  markerfacecolor=effector_colors[itr], markersize=12, linestyle="None")
        )
nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='red', alpha=0.5)
ax.set_facecolor('white')
legend_elements.extend(
    [Line2D([0], [0], marker='o', color='black', label='Genes',
                              markerfacecolor='black', markersize=4, linestyle="None"),
#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
                              markerfacecolor='black', markersize=0, linestyle="-"),
                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
                              markerfacecolor='#018571', markersize=0, linestyle="-"),
                   Line2D([0], [0], marker='o', color='blue', label= 'Effector-Effector edges',
                              markerfacecolor='#a6611a', markersize=0, linestyle="-")]
)
lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))

nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
plt.savefig('tmp_nw.png',bbox_inches='tight')

```

```{r}
effector_pcc <- py$effector_pcc
sensors_pcc <- py$sensors_pcc %>% mutate(go_group = (as.character(go_group)), go_group = ifelse(go_group == "NaN", NA, go_group))%>%drop_na()
# library(tidyverse)
effector_pcc$go_group <- as.factor(effector_pcc$go_group)

# res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
# res.aov
effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
effector_eff_pval$res[effector_eff_pval$res$P.adj < 0.1, ]
effector_deg_pval <- FSA::dunnTest(deg ~ go_group, effector_pcc)
effector_deg_pval$res[effector_deg_pval$res$P.adj < 0.1, ]

eff_deg_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(
    values = effector_colors,
#    labels = c("Chromosome\nSegragetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")
  ) +
  xlab("") +
  ylab("Degree") +
  theme_bw() +
  geom_signif(
    comparisons = list(c("golgi", "chromatin"), c("golgi", "mito"), c("mito", "chromatin")),
    annotation = c("**", "***", "ns"),
    y_position = c(110, 115, 120)
  ) +
  theme(axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
  geom_boxplot() +
  # scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ggpubr::stat_compare_means(method = "kruskal.test") +
  scale_fill_manual(values = effector_colors) +
  ylab("Effectiveness") +
  theme_bw() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())
ggsave("tmp.png", plot = eff_eff_comp)

sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot() +
  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = sensor_colors) +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
    axis.text.x = element_blank(), legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  ) # , legend.spacing.y = unit(2,'cm'))
sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]

sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
  geom_boxplot() +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
#  geom_signif(
#    comparisons = list(
#      c("hexose metabolic\nprocess", "phenylalanine\ntransport"), c("tricarboxylic\nacid cycle", "phenylalanine\ntransport"),
#      c("phenylalanine\ntransport", "protein folding")
#    ),
#    annotation = c("**", "**", "*"), y_position = c(0.007, 0.0075, 0.008)
#  ) +
  #    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
  xlab("") +
  ylab("Sensitivity") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())

img <- "tmp_nw.png" %>%
  magick::image_read() # %>%
# magick::image_resize("570x380")

nw_img <- cowplot::ggdraw() +
  cowplot::draw_image(img, width = 1)
go_plots <- cowplot::plot_grid(
  sens_deg_comp + theme(legend.position = "none"),
  sens_sens_comp + theme(legend.position = "none"),
  cowplot::get_legend(sens_deg_comp), eff_deg_comp + theme(legend.position = "none"),
  eff_eff_comp + theme(legend.position = "none"),
  cowplot::get_legend(eff_deg_comp),
  ncol = 3, labels = c("B", "C", "", "D", "E", "")
)
combined <- cowplot::plot_grid(nw_img, go_plots, nrow = 2, rel_heights = c(0.4, 0.6), labels = c("A", ""))
ggsave(glue("{figure_folder}/fig6.png"), plot = combined, width = 9, height = 12)

```

### 2021-05-11 notebooks/paper_plots_1213_pcc_only.Rmd
more paper figures

@@
 use_condaenv("enm")
-setwd("../")
+#setwd("../")
 source("src/R/plot_density_prs.R")

### 2021-05-11 src/enm.py

@@ -332,6 +332,7 @@ class Enm():
             nx.set_edge_attributes(self.graph_gc,0,'weight')
         if node_weight is None:
             node_weight = (1/self.prs_mat_df.loc[source,:]).to_dict()
+#            node_weight[source] = 1
         if target is not None:
             distances = nx.single_source_dijkstra(self.graph_gc, source=source,target=target, weight=weight, node_weight=node_weight)
         else:

### 2021-05-11 src/features/effector_sensor_paths.py

@@ -1,0 +1,162 @@
+from matplotlib.lines import Line2D
+import qgrid
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import networkx as nx
+import numpy as np
+import pandas as pd
+import pickle
+import os
+import re
+import itertools as itr
+from src.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
+from src.enm import Enm
+from src.utils import *
+
+with open('data/interim/pcc_021521_withclustering//pcc_10_r.pickle','rb') as f:
+    e_pcc = pickle.load(f)
+e_pcc.get_sensor_effector(use_threshold=True)
+sensor_colors = [
+"#bfd3e6",
+"#9ebcda",
+"#8c96c6",
+"#8c6bb1",
+"#88419d",
+"#810f7c",
+"#4d004b"]
+effector_colors = ['#bae4b3',
+'#74c476',
+'#238b45']
+
+sensors_pcc = e_pcc.df.loc[e_pcc.df.sens>np.quantile(e_pcc.df.sens,0.99)]
+#sensor_sub_pcc = get_subnetwork(e_pcc.graph_gc, sensors_pcc.orf_name.values)
+#is_sensor = dict(zip(sensor_sub_pcc.nodes, [True if i in sensors_pcc.orf_name.values else False  for i in sensor_sub_pcc.nodes]))
+#nx.set_node_attributes(sensor_sub_pcc, is_sensor, 'is_sensor')
+sensor_go_terms_separate = [
+    'iron ion\ntransport',
+    'phenylalanine\ntransport',
+    None, 
+    None,
+    None,
+    None,
+    'tricarboxylic\nacid cycle', 
+    'hexose metabolic\nprocess',
+    'protein folding',
+    'mitochondria-nucleus\nsignaling pathway/TCA',
+    None,
+    None,
+    None,
+    None,
+    None,
+    None,
+    None,
+]
+sensor_connected_components = sorted([sorted(list(i)) for i in nx.connected_components(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name))], key=lambda x: x[0])
+sensor_go_terms= {}
+for i in range(len(sensor_go_terms_separate)):
+    for j in sensor_connected_components[i]:
+        sensor_go_terms[j] = sensor_go_terms_separate[i]
[…]

### 2021-05-11 src/utils.py

@@ -267,3 +267,56 @@ def jaccard_index(G, a,b):
     intersect = np.intersect1d(a_neigh,b_neigh)
     jaccard = len(intersect)/len(union)
     return jaccard
+
+def get_max_path(enm, target_cluster, source_cluster):
+    """Calculate max information carrying path between 2 clusters by finding all possible nodes and returns based on maximum distance
+
+    :param enm: this will be used to calculate prs weighted paths
+    :type enm: Enm object
+    :param target_cluster: cluster which contains possible target nodes
+    :type target_cluster: networkx graph
+    :param source_cluster: cluster which contains possible source nodes
+    :type source_cluster: networkx graph
+    """
+    wmin = np.inf
+    lmin = 0
+    for source in source_cluster.nodes:
+        for target in target_cluster.nodes:
+            w, l1 = enm.get_prs_weighted_path(source,target)
+            #print(w)
+            num_of_sources = len([i for i in l1 if i in source_cluster.nodes])
+            if num_of_sources > 1 :
+                continue
+            if w < wmin :
+                lmin=l1
+    #if lmin == 0 :
+     #   lmin = l1
+    return wmin, lmin
+def get_path_positions(enm, sensors_sub, effectors_sub):
+    """
+        calculate positions for effectors and sensors
+        choose a random source and target form these, respectively
+        get PRS path between source and target
+        put the nodes on the path linearly in between clusters
+        change the source and target positions based on the initial cluster positions
+
+        :param enm: this will be used to calculate prs weighted paths
+        :type enm: Enm object
+    """
+    sensor_pos = nx.spring_layout(sensors_sub,center=(5,0))
+    effector_pos = nx.spring_layout(effectors_sub, center=(5,10),scale=2)
+    wmin, l1 = get_max_path(enm, sensors_sub, effectors_sub)
+#    source = random.choice([i for i in effector_pos.keys()])
+#    target = random.choice([i for i in sensor_pos.keys()])
+    #e_pcc.prs_mat_df=pd.DataFrame(e_pcc.prs_mat,columns=e_pcc.nodes, index=e_pcc.nodes)
+#    l1 = e_pcc.get_prs_weighted_path(source,target)[1]
+    #l1.extend(['fum1', 'fbp1'])
+    sub = nx.induced_subgraph(enm.graph_gc, l1)
[…]

### 2021-05-12 notebooks/17-PRS_dendrogram_cluster_investigation-020921.Rmd
changed package references and added 3rules

@@
 setwd('../')
-#source('src/R/plot_density_prs.R')
-source('src/R/get.subclusters.dendrogram.R')
+#source('enm/R/plot_density_prs.R')
+source('enm/R/get.subclusters.dendrogram.R')
 library(RColorBrewer)
@@
 import itertools as itr
-from src.enm import Enm
-from src.utils import *
+from enm.enm import Enm
+from enm.utils import *
 import scipy.cluster.hierarchy as sch
@@
 
-# Import goatools functions from src/utils.py
-utils <- import('src.utils')
+# Import goatools functions from enm/utils.py
+utils <- import('enm.utils')
 create_goa = utils$create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/costanzo_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')

### 2021-05-12 notebooks/CSHL_plots_022621.Rmd
changed package references and added 3rules

@@
 setwd("../")
-source("src/R/plot_density_prs.R")
-source("src/R/get.subclusters.dendrogram.R")
+source("enm/R/plot_density_prs.R")
+source("enm/R/get.subclusters.dendrogram.R")
 ```
@@
 import itertools as itr
-from src.enm import Enm
+from enm.enm import Enm
 
@@
 
-from src.visualize.visualize import heatmap_annotated
-#import src
+from enm.visualize.visualize import heatmap_annotated
+#import enm
 #import importlib
-#importlib.reload(src.visualize.visualize)
+#importlib.reload(enm.visualize.visualize)
 heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path=r.figure_folder, row_linkage=e_pcc.row_linkage, col_linkage=e_pcc.col_linkage, save_figure=True)#,

### 2021-05-12 notebooks/paper_plots_0216_pcc_only_clustered.Rmd
changed package references and added 3rules

@@
 
-from src.visualize.visualize import heatmap_annotated
-#import src
+from enm.visualize.visualize import heatmap_annotated
+#import enm
 #import importlib
-importlib.reload(src.visualize.visualize)
+importlib.reload(enm.visualize.visualize)
 heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path=r.figure_folder, row_linkage=e_pcc.row_linkage, col_linkage=e_pcc.col_linkage, save_figure=True)#,

### 2021-05-12 notebooks/paper_plots_0909.Rmd
changed package references and added 3rules

@@
 setwd('../')
-source('src/R/plot_density_prs.R')
+source('enm/R/plot_density_prs.R')
 ```

### 2021-05-12 notebooks/paper_plots_1213_pcc_only.Rmd
changed package references and added 3rules

--- 2021-04-05 notebooks/paper_plots_1213_pcc_only.Rmd
@@
 use_condaenv("enm")
-setwd("../")
-source("src/R/plot_density_prs.R")
+#setwd("../")
+source("enm/R/plot_density_prs.R")
 figure_path = 'reports/figures/0404_paperfigure_sensors/'

### 2021-05-12 enm/data/huri_psn.py

@@ -1,10 +1,10 @@
-import src
+import enm
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 import networkx as nx
-from src.enm import *
-from src.utils import *
+from enm.enm import *
+from enm.utils import *
 
 
 #huri = Enm('huri')

### 2021-05-12 enm/features/deletion_analysis.py

@@ -16,8 +16,8 @@ from mlxtend.evaluate import permutation_test
 import pickle
 import random
 from tqdm import tqdm
-from src.utils import sequential_deletion
-from src.enm import Enm
+from enm.utils import sequential_deletion
+from enm.enm import Enm
 
 with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
     e_pcc = pickle.load(f)

### 2021-05-12 enm/features/effector_sensor_paths.py

@@ -9,9 +9,9 @@ import pickle
 import os
 import re
 import itertools as itr
-from src.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
-from src.enm import Enm
-from src.utils import *
+from enm.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
+from enm.enm import Enm
+from enm.utils import *
 
 with open('data/interim/pcc_021521_withclustering//pcc_10_r.pickle','rb') as f:
     e_pcc = pickle.load(f)

### 2021-05-12 enm/features/gi_go.py

@@ -1,11 +1,11 @@
-import src
+import enm
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 import networkx as nx
 import pickle
-from src.enm import *
-from src.utils import *
+from enm.enm import *
+from enm.utils import *
 
 with open('data/interim/gi_1205_0.2/gi_100.pickle','rb') as f:
     e_gi = pickle.load(f)

### 2021-05-12 enm/features/huri_go.py

@@ -1,11 +1,11 @@
-import src
+import enm
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 import networkx as nx
 import pickle
-from src.enm import *
-from src.utils import *
+from enm.enm import *
+from enm.utils import *
 
 with open('data/interim/huri_0916/huri.pickle','rb') as f:
     e_huri = pickle.load(f)

### 2021-05-12 enm/features/huri_psn.py

@@ -1,12 +1,12 @@
-import src
+import enm
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 import networkx as nx
 import pickle
 from tqdm import tqdm
-from src.enm import *
-from src.utils import *
+from enm.enm import *
+from enm.utils import *
 
 
 

### 2021-05-12 enm/features/pcc_go.py

@@ -1,11 +1,11 @@
-import src
+import enm
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 import networkx as nx
 import pickle
-from src.enm import *
-from src.utils import *
+from enm.enm import *
+from enm.utils import *
 
 with open('data/interim/pcc_0909/pcc.pickle','rb') as f:
     e_pcc = pickle.load(f)

### 2021-05-12 enm/features/run_go.py

@@ -1,8 +1,8 @@
 import pickle
 import numpy as np
 import pandas as pd
-from src.enm import Enm
-from src.utils import create_goea
+from enm.enm import Enm
+from enm.utils import create_goea
 from goatools.obo_parser import GODag
 from goatools.anno.genetogo_reader import Gene2GoReader
 from goatools.anno.gaf_reader import GafReader

### 2021-05-12 enm/features/sensor_connectivity.py

@@ -8,8 +8,8 @@ import pickle
 import os
 import re
 import itertools as itr
-from src.enm import Enm
-from src.utils import *
+from enm.enm import Enm
+from enm.utils import *
 
 with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
     e_pcc = pickle.load(f)

### 2021-05-12 enm/features/yuri_enm.py

@@ -1,10 +1,10 @@
-import src
+import enm
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 import networkx as nx
-from src.enm import *
-from src.utils import *
+from enm.enm import *
+from enm.utils import *
 from Bio import SeqIO
 
 

### 2021-05-12 enm/features/yuri_go.py

@@ -1,11 +1,11 @@
-import src
+import enm
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
 import networkx as nx
 import pickle
-from src.enm import *
-from src.utils import *
+from enm.enm import *
+from enm.utils import *
 
 with open('data/interim/yuri_0916/yuri.pickle','rb') as f:
     e_yuri = pickle.load(f)

### 2021-05-12 enm/visualize/paper_figures.py

@@ -7,7 +7,7 @@ import pickle
 import os
 import re
 import itertools as itr
-from src.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
+from enm.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
 from mlxtend.evaluate import permutation_test 
 
 # Random collectivity

### 2021-05-12 notebooks/03-PRS_costanzo_07132020.py

@@ -29,8 +29,8 @@ import pickle
 import os
 import re
 import itertools as itr
-from src.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
-from src.enm import Enm
+from enm.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
+from enm.enm import Enm
 
 # %%
 import statsmodels.api as sm
@@ -337,7 +337,7 @@ val  = plot_subnetwork(e_pcc.graph_gc, pos=e_pcc.graph_gc.nodes('pos'),attr='sen
 e_pcc.plot_network_spring(node_color = e_pcc.df.sens.values,facecolor='white',figsize=(10,10),node_size=50)
 
 # %%
-from src.visualize.visualize import plot_network_spring
+from enm.visualize.visualize import plot_network_spring
 
 # %%
 

### 2021-05-12 scripts/pcc.py

@@ -1,0 +1,31 @@
+import numpy as np
+import networkx as nx
+import pickle
+from enm.enm import *
+from enm.utils import *
+
+network_file = snakemake.input['network_file']
+output_path = snakemake.params.output_path
+#figure_path = 'reports/figures/pcc_0603'
+enm = Enm('enm')
+enm.read_network(network_file,sep=',')
+enm.gnm_analysis(normalized=False)
+
+neigbor_btw = []
+neighbor_degree = []
+for i in enm.graph_gc.nodes:
+    neigbor_btw.append(np.average([enm.df.loc[enm.df.orf_name==a,'btw'].values for a in nx.neighbors(enm.graph_gc,i)]))
+    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
+
+enm.df['neighbor_btw'] = neigbor_btw
+enm.df['neighbor_degree'] = neighbor_degree
+
+#enm.figure_path=figure_path
+enm.output_path = output_path
+#enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
+enm.spring_pos()
+
+with open(f"{enm.output_path}/pcc_10.pickle",'wb') as f:
+    pickle.dump(enm,f, protocol=4)
+
+

### 2021-05-12 scripts/read_costanzo_data.py

@@ -1,0 +1,13 @@
+import numpy as np
+import pandas as pd
+input_file = snakemake.input[0]#"data/raw/Data File S3. Genetic interaction profile similarity matrices/cc_ALL.txt"
+output_file=snakemake.output[0]
+
+df = pd.read_csv(input_file,'\t',index_col=[0,1], header=[0,1])
+
+df_long = df.melt(ignore_index=False, col_level=0)
+
+df_long_renamed = df_long.reset_index(inplace=False).rename(columns = {'level_0':'gene1','level_1':'gene1_sys', 'variable':'gene2','value':'pcc'})
+
+df_long_renamed.loc[df_long_renamed.pcc>=0.2,['gene1','gene2','pcc']].to_csv(output_file, index=False,float_format="%.6f")
+#df = df.rename(columns = {'index':'new column name'})

### 2021-05-12 scripts/rewiring.py

@@ -1,0 +1,29 @@
+import numpy as np
+import networkx as nx
+import pickle
+from enm.enm import *
+from enm.utils import *
+
+gaf = snakemake.input['gaf']
+obo = snakemake.input['obo']
+background_file = snakemake.input['background_file']
+sgd_info = snakemake.input['sgd_info']
+pickle_file = snakemake.input[0]
+with open(pickle_file,'rb') as f:
+    enm = pickle.load(f)
+
+print('clustering')
+enm.get_sensor_effector(use_threshold=False)
+
+print('go analysis')
+goea, geneid2name = create_goea(gaf = gaf, obo_fname=obo, 
+                                background=background_file, sgd_info_tab = sgd_info)
+enm.analyze_components_biology(goea, geneid2name, True)
+enm.analyze_components_biology(goea, geneid2name, False)
+
+print('rewiring')
+#Don't run
+enm.simulate_rewire(output_name=snakemake.output['rewired_dataframe'],save=True, normalized=False,sim_num=snakemake.params.n_sim)
+
+with open(snakemake.output['pickle_file'],'wb') as f:
+    pickle.dump(enm,f, protocol=4)

### 2021-05-12 tests/test_enm.py

@@ -1,5 +1,5 @@
 import pytest
-from src.enm import Enm
+from enm.enm import Enm
 import numpy as np
 import networkx as nx
 import matplotlib.pyplot as plt

### 2021-05-19 notebooks/23-Figure2-051321.Rmd
added rmd for figure 2and3

---
title: "23-Figure2-051321"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r, message=FALSE,warning=FALSE}
library(tidyverse)
library(glue)
library(cowplot)
library(ggpubr)
library(ggsignif)
source("../enm/R/plot_density_prs.R")#paste function in this file
```

# Load input dataframe
```{r}
#df_filename <-snakemake$input$df_filename
#random_df_filename <-snakemake$input$df_filename
pcc_df <- read_csv('../data/interim/pcc_df.csv')
pcc_df_random <- read_csv('../data/interim/pcc_df_random.csv')
pcc_df <- pcc_df %>%
  mutate(data = "pcc") %>%
  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real") %>%
  bind_rows(
    pcc_df_random %>% mutate(data = "pcc") %>% mutate(sens_norm = sens / nrow(pcc_df), eff_norm = eff / nrow(pcc_df), group = "random")
  ) %>%
  mutate(group = fct_relevel(group, c("real", "random")))

```

# Figure 2, G and F
```{r}
pcc_eff_dens <-
  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness")
dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
pcc_eff_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
    coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
    scale_x_continuous(
      breaks = scales::trans_breaks("log10", function(x) 10^x),
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    )) #+
#   cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity") + theme(legend.position = "none")) #+
#        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
pcc_dens_comb <- cowplot::plot_grid(pcc_eff_dens + theme(legend.position = "none"),
  pcc_sensitivity_dens + theme(legend.position = "none"),
  #+theme(legend.position='none'),
  labels = c("F", "G"), ncol = 2
)
# pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
# dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
#dens_plots <- 
  pcc_dens_comb

```

# Figure2 A,B
```{r}
real_random_labels <- c("PSN", "Rewired\nnetwork")
names(real_random_labels) <- c("real", "random")
pcc_deg_eff <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = eff_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Effectiveness") +
  xlab("Degree") +
  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
pcc_deg_sens <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = sens_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Sensitivity") +
  xlab("Degree") +
  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
  labels = c("A", "B"),
  ncol = 2
)
deg_scatter_plots
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig2.png", plot = deg_scatter_plots, width = 10, height = 10)
```

# Figure2 C,D,E
```{r}
pcc_rewire_df <- pcc_df_random%>%group_by(random_id)%>%
  summarise(
    eff_deg_pearson = cor.test(eff,deg)$estimate,
    sens_deg_spearman = cor.test(sens,deg, method="spearman")$estimate
  )
rewire_df <- pcc_rewire_df %>% mutate(data = "pcc")
network_labels <- c("Yeast GI Profile Similarity")
facet_labels <- network_labels
names(facet_labels) <- c("pcc")
combined_rewire_df <- rewire_df %>%
  select(data, eff_deg_pearson, sens_deg_spearman) %>%
  mutate(type = "random") %>%
  bind_rows(
    data.frame(
      sens_deg_spearman = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$sens, method = "spearman")),
      eff_deg_pearson = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$eff, method = "pearson")), type = "real", data = c("pcc")
    )
  ) %>%
  mutate(data = fct_relevel(data, c("pcc")))

p3 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = eff_deg_pearson, color = type, y = ..scaled..), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = eff_deg_pearson, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Effectiveness degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines")) +
  scale_y_continuous(expand = c(0, 0))
p4 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = sens_deg_spearman, y = ..scaled.., color = type), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = sens_deg_spearman, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Sensitivity degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines"), legend.position = "bottom") +
  scale_color_discrete(labels = c("Random networks", "Genetic network")) +
  scale_y_continuous(expand = c(0, 0))
lgn34 <- cowplot::get_legend(p4)
distr_plots <- plot_grid(pcc_degree_dens + theme(legend.position = ""),
  ggdraw(p3 + theme(legend.position = "")),
  ggdraw(p4 + theme(legend.position = "")),
  labels = c("C", "D", "E"), nrow = 1
)
# distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
# nrow=2,rel_heights = c(0.9,0.1))
# ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
plot_grid(deg_scatter_plots, distr_plots, dens_plots, nrow = 3, rel_heights = c(0.3, 0.4, .3))
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig3.pdf", width = 10, height = 12)
```

### 2021-05-19 notebooks/25-Figure3-051821.Rmd
added rmd for figure 2and3

---
title: "25-Figure3-051821"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r, message=FALSE,warning=FALSE}
library(tidyverse)
library(glue)
library(cowplot)
library(ggpubr)
library(ggsignif)
source("../enm/R/plot_density_prs.R")#paste function in this file
```

# Sensor connectivity and neighbor degree

```{r}
sensor_connectivity_df <- read_csv("../data/interim/sensor_connectivity_df.csv") %>%
  #mutate(data = fct_relevel(data, c("pcc", "gi", "yuri", "huri"))) %>%
  filter(data == "pcc")
pcc_df <- read_csv('../data/interim/pcc_df.csv')
# effector_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/effector_connectivity_df.csv')%>%
#    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))%>%filter(data=='pcc')
# effector_connectivity_plot <-
#    ggplot()+
##    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
##    geom_boxplot()+
##    geom_jitter()+
#    geom_density(data =effector_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
#    geom_vline(data =effector_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
#    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
#    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
#    theme_bw()+
#    scale_color_discrete(labels=c('Random sampled set', 'Effectors'))+
#    theme(legend.position='bottom')+
#    scale_y_continuous(expand = c(0, 0))
eff_neighbor_degree_plot <- pcc_df %>%
  #filter(group == "real") %>%
  #group_by(data) %>%
  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real")%>%
  mutate(is_effector = factor(ifelse(eff_norm > quantile(eff_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
  #    mutate(is_effector = fct_relevel(is_effector,c(TRUE,FALSE)))%>%
  ggplot(aes(x = is_effector, y = log(neighbor_degree))) +
  #    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
  #    geom_point()+
  geom_boxplot() +
  theme_bw() +
  ylab("Log(Average neighbor degree)") +
  xlab("") +
  stat_compare_means() +
  scale_x_discrete(labels = c("Effector", "Not Effector"))
sensor_connectivity_plot <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = sensor_connectivity_df %>% filter(type != "real"), aes(x = ratio, color = type)) +
  geom_vline(data = sensor_connectivity_df %>% filter(type == "real"), aes(xintercept = ratio, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Ratio of between group edges\nto outgroup edges") +
  theme_bw() +
  scale_color_discrete(labels = c("Random sampled set", "Sensors")) +
  theme(legend.position = "bottom") +
  scale_y_continuous(expand = c(0, 0))
sensor_connectivity_plot
neighbor_degree_plot <- combined_df %>%
  filter(group == "real") %>%
  group_by(data) %>%
  mutate(is_sensor = factor(ifelse(sens_norm > quantile(sens_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
  #    mutate(is_sensor = fct_relevel(is_sensor,c(TRUE,FALSE)))%>%
  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
  #    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
  #    geom_point()+
  geom_boxplot() +
  theme_bw() +
  ylab("Log(Average neighbor degree)") +
  xlab("") +
  stat_compare_means() +
  scale_x_discrete(labels = c("Sensor", "Not Sensor"))
sensor_conn_lgn <- get_legend(sensor_connectivity_plot + theme(legend.position = "right"))
plot_grid(neighbor_degree_plot,
  sensor_connectivity_plot + theme(legend.position = "none"), # effector_connectivity_plot,
  eff_neighbor_degree_plot, sensor_conn_lgn,
  nrow = 2,
  labels = c("A", "B", "C", "")
) # %>%
#    plot_grid(, labels=c('','C'),nrow=2, rel_widths=c(2,1))
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig5.pdf", width = 6, height = 6)
sensor_connectivity_df$ratio[sensor_connectivity_df$type=='random']/mean(sensor_connectivity_df$ratio[sensor_connectivity_df$type=='random'])
```

### 2021-05-19 enm/utils.py

@@ -18,7 +18,7 @@ def create_goea(gaf = '../data/raw/ontology/sgd.gaf', obo_fname = '../data/raw/o
     
     #background='../data/raw/ontology/sgd_costanzogenes'
     obodag = GODag(obo_fname)
-    objanno = GafReader(gaf)
+    objanno = GafReader(gaf,namespaces=set(['BP']))
 #    ns2assoc = objanno.get_ns2assc()
 
     ns2assoc_excl = objanno.get_ns2assc( ev_exclude = {'HGI' , 'IGI'})
@@ -35,7 +35,7 @@ def create_goea(gaf = '../data/raw/ontology/sgd.gaf', obo_fname = '../data/raw/o
         obodag,  # Ontologies
         propagate_counts=False,
         alpha=0.1,  # default significance cut-off
-        methods=['fdr', 'bonferroni','fdr_bh'], prt=None)
+        methods=['fdr','fdr_bh'], prt=None)
 
     return goeaobj, geneid2name#, objanno, ns2assoc, ns2assoc_excl
 
@@ -123,7 +123,7 @@ def query_goatools(query, goea,geneid2name):
     """
     query_gene_ids = [key for key,value in geneid2name.items() if value in query.loc[:,'Systematic gene name'].unique()]
     goea_res_all = goea.run_study(query_gene_ids)
-    goea_res_sig = [r for r in goea_res_all if r.p_fdr <0.1]
+    goea_res_sig = [r for r in goea_res_all if r.p_fdr<0.1]
     go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
     return go_df_sensor
 
@@ -235,7 +235,7 @@ def get_in_to_out_edge_ratio(G, nodes_df):
 
 def get_random_in_to_out_ratio(gnm_df, df , G):
     random_ratio_list = []
-    for i in range(100):
+    for i in range(10000):
         rand_nodes = sample_nodes_with_degree(gnm_df, df)
     #    print(len(rand_nodes))
         random_ratio_list.append(get_in_to_out_edge_ratio(G, rand_nodes))

### 2021-05-19 scripts/connectivity.py

@@ -1,7 +1,7 @@
 import pandas as pd
 import pickle 
 import itertools as itr
-from enm.enm import Enm
+from enm.Enm import Enm
 from enm.utils import *
 
 with open(snakemake.input[0],'rb') as f:

### 2021-05-19 notebooks/23-Figure2-051321.Rmd
figure2 rmarkdown

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
 ```
@@
 library(ggsignif)
-source("../enm/R/plot_density_prs.R")#paste function in this file
+
+plot_density_prs <- 			# 
+    function
+(
+ 	df , x , xlab= 'Effectiveness', ylab='Density', coord_trans='log10', linesize = 1
+)
+{
+    color_pal <- c('#00BFC4','#F8766D')
+dens_plot <- 
+    ggplot()+
+    #facet_grid(rows=vars(data))+
+#    geom_density()+
+    geom_line(data= df%>%filter(group=='real'),
+               aes(x={{x}} ,y=..scaled.., color=group),
+               stat = 'density')+#, binwidth = 0.1) + 
+    geom_line(data= df%>%filter(group=='random'),
+               aes(x={{x}} ,y=..scaled..,fill=random_id, color=group),linetype='dashed',
+               stat = 'density' ,show.legend=F)+#, binwidth = 0.1) + 
+    geom_vline(data= df%>%filter(group=='real')%>%mutate(g = T),aes(xintercept = mean({{x}}), linetype='Real'),color=color_pal[1],size=linesize, show.legend=NA)+
+    geom_vline(data= df%>%filter(group=='random')%>%mutate(g = F),aes(xintercept = mean({{x}}),linetype='Random', group=random_id),color=color_pal[2], size=linesize,show.legend=NA)+
+    scale_linetype_manual(name = "Limits", labels = c("real", "random"), values = c("Real" = 3, "Random" = 3)) +
+    guides(colour=guide_legend(override.aes = list(linetype=1)),
+           linetype=guide_legend(override.aes=list(colour=color_pal)))+
+    theme_bw()+
+    ylab(ylab)+
+    xlab(xlab)+
+    coord_trans(x = coord_trans)+
+scale_x_continuous(
+   breaks = scales::trans_breaks("log10", function(x) 10^x),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))
+ ) +
+    scale_color_discrete(labels=c('Rewired\nnetworks','PSN'))+
+theme(legend.text = element_text(margin = margin(b = 10)), panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
+dens_plot
+}
+
 ```
@@
 pcc_df <- read_csv('../data/interim/pcc_df.csv')
-pcc_df_random <- read_csv('../data/interim/pcc_df_random.csv')
+pcc_df_random <- read_csv('../data/interim/pcc_df_random_100.csv')%>%mutate(random_id=factor(random_id))
 pcc_df <- pcc_df %>%
@@
   mutate(group = fct_relevel(group, c("real", "random")))
-
-```
-
-# Figure 2, G and F
-```{r}
-pcc_eff_dens <-
-  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness")
-dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
-pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
-#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
-pcc_eff_dens <-
-  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
-    coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
-    scale_x_continuous(
-      breaks = scales::trans_breaks("log10", function(x) 10^x),
-      labels = scales::trans_format("log10", scales::math_format(10^.x))
-    )) #+
-#   cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
-# annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
-pcc_sensitivity_dens <-
-  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity") + theme(legend.position = "none")) #+
-#        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
-# title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
-pcc_dens_comb <- cowplot::plot_grid(pcc_eff_dens + theme(legend.position = "none"),
-  pcc_sensitivity_dens + theme(legend.position = "none"),
-  #+theme(legend.position='none'),
-  labels = c("F", "G"), ncol = 2
-)
-# pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
-# dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
-#dens_plots <- 
-  pcc_dens_comb
 
@@
 # ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
-plot_grid(deg_scatter_plots, distr_plots, dens_plots, nrow = 3, rel_heights = c(0.3, 0.4, .3))
+distr_plots
+#plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.4, .3))
+#
 #ggsave("reports/figures/paper_figures_0202_pcc_only/fig3.pdf", width = 10, height = 12)
 ```
+
+# Figure 2, G and F
+```{r}
+pcc_eff_dens <-
+  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness")
+dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
+pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
+#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
+pcc_eff_dens <-
+  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
+    coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
+    scale_x_continuous(
+      breaks = scales::trans_breaks("log10", function(x) 10^x),
+      labels = scales::trans_format("log10", scales::math_format(10^.x))
+    )) #+
+#   cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
+# annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
+pcc_sensitivity_dens <-
+  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity") + theme(legend.position = "none")) #+
+#        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
+# title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
+pcc_dens_comb <- cowplot::plot_grid(pcc_eff_dens + theme(legend.position = "none"),
+  pcc_sensitivity_dens + theme(legend.position = "none"),
+  #+theme(legend.position='none'),
+  labels = c("F", "G"), ncol = 2
+)
+# pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
+# dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
+#dens_plots <- 
+  pcc_dens_comb
+
+```

### 2021-05-22 notebooks/23-Figure2-051321.Rmd
edited README finished notebooks for figure creation

@@
 lgn34 <- cowplot::get_legend(p4)
+
+pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
 distr_plots <- plot_grid(pcc_degree_dens + theme(legend.position = ""),
@@
 dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
-pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
 #  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)

### 2021-05-22 notebooks/25-Figure3-051821.Rmd
edited README finished notebooks for figure creation

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
 ```
@@
 library(ggsignif)
-source("../enm/R/plot_density_prs.R")#paste function in this file
+library(RColorBrewer)
+col <- brewer.pal(n = 9, name = "Set1")
+sensor_colors <- col[2:6] # brewer.pal(n = 6, name = "Set1")
+effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
 ```
 
-# Sensor connectivity and neighbor degree
+# Load necessary data
+```{r}
 
+sensor_connectivity_df <- read_csv("../data/interim/sensor_connectivity_df.csv") 
+pcc_df <- read_csv('../data/interim/pcc_df.csv')
+sensors_pcc <- read_csv('../data/interim/sensors_df.csv')%>% mutate(go_group = (as.character(go_group)), go_group = ifelse(go_group == "NULL", NA, go_group))
+effector_pcc <- read_csv('../data/interim/effectors_df.csv')
+
+# Ranked groups GO enrichment results
+rwr_row <- read_csv('../data/interim/rwr_ranked_goa_rows.csv')%>%mutate(data = 'rwr_row')
+prs_row <- read_csv('../data/interim/prs_ranked_goa_rows.csv')%>%mutate(data = 'prs_row')
+rwr_column <- read_csv('../data/interim/rwr_ranked_goa_columns.csv')%>%mutate(data = 'rwr_col')
+prs_column <- read_csv('../data/interim/prs_ranked_goa_columns.csv')%>%mutate(data = 'prs_col')
+go_combined <- data.table::rbindlist(list(rwr_row,prs_row,rwr_column,prs_column))
+```
+# Figure3
+## A
 ```{r}
-sensor_connectivity_df <- read_csv("../data/interim/sensor_connectivity_df.csv") %>%
-  #mutate(data = fct_relevel(data, c("pcc", "gi", "yuri", "huri"))) %>%
-  filter(data == "pcc")
-pcc_df <- read_csv('../data/interim/pcc_df.csv')
-# effector_connectivity_df <- read_csv('data/interim/sensor_connectivity_1205/effector_connectivity_df.csv')%>%
-#    mutate(data= fct_relevel(data, c('pcc','gi','yuri','huri')))%>%filter(data=='pcc')
-# effector_connectivity_plot <-
-#    ggplot()+
-##    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
-##    geom_boxplot()+
-##    geom_jitter()+
-#    geom_density(data =effector_connectivity_df%>%filter(type!='real'),aes(x=ratio,color=type, y=..scaled..),linetype = "dashed")+
-#    geom_vline(data =effector_connectivity_df%>%filter(type=='real'),aes(xintercept=ratio,color=type))+
-#    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
-#    ylab('Density')+xlab('Ratio of between group edges to outgroup edges')+
-#    theme_bw()+
-#    scale_color_discrete(labels=c('Random sampled set', 'Effectors'))+
-#    theme(legend.position='bottom')+
-#    scale_y_continuous(expand = c(0, 0))
-eff_neighbor_degree_plot <- pcc_df %>%
-  #filter(group == "real") %>%
-  #group_by(data) %>%
-  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real")%>%
-  mutate(is_effector = factor(ifelse(eff_norm > quantile(eff_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
-  #    mutate(is_effector = fct_relevel(is_effector,c(TRUE,FALSE)))%>%
-  ggplot(aes(x = is_effector, y = log(neighbor_degree))) +
-  #    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
-  #    geom_point()+
+sensor_neighbor_degree_plot <- pcc_df %>%
+  mutate(is_sensor = factor(ifelse(sens > quantile(sens, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
+  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
   geom_boxplot() +
@@
   stat_compare_means() +
-  scale_x_discrete(labels = c("Effector", "Not Effector"))
+  scale_x_discrete(labels = c("Sensor", "Not Sensor"))
+  sensor_neighbor_degree_plot
+
+```
+
+## B
+```{r}
 sensor_connectivity_plot <-
   ggplot() +
-  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
-  #    geom_boxplot()+
-  #    geom_jitter()+
   geom_density(data = sensor_connectivity_df %>% filter(type != "real"), aes(x = ratio, color = type)) +
@@
   sensor_connectivity_plot
-neighbor_degree_plot <- combined_df %>%
-  filter(group == "real") %>%
-  group_by(data) %>%
-  mutate(is_sensor = factor(ifelse(sens_norm > quantile(sens_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
-  #    mutate(is_sensor = fct_relevel(is_sensor,c(TRUE,FALSE)))%>%
-  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
-  #    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
-  #    geom_point()+
+```
+
+## D
+```{r}
+
+sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
+  geom_boxplot(
+    outlier.shape=NA) +
+  xlab("") +
+  ylab("Degree") +
+  scale_fill_manual(values = c(sensor_colors[1:5],'black')) +
+  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
+  theme_bw() +
+  theme(
+        axis.title.y=element_text(size=14),
+        axis.text.y=element_text(size=10),
+    axis.text.x = element_blank(), legend.title = element_blank(),
+    legend.text = element_text(margin = margin(t = 10, b = 10))
+  )+scale_y_log10()
+sens_deg_comp
+
+```
+
+## E
+```{r}
+
+sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
+sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
+sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]
+
+sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
+  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
+  geom_boxplot() +
+  geom_signif(
+    comparisons = list(
+      c("hexose metabolic process", "phenylalanine transport"), c("tricarboxylic acid cycle", "phenylalanine transport")#,
+      #c("phenylalanine\ntransport", "protein folding")
+    ),
+    annotation = c("**", "**"), y_position = c(0.007, 0.0075)#, 0.008)
+  ) +
+  xlab("") +
+  ylab("Sensitivity") +
+  scale_fill_manual(values = sensor_colors) +
+  theme_bw() +
+  theme(
+        axis.title.y=element_text(size=14),
+        axis.text.y=element_text(size=10),
+        axis.text.x = element_blank(), legend.title = element_blank())
+
+sens_sens_comp
+```
+
+# Figure4
+## A
+```{r}
+eff_neighbor_degree_plot <- pcc_df %>%
+  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real")%>%
+  mutate(is_effector = factor(ifelse(eff_norm > quantile(eff_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
+  ggplot(aes(x = is_effector, y = log(neighbor_degree))) +
   geom_boxplot() +
@@
   stat_compare_means() +
-  scale_x_discrete(labels = c("Sensor", "Not Sensor"))
-sensor_conn_lgn <- get_legend(sensor_connectivity_plot + theme(legend.position = "right"))
-plot_grid(neighbor_degree_plot,
-  sensor_connectivity_plot + theme(legend.position = "none"), # effector_connectivity_plot,
-  eff_neighbor_degree_plot, sensor_conn_lgn,
-  nrow = 2,
-  labels = c("A", "B", "C", "")
-) # %>%
-#    plot_grid(, labels=c('','C'),nrow=2, rel_widths=c(2,1))
-#ggsave("reports/figures/paper_figures_0202_pcc_only/fig5.pdf", width = 6, height = 6)
-sensor_connectivity_df$ratio[sensor_connectivity_df$type=='random']/mean(sensor_connectivity_df$ratio[sensor_connectivity_df$type=='random'])
+  scale_x_discrete(labels = c("Effector", "Not Effector"))
+eff_neighbor_degree_plot
 ```
+
+## C
+```{r}
+effector_pcc$go_group <- as.factor(effector_pcc$go_group)
+
+# res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
+# res.aov
+effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
+effector_eff_pval$res[effector_eff_pval$res$P.adj < 0.1, ]
+effector_deg_pval <- FSA::dunnTest(deg ~ go_group, effector_pcc)
+effector_deg_pval$res[effector_deg_pval$res$P.adj < 0.1, ]
+
+eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_reorder(go_group, eff),go_group=fct_relevel(go_group,'Others',after=Inf)),
+                       aes(x = go_group, y = deg, fill = go_group)) +
+  geom_boxplot(outlier.shape = NA) +
+  scale_fill_manual(
+    values = c(effector_colors,'black'),
+    labels = c("Chromosome\nSegregetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
+  ) +
+  xlab("") +
+  ylab("Degree") +
+  theme_bw() +
+  geom_signif(
+    comparisons = list(c("golgi", "chromatin"), c("golgi", "mito"), c("mito", "chromatin")),
+    annotation = c("**", "***", "ns"),
+    y_position = c(115, 120, 130)
+  ) +
+  theme(
+       axis.text.y=element_text(size=10),
+        axis.title.y=element_text(size=14), axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
+eff_deg_comp
+```
+
+## D
+```{r}
+
+eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
+  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
+  geom_boxplot() +
+  xlab("") +
+  ggpubr::stat_compare_means(method = "kruskal.test") +
+  scale_fill_manual(values = effector_colors,
+  labels = c("Chromosome\nSegregetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
+  ylab("Effectiveness") +
+  theme_bw() +
+  theme(
+        axis.text.y=element_text(size=10),
+        axis.title.y=element_text(size=14),axis.text.x = element_blank(), legend.title = element_blank())
+eff_eff_comp
+```
+
+# Figure 5
+## B
+```{r}
+ci <- function(p,n){
+   sd = sqrt(p*(1-p)/n)
+   ci = 1.96*sd
+   ci
+}
+# New facet label names for dose variable
+axis.labs <- c("Row-based", "Column-based")
+names(axis.labs) <- c("row", "col")
+go_summarised <- go_combined%>%
+  group_by(data)%>%
+  summarise(positives=n_distinct(orf_name_id))%>%
+  mutate(n_tot=5183, prop = positives/n_tot, ci_min=prop-ci(prop,n_tot),ci_max=prop+ci(prop,n_tot))%>%
+  separate(data,into=c('method','axis'))%>%
+  mutate(axis=factor(axis,levels=c('row','col')))
+
+p_val_row  <- go_summarised%>%
+  mutate(negatives = n_tot-positives)%>%
+  dplyr::filter(axis=="row")%>%
+  select(positives,negatives)%>%
+  as.matrix()%>%
+  prop.test(correct=FALSE)
+p_val_col <- go_summarised%>%
+  mutate(negatives = n_tot-positives)%>%
+  dplyr::filter(axis=="col")%>%
+  select(positives,negatives)%>%
+  as.matrix()%>%
+  prop.test(correct=FALSE)
+
+annotation_df <- data.frame(
+  axis = factor(c("row", "col")),
+  start = c("prs", "prs"),
+  end = c("rwr", "rwr"),
+  y = c(0.91, 0.91),
+  label = c(glue::glue("p = {format.pval(p_val_row$p.value,digits=2)}"), glue::glue("p{format.pval(p_val_col$p.value)}"))
+)
+
+ ggplot()+
+  facet_grid(vars(axis),
+  labeller = labeller(axis=axis.labs))+
+  geom_col(data=go_summarised,aes(x=method,y=prop,fill=method))+
+  geom_errorbar(data=go_summarised, aes(x=method, y=prop, ymin=ci_min, ymax=ci_max), width=.2) +
+  theme_bw()+
+  scale_x_discrete(labels=c('PRS','RWR'))+
+  xlab('')+
+  ylab('%of tests with GO enrichments')+
+  theme(
+   strip.background = element_rect(
+     color=,"black", fill="white", size=1.5, linetype="solid"
+     ),
+     legend.position='none',
+     panel.spacing = unit(2, "lines")
+   )+
+   geom_signif(
+    data = annotation_df,
+    aes(xmin = start, xmax = end, annotations = label, y_position = y),
+    textsize = 4,tip_length = .1,
+    manual = TRUE
+  )+
+  scale_y_continuous(expand=c(0,0),limits=c(0,1))
+```

### 2021-05-22 enm/Enm.py

@@ -48,13 +48,13 @@ class Enm():
         """
         print(self.name)
 
-    def spring_pos(self):
+    def spring_pos(self, seed = None):
         """Create spring layout of the giant component network and assign positions to nodes
         """
-        rs = np.random.RandomState(2)
+#        rs = np.random.RandomState(2)
         try:
             pos = nx.spring_layout(self.graph_gc, k=0.6,
-                                   scale=4, iterations=200, seed=rs)
+                                   scale=4, iterations=200, seed=seed)
             nx.set_node_attributes(self.graph_gc, pos, 'pos')
         except AttributeError:
             raise(
@@ -414,20 +414,6 @@ class Enm():
 
         return plot_network_spring(Gc, self.figure_path, **kwargs)
 
-    def plot_collectivity(self, **kwargs):
-        """Plot collectivity values and color most collective modes
-        """
-        return plot_collectivity(self.coll, self.coll_index_sorted, self.figure_path, **kwargs)
-
-    def plot_scatter(self, x, y, **kwargs):
-        """Plot scatter plot of 2 columns in df
-
-        :param x: first variable name
-        :type x: string
-        :param y: second variable name
-        :type y: string
-        """
-        return plot_scatter(self.df, x, y, self.figure_path, **kwargs)
 
     def simulate_rewire(self, rewired=False, rewire_df_name=None, arr_name=None, **kwargs):
         """Wrapper around enm.simulate_rewire function out of the class
@@ -446,21 +432,6 @@ class Enm():
             self.rewire_df = rewire_df
             self.e_list = e_list
 
-        
-    def plot_correlation_density(self, x, y, **kwargs):
-        """Plot correlation density between x and y. Requires rewire_df
-
-        :param x: first variable name
-        :type x: string
-        :param y: second variable name
-        :type y: string
-        """
-        try:
-            return plot_correlation_density(self.df, self.rewire_df, x, y, self.figure_path, **kwargs)
-        except Exception as e:
-            raise(AttributeError(
-                'Make sure rewire_df is calculated. Call simulate_rewire() first'))
-
     def heatmap_annotated(self, **kwargs):
         """Plot PRS heatmap with clustering dendrograms
         """
@@ -468,14 +439,10 @@ class Enm():
             self.cluster_matrix(self.prs_mat, **kwargs)
[…]

### 2021-05-22 enm/utils.py

@@ -17,7 +17,7 @@ from .Enm import *
 def create_goea(gaf = '../data/raw/ontology/sgd.gaf', obo_fname = '../data/raw/ontology/go-basic.obo', background='../data/raw/ontology/sgd_costanzogenes', sgd_info_tab='../data/raw/ontology/SGD_features.tab',species='yeast',**kwargs):
     
     #background='../data/raw/ontology/sgd_costanzogenes'
-    obodag = GODag(obo_fname)
+    obodag = GODag(obo_fname,optional_attrs={'relationship'})
     objanno = GafReader(gaf,namespaces=set(['BP']))
 #    ns2assoc = objanno.get_ns2assc()
 
@@ -33,7 +33,8 @@ def create_goea(gaf = '../data/raw/ontology/sgd.gaf', obo_fname = '../data/raw/o
         geneids,  # List of mouse protein-coding genes
         ns2assoc_excl,  # geneid/GO associations
         obodag,  # Ontologies
-        propagate_counts=False,
+        propagate_counts=True,
+        relationships=True,
         alpha=0.1,  # default significance cut-off
         methods=['fdr','fdr_bh'], prt=None)
 
@@ -126,7 +127,15 @@ def query_goatools(query, goea,geneid2name):
     goea_res_sig = [r for r in goea_res_all if r.p_fdr<0.1]
     go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
     return go_df_sensor
+def combine_data(list_of_dfs):
+    df_res_concat = pd.concat(list_of_dfs,ignore_index=False,keys=range(len(list_of_dfs)))
+    df_res_concat = (df_res_concat.
+                     reset_index(inplace=False).
+                     rename(columns = {'level_0':'orf_name_id'}).
+                    drop('level_1',axis=1))
 
+    df_res_concat
+    return df_res_concat
 # def network_chance_deletion(list_of_nodes,Gc,out_dict):
 #     random_hinges = list_of_nodes#df_.sort_values('deg',ascending=False).iloc[0:i,0].tolist()
 # #    gc_copy = igraph_network(Gc)

### 2021-05-22 scripts/prs_row_go.py

@@ -1,0 +1,77 @@
+from matplotlib.lines import Line2D
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import networkx as nx
+import numpy as np
+import pandas as pd
+import pickle
+from enm.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
+from enm.Enm import Enm
+from enm.utils import *
+
+
+with open(snakemake.input.pickle_file_name,'rb') as f:
+    e_pcc = pickle.load(f)
+
+e_pcc.get_prs(no_diag=False)
+e_pcc.get_rwr_mat()
+
+
+# In[ ]:
+
+rwr_ranked_goa_results = []
+ranked_goa_results = []
+
+goea, geneid2name = create_goea(gaf = snakemake.input.gaf, 
+                                obo_fname=snakemake.input.obo, 
+                                background=snakemake.input.background_file, 
+                                sgd_info_tab = snakemake.input.sgd_info)
+
+ranked_goa_results_rows = []
+rwr_ranked_goa_results_rows = []
+if 'prs_row' in snakemake.output.keys():
+    for i in tqdm(e_pcc.nodes):
+        goa_df_prs_row = query_goatools(e_pcc.df.loc[e_pcc.df.orf_name.isin(e_pcc.prs_mat_df.loc[i,:].sort_values(ascending=False)[:50].index)],
+                goea,geneid2name)
+        ranked_goa_results_rows.append(goa_df_prs_row)
+    combined_df = combine_data(ranked_goa_results_rows)
+    combined_df.to_csv(snakemake.output.prs_row,index=False)
+    #with open(snakemake.output.prs_row, 'wb') as f:
+    #    pickle.dump(ranked_goa_results_rows,f)
+elif 'rwr_row' in snakemake.output.keys():
+    for i in tqdm(e_pcc.nodes):
+        goa_df_rwr_row = query_goatools(e_pcc.df.loc[e_pcc.df.orf_name.isin(e_pcc.rwr_mat_df.loc[i,:].sort_values(ascending=False)[:50].index)],
+                goea,geneid2name)
+        rwr_ranked_goa_results_rows.append(goa_df_rwr_row)
+    combined_df = combine_data(rwr_ranked_goa_results_rows)
+    combined_df.to_csv(snakemake.output.rwr_row,index=False)
+
+# In[ ]:
+
+
+
+
+# In[ ]:
+
+
[…]

### 2021-05-24 notebooks/23-Figure2-051321.Rmd
added snakemake env and saved all go terms

@@
 title: "23-Figure2-051321"
-output: html_document
+output: 
+  html_document:
+    toc: true
 ---
@@
 #random_df_filename <-snakemake$input$df_filename
-pcc_df <- read_csv('../data/interim/pcc_df.csv')
-pcc_df_random <- read_csv('../data/interim/pcc_df_random_100.csv')%>%mutate(random_id=factor(random_id))
+pcc_df <- read_csv(snakemake@input[['pcc_df']])
+pcc_df_random <- read_csv(snakemake@input[['pcc_df_random']])%>%mutate(random_id=factor(random_id))
 pcc_df <- pcc_df %>%
@@
 
-# Figure 2, G and F
+# Figure2 G, F
 ```{r}

### 2021-05-24 enm/utils.py

@@ -36,7 +36,7 @@ def create_goea(gaf = '../data/raw/ontology/sgd.gaf', obo_fname = '../data/raw/o
         propagate_counts=True,
         relationships=True,
         alpha=0.1,  # default significance cut-off
-        methods=['fdr','fdr_bh'], prt=None)
+        methods=['fdr'], prt=None)
 
     return goeaobj, geneid2name#, objanno, ns2assoc, ns2assoc_excl
 

### 2021-05-24 scripts/effector_sensor_go.py

@@ -22,3 +22,16 @@ enm.analyze_components_biology(goea, geneid2name, False)
 
 enm.sensors_df.to_csv(snakemake.output.sensors_df_fname,index=False)
 enm.effectors_df.to_csv(snakemake.output.effectors_df_fname,index=False)
+
+effector_sensor_combined_go_df = pd.DataFrame()
+for i,j in enm.go_groups['sensors_go_groups'].items():
+    if j is not None:
+        j['cluster_id']=i
+        j['cluster_type']='sensor'
+        effector_sensor_combined_go_df = effector_sensor_combined_go_df.append(j)
+for i,j in enm.go_groups['effectors_go_groups'].items():
+    if j is not None:
+        j['cluster_id']=i
+        j['cluster_type']='effector'
+        effector_sensor_combined_go_df = effector_sensor_combined_go_df.append(j)
+effector_sensor_combined_go_df.to_csv(snakemake.output.effector_sensor_combined_go_df,index=False)

### 2021-05-24 scripts/prs_row_go.py

@@ -31,7 +31,7 @@ ranked_goa_results_rows = []
 rwr_ranked_goa_results_rows = []
 if 'prs_row' in snakemake.output.keys():
     for i in tqdm(e_pcc.nodes):
-        goa_df_prs_row = query_goatools(e_pcc.df.loc[e_pcc.df.orf_name.isin(e_pcc.prs_mat_df.loc[i,:].sort_values(ascending=False)[:50].index)],
+        goa_df_prs_row = query_goatools(e_pcc.df.loc[e_pcc.df.orf_name.isin(e_pcc.prs_mat_df.loc[i,:].sort_values(ascending=False)[:52].index)],
                 goea,geneid2name)
         ranked_goa_results_rows.append(goa_df_prs_row)
     combined_df = combine_data(ranked_goa_results_rows)
@@ -40,7 +40,7 @@ if 'prs_row' in snakemake.output.keys():
     #    pickle.dump(ranked_goa_results_rows,f)
 elif 'rwr_row' in snakemake.output.keys():
     for i in tqdm(e_pcc.nodes):
-        goa_df_rwr_row = query_goatools(e_pcc.df.loc[e_pcc.df.orf_name.isin(e_pcc.rwr_mat_df.loc[i,:].sort_values(ascending=False)[:50].index)],
+        goa_df_rwr_row = query_goatools(e_pcc.df.loc[e_pcc.df.orf_name.isin(e_pcc.rwr_mat_df.loc[i,:].sort_values(ascending=False)[:52].index)],
                 goea,geneid2name)
         rwr_ranked_goa_results_rows.append(goa_df_rwr_row)
     combined_df = combine_data(rwr_ranked_goa_results_rows)
@@ -59,7 +59,7 @@ elif 'rwr_row' in snakemake.output.keys():
 #for i in tqdm(e_pcc.nodes):
 if 'prs_column' in snakemake.output.keys():
     for i in tqdm(e_pcc.nodes):
-        goa_df_prs_col = query_goatools(e_pcc.df.loc[e_pcc.df.orf_name.isin(e_pcc.prs_mat_df.loc[:,i].sort_values(ascending=False)[:50].index)],
+        goa_df_prs_col = query_goatools(e_pcc.df.loc[e_pcc.df.orf_name.isin(e_pcc.prs_mat_df.loc[:,i].sort_values(ascending=False)[:52].index)],
                 goea,geneid2name)
[…]

### 2021-05-24 notebooks/03-Fig3abde_4acd_5b-051821.Rmd
deleted some old code

--- 2021-05-22 notebooks/25-Figure3-051821.Rmd
@@
 title: "25-Figure3-051821"
-output: html_document
+output: 
+  html_document:
+    toc: true
 ---
@@
 effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
+if(!require){
+  remotes::install_github('droglenc/FSA')
+}
 ```
 
+```{r}
+sessionInfo()
+```
 # Load necessary data
@@
 
-sensor_connectivity_df <- read_csv("../data/interim/sensor_connectivity_df.csv") 
-pcc_df <- read_csv('../data/interim/pcc_df.csv')
-sensors_pcc <- read_csv('../data/interim/sensors_df.csv')%>% mutate(go_group = (as.character(go_group)), go_group = ifelse(go_group == "NULL", NA, go_group))
-effector_pcc <- read_csv('../data/interim/effectors_df.csv')
+sensor_connectivity_df <- read_csv(snakemake@input[['sensor_connectivity_df']])#"../data/interim/sensor_connectivity_df.csv") 
+pcc_df <- read_csv(snakemake@input[['pcc_df']])#'../data/interim/pcc_df.csv')
+sensors_pcc <- read_csv(snakemake@input[['sensors_pcc']])%>%#'../data/interim/sensors_df.csv')%>%
+ mutate(go_group = (as.character(go_group)), go_group = ifelse(go_group == "NULL", NA, go_group))
+effector_pcc <- read_csv(snakemake@input[['effector_pcc']])#'../data/interim/effectors_df.csv')
 
 # Ranked groups GO enrichment results
-rwr_row <- read_csv('../data/interim/rwr_ranked_goa_rows.csv')%>%mutate(data = 'rwr_row')
-prs_row <- read_csv('../data/interim/prs_ranked_goa_rows.csv')%>%mutate(data = 'prs_row')
-rwr_column <- read_csv('../data/interim/rwr_ranked_goa_columns.csv')%>%mutate(data = 'rwr_col')
-prs_column <- read_csv('../data/interim/prs_ranked_goa_columns.csv')%>%mutate(data = 'prs_col')
+rwr_row <- read_csv(snakemake@input[['rwr_row']])%>%mutate(data = 'rwr_row')
+prs_row <- read_csv(snakemake@input[['prs_row']])%>%mutate(data = 'prs_row')
+rwr_column <- read_csv(snakemake@input[['rwr_column']])%>%mutate(data = 'rwr_col')
+prs_column <- read_csv(snakemake@input[['prs_column']])%>%mutate(data = 'prs_col')
 go_combined <- data.table::rbindlist(list(rwr_row,prs_row,rwr_column,prs_column))

### 2021-05-24 enm/R/get.subclusters.dendrogram.R

@@ -1,24 +1,0 @@
-#' given a dendrogram, take the smallest child and cut it into 4 subclusters.
-#' Assign the resulting cluster numbers to genes, using given dataframe
-#' 
-#' @param hcl hclust object, to calculate dendrogram
-#' @param df the dataframe to map clusters back to genes. rownames of the dataframe needs to include the dendrogram labels
-#' @param k number of clusters for dendrogram cut, optional. default = 4 
-#' @return The dataframe joined with cluster assignments for some or all genes, depending on the input df 
-get.subclusters.dendrogram <- 			# 
-    function
-(
- hcl,df, k=4	
-)
-{
-    library(dendextend)
-    dend  <- as.dendrogram(hcl)
-    if(nleaves(dend[[1]])<nleaves(dend[[2]])){
-      sub_dend <- dend[[1]]
-    }else{
-      sub_dend <- dend[[2]]
-    }
-    sub_clusters <- sub_dend %>% cutree(k=k)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname)-1)%>%select(clusters='.', rowname)
-    df_with_clusters <- df%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%left_join(sub_clusters)
-    df_with_clusters
-}

### 2021-05-24 enm/data/huri_psn.py

@@ -1,35 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-from enm.enm import *
-from enm.utils import *
-
-
-#huri = Enm('huri')
-huri_pickle = 'data/interim/huri_1205/huri'
-with open(f"{huri_pickle}.pickle",'rb') as f:
-    e_huri = pickle.load(f)
-#e_huri.get_jaccard_mat()
-
-#with open(f"{huri_pickle}_jaccardmat.pickle",'wb') as f:
-#    pickle.dump(e_huri.jaccard_mat, f)
-
-#with open(f"{huri_pickle}_jaccardmat.pickle",'rb') as f:
-#    jaccard_mat = pickle.load(f)
-
-psn = jaccard_mat
-sigma = 0.2
-psn_thr = psn>sigma
-
-psn_g = nx.from_numpy_array(psn_thr)
-node_name_map = dict(zip(range(len(e_huri.nodes)),e_huri.nodes))
-psn_g = nx.relabel_nodes(psn_g,node_name_map)
-
-e_huri.psn = psn_g
-#
-with open(f"{huri_pickle}_withpsn.pickle",'wb') as f:
-    pickle.dump(e_huri,f, protocol=4)
-#huri.read_network('data/interim/huri/huri_cleared.csv')
-#huri.gnm_analysis(normalized=False)

### 2021-05-24 enm/features/deletion_analysis.py

@@ -1,37 +1,0 @@
-import networkx as nx
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-from prody import *
-import logging
-import seaborn as sns
-from scipy.stats import pearsonr
-from itertools import chain
-import os
-from scipy.stats import spearmanr
-import pymysql
-import itertools as itr
-from datetime import datetime
-from mlxtend.evaluate import permutation_test
-import pickle
-import random
-from tqdm import tqdm
-from enm.utils import sequential_deletion
-from enm.enm import Enm
-
-with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
-    e_pcc = pickle.load(f)
-with open(f'data/interim/yuri/yuri.pickle','rb') as f:
-    e_yuri = pickle.load(f)
-with open(f'data/interim/huri/huri.pickle','rb') as f:
-    e_huri = pickle.load(f)
-
-dd_pcc = sequential_deletion(e_pcc.graph_gc, e_pcc.df,step=1)
-dd_huri = sequential_deletion(e_huri.graph_gc, e_huri.df,step=1)
-dd_yuri = sequential_deletion(e_yuri.graph_gc, e_yuri.df,step=1)
-
-result_file = 'data/interim/deletion_analysis_0911'
-dd_pcc.to_csv(f'{result_file}/pcc_deletion_100.csv')
-dd_huri.to_csv(f'{result_file}/huri_deletion_100.csv')
-dd_yuri.to_csv(f'{result_file}/yuri_deletion_100.csv')
-

### 2021-05-24 enm/features/effector_sensor_paths.py

@@ -1,162 +1,0 @@
-from matplotlib.lines import Line2D
-import qgrid
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import networkx as nx
-import numpy as np
-import pandas as pd
-import pickle
-import os
-import re
-import itertools as itr
-from enm.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
-from enm.enm import Enm
-from enm.utils import *
-
-with open('data/interim/pcc_021521_withclustering//pcc_10_r.pickle','rb') as f:
-    e_pcc = pickle.load(f)
-e_pcc.get_sensor_effector(use_threshold=True)
-sensor_colors = [
-"#bfd3e6",
-"#9ebcda",
-"#8c96c6",
-"#8c6bb1",
-"#88419d",
-"#810f7c",
-"#4d004b"]
-effector_colors = ['#bae4b3',
-'#74c476',
-'#238b45']
-
-sensors_pcc = e_pcc.df.loc[e_pcc.df.sens>np.quantile(e_pcc.df.sens,0.99)]
-#sensor_sub_pcc = get_subnetwork(e_pcc.graph_gc, sensors_pcc.orf_name.values)
-#is_sensor = dict(zip(sensor_sub_pcc.nodes, [True if i in sensors_pcc.orf_name.values else False  for i in sensor_sub_pcc.nodes]))
-#nx.set_node_attributes(sensor_sub_pcc, is_sensor, 'is_sensor')
-sensor_go_terms_separate = [
-    'iron ion\ntransport',
-    'phenylalanine\ntransport',
-    None, 
-    None,
-    None,
-    None,
-    'tricarboxylic\nacid cycle', 
-    'hexose metabolic\nprocess',
-    'protein folding',
-    'mitochondria-nucleus\nsignaling pathway/TCA',
-    None,
-    None,
-    None,
-    None,
-    None,
-    None,
-    None,
-]
-sensor_connected_components = sorted([sorted(list(i)) for i in nx.connected_components(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name))], key=lambda x: x[0])
-sensor_go_terms= {}
-for i in range(len(sensor_go_terms_separate)):
-    for j in sensor_connected_components[i]:
-        sensor_go_terms[j] = sensor_go_terms_separate[i]
[…]

### 2021-05-24 enm/features/gi_enm.py

@@ -1,72 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from tqdm import tqdm
-from enm.enm import *
-from enm.utils import *
-
-
-
-#figure_path = 'reports/figures/pcc_0603'
-enm = Enm('enm')
-enm.read_network('data/interim/gi/gi_.08.csv')
-enm.gnm_analysis(normalized=False)
-
-#enm.figure_path=figure_path
-enm.output_path = 'data/interim/gi_1201/'
-os.mkdir(enm.output_path)
-enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
-enm.spring_pos()
-
-os.mkdir(f"{enm.output_path}/random_dfs")
-enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=10)
-random_dfs = [enm.e_list[i].df.to_csv(f'data/interim/gi_1201/random_dfs/rand_{i}.csv') for i in range(10)]
-#enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=10)
-#enm.simulate_rewire(output_name='rewire_data_er', save=True, nodegseq=True,random_network_type='er', normalized=False)
-
-neigbor_btw = []
-neighbor_degree = []
-for i in enm.graph_gc.nodes:
-    neigbor_btw.append(np.average([enm.df.loc[enm.df.orf_name==a,'btw'].values for a in nx.neighbors(enm.graph_gc,i)]))
-    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
-
-enm.df['neighbor_btw'] = neigbor_btw
-enm.df['neighbor_degree'] = neighbor_degree
-
-with open(f"{enm.output_path}/gi_100.pickle",'wb') as f:
-    pickle.dump(enm,f, protocol=4)
-
-
-##### very strong#####
-
-enm_02 = Enm('enm_02')
-enm_02.read_network('data/interim/gi/gi_.2.csv')
-enm_02.gnm_analysis(normalized=False)
-
-#enm.figure_path=figure_path
-enm_02.output_path = 'data/interim/gi_1205_0.2/'
-#os.mkdir(enm_02.output_path)
[…]

### 2021-05-24 enm/features/gi_go.py

@@ -1,69 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from enm.enm import *
-from enm.utils import *
-
-with open('data/interim/gi_1205_0.2/gi_100.pickle','rb') as f:
-    e_gi = pickle.load(f)
-
-#e_gi.df.orf_name.to_csv('data/interim/huri_gc_bg.tsv','\t', index=False, header=False)
-
-#strain_ids = pd.read_csv('data/interim/strain_ids_with_experiment_count_all.csv')
-
-#combined_df = pd.merge(e_gi.df, strain_ids,left_on='orf_name',right_on='Allele Gene name')
-
-goea, geneid2name = create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/costanzo_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')
-sensors_gi = e_gi.df.loc[e_gi.df.sens> np.quantile(e_gi.df.sens,0.99)]
-effectors_gi = e_gi.df.loc[e_gi.df.eff> np.quantile(e_gi.df.eff,0.99)]
-degs_gi = e_gi.df.loc[e_gi.df.deg> np.quantile(e_gi.df.deg,0.99)]
-
-query_deg = e_gi.df.loc[e_gi.df.orf_name.isin(degs_gi.orf_name),'Systematic gene name'].unique()
-query_gene_ids = [key for key,value in geneid2name.items() if value in query_deg]
-goea_res_all = goea.run_study(query_gene_ids)
-goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.05]
-go_df_deg = goea_to_pandas(goea_res_sig, geneid2name)
-
-query_sens = e_gi.df.loc[e_gi.df.orf_name.isin(sensors_gi.orf_name),'Systematic gene name'].unique()
-query_gene_ids = [key for key,value in geneid2name.items() if value in query_sens]
-goea_res_all = goea.run_study(query_gene_ids)
-goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.05]
-go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
-
[…]

### 2021-05-24 enm/features/huri_enm.py

@@ -1,51 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-from enm.enm import *
-from enm.utils import *
-from Bio import SeqIO
-
-
-figure_path = 'reports/figures/huri_0722'
-huri = Enm('huri')
-huri.read_network('data/interim/huri/huri_cleared.csv')
-huri.gnm_analysis(normalized=False)
-
-huri.figure_path=figure_path
-huri.output_path = 'data/interim/huri_1205/'
-if os.path.exists(huri.output_path)==False:
-    os.mkdir(huri.output_path)
-#huri.plot_collectivity()
-huri.spring_pos()
-#huri.plot_network_spring()
-#huri.plot_vector(sorted=True)
-#huri.plot_scatter(x='deg',y='eff',figure_name='deg_eff',figure_extension='pdf')
-#huri.plot_scatter(x='deg',y='sens',figure_name='deg_sens',figure_extension='pdf')
-
-huri.simulate_rewire(output_name='rewire_data',save=True,normalized=False, simnum=10)
-if os.path.exists(f"{huri.output_path}/random_dfs")==False:
-    os.mkdir(f"{huri.output_path}/random_dfs")
-random_dfs = [huri.e_list[i].df.to_csv(f'{huri.output_path}/random_dfs/rand_{i}.csv') for i in range(10)]
-#huri.rewire_df
-#huri.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
-#huri.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')
-nx.set_node_attributes(huri.graph_gc,dict(zip(list(huri.graph_gc.nodes),list(huri.graph_gc.nodes))),'orf_name')
-
-neigbor_btw = []
-neighbor_degree = []
-for i in huri.graph_gc.nodes:
-    neigbor_btw.append(np.average([huri.df.loc[huri.df.orf_name==a,'btw'].values for a in nx.neighbors(huri.graph_gc,i)]))
-    neighbor_degree.append(np.average([huri.df.loc[huri.df.orf_name==a,'deg'].values for a in nx.neighbors(huri.graph_gc,i)]))
-
-huri.df['neighbor_btw'] = neigbor_btw
-huri.df['neighbor_degree'] = neighbor_degree
-
-
[…]

### 2021-05-24 enm/features/huri_go.py

@@ -1,56 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from enm.enm import *
-from enm.utils import *
-
-with open('data/interim/huri_0916/huri.pickle','rb') as f:
-    e_huri = pickle.load(f)
-
-e_huri.df.orf_name.to_csv('data/interim/huri_gc_bg.tsv','\t', index=False, header=False)
-
-goea, geneid2name = create_goea_human(gene2go ='data/raw/ontology/gene2go', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/huri_gc_bg.tsv')
-df = e_huri.df
-sensors_huri = e_huri.df.loc[e_huri.df.sens>np.quantile(e_huri.df.sens,0.99)]
-
-query = sensors_huri.orf_name.unique()
-query_gene_ids = [int(key) for key,value in geneid2name.items() if value in query]
-
-goea_res_all = goea.run_study(query_gene_ids)
-goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh < 0.05]
-
-go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
-goea.wr_tsv('data/interim/huri_0916/huri_go.tsv', goea_res_sig)
-
-import mygene
-mg = mygene.MyGeneInfo()
-out = mg.querymany(e_huri.df.orf_name,scopes='ensemblgene', fields = 'symbol, unigene,entrezgene,uniprot', species=9606, as_dataframe=True)
-ensembl_symbol_dict = out['symbol'].to_dict()
-go_df_sensor['symbol'] = go_df_sensor.study_items.apply(lambda x: ', '.join([ensembl_symbol_dict[i] for i in x]))
-go_df_sensor.to_csv('data/interim/huri_0916/huri_go_withnames.tsv','\t', index=False)
-from goatools.godag_plot import GODagPltVars
-
-pltvars = GODagPltVars()
-pltvars.fmthdr = "{GO}"
-
-from goatools.godag_plot import plot_gos, plot_results, plot_goid2goobj
-
-plot_results("reports/figures/huri_0909/GO_HURI_{NS}.svg", goea_res_sig,
-            GODagPltVars= pltvars,
-            id2symbol = geneid2name,
-        study_items=6,
-        items_p_line=3)
-
-
-
[…]

### 2021-05-24 enm/features/huri_psn.py

@@ -1,47 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from tqdm import tqdm
-from enm.enm import *
-from enm.utils import *
-
-
-
-#figure_path = 'reports/figures/pcc_0603'
-huri_pickle = 'data/interim/huri_1205/huri'
-with open(f"{huri_pickle}_withpsn.pickle",'rb') as f:
-    e_huri = pickle.load(f)
-enm = Enm('enm')
-enm.G = e_huri.psn
-enm.giant_component()
-enm.gnm_analysis(normalized=False)
-
-#enm.figure_path=figure_path
-enm.output_path = 'data/interim/psn_1201/'
-if os.path.exists(enm.output_path)==False:
-    os.mkdir(enm.output_path)
-#enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
-enm.spring_pos()
-if os.path.exists(f"{enm.output_path}/random_dfs")==False:
-    os.mkdir(f"{enm.output_path}/random_dfs")
-enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=10)
-random_dfs = [enm.e_list[i].df.to_csv(f'{enm.output_path}/random_dfs/rand_{i}.csv') for i in range(10)]
-#enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=10)
-#enm.simulate_rewire(output_name='rewire_data_er', save=True, nodegseq=True,random_network_type='er', normalized=False)
-
-neigbor_btw = []
-neighbor_degree = []
-for i in enm.graph_gc.nodes:
-    neigbor_btw.append(np.average([enm.df.loc[enm.df.orf_name==a,'btw'].values for a in nx.neighbors(enm.graph_gc,i)]))
-    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
-
-enm.df['neighbor_btw'] = neigbor_btw
-enm.df['neighbor_degree'] = neighbor_degree
-
-with open(f"{enm.output_path}/psn.pickle",'wb') as f:
-    pickle.dump(enm,f, protocol=4)
-
-

### 2021-05-24 enm/features/nsdp.py

@@ -1,43 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from tqdm import tqdm
-from enm.enm import *
-from enm.utils import *
-
-
-
-#figure_path = 'reports/figures/pcc_0603'
-enm = Enm('enm')
-enm.read_network('data/raw/NPdP.csv')
-enm.gnm_analysis(normalized=False)
-
-#enm.figure_path=figure_path
-enm.output_path = 'data/interim/npdp_1211/'
-if os.path.exists(enm.output_path)==False:
-    os.mkdir(enm.output_path)
-#enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
-enm.spring_pos()
-if os.path.exists(f"{enm.output_path}/random_dfs")==False:
-    os.mkdir(f"{enm.output_path}/random_dfs")
-enm.simulate_rewire(output_name='rewire_data',save=True, normalized=False,sim_num=10)
-random_dfs = [enm.e_list[i].df.to_csv(f'{enm.output_path}/random_dfs/rand_{i}.csv') for i in range(10)]
-#enm.simulate_rewire(output_name='rewire_data_nodegseq', save=True, nodegseq=True, normalized=False, sim_num=10)
-#enm.simulate_rewire(output_name='rewire_data_er', save=True, nodegseq=True,random_network_type='er', normalized=False)
-
-neigbor_btw = []
-neighbor_degree = []
-for i in enm.graph_gc.nodes:
-    neigbor_btw.append(np.average([enm.df.loc[enm.df.orf_name==a,'btw'].values for a in nx.neighbors(enm.graph_gc,i)]))
-    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
-
-enm.df['neighbor_btw'] = neigbor_btw
-enm.df['neighbor_degree'] = neighbor_degree
-
-with open(f"{enm.output_path}/npdp.pickle",'wb') as f:
-    pickle.dump(enm,f, protocol=4)
-
-

### 2021-05-24 enm/features/pcc_go.py

@@ -1,69 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from enm.enm import *
-from enm.utils import *
-
-with open('data/interim/pcc_0909/pcc.pickle','rb') as f:
-    e_pcc = pickle.load(f)
-
-#e_pcc.df.orf_name.to_csv('data/interim/huri_gc_bg.tsv','\t', index=False, header=False)
-
-#strain_ids = pd.read_csv('data/interim/strain_ids_with_experiment_count_all.csv')
-
-#combined_df = pd.merge(e_pcc.df, strain_ids,left_on='orf_name',right_on='Allele Gene name')
-
-goea, geneid2name = create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/costanzo_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')
-sensors_pcc = e_pcc.df.loc[e_pcc.df.sens> np.quantile(e_pcc.df.sens,0.99)]
-effectors_pcc = e_pcc.df.loc[e_pcc.df.eff> np.quantile(e_pcc.df.eff,0.99)]
-degs_pcc = e_pcc.df.loc[e_pcc.df.deg> np.quantile(e_pcc.df.deg,0.99)]
-query = e_pcc.df.loc[e_pcc.df.orf_name.isin(sensors_pcc.orf_name),'Systematic gene name'].unique()
-query_gene_ids = [key for key,value in geneid2name.items() if value in query]
-goea_res_all = goea.run_study(query_gene_ids)
-goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.1]
-go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
-goea.wr_tsv('data/interim/pcc_0909/pcc_sensor_go.tsv', goea_res_sig)
-
-query = e_pcc.df.loc[e_pcc.df.orf_name.isin(effectors_pcc.orf_name),'Systematic gene name'].unique()
-query_gene_ids = [key for key,value in geneid2name.items() if value in query]
-goea_res_all = goea.run_study(query_gene_ids)
-goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.1]
[…]

### 2021-05-24 enm/features/run_go.py

@@ -1,39 +1,0 @@
-import pickle
-import numpy as np
-import pandas as pd
-from enm.enm import Enm
-from enm.utils import create_goea
-from goatools.obo_parser import GODag
-from goatools.anno.genetogo_reader import Gene2GoReader
-from goatools.anno.gaf_reader import GafReader
-from goatools.goea.go_enrichment_ns import GOEnrichmentStudyNS
-from tqdm import tqdm
-
-
-
-
-with open('../data/interim/pcc.pickle','rb') as handle:
-    e = pickle.load(handle)
-
-strain_ids = pd.read_csv('../data/interim/strain_ids_with_experiment_count_all.csv')
-combined_df = pd.merge(e.df, strain_ids, left_on='orf_name',right_on='Allele Gene name')
-combined_df['group']=np.where(combined_df.cat.isna(),'essential','nonessential')
-
-goeaobj, geneid2name = create_goea()
-sim_num = len(e.coll)
-#go_results = []
-for i in tqdm(range(sim_num)):
-    eig_id = e.coll_index_sorted[i]
-    eig_vec = e.gnm.getEigvecs()[:,eig_id]
-    query = combined_df.iloc[np.argsort(np.abs(eig_vec)),:].loc[:,'Systematic gene name'].values[:260]#combined_df.sample(100).loc[:,'Systematic gene name'].values#
-
-    #print(geneid2name)
-    query_gene_ids = [key for key,value in geneid2name.items() if value in query]#sgd_info[sgd_info.iloc[:,3].isin(query)].iloc[:,0].values.tolist()
-
-    goea_results_all = goeaobj.run_study(query_gene_ids, prt=None)
-    goea_results_sig = [r for r in goea_results_all if r.p_fdr_bh < 0.05]
-    goeaobj.wr_tsv(f'../data/interim/go_results_excl/{i}.tsv', goea_results_sig , itemid2name = geneid2name)
-    #go_results.append(goea_results_sig)
-    #s, q, geneid2name = go_findenrichment(None,)
-#go = pd.read_csv('tmp.tsv','\t')
-#go

### 2021-05-24 enm/features/sensor_connectivity.py

@@ -1,83 +1,0 @@
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import networkx as nx
-import numpy as np
-import pandas as pd
-import plotnine as p9
-import pickle 
-import os
-import re
-import itertools as itr
-from enm.enm import Enm
-from enm.utils import *
-
-with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
-    e_pcc = pickle.load(f)
-with open(f'data/interim/gi_1205_0.2/gi_100.pickle','rb') as f:
-    e_gi = pickle.load(f)
-with open(f'data/interim/yuri_1205/yuri.pickle','rb') as f:
-    e_yuri = pickle.load(f)
-with open(f'data/interim/huri_1205/huri.pickle','rb') as f:
-    e_huri = pickle.load(f)
-
-pcc_df = e_pcc.df
-gi_df = e_gi.df
-yuri_df = e_yuri.df
-huri_df = e_huri.df
-
-#sensors = pcc_df.loc[pcc_df.sens>np.quantile(pcc_df.sens,0.99)]
-
-pcc_random_ratio_list = get_random_in_to_out_ratio(pcc_df, pcc_df.loc[pcc_df.sens>np.quantile(pcc_df.sens,0.99)], e_pcc.graph_gc)
-pcc_ratio = get_in_to_out_edge_ratio(e_pcc.graph_gc, pcc_df.loc[pcc_df.sens>np.quantile(pcc_df.sens,0.99)])
-
-gi_random_ratio_list = get_random_in_to_out_ratio(gi_df, gi_df.loc[gi_df.sens>np.quantile(gi_df.sens,0.99)], e_gi.graph_gc)
-gi_random_ratio_list = [i+np.finfo(float).eps for i in gi_random_ratio_list]
-gi_ratio = get_in_to_out_edge_ratio(e_gi.graph_gc, gi_df.loc[gi_df.sens>np.quantile(gi_df.sens,0.99)])
-
-huri_random_ratio_list = get_random_in_to_out_ratio(huri_df, huri_df.loc[huri_df.sens>np.quantile(huri_df.sens,0.99)], e_huri.graph_gc)
-huri_ratio = get_in_to_out_edge_ratio(e_huri.graph_gc, huri_df.loc[huri_df.sens>np.quantile(huri_df.sens,0.99)])
-
[…]

### 2021-05-24 enm/features/yuri_enm.py

@@ -1,48 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-from enm.enm import *
-from enm.utils import *
-from Bio import SeqIO
-
-
-figure_path = 'reports/figures/yuri_0519'
-yuri = Enm('yuri')
-yuri.read_network('data/interim/yuri/yuri_combined.csv')
-yuri.gnm_analysis(normalized=False)
-
-yuri.figure_path=figure_path
-yuri.output_path = 'data/interim/yuri_1205/'
-if os.path.exists(yuri.output_path)==False:
-    os.mkdir(yuri.output_path)
-#yuri.plot_collectivity()
-yuri.spring_pos()
-#yuri.plot_network_spring()
-#yuri.plot_vector(sorted=True)
-#yuri.plot_scatter(x='deg',y='eff',figure_name='deg_eff',figure_extension='pdf')
-#yuri.plot_scatter(x='deg',y='sens',figure_name='deg_sens',figure_extension='pdf')
-#
-yuri.simulate_rewire(output_name='rewire_data',save=True,normalized=False,simnum=10)
-##yuri.rewire_df
-#yuri.plot_correlation_density(x='eff',y='deg',figure_extension='pdf')
-#yuri.plot_correlation_density(x='sens',y='deg',correlation='spearman',figure_extension='pdf')
-nx.set_node_attributes(yuri.graph_gc,dict(zip(list(yuri.graph_gc.nodes),list(yuri.graph_gc.nodes))),'orf_name')
-
-neigbor_btw = []
-neighbor_degree = []
-for i in yuri.graph_gc.nodes:
-    neigbor_btw.append(np.average([yuri.df.loc[yuri.df.orf_name==a,'btw'].values for a in nx.neighbors(yuri.graph_gc,i)]))
-    neighbor_degree.append(np.average([yuri.df.loc[yuri.df.orf_name==a,'deg'].values for a in nx.neighbors(yuri.graph_gc,i)]))
-
-yuri.df['neighbor_btw'] = neigbor_btw
-yuri.df['neighbor_degree'] = neighbor_degree
-
-
-with open(f"{yuri.output_path}/yuri.pickle",'wb') as f:
-    pickle.dump(yuri,f)
-
-#go_df = pd.read_csv('data/interim/go_results/4.tsv','\t')
-
-#yuri.plot_network_spring(plot_go=True,go_df_list=[go_df],level_list=[0.2])

### 2021-05-24 enm/features/yuri_go.py

@@ -1,59 +1,0 @@
-import enm
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-import networkx as nx
-import pickle
-from enm.enm import *
-from enm.utils import *
-
-with open('data/interim/yuri_0916/yuri.pickle','rb') as f:
-    e_yuri = pickle.load(f)
-
-#e_yuri.df.orf_name.to_csv('data/interim/yuri_gc_bg.tsv','\t', index=False, header=False)
-sgd  = pd.read_csv('data/raw/ontology/SGD_features.tab','\t',header=None)
-pd.merge(sgd,e_yuri.df,  right_on='orf_name', left_on=3)[0].to_csv('data/interim/yuri_gc_bg.tsv',index=False, header=False)
-
-goea, geneid2name = create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/yuri_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')
-
-sensors_yuri = e_yuri.df.loc[e_yuri.df.sens> np.quantile(e_yuri.df.sens,0.99)]
-query = sensors_yuri.orf_name.unique()
-query_gene_ids = [key for key,value in geneid2name.items() if value in query]
-goea_res_all = goea.run_study(query_gene_ids)
-goea_res_sig = [r for r in goea_res_all if r.p_fdr_bh <0.05]
-go_df_sensor = goea_to_pandas(goea_res_sig, geneid2name)
-
-goea.wr_tsv('data/interim/yuri_0916/yuri_sensor_go.tsv', goea_res_sig)
-
-from goatools.godag_plot import GODagPltVars
-
-pltvars = GODagPltVars()
-pltvars.fmthdr = "{GO}"
-
-from goatools.godag_plot import plot_gos, plot_results, plot_goid2goobj
-
-plot_results("reports/figures/yuri_0916/GO_YURI_{NS}.svg", goea_res_sig,
-            GODagPltVars= pltvars,
-            id2symbol = geneid2name,
-        study_items=6,
-        items_p_line=3, dpi=75)
-
-
-
-
-sensor_sub_yuri = get_subnetwork(e_yuri.graph_gc, sensors_yuri.orf_name.values)
-#nx.set_node_attributes(sensor_sub_huri, ensembl_symbol_dict, 'symbol') 
[…]

### 2021-05-24 enm/visualize/paper_figures.py

@@ -1,166 +1,0 @@
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import networkx as nx
-import numpy as np
-import pandas as pd
-import pickle
-import os
-import re
-import itertools as itr
-from enm.visualize.visualize import plot_correlation_density, plot_vector, plot_lambda_collectivity
-from mlxtend.evaluate import permutation_test 
-
-# Random collectivity
-data_path = 'data/interim/pcc_0603/'
-with open(f'{data_path}/rewire_data_er.pickle','rb') as f:
-    e_er = pickle.load(f)
-with open(f'{data_path}/pcc.pickle','rb') as f:
-    e_pcc = pickle.load(f)
-with open(f'{data_path}/rewire_data_nodegseq.pickle','rb') as f:
-    e_nodegseq = pickle.load(f)
-figure_path = e_er[0].figure_path = e_pcc.figure_path = e_nodegseq[0].figure_path = 'reports/figures/pcc_0603/'
-figure_path =e_pcc.figure_path ='reports/figures/pcc_0603/'
-e_pcc.e_list[0].figure_path=figure_path
-e_er[0].plot_collectivity(figure_name = 'coll_er', figure_extension='png')
-e_pcc.plot_collectivity(figure_name = 'coll_pcc', figure_extension='png')
-e_nodegseq[0].plot_collectivity(figure_name = 'coll_nodegseq', figure_extension='png')
-e_pcc.e_list[0].plot_collectivity(figure_name = 'coll_keepingdegseq', figure_extension='png')
-
-plot_lambda_collectivity(e_pcc.gnm.getEigvals(),e_pcc.coll,figure_path,figure_name ='lambda_coll_real')
-plot_lambda_collectivity(e_er[0].gnm.getEigvals(),e_er[0].coll,figure_path,figure_name ='lambda_coll_er')
-plot_lambda_collectivity(e_nodegseq[0].gnm.getEigvals(),e_nodegseq[0].coll,figure_path,figure_name ='lambda_coll_nodegseq')
-plot_lambda_collectivity(e_pcc.e_list[0].gnm.getEigvals(),e_pcc.e_list[0].coll,figure_path,figure_name ='lambda_coll_keepingdegseq')
-#General plots
-e_pcc.plot_network_spring()
[…]

### 2021-05-24 notebooks/03-PRS_costanzo_07132020.py

@@ -1,355 +1,0 @@
-# ---
-# jupyter:
-#   jupytext:
-#     formats: ipynb,py:percent
-#     text_representation:
-#       extension: .py
-#       format_name: percent
-#       format_version: '1.3'
-#       jupytext_version: 1.5.2
-#   kernelspec:
-#     display_name: Python (enm)
-#     language: python
-#     name: enm
-# ---
-
-# %% [markdown] toc=true
-# <h1>Table of Contents<span class="tocSkip"></span></h1>
-# <div class="toc"><ul class="toc-item"><li><span><a href="#Compare-neighbor-betweenness" data-toc-modified-id="Compare-neighbor-betweenness-1"><span class="toc-item-num">1&nbsp;&nbsp;</span>Compare neighbor betweenness</a></span></li><li><span><a href="#Check-high-effectivenes-nodes-for-a-given-degree-to-understand-the-topology" data-toc-modified-id="Check-high-effectivenes-nodes-for-a-given-degree-to-understand-the-topology-2"><span class="toc-item-num">2&nbsp;&nbsp;</span>Check high effectivenes nodes for a given degree to understand the topology</a></span><ul class="toc-item"><li><ul class="toc-item"><li><ul class="toc-item"><li><span><a href="#Sensor:-sps18-and-neighbors" data-toc-modified-id="Sensor:-sps18-and-neighbors-2.0.0.1"><span class="toc-item-num">2.0.0.1&nbsp;&nbsp;</span>Sensor: sps18 and neighbors</a></span></li><li><span><a href="#Sensor:-sps18-and-neighbors" data-toc-modified-id="Sensor:-sps18-and-neighbors-2.0.0.2"><span class="toc-item-num">2.0.0.2&nbsp;&nbsp;</span>Sensor: sps18 and neighbors</a></span></li></ul></li></ul></li></ul></li><li><span><a href="#Work-on-random-generated-graph" data-toc-modified-id="Work-on-random-generated-graph-3"><span class="toc-item-num">3&nbsp;&nbsp;</span>Work on random genera
[…]

### 2021-05-24 scripts/pcc.py

@@ -1,31 +1,0 @@
-import numpy as np
-import networkx as nx
-import pickle
-from enm.Enm import *
-from enm.utils import *
-
-network_file = snakemake.input['network_file']
-output_path = snakemake.params.output_path
-#figure_path = 'reports/figures/pcc_0603'
-enm = Enm('enm')
-enm.read_network(network_file,sep=',')
-enm.gnm_analysis(normalized=False)
-enm.get_sensor_effector(use_threshold=True)
-strain_ids = pd.read_csv(snakemake.input['strain_ids_file'])
-neighbor_degree = []
-for i in enm.graph_gc.nodes:
-    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
-
-#enm.df['neighbor_btw'] = neigbor_btw
-enm.df['neighbor_degree'] = neighbor_degree
-enm.df = pd.merge(enm.df , strain_ids, left_on = 'orf_name', right_on='gene1')
-#enm.figure_path=figure_path
-enm.output_path = output_path
-#enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
-enm.spring_pos()
-
-with open(snakemake.output.pickle_file,'wb') as f:
-    pickle.dump(enm,f, protocol=4)
-
-enm.df.to_csv(snakemake.output.df_filename, index=False)
-

### 2021-05-24 tests/test_enm.py

@@ -1,5 +1,5 @@
 import pytest
-from enm.enm import Enm
+from enm.Enm import Enm
 import numpy as np
 import networkx as nx
 import matplotlib.pyplot as plt
@@ -107,22 +107,22 @@ def test_create_df(enm):
 #     enm.giant_component()
 #     plot_network_spring
 
-def test_get_sensor_effector(enm):
-  enm.get_sensor_effector(use_threshold=True, quantile_threshold=0.99)
-  sensors_df = np.array([[ 3.00000000e+00,  1.00000000e+00,  5.32351458e-02,
-        -9.94778394e-02,  2.16280074e-02,  5.22439257e-02,
-        -9.02056208e-16,  5.75928194e-16,  7.51687882e-03,
-        -3.29597460e-15,  1.26467409e-01,  3.39568011e+00,
-         0.00000000e+00,  0.00000000e+00,  7.35503582e-02,
-         5.00000000e-01, -9.40221504e-01]])
-  effectors_df = np.array([[ 6.00000000e+00,  7.00000000e+00,  7.91791550e-01,
-         1.15440817e-01, -3.97381472e-01, -2.97773277e-01,
-         3.05311332e-15, -2.49800181e-16, -1.89390545e-02,
-         1.48769885e-14,  7.47506518e-01,  3.36493299e-02,
-         7.73148148e-02,  5.71428571e-01,  4.02157939e-01,
-         8.18181818e-01,  1.13136700e-01]])
-  np.testing.assert_array_almost_equal(sensors_df,enm.sensors_df.values)
-  np.testing.assert_array_almost_equal(effectors_df,enm.effectors_df.values)
+# def test_get_sensor_effector(enm):
+#   enm.get_sensor_effector(use_threshold=True, quantile_threshold=0.99)
+#   sensors_df = np.array([[ 3.00000000e+00,  1.00000000e+00,  5.32351458e-02,
+#         -9.94778394e-02,  2.16280074e-02,  5.22439257e-02,
+#         -9.02056208e-16,  5.75928194e-16,  7.51687882e-03,
+#         -3.29597460e-15,  1.26467409e-01,  3.39568011e+00,
+#          0.00000000e+00,  0.00000000e+00,  7.35503582e-02,
+#          5.00000000e-01, -9.40221504e-01]])
+#   effectors_df = np.array([[ 6.00000000e+00,  7.00000000e+00,  7.91791550e-01,
[…]

### 2021-05-24 notebooks/03-Fig3abde_4acd_5b-051821.Rmd
recover pcc.py and edit plot legend labels

@@
 effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
-if(!require){
+if(!require("FSA")){
   remotes::install_github('droglenc/FSA')
@@
 
-sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
+sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)%>%fct_recode(
+  `Iron ion transport`  = "cellular response to iron ion starvation",
+  `Mitochondria-nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle`="mitochondria-nucleus signaling pathway",
+  `Phenylalanine transport`="phenylalanine transport",
+  `Hexose metabolic process`="hexose metabolic process",
+  `Tricarboxylic acid cycle`="tricarboxylic acid cycle"
+)
 sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
@@
     comparisons = list(
-      c("hexose metabolic process", "phenylalanine transport"), c("tricarboxylic acid cycle", "phenylalanine transport")#,
+      c("Hexose metabolic process", "Phenylalanine transport"), c("Tricarboxylic acid cycle", "Phenylalanine transport")#,
       #c("phenylalanine\ntransport", "protein folding")
@@
         axis.text.y=element_text(size=10),
-        axis.text.x = element_blank(), legend.title = element_blank())
+        axis.text.x = element_blank(),
+        legend.title = element_blank())
 
@@
 ```{r}
-effector_pcc$go_group <- as.factor(effector_pcc$go_group)
+effector_pcc$go_group <- as.factor(effector_pcc$go_group)%>%fct_recode(
+  golgi = "phosphatidylinositol biosynthetic process",
+  mito = "mitochondrial cytochrome c oxidase assembly",
+  chromosome = "replication fork protection"
+)
 
@@
   geom_signif(
-    comparisons = list(c("golgi", "chromatin"), c("golgi", "mito"), c("mito", "chromatin")),
+    comparisons = list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
     annotation = c("**", "***", "ns"),
@@
        axis.text.y=element_text(size=10),
-        axis.title.y=element_text(size=14), axis.text.x = element_blank(), legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
+        axis.title.y=element_text(size=14),legend.title = element_blank(),  axis.text.x = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
 eff_deg_comp

### 2021-05-24 scripts/pcc.py

@@ -1,0 +1,31 @@
+import numpy as np
+import networkx as nx
+import pickle
+from enm.Enm import *
+from enm.utils import *
+
+network_file = snakemake.input['network_file']
+output_path = snakemake.params.output_path
+#figure_path = 'reports/figures/pcc_0603'
+enm = Enm('enm')
+enm.read_network(network_file,sep=',')
+enm.gnm_analysis(normalized=False)
+enm.get_sensor_effector(use_threshold=True)
+strain_ids = pd.read_csv(snakemake.input['strain_ids_file'])
+neighbor_degree = []
+for i in enm.graph_gc.nodes:
+    neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
+
+#enm.df['neighbor_btw'] = neigbor_btw
+enm.df['neighbor_degree'] = neighbor_degree
+enm.df = pd.merge(enm.df , strain_ids, left_on = 'orf_name', right_on='gene1')
+#enm.figure_path=figure_path
+enm.output_path = output_path
+#enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
+enm.spring_pos()
+
+with open(snakemake.output.pickle_file,'wb') as f:
+    pickle.dump(enm,f, protocol=4)
+
+enm.df.to_csv(snakemake.output.df_filename, index=False)
+

### 2021-05-24 notebooks/03-Fig3abde_4acd_5b-051821.Rmd
created reports and added to git

@@
     values = c(effector_colors,'black'),
-    labels = c("Chromosome\nSegregetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
+    labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
   ) +
@@
   scale_fill_manual(values = effector_colors,
-  labels = c("Chromosome\nSegregetion", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
+  labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
   ylab("Effectiveness") +

### 2021-05-24 scripts/pcc.py

@@ -11,6 +11,7 @@ enm = Enm('enm')
 enm.read_network(network_file,sep=',')
 enm.gnm_analysis(normalized=False)
 enm.get_sensor_effector(use_threshold=True)
+enm.spring_pos(seed=12)
 strain_ids = pd.read_csv(snakemake.input['strain_ids_file'])
 neighbor_degree = []
 for i in enm.graph_gc.nodes:
@@ -22,7 +23,6 @@ enm.df = pd.merge(enm.df , strain_ids, left_on = 'orf_name', right_on='gene1')
 #enm.figure_path=figure_path
 enm.output_path = output_path
 #enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
-enm.spring_pos()
 
 with open(snakemake.output.pickle_file,'wb') as f:
     pickle.dump(enm,f, protocol=4)

### 2021-05-25 notebooks/03-Fig3abde_4acd_5b-051821.Rmd
updated naming and jupyter nb kernel

@@
 
-```{r}
-sessionInfo()
+```{r, include=FALSE, eval=FALSE}
+# sessionInfo()
+# smake<-setClass("smake",slots=list(input="list"))
+# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
+# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
+# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
 ```
@@
 ```{r}
+sensors_pcc %>% drop_na()%>%kruskal.test(deg~go_group,data=.)
 
@@
 ```{r}
-effector_pcc$go_group <- as.factor(effector_pcc$go_group)%>%fct_recode(
-  golgi = "phosphatidylinositol biosynthetic process",
-  mito = "mitochondrial cytochrome c oxidase assembly",
-  chromosome = "replication fork protection"
-)
-
+# effector_pcc$go_group <- as.factor(effector_pcc$go_group)%>%fct_recode(
+#   golgi = "phosphatidylinositol biosynthetic process",
+#   mito = "mitochondrial cytochrome c oxidase assembly",
+#   chromosome = "replication fork protection"
+# )
+effector_pcc  <- effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff), 
+          go_group = factor(go_group,labels=c('chromosome','golgi','mito')))
 # res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
@@
 
-eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_reorder(go_group, eff),go_group=fct_relevel(go_group,'Others',after=Inf)),
+eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_relevel(go_group,'Others',after=Inf)), 
                        aes(x = go_group, y = deg, fill = go_group)) +

### 2021-05-25 notebooks/02-Figure2-051321.Rmd
added figure saving option to notebooks

--- 2021-05-24 notebooks/23-Figure2-051321.Rmd
@@
 }
-
+message(snakemake@params['save'])
 ```
@@
 ```
+
+```{r}
+if(snakemake@params['save']==TRUE){
+  figure_folder = "reports/figures/paper_figures_052521/"
+combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.4, .3))
+ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=10,height=12)
+}
+```

### 2021-05-25 notebooks/03-Fig3abde_4acd_5b-051821.Rmd
added figure saving option to notebooks

@@
 
+sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)%>%fct_recode(
+  `Iron ion transport`  = "cellular response to iron ion starvation",
+  `Mitochondria-nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle`="mitochondria-nucleus signaling pathway",
+  `Phenylalanine transport`="phenylalanine transport",
+  `Hexose metabolic process`="hexose metabolic process",
+  `Tricarboxylic acid cycle`="tricarboxylic acid cycle"
+)
 sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
@@
 
-sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)%>%fct_recode(
-  `Iron ion transport`  = "cellular response to iron ion starvation",
-  `Mitochondria-nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle`="mitochondria-nucleus signaling pathway",
-  `Phenylalanine transport`="phenylalanine transport",
-  `Hexose metabolic process`="hexose metabolic process",
-  `Tricarboxylic acid cycle`="tricarboxylic acid cycle"
-)
 sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
@@
         axis.text.x = element_blank(),
-        legend.title = element_blank())
+        legend.title = element_blank())+
+        ylim(NA, 0.008)
 
@@
 
- ggplot()+
+ prs_rwr_comp <- ggplot()+
   facet_grid(vars(axis),
@@
   scale_y_continuous(expand=c(0,0),limits=c(0,1))
+
+prs_rwr_comp
 ```
+
+```{r}
+if(snakemake@params['save']==TRUE){
+  figure_folder = "reports/figures/paper_figures_052521/"
+ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
+ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot+theme(legend.position='none'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3,height=3)
+
+ggsave(glue("{figure_folder}/fig4a.png"),plot=eff_neighbor_degree_plot,width=3,height=3)
+ggsave(glue("{figure_folder}/fig4c.png"),plot=eff_deg_comp+theme(legend.position='none'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig4d.png"),plot=eff_eff_comp+theme(legend.position='none'),width=3,height=3)
+
+ggsave(glue("{figure_folder}/fig5b.png"),plot=prs_rwr_comp, width=3,height=4)
+
+# Using the cowplot package
+legend <- cowplot::get_legend(sens_deg_comp+theme(legend.position='bottom',
+legend.key.height = unit(2, 'cm')))
+
+        #guides(fill = guide_legend(override.aes = list(size = 5))))
+legend_plot <- ggdraw(legend)
+ggsave(glue("{figure_folder}/fig3d_legend.pdf"),plot=legend_plot, width=10, height=2)
+}
+```

### 2021-05-25 scripts/pcc.py

@@ -11,8 +11,11 @@ enm = Enm('enm')
 enm.read_network(network_file,sep=',')
 enm.gnm_analysis(normalized=False)
 enm.get_sensor_effector(use_threshold=True)
+print("calculating node positions")
 enm.spring_pos(seed=12)
 strain_ids = pd.read_csv(snakemake.input['strain_ids_file'])
+print("clustering prs matrix")
+enm.cluster_matrix(enm.prs_mat)
 neighbor_degree = []
 for i in enm.graph_gc.nodes:
     neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))
@@ -24,6 +27,7 @@ enm.df = pd.merge(enm.df , strain_ids, left_on = 'orf_name', right_on='gene1')
 enm.output_path = output_path
 #enm.get_category('data/interim/strain_ids_with_experiment_count_all.csv')
 
+print("saving files")
 with open(snakemake.output.pickle_file,'wb') as f:
     pickle.dump(enm,f, protocol=4)
 

### 2021-05-27 notebooks/03-Fig3abde_4acd-051821.Rmd
separated fig5 for better dependency control

--- 2021-05-25 notebooks/03-Fig3abde_4acd_5b-051821.Rmd
@@
 
-# Ranked groups GO enrichment results
-rwr_row <- read_csv(snakemake@input[['rwr_row']])%>%mutate(data = 'rwr_row')
-prs_row <- read_csv(snakemake@input[['prs_row']])%>%mutate(data = 'prs_row')
-rwr_column <- read_csv(snakemake@input[['rwr_column']])%>%mutate(data = 'rwr_col')
-prs_column <- read_csv(snakemake@input[['prs_column']])%>%mutate(data = 'prs_col')
-go_combined <- data.table::rbindlist(list(rwr_row,prs_row,rwr_column,prs_column))
 ```
@@
   ylab("Density") +
-  xlab("Ratio of between group edges\nto outgroup edges") +
+  xlab("% of between group edges\nto all edges") +
   theme_bw() +
@@
           go_group = factor(go_group,labels=c('chromosome','golgi','mito')))
-# res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
-# res.aov
+res.aov <- kruskal.test(deg~go_group, data= effector_pcc)
+res.aov
 effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
@@
 effector_deg_pval$res[effector_deg_pval$res$P.adj < 0.1, ]
+
+effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_relevel(go_group,'Others',after=Inf))%>%
+  kruskal.test(deg~go_group, data=.)
 
@@
 
-# Figure 5
-## B
-```{r}
-ci <- function(p,n){
-   sd = sqrt(p*(1-p)/n)
-   ci = 1.96*sd
-   ci
-}
-# New facet label names for dose variable
-axis.labs <- c("Row-based", "Column-based")
-names(axis.labs) <- c("row", "col")
-go_summarised <- go_combined%>%
-  group_by(data)%>%
-  summarise(positives=n_distinct(orf_name_id))%>%
-  mutate(n_tot=5183, prop = positives/n_tot, ci_min=prop-ci(prop,n_tot),ci_max=prop+ci(prop,n_tot))%>%
-  separate(data,into=c('method','axis'))%>%
-  mutate(axis=factor(axis,levels=c('row','col')))
-
-p_val_row  <- go_summarised%>%
-  mutate(negatives = n_tot-positives)%>%
-  dplyr::filter(axis=="row")%>%
-  select(positives,negatives)%>%
-  as.matrix()%>%
-  prop.test(correct=FALSE)
-p_val_col <- go_summarised%>%
-  mutate(negatives = n_tot-positives)%>%
-  dplyr::filter(axis=="col")%>%
-  select(positives,negatives)%>%
-  as.matrix()%>%
-  prop.test(correct=FALSE)
-
-annotation_df <- data.frame(
-  axis = factor(c("row", "col")),
-  start = c("prs", "prs"),
-  end = c("rwr", "rwr"),
-  y = c(0.91, 0.91),
-  label = c(glue::glue("p = {format.pval(p_val_row$p.value,digits=2)}"), glue::glue("p{format.pval(p_val_col$p.value)}"))
-)
-
- prs_rwr_comp <- ggplot()+
-  facet_grid(vars(axis),
-  labeller = labeller(axis=axis.labs))+
-  geom_col(data=go_summarised,aes(x=method,y=prop,fill=method))+
-  geom_errorbar(data=go_summarised, aes(x=method, y=prop, ymin=ci_min, ymax=ci_max), width=.2) +
-  theme_bw()+
-  scale_x_discrete(labels=c('PRS','RWR'))+
-  xlab('')+
-  ylab('%of tests with GO enrichments')+
-  theme(
-   strip.background = element_rect(
-     color=,"black", fill="white", size=1.5, linetype="solid"
-     ),
-     legend.position='none',
-     panel.spacing = unit(2, "lines")
-   )+
-   geom_signif(
-    data = annotation_df,
-    aes(xmin = start, xmax = end, annotations = label, y_position = y),
-    textsize = 4,tip_length = .1,
-    manual = TRUE
-  )+
-  scale_y_continuous(expand=c(0,0),limits=c(0,1))
-
-prs_rwr_comp
-```
-
 ```{r}
@@
 
-ggsave(glue("{figure_folder}/fig5b.png"),plot=prs_rwr_comp, width=3,height=4)
-
 # Using the cowplot package

### 2021-05-27 notebooks/04-Fig5b-052721.Rmd
separated fig5 for better dependency control

--- 2021-05-24 notebooks/03-Fig3abde_4acd_5b-051821.Rmd
@@
 ---
-title: "25-Figure3-051821"
+title: "04-Figure5b"
 output: 
@@
 library(ggsignif)
-library(RColorBrewer)
-col <- brewer.pal(n = 9, name = "Set1")
-sensor_colors <- col[2:6] # brewer.pal(n = 6, name = "Set1")
-effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
-if(!require("FSA")){
-  remotes::install_github('droglenc/FSA')
-}
 ```
 
+# Figure 5
+## B
 ```{r}
-sessionInfo()
-```
-# Load necessary data
-```{r}
-
-sensor_connectivity_df <- read_csv(snakemake@input[['sensor_connectivity_df']])#"../data/interim/sensor_connectivity_df.csv") 
-pcc_df <- read_csv(snakemake@input[['pcc_df']])#'../data/interim/pcc_df.csv')
-sensors_pcc <- read_csv(snakemake@input[['sensors_pcc']])%>%#'../data/interim/sensors_df.csv')%>%
- mutate(go_group = (as.character(go_group)), go_group = ifelse(go_group == "NULL", NA, go_group))
-effector_pcc <- read_csv(snakemake@input[['effector_pcc']])#'../data/interim/effectors_df.csv')
 
@@
 go_combined <- data.table::rbindlist(list(rwr_row,prs_row,rwr_column,prs_column))
-```
-# Figure3
-## A
-```{r}
-sensor_neighbor_degree_plot <- pcc_df %>%
-  mutate(is_sensor = factor(ifelse(sens > quantile(sens, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
-  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
-  geom_boxplot() +
-  theme_bw() +
-  ylab("Log(Average neighbor degree)") +
-  xlab("") +
-  stat_compare_means() +
-  scale_x_discrete(labels = c("Sensor", "Not Sensor"))
-  sensor_neighbor_degree_plot
-
-```
-
-## B
-```{r}
-sensor_connectivity_plot <-
-  ggplot() +
-  geom_density(data = sensor_connectivity_df %>% filter(type != "real"), aes(x = ratio, color = type)) +
-  geom_vline(data = sensor_connectivity_df %>% filter(type == "real"), aes(xintercept = ratio, color = type)) +
-  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
-  ylab("Density") +
-  xlab("Ratio of between group edges\nto outgroup edges") +
-  theme_bw() +
-  scale_color_discrete(labels = c("Random sampled set", "Sensors")) +
-  theme(legend.position = "bottom") +
-  scale_y_continuous(expand = c(0, 0))
-  sensor_connectivity_plot
-```
-
-## D
-```{r}
-
-sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
-  geom_boxplot(
-    outlier.shape=NA) +
-  xlab("") +
-  ylab("Degree") +
-  scale_fill_manual(values = c(sensor_colors[1:5],'black')) +
-  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
-  theme_bw() +
-  theme(
-        axis.title.y=element_text(size=14),
-        axis.text.y=element_text(size=10),
-    axis.text.x = element_blank(), legend.title = element_blank(),
-    legend.text = element_text(margin = margin(t = 10, b = 10))
-  )+scale_y_log10()
-sens_deg_comp
-
-```
-
-## E
-```{r}
-
-sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)%>%fct_recode(
-  `Iron ion transport`  = "cellular response to iron ion starvation",
-  `Mitochondria-nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle`="mitochondria-nucleus signaling pathway",
-  `Phenylalanine transport`="phenylalanine transport",
-  `Hexose metabolic process`="hexose metabolic process",
-  `Tricarboxylic acid cycle`="tricarboxylic acid cycle"
-)
-sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
-sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]
-
-sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
-  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
-  geom_boxplot() +
-  geom_signif(
-    comparisons = list(
-      c("Hexose metabolic process", "Phenylalanine transport"), c("Tricarboxylic acid cycle", "Phenylalanine transport")#,
-      #c("phenylalanine\ntransport", "protein folding")
-    ),
-    annotation = c("**", "**"), y_position = c(0.007, 0.0075)#, 0.008)
-  ) +
-  xlab("") +
-  ylab("Sensitivity") +
-  scale_fill_manual(values = sensor_colors) +
-  theme_bw() +
-  theme(
-        axis.title.y=element_text(size=14),
-        axis.text.y=element_text(size=10),
-        axis.text.x = element_blank(),
-        legend.title = element_blank())
-
-sens_sens_comp
-```
-
-# Figure4
-## A
-```{r}
-eff_neighbor_degree_plot <- pcc_df %>%
-  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real")%>%
-  mutate(is_effector = factor(ifelse(eff_norm > quantile(eff_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
-  ggplot(aes(x = is_effector, y = log(neighbor_degree))) +
-  geom_boxplot() +
-  theme_bw() +
-  ylab("Log(Average neighbor degree)") +
-  xlab("") +
-  stat_compare_means() +
-  scale_x_discrete(labels = c("Effector", "Not Effector"))
-eff_neighbor_degree_plot
-```
-
-## C
-```{r}
-effector_pcc$go_group <- as.factor(effector_pcc$go_group)%>%fct_recode(
-  golgi = "phosphatidylinositol biosynthetic process",
-  mito = "mitochondrial cytochrome c oxidase assembly",
-  chromosome = "replication fork protection"
-)
-
-# res.aov <- kruskal.test(eff~go_group, data= effector_pcc)
-# res.aov
-effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
-effector_eff_pval$res[effector_eff_pval$res$P.adj < 0.1, ]
-effector_deg_pval <- FSA::dunnTest(deg ~ go_group, effector_pcc)
-effector_deg_pval$res[effector_deg_pval$res$P.adj < 0.1, ]
-
-eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_reorder(go_group, eff),go_group=fct_relevel(go_group,'Others',after=Inf)),
-                       aes(x = go_group, y = deg, fill = go_group)) +
-  geom_boxplot(outlier.shape = NA) +
-  scale_fill_manual(
-    values = c(effector_colors,'black'),
-    labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
-  ) +
-  xlab("") +
-  ylab("Degree") +
-  theme_bw() +
-  geom_signif(
-    comparisons = list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
-    annotation = c("**", "***", "ns"),
-    y_position = c(115, 120, 130)
-  ) +
-  theme(
-       axis.text.y=element_text(size=10),
-        axis.title.y=element_text(size=14),legend.title = element_blank(),  axis.text.x = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
-eff_deg_comp
-```
-
-## D
-```{r}
-
-eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
-  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
-  geom_boxplot() +
-  xlab("") +
-  ggpubr::stat_compare_means(method = "kruskal.test") +
-  scale_fill_manual(values = effector_colors,
-  labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
-  ylab("Effectiveness") +
-  theme_bw() +
-  theme(
-        axis.text.y=element_text(size=10),
-        axis.title.y=element_text(size=14),axis.text.x = element_blank(), legend.title = element_blank())
-eff_eff_comp
-```
-
-# Figure 5
-## B
-```{r}
 ci <- function(p,n){
@@
 }
+
 # New facet label names for dose variable
@@
   scale_y_continuous(expand=c(0,0),limits=c(0,1))
+
+prs_rwr_comp
 ```
+
+```{r}
+if(snakemake@params['save']==TRUE){
+
+  figure_folder = "reports/figures/paper_figures_052521/"
+    ggsave(glue("{figure_folder}/fig5b.png"),plot=prs_rwr_comp, width=3,height=4)
+}
+
+```

### 2021-05-27 enm/Enm.py

@@ -284,7 +284,7 @@ class Enm():
             nx.set_edge_attributes(self.graph_gc,0,'weight')
         if node_weight is None:
             node_weight = (1/self.prs_mat_df.loc[source,:]).to_dict()
-#            node_weight[source] = 1
+            node_weight[source] = 1
         if target is not None:
             distances = nx.single_source_dijkstra(self.graph_gc, source=source,target=target, weight=weight, node_weight=node_weight)
         else:

### 2021-05-27 notebooks/04-Fig5b-052721.Rmd
update on calculating effector name intersections

@@
 }
+
+prs_column$tolist  <-  str_remove_all(prs_column$study_items,'\\[|\\]')%>%
+  #str_split(.,', ')%>%
+  str_extract_all(.,"[^',]+[^']")# %>%list()
+
+df <- data.frame(matrix(ncol = 2, nrow = 0))
+colnames(df) <- c("orf_name_id", "count")
+for(i in unique(prs_column$orf_name_id)){
+  all_set = unlist(prs_column$tolist[prs_column$orf_name_id==i])
+  int_ <- length(intersect(all_set,effector_pcc$`Systematic gene name`))
+  df <- bind_rows(df,data.frame(orf_name_id=i,count=int_))
+}
+num_of_groups_with_effectors <- df%>%filter(count>0)%>%nrow()
 

### 2021-05-30 notebooks/02-Figure2-051321.Rmd
install r dependencies using remotes, instead of conda

@@
 ```{r, message=FALSE,warning=FALSE}
+if (!require('tidyverse')) {
+   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
    library(tidyverse)
+}
+if (!require('glue')) {
+   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
    library(glue)
+}
+if (!require('cowplot')) {
+   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
    library(cowplot)
+}
+if (!require('ggpubr')) {
+   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
+   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
    library(ggpubr)
+}
+if (!require('ggsignif')) {
+   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
    library(ggsignif)
+}
+if (!require('RColorBrewer')) {
+   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
+   library(RColorBrewer)
+}
 

### 2021-05-30 notebooks/03-Fig3abde_4acd-051821.Rmd
install r dependencies using remotes, instead of conda

@@
 ```{r, message=FALSE,warning=FALSE}
+#library(tidyverse)
+if (!require('tidyverse')) {
+   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
    library(tidyverse)
+}
+if (!require('glue')) {
+   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
    library(glue)
+}
+if (!require('cowplot')) {
+   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
    library(cowplot)
+}
+if (!require('ggpubr')) {
+   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
+   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
    library(ggpubr)
+}
+if (!require('ggsignif')) {
+   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
    library(ggsignif)
+}
+if (!require('RColorBrewer')) {
+   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
    library(RColorBrewer)
+}
 col <- brewer.pal(n = 9, name = "Set1")

### 2021-05-30 notebooks/04-Fig5b-052721.Rmd
install r dependencies using remotes, instead of conda

@@
 ```{r, message=FALSE,warning=FALSE}
+if (!require('tidyverse')) {
+   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
    library(tidyverse)
+}
+if (!require('glue')) {
+   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
    library(glue)
+}
+if (!require('cowplot')) {
+   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
    library(cowplot)
+}
+if (!require('ggpubr')) {
+   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
+   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
    library(ggpubr)
+}
+if (!require('ggsignif')) {
+   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
    library(ggsignif)
+}
 ```
@@
 # Ranked groups GO enrichment results
+effector_pcc <- read_csv(snakemake@input[['effector_pcc']])#'../data/interim/effectors_df.csv')
 rwr_row <- read_csv(snakemake@input[['rwr_row']])%>%mutate(data = 'rwr_row')

### 2021-06-01 notebooks/02-Figure2-051321.Rmd
adjusted network legends

--- 2021-05-24 notebooks/23-Figure2-051321.Rmd
@@
 }
-
 ```
@@
 #ggsave("reports/figures/paper_figures_0202_pcc_only/fig2.png", plot = deg_scatter_plots, width = 10, height = 10)
+print(cor.test(pcc_df$deg[pcc_df$deg<10],pcc_df$sens[pcc_df$deg<10],method='spearman',exact=FALSE))
 ```
@@
 ```
+
+```{r}
+if(snakemake@params['save']==TRUE){
+  figure_folder = "../reports/figures/paper_figures_052521/"
+combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
+ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=10,height=12)
+}
+```

### 2021-06-02 notebooks/02-Figure2-051321.Rmd
added a.u. to plots

--- 2021-05-30 notebooks/02-Figure2-051321.Rmd
@@
 knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
+Sys.setenv(TAR = "/bin/tar")
 ```
@@
 (
- 	df , x , xlab= 'Effectiveness', ylab='Density', coord_trans='log10', linesize = 1
+ 	df , x , xlab= 'Effectiveness (a.u.)', ylab='Density', coord_trans='log10', linesize = 1
 )
@@
 }
-message(snakemake@params['save'])
 ```
@@
   theme_bw() +
-  ylab("Effectiveness") +
+  ylab("Effectiveness (a.u.)") +
   xlab("Degree") +
@@
   theme_bw() +
-  ylab("Sensitivity") +
+  ylab("Sensitivity (a.u.)") +
   xlab("Degree") +
@@
 pcc_sensitivity_dens <-
-  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity") + theme(legend.position = "none")) #+
+  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity (a.u.)") + theme(legend.position = "none")) #+
 #        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
@@
   figure_folder = "reports/figures/paper_figures_052521/"
-combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.4, .3))
+combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
 ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=10,height=12)

### 2021-06-02 notebooks/03-Fig3abde_4acd-051821.Rmd
added a.u. to plots

@@
   xlab("") +
-  ylab("Sensitivity") +
+  ylab("Sensitivity (a.u.)") +
   scale_fill_manual(values = sensor_colors) +
@@
   labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
-  ylab("Effectiveness") +
+  ylab("Effectiveness (a.u.)") +
   theme_bw() +

### 2021-06-04 notebooks/02-Figure2-051321.Rmd
changed significance star levels

@@
 pcc_eff_dens <-
-  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness")
+  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness (a.u.)")
 dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
@@
 pcc_eff_dens <-
-  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
+  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness (a.u.)") + theme(legend.position = "none") +
     coord_trans(x = "log10", xlim = c(NA, 10e-2)) +

### 2021-06-04 notebooks/03-Fig3abde_4acd-051821.Rmd
changed significance star levels

@@
     ),
-    annotation = c("**", "**"), y_position = c(0.007, 0.0075)#, 0.008)
+    annotation = c("*", "*"), y_position = c(0.007, 0.0075)#, 0.008)
   ) +
@@
     comparisons = list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
-    annotation = c("**", "***", "ns"),
+    annotation = c("*", "***", "ns"),
     y_position = c(115, 120, 130)

### 2021-08-23 notebooks/7-different-network-sizes.py
compare analysis with different networks thresholds

@@ -1,0 +1,197 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:percent
+#     text_representation:
+#       extension: .py
+#       format_name: percent
+#       format_version: '1.3'
+#       jupytext_version: 1.5.2
+#   kernelspec:
+#     display_name: Python (enm)
+#     language: python
+#     name: enm
+# ---
+
+# %%
+import pandas as pd
+import networkx as nx
+import numpy as np
+import matplotlib.pyplot as plt
+
+# %%
+cpcc = pd.read_csv('../data/interim/costanzo_pcc_ALL')
+
+
+# %%
+def get_giant_component(G):
+    Gc = max([G.subgraph(c).copy() for c in nx.connected_components(G)], key=len)
+    return Gc
+
+
+# %%
+ne_ratio_list = []
+nv_ratio_list = []
+
+# %%
+thr_list =  [0.05,0.1,0.2,0.25,0.3,0.35,0.4,0.45,0.5]
+
+# %%
+for i in np.arange(0.2,0.75,0.05):
+    df = cpcc.loc[cpcc.pcc>i]
+    nw = nx.from_pandas_edgelist(df,source='gene1',target='gene2')
+    nw_g = get_giant_component(nw)
+    n_e = len(nw_g.edges)
+    ne_ratio_list.append(n_e/len(nw.edges))
+    n_v = len(nw_g.nodes)
+    nv_ratio_list.append(n_v/len(nw.nodes))
+
+    print(f"{i} : ne = {n_e}, ne_ratio: {n_e/len(nw.edges)}, nv = {n_v}, nv_ratio = {n_v/len(nw.nodes)}")
+
+# %%
+xlab = "Pearson's Correlation Coefficient threshold"
+
+# %%
+fig, ax = plt.subplots(1,1,figsize=(8,8))
+ax.plot(np.arange(0.2,0.75,0.05),nv_ratio_list,'o-')
+ax.set_ylabel('Giant component size to network size')
+ax.set_xlabel(xlab)
+
+# %%
+sensor_df_names = [ ]
+
+
+# %%
+def get_result_dfs(fname, thr_list, default_thr):
+    dfs = {thr: pd.read_csv(f"../data/interim_{thr}/{fname}.csv") for thr in thr_list if thr!=default_thr}
+    dfs[default_thr] = pd.read_csv(f"../data/interim/{fname}.csv")
[…]

### 2021-08-23 notebooks/03-Fig3abde_4acd-051821.Rmd
adjusted notebooks by removing default labels that cause errors

--- 2021-05-30 notebooks/03-Fig3abde_4acd-051821.Rmd
@@
 # Load packages
-```{r, message=FALSE,warning=FALSE}
+```{r message=FALSE, warning=FALSE}
 #library(tidyverse)
@@
 
-```{r, include=FALSE, eval=FALSE}
+```{r include=FALSE, eval=FALSE}
 # sessionInfo()
@@
 ```{r}
-sensors_pcc %>% drop_na()%>%kruskal.test(deg~go_group,data=.)
+#sensors_pcc %>% drop_na()%>%kruskal.test(deg~go_group,data=.)
 
-sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)%>%fct_recode(
-  `Iron ion transport`  = "cellular response to iron ion starvation",
-  `Mitochondria-nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle`="mitochondria-nucleus signaling pathway",
-  `Phenylalanine transport`="phenylalanine transport",
-  `Hexose metabolic process`="hexose metabolic process",
-  `Tricarboxylic acid cycle`="tricarboxylic acid cycle"
-)
+sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
 sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
@@
   scale_fill_manual(values = c(sensor_colors[1:5],'black')) +
-  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
+  #ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
   theme_bw() +
@@
 
-sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
-sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]
-
-sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
+if(nrow(sensors_pcc%>%drop_na(go_group))!=0){
+sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% #mutate(go_group = fct_reorder(go_group, sens)) %>%
   mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
   geom_boxplot() +
-  geom_signif(
-    comparisons = list(
-      c("Hexose metabolic process", "Phenylalanine transport"), c("Tricarboxylic acid cycle", "Phenylalanine transport")#,
-      #c("phenylalanine\ntransport", "protein folding")
-    ),
-    annotation = c("**", "**"), y_position = c(0.007, 0.0075)#, 0.008)
-  ) +
+#   geom_signif(
+#     comparisons = list(
+#       c("Hexose metabolic process", "Phenylalanine transport"), c("Tricarboxylic acid cycle", "Phenylalanine transport")#,
+#       #c("phenylalanine\ntransport", "protein folding")
+#     ),
+#     annotation = c("*", "*"), y_position = c(0.007, 0.0075)#, 0.008)
+#   ) +
   xlab("") +
-  ylab("Sensitivity") +
+  ylab("Sensitivity (a.u.)") +
   scale_fill_manual(values = sensor_colors) +
@@
 
-sens_sens_comp
+sens_sens_comp}
 ```
@@
 # )
-effector_pcc  <- effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff), 
-          go_group = factor(go_group,labels=c('chromosome','golgi','mito')))
-res.aov <- kruskal.test(deg~go_group, data= effector_pcc)
-res.aov
+effector_pcc  <- effector_pcc#%>%mutate(go_group=fct_reorder(go_group, eff))
+# res.aov <- kruskal.test(deg~go_group, data= effector_pcc)
+# res.aov
 effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
@@
 
-effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_relevel(go_group,'Others',after=Inf))%>%
-  kruskal.test(deg~go_group, data=.)
+effector_pcc %>% right_join(pcc_df)
 
@@
   geom_boxplot(outlier.shape = NA) +
-  scale_fill_manual(
-    values = c(effector_colors,'black'),
-    labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
-  ) +
+#   scale_fill_manual(
+#     values = c(effector_colors,'black'),
+#     labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
+#   ) +
   xlab("") +
@@
   theme_bw() +
-  geom_signif(
-    comparisons = list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
-    annotation = c("**", "***", "ns"),
-    y_position = c(115, 120, 130)
-  ) +
+#   geom_signif(
+#     comparisons = list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
+#     annotation = c("*", "***", "ns"),
+#     y_position = c(115, 120, 130)
+#   ) +
   theme(
@@
 
-eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
+eff_eff_comp <- ggplot(effector_pcc %>% #mutate(go_group = fct_reorder(go_group, eff)) %>%
   mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
@@
   xlab("") +
-  ggpubr::stat_compare_means(method = "kruskal.test") +
-  scale_fill_manual(values = effector_colors,
-  labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
-  ylab("Effectiveness") +
+  #ggpubr::stat_compare_means(method = "kruskal.test") +
+#   scale_fill_manual(values = effector_colors,
+#   labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
+  ylab("Effectiveness (a.u.)") +
   theme_bw() +

### 2021-08-23 notebooks/01-Fig1bcd_3c_4b_5df-052421.py

@@ -1,0 +1,542 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:percent
+#     text_representation:
+#       extension: .py
+#       format_name: percent
+#       format_version: '1.3'
+#       jupytext_version: 1.5.2
+#   kernelspec:
+#     display_name: Python 3
+#     language: python
+#     name: python3
+# ---
+
+# %% [markdown] toc=true
+# <h1>Table of Contents<span class="tocSkip"></span></h1>
+# <div class="toc"><ul class="toc-item"><li><span><a href="#Import-packages" data-toc-modified-id="Import-packages-1"><span class="toc-item-num">1&nbsp;&nbsp;</span>Import packages</a></span></li><li><span><a href="#Read-Enm-pickle-object" data-toc-modified-id="Read-Enm-pickle-object-2"><span class="toc-item-num">2&nbsp;&nbsp;</span>Read Enm pickle object</a></span></li><li><span><a href="#Calculate-node-positions-with-spring-layout" data-toc-modified-id="Calculate-node-positions-with-spring-layout-3"><span class="toc-item-num">3&nbsp;&nbsp;</span>Calculate node positions with spring layout</a></span></li><li><span><a href="#Network-plot" data-toc-modified-id="Network-plot-4"><span class="toc-item-num">4&nbsp;&nbsp;</span>Network plot</a></span><ul class="toc-item"><li><span><a href="#Figure-1B,-left" data-toc-modified-id="Figure-1B,-left-4.1"><span class="toc-item-num">4.1&nbsp;&nbsp;</span>Figure 1B, left</a></span></li><li><span><a href="#Figure-1B,-right" data-toc-modified-id="Figure-1B,-right-4.2"><span class="toc-item-num">4.2&nbsp;&nbsp;</span>Figure 1B, right</a></span></li></ul></li><li><span><a href="#Figure-1C" data-toc-modified-id="Figure-1C-5"><span class="toc-item-num">5&nbsp;&nbsp;</span>Figure 1C</a></span></li><li><span><a href="#Figure-1D" data-toc-modified-id="Figure-1D-6"><span class="toc-item-num">6&nbsp;&nbsp;</span>Figure 1D</a></span></li><li><span><a href="#Figure-3C" data-toc-modified-id="Figure-3C-7"><span class="toc-item-num">7&nbsp;&nbsp;</span>Figure 3C</a></span></li><li><span><a href="#Figure-4B" dat
[…]

### 2021-09-11 notebooks/03-Fig3abde_4acd-051821.Rmd
fixed sensor plots to include non-go enriched for 0.2

@@
 col <- brewer.pal(n = 9, name = "Set1")
-sensor_colors <- col[2:6] # brewer.pal(n = 6, name = "Set1")
+sensor_colors <- brewer.pal(n = 12, name = "Set3")
 effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
@@
   scale_color_discrete(labels = c("Random sampled set", "Sensors")) +
-  theme(legend.position = "bottom") +
+  theme(legend.position = "right") +
   scale_y_continuous(expand = c(0, 0))
@@
 ```{r}
-#sensors_pcc %>% drop_na()%>%kruskal.test(deg~go_group,data=.)
+# sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)%>%fct_recode(
+#   `Iron ion transport`  = "cellular response to iron ion starvation",
+#   `Mitochondria nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle`="mitochondria-nucleus signaling pathway",
+#   `Phenylalanine transport`="phenylalanine transport",
+#   `Hexose metabolic process`="hexose metabolic process",
+#   `Tricarboxylic acid cycle`="tricarboxylic acid cycle"
+# )
 
-sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
-sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
+# sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
+# sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]
+```
+
+```{r}
+sensors_pcc<- sensors_pcc%>%
+    mutate(sensor_cluster=factor(replace_na(as.character(sensor_cluster),"Unclustered")),
+    sensor_cluster = fct_reorder(sensor_cluster, sens))%>%
+    group_by(sensor_cluster)%>%
+    mutate(gid = cur_group_id())%>%ungroup()%>%
+    mutate(cluster_or_go = ifelse(sensor_cluster=='Unclustered','Unclustered',
+                                  ifelse(is.na(as.character(go_group)), gid, as.character(go_group))))%>%
+    mutate(cluster_or_go = fct_recode(as.factor(cluster_or_go), `Iron ion\ntransport`  = "cellular response to iron ion starvation",
+`Mitochondria nucleus\nsignaling pathway`="mitochondria-nucleus signaling pathway",
+`Phenylalanine\ntransport`="phenylalanine transport",
+`Hexose metabolic\nprocess`="hexose metabolic process",
+`Tricarboxylic acid\ncycle`="tricarboxylic acid cycle"))%>%
+    mutate(label = as.factor(case_when(
+        cluster_or_go == 'Unclustered' ~ 'Unclustered',
+        is.na(as.numeric(as.character(cluster_or_go))) == FALSE ~ paste0('SC',(gid-1)),
+        TRUE ~ paste0('SC',gid-1,'\n(',cluster_or_go,')')
+    )))
+```
+
+```{r}
+sensors_sens_pval <- FSA::dunnTest(sens ~ as.factor(label), sensors_pcc)
+sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]
+```
+
+```{r}
+sensors_pcc %>% drop_na()%>%kruskal.test(deg~label,data=.)
+
+#sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
+sens_deg_comp <- ggplot(sensors_pcc %>% right_join(pcc_df)%>% 
+                        mutate(label = factor(replace_na(as.character(label),"Non-sensor genes")),
+                               label=fct_reorder(label, sens),
+                               label=fct_relevel(label,'Non-sensor genes',after=Inf)), 
+                        aes(x = as.factor(label), y = deg, fill = as.factor(label))) +
   geom_boxplot(
@@
   ylab("Degree") +
-  scale_fill_manual(values = c(sensor_colors[1:5],'black')) +
-  #ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
+  scale_fill_manual(values = c(sensor_colors[1:10],'black')) +
+  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
   theme_bw() +
@@
         axis.text.y=element_text(size=10),
-    axis.text.x = element_blank(), legend.title = element_blank(),
+        axis.text.x = element_blank(), 
+        legend.title = element_blank(),
     legend.text = element_text(margin = margin(t = 10, b = 10))
@@
 ```{r}
+comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)]
+```
+
+```{r}
+comparisons <- str_split(sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]$Comparison,' - ',2)
 
 if(nrow(sensors_pcc%>%drop_na(go_group))!=0){
-sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% #mutate(go_group = fct_reorder(go_group, sens)) %>%
-  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
+sens_sens_comp <- ggplot(sensors_pcc %>% mutate(label = fct_reorder(label, sens)) %>%
+  mutate(sens_norm = sens / 5183), aes(x = (label), y = sens_norm, fill =(label))) +
   geom_boxplot() +
-#   geom_signif(
-#     comparisons = list(
-#       c("Hexose metabolic process", "Phenylalanine transport"), c("Tricarboxylic acid cycle", "Phenylalanine transport")#,
-#       #c("phenylalanine\ntransport", "protein folding")
-#     ),
-#     annotation = c("*", "*"), y_position = c(0.007, 0.0075)#, 0.008)
-#   ) +
+  geom_signif(
+    comparisons = comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)],
+    annotation = c("***","*" , "*" ,  "***"), y_position = c(0.007, 0.005,0.0055, 0.0075)#, 0.008)
+  ) +
   xlab("") +
@@
 
-effector_pcc %>% right_join(pcc_df)
+#effector_pcc %>% right_join(pcc_df)
 
@@
 ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
-ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot+theme(legend.position='none'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
 ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3,height=3)

### 2021-09-11 enm/utils.py

@@ -12,7 +12,7 @@ from goatools.anno.gaf_reader import GafReader
 from goatools.goea.go_enrichment_ns import GOEnrichmentStudyNS
 
 
-from .Enm import *
+#from .Enm import *
 
 def create_goea(gaf = '../data/raw/ontology/sgd.gaf', obo_fname = '../data/raw/ontology/go-basic.obo', background='../data/raw/ontology/sgd_costanzogenes', sgd_info_tab='../data/raw/ontology/SGD_features.tab',species='yeast',**kwargs):
     
@@ -167,14 +167,14 @@ def get_random_in_to_out_ratio(gnm_df, df , G):
         random_ratio_list.append(get_in_to_out_edge_ratio(G, rand_nodes))
     return random_ratio_list
 
-# def get_subnetwork(gc, subset):
-#     neighbors =[[n for n in nx.neighbors(gc, i)] for i in subset]
-#     flat_list = [item for sublist in neighbors for item in sublist]
-#     flat_list.extend(subset)
-#     sub_gc = nx.induced_subgraph(gc, flat_list).copy()
-#     for (n,d) in sub_gc.nodes(data=True):
-#         del d["pos"]
-#     return sub_gc
+def get_subnetwork(gc, subset, radius = 1):
+    neighbors =[[n for n in nx.ego_graph(gc, i, radius=radius).nodes] for i in subset]
+    flat_list = [item for sublist in neighbors for item in sublist]
+    flat_list.extend(subset)
+    sub_gc = nx.induced_subgraph(gc, flat_list).copy()
+    for (n,d) in sub_gc.nodes(data=True):
+        del d["pos"]
+    return sub_gc
 
 
 # def get_maximal_subsets(sets):
@@ -246,3 +246,28 @@ def get_path_positions(enm, sensors_sub, effectors_sub):
         if i in sensor_pos.keys():
             path_init_pos[i]=sensor_pos[i]
     return sensor_pos, effector_pos, path_init_pos,sub, l1, wmin
+
+def convert_rpy2_to_pandas(df):
+    import rpy2.robjects as ro
+    from rpy2.robjects import pandas2ri
+
+    with ro.conversion.localconverter(ro.default_converter + pandas2ri.converter):
+        pd_from_r_df = ro.conversion.rpy2py(df)
+
+    return pd_from_r_df
+
+def get_result_dfs(fname, thr_list, default_thr=None):
+    def read_csv(fname):
+        try:
+            df = pd.read_csv(fname)
+        except pd.errors.EmptyDataError:
[…]

### 2021-09-11 notebooks/01-Fig1bcd_3c_4b_5df-052421.py

@@ -1,3 +1,4 @@
+# -*- coding: utf-8 -*-
 # ---
 # jupyter:
 #   jupytext:
@@ -8,9 +9,9 @@
 #       format_version: '1.3'
 #       jupytext_version: 1.5.2
 #   kernelspec:
-#     display_name: Python 3
+#     display_name: Python (enm)
 #     language: python
-#     name: python3
+#     name: enm
 # ---
 
 # %% [markdown] toc=true
@@ -68,7 +69,7 @@ pos =e_pcc.graph_gc.nodes('pos')
 # ## Figure 1B, left
 
 # %%
-fig, ax =plt.subplots(figsize=(5,5))
+fig, ax =plt.subplots(figsize=(4,4))
 
 nx.draw_networkx_nodes(e_pcc.graph_gc,
                            node_size=0.2,
@@ -84,6 +85,15 @@ nx.draw_networkx_edges(e_pcc.graph_gc,
                            edge_color='k',
                            pos=pos,
                            label='PCC>0.2',ax=ax)
+legend_elements = [Line2D([0], [0], marker='o', color='black', label='Genes',
+                              markerfacecolor='black', markersize=12, linestyle="None"),
+                       Line2D([0], [0], marker='o', color='black', label= 'High\nfunctional\nsimilarity\n(PCC≥0.2)',
+                              markerfacecolor='black', markersize=0, linestyle="-", alpha=0.5,lw=5)
+    ]
+
+lgd = ax.legend(handles=legend_elements, fontsize=12,loc='center left', bbox_to_anchor=(1, 0.5), frameon=False)
+
+ax.axis('off')
 if snakemake.params['save']:
     plt.savefig(f'{figure_folder}/fig1b_left.png',bbox_inches='tight',dpi=150)
 
@@ -148,28 +158,40 @@ pval_cc
 # %%
 import seaborn as sns
 color = {'cc': 'orange','other':'k','rc':'orangered'}
-fig, ax = plt.subplots(1,2,figsize=(8,4))
+fig, ax = plt.subplots(2,1,figsize=(3.5,2.8))
 
-sns.boxplot(data=df, x='rc',y='eff_norm',order=['rc','other'],palette=color,ax=ax[0])
-ax[0].set_xticklabels(['Distinct\nRow\nCluster', 'Other genes'])
-ax[0].set_xlabel('Row clusters')
[…]

### 2021-09-11 scripts/effector_sensor_go.py

@@ -4,6 +4,7 @@ import pickle
 from enm.Enm import *
 from enm.utils import *
 
+#snakemake = {'input': {'gaf': '../data/raw/ontology/sgd.gaf' , 'obo':'../data/raw/ontology/go-basic.obo', "background_file" :'../data/raw/ontology/sgd_costanzogenes', "sgd_info": '../data/raw/ontology/SGD_features.tab','pickle_file_name':'../data/interim_0.2/pcc.pickle'}}
 gaf = snakemake.input['gaf']
 obo = snakemake.input['obo']
 background_file = snakemake.input['background_file']
@@ -20,7 +21,27 @@ goea, geneid2name = create_goea(gaf = gaf, obo_fname=obo,
 enm.analyze_components_biology(goea, geneid2name, True)
 enm.analyze_components_biology(goea, geneid2name, False)
 
-enm.sensors_df.to_csv(snakemake.output.sensors_df_fname,index=False)
+sensors_df = enm.sensors_df.reset_index(drop=True)
+sensors_df['sensor_cluster'] = sensors_df.fillna(value={'sensor_cluster':'Unclustered'}).sensor_cluster.astype("category")
+
+order = sensors_df.groupby('sensor_cluster').median()['sens'].sort_values().index.values
+sensors_df['sensor_cluster'].cat.reorder_categories(list(order),ordered=True, inplace=True)
+sensors_df['gid'] = sensors_df.groupby('sensor_cluster').ngroup()
+sensors_df['cluster_or_go'] = ['Unclustered' if sensors_df.at[i,'sensor_cluster'] == 'Unclustered'
+                            else sensors_df.at[i,'gid'] if pd.isna(sensors_df.at[i,'go_group']) 
+                            else sensors_df.at[i,'go_group'] for i in range(sensors_df.shape[0])]
+di = {"cellular response to iron ion starvation":"Iron ion\ntransport" ,
+"mitochondria-nucleus signaling pathway":"Mitochondria nucleus\nsignaling pathway",
+"phenylalanine transport":"Phenylalanine\ntransport",
+"hexose metabolic process":"Hexose metabolic\nprocess",
+"tricarboxylic acid cycle":"Tricarboxylic acid\ncycle"}
+sensors_df.replace({'cluster_or_go': di},inplace=True)
+
+sensors_df['label'] = ["Unclustered" if sensors_df.at[i,'cluster_or_go']=='Unclustered' 
[…]

### 2021-09-11 scripts/read_costanzo_data.py

@@ -2,13 +2,15 @@ import numpy as np
 import pandas as pd
 input_file = snakemake.input[0]#"data/raw/Data File S3. Genetic interaction profile similarity matrices/cc_ALL.txt"
 output_file=snakemake.output[0]
+thr = float(snakemake.params['threshold'])
+
 df = pd.read_csv(input_file,'\t',index_col=[0,1], header=[0,1])
 
 df_long = df.melt(ignore_index=False, col_level=0)
 
 df_long_renamed = df_long.reset_index(inplace=False).rename(columns = {'level_0':'gene1','level_1':'Systematic gene name', 'variable':'gene2','value':'pcc'})
 
-df_long_renamed.loc[df_long_renamed.pcc>=0.2,['gene1','gene2','pcc']].to_csv(output_file, index=False,float_format="%.6f")
+df_long_renamed.loc[df_long_renamed.pcc>=thr,['gene1','gene2','pcc']].to_csv(output_file, index=False,float_format="%.6f")
 #df = df.rename(columns = {'index':'new column name'})
 
 df_long_renamed.iloc[:,[0,1]].drop_duplicates().to_csv(snakemake.output[1],index=False)

### 2021-09-12 notebooks/06-Fig1b-091121.Rmd
converted fig1b to complexheatmap in R

---
title: "PRS dendrogram clusters"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
#source('enm/R/plot_density_prs.R')
#source('enm/R/get.subclusters.dendrogram.R')
library(RColorBrewer)
col =brewer.pal(n=8,name='Set1')
sensor_colors = col[1:4]
effector_colors = col[5:8]
```

# Read data
Read data in python, from pickle file saved earlier.
```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from enm.Enm import Enm
from enm.utils import *
import scipy.cluster.hierarchy as sch
print(os.getcwd())
with open(f'../data/interim/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))

```

Use scipy distance calculation and pass the square form of the distance matrix to R.
This is done because R's `dist` function is significantly slower than scipy.

```{python}
prs_mat = e_pcc.prs_mat
quantile_threshold =  0.95
method = 'ward'
metric = 'seuclidean'
q99 = np.quantile(prs_mat, quantile_threshold)
prs_mat_cl = copy.deepcopy(prs_mat)
prs_mat_cl[prs_mat_cl > q99] = q99
prs_mat_cl_orig = prs_mat_cl
# , optimal_ordering=True)
#row_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl), method=method)
# ,optimal_ordering=True)
#col_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl.T), method=method)

row_dist_orig = sch.distance.pdist((prs_mat),metric = metric)
col_dist_orig = sch.distance.pdist((prs_mat.T),metric = metric)
row_dist_orig_sqr = sch.distance.squareform(row_dist_orig)
col_dist_orig_sqr = sch.distance.squareform(col_dist_orig)

row_dist = sch.distance.pdist(prs_mat_cl,metric = metric)
col_dist = sch.distance.pdist(prs_mat_cl.T,metric = metric)

row_dist_sqr = sch.distance.squareform(row_dist)
col_dist_sqr = sch.distance.squareform(col_dist)

```
# Plot heatmap
Using the clustering with `seuclidian` distance and `ward` linkage, plot the heatmap with row and column colors are the GO term annotations found from effector and sensor analysis

```{r}
library(tidyverse)
library(ComplexHeatmap)
cluster_method = 'ward.D2'
dist_row = as.dist(py$row_dist_sqr)
hclust_row = hclust(dist_row, cluster_method)
dist_col = as.dist(py$col_dist_sqr)
hclust_col = hclust(dist_col, cluster_method)
row_dend = as.dendrogram(hclust_row)%>% dendextend::color_branches(k=2, col = c('black', '#f15a24'))
col_dend = as.dendrogram(hclust_col)%>%  dendextend::color_branches(k=2, col = c('#f7931e', 'black'))
#row_dend <- row_dend %>%

# go_color_map = unlist(append(py$effector_colors_dict,py$sensor_colors_dict))
# go_color_map['none'] = 'white'
# clrs = go_color_map# map(py$eff_sens_go_list, ~ifelse(is.null(.x), 'none',.x))%>%unlist()

# rowColors = rowAnnotation(rowColors=py$e_pcc$df%>%left_join(py$effector_pcc)%>%select(go_term)%>%pull%>%map(~ifelse(is.na(.x), 'none',.x))%>%unlist(),
#                           col=list(rowColors = go_color_map ),
#                           #width=unit(100,'mm'),
#                           simple_anno_size=unit(3,'cm'),
#                           show_annotation_name=FALSE,
#                           show_legend=FALSE)
# colColors = columnAnnotation(colColors=py$e_pcc$df%>%left_join(py$sensors_pcc)%>%select(go_term)%>%pull%>%map(~ifelse(is.null(.x), 'none',
#                                                                                                                       ifelse(is.nan(.x),'none',.x)))%>%unlist(),
#                           col=list(colColors = go_color_map ),
#                           simple_anno_size=unit(3,'cm'),
#                           #annotation_height=unit(20,'mm'),
#                           show_annotation_name=FALSE,
#                           show_legend=FALSE)
rowAnnot = HeatmapAnnotation(Effectiveness=anno_lines(rowSums(py$prs_mat), border=FALSE,
                            width = unit(0.2, 'in'),
                            axis=FALSE),
                            which='row',
                            #name='', 
                            gp = gpar(col='blue'),
                            annotation_name_side = 'top',
                            annotation_name_rot= 90,
                            border=FALSE,
                            #annotation_name_gp= gpar(fontsize = 0)
                            show_annotation_name=FALSE,
                          show_legend=FALSE
)
colAnnot = HeatmapAnnotation(Sensitivity=anno_lines(colSums(py$prs_mat), 
                            axis = FALSE, border=FALSE,height = unit(0.2, 'in')), 
                             which='col', 
                            # name='',
                            gp = gpar(col='blue'),
                            #annotation_name_gp= gpar(fontsize = 0)
                            annotation_name_side = 'left',
                            annotation_name_rot=0,
                            border=FALSE,
                            show_annotation_name=FALSE,
                          show_legend=FALSE
)

png('tmp_heatmap.png', width = 3, height=2.5, units='in', res=150 )
hm<-Heatmap(py$prs_mat_cl, 
        cluster_rows = row_dend,#as.dendrogram(hclust_row),
        cluster_columns= col_dend,#as.dendrogram(hclust_col),
        col=RColorBrewer::brewer.pal(9,'YlGnBu'),
        row_dend_width = unit(0.2,'in'),
        column_dend_height = unit(0.2,'in'),
        right_annotation=rowAnnot,
#        left_annotation = rowColors,
        bottom_annotation=colAnnot,
#        top_annotation=colColors,
show_heatmap_legend = FALSE,
)
draw(hm ,padding = unit(c(0, 0.5, 0, 0), "in"))

dev.off()

png('tmp_heatmap_lgn.png', width = 3, height=2.5, units='in', res=150 )

lgd = Legend(title = "", 
            at = c(0, 1e-4,2e-4,3e-4,4e-4), col_fun = circlize::colorRamp2(c(0, 1e-4,2e-4,3e-4,4e-4), RColorBrewer::brewer.pal(5,'YlGnBu')) , labels_gp = gpar(font=6), title_position = 'leftcenter-rot', legend_width=unit(0.05, 'in'),labels_rot=45)
#
draw(lgd, x = unit(0.1, "npc"), y = unit(0.8, "npc"))

dev.off()
```

### 2021-09-17 notebooks/7-different-network-sizes.py
cleared supp figure notebook

@@ -81,8 +81,6 @@ sensor_dfs[0.2].dropna(subset=['sensor_cluster']).loc[:,'sensor_cluster'].nuniqu
 
 
 # %%
-
-# %%
 def plot_go_thr_comparison(dfs, col, yaxis,plotname, xlab='PCC Threshold'):
     n_goterms = []
     rat_goterms = []
@@ -115,13 +113,7 @@ def plot_go_thr_comparison(dfs, col, yaxis,plotname, xlab='PCC Threshold'):
 plot_go_thr_comparison(sensor_dfs,'sensor_cluster', 'sensor',plotname='thr_num_sensor_clusters')
 
 # %%
-plot_go_thr_comparison(effector_dfs,'effector_cluster', 'effector')
-
-# %%
-effector_sensor_go_dfs[0.2]
-
-# %%
-help(t.set_text)
+plot_go_thr_comparison(effector_dfs,'effector_cluster', 'effector',plotname='thr_num_effector_clusters')
 
 # %%
 #effector_sensor_go_dfs
@@ -158,141 +150,5 @@ plot_heatmap_overlap(sensor_overlap, 'sensor_overlap', 'Sensor overlap for diffe
 
 # %%
 plot_heatmap_overlap(effector_overlap, 'effector_overlap', 'Effector overlap for different thresholds', figsize=(5,5))
-
-# %%
-
-sensor_overlap = pd.DataFrame({thr : [len(np.intersect1d(sensor_dfs[thr].orf_name, sensor_dfs[i].orf_name)) for i in thr_list] for thr in sorted(thr_list)})
-sensor_overlap.index = thr_list
-
-effector_overlap = pd.DataFrame({thr : [len(np.intersect1d(effector_dfs[thr].orf_name, effector_dfs[i].orf_name)) for i in thr_list] for thr in sorted(thr_list)})
-effector_overlap.index = thr_list
-
-mask1 = np.zeros_like(sensor_overlap)
-mask1[np.tril_indices_from(mask1, k=-1)] = True
-mask2 = np.zeros_like(effector_overlap)
-mask2[np.tril_indices_from(mask2,k=-1)] = True
-with sns.axes_style("white"):
-    f, ax = plt.subplots(1,3,figsize=(16, 6), gridspec_kw={'width_ratios': [10,10, 1]})
[…]

### 2021-09-17 notebooks/05-Rewired-network-sensors.py
added notebook for rewired network sensors data

@@ -1,0 +1,174 @@
+# ---
+# jupyter:
+#   jupytext:
+#     formats: ipynb,py:percent
+#     text_representation:
+#       extension: .py
+#       format_name: percent
+#       format_version: '1.3'
+#       jupytext_version: 1.5.2
+#   kernelspec:
+#     display_name: Python (enm)
+#     language: python
+#     name: enm
+# ---
+
+# %%
+# %config Completer.use_jedi = False
+
+# %%
+import pandas as pd
+import numpy as np
+import networkx as nx
+import matplotlib.pyplot as plt
+
+# %%
+from enm.Enm import Enm, rewire_network
+from enm.utils import *
+
+# %%
+e = Enm('rew')
+
+# %%
+e.read_network('../data/interim/costanzo_pcc_ALL',sep=',')
+
+# %%
+gc_rew = rewire_network(e.graph_gc)
+
+# %%
+gc_rew
+
+# %%
+e_rew = Enm('rewired')
+
+# %%
+e_rew.G=gc_rew
+
+# %%
+e_rew.giant_component()
+
+# %%
+e_rew.gnm_analysis()
+
+# %%
+strain_ids =pd.read_csv('../data/interim/strain_ids.csv')
+e_rew.df = pd.merge(e_rew.df,strain_ids, left_on='orf_name',right_on='gene1')
+
+# %%
+e_rew.get_sensor_effector(True)
+
+# %%
+goea, geneid2name = create_goea(gaf='../data/raw/ontology/sgd.gaf', obo='../data/raw/ontology/go-basic.obo',background='../data/interim/go_background_list',
+                               sdg_info_tab='../data/raw/ontology/SGD_features.tab')
+
+# %% jupyter={"outputs_hidden": true}
+e_rew.analyze_components_biology(goea, geneid2name,True)
+e_rew.analyze_components_biology(goea, geneid2name,False)
+
+# %%
+e_rew.get_sensor_effector()
+
+# %%
+sensors_pcc = e_rew.sensors_df
+
+# %%
+pos = e_rew.graph_gc.nodes('pos')
+
+# %%
+from matplotlib.lines import Line2D
+
+fig, ax = plt.subplots(figsize=(9,9))
+#axs = ax.ravel()
+legend_elements = [    ]
+
+#for i in range(len(sensor_order)):
+e_rew.plot_network_spring(ax=ax,
+                          node_size=1,
+                          node_color='black',
[…]

### 2021-09-17 notebooks/03-Fig3abde_4acd-051821.Rmd
notebook03 changed colors and figure sizes

@@
     mutate(label = as.factor(case_when(
-        cluster_or_go == 'Unclustered' ~ 'Unclustered',
-        is.na(as.numeric(as.character(cluster_or_go))) == FALSE ~ paste0('SC',(gid-1)),
-        TRUE ~ paste0('SC',gid-1,'\n(',cluster_or_go,')')
+        cluster_or_go == 'Unclustered' ~ '\nUnclustered',
+       # is.na(as.numeric(as.character(cluster_or_go))) == FALSE ~ paste0('SC',(gid-1)),
+        TRUE ~ paste0('SC',gid-1)
     )))
@@
 sens_deg_comp <- ggplot(sensors_pcc %>% right_join(pcc_df)%>% 
-                        mutate(label = factor(replace_na(as.character(label),"Non-sensor genes")),
+                        mutate(label = factor(replace_na(as.character(label),"\nNon-sensor\ngenes")),
                                label=fct_reorder(label, sens),
-                               label=fct_relevel(label,'Non-sensor genes',after=Inf)), 
+                               label=fct_relevel(label,'\nNon-sensor\ngenes',after=Inf)), 
                         aes(x = as.factor(label), y = deg, fill = as.factor(label))) +
@@
   scale_fill_manual(values = c(sensor_colors[1:10],'black')) +
-  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
+  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3, size=3, vjust = 1.5) +
   theme_bw() +
@@
         axis.text.y=element_text(size=10),
-        axis.text.x = element_blank(), 
+        axis.text.x = element_text(size=7), 
         legend.title = element_blank(),
@@
     comparisons = comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)],
-    annotation = c("***","*" , "*" ,  "***"), y_position = c(0.007, 0.005,0.0055, 0.0075)#, 0.008)
+    annotation = c("***","*" , "*" ,  "***"), y_position = c(0.007, 0.005,0.0058, 0.0078),
+                                           textsize = 3#, 0.008)
   ) +
@@
         axis.text.y=element_text(size=10),
-        axis.text.x = element_blank(),
+        axis.text.x = element_text(size=7),
         legend.title = element_blank())+
@@
 if(snakemake@params['save']==TRUE){
-  figure_folder = "reports/figures/paper_figures_052521/"
+  figure_folder = "../reports/figures/paper_figures_052521/"
 ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
 ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
-ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3,height=3)
-ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3.9,height=2.1)
+ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3.9,height=2.1)
 

### 2021-10-16 notebooks/03-Fig3abde_4acd-051821.Rmd
rew sensors and gprofiler analysis

@@
 ```{r}
-comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)]
+#comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)]
 ```
@@
 # )
-effector_pcc  <- effector_pcc#%>%mutate(go_group=fct_reorder(go_group, eff))
+effector_pcc  <- effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff))
 # res.aov <- kruskal.test(deg~go_group, data= effector_pcc)
@@
 
-#effector_pcc %>% right_join(pcc_df)
+comparisons_effectors <- str_split(effector_deg_pval$res$Comparison,' - ',2)
 
-eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_relevel(go_group,'Others',after=Inf)), 
+eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% 
+                       mutate(go_group = factor(replace_na(as.character(go_group),"Others")),
+                              go_group=fct_reorder(go_group, eff),
+                              go_group= fct_relevel(go_group,'Others',after=Inf)), 
                        aes(x = go_group, y = deg, fill = go_group)) +
   geom_boxplot(outlier.shape = NA) +
-#   scale_fill_manual(
-#     values = c(effector_colors,'black'),
-#     labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
-#   ) +
+   scale_fill_manual(
+     values = c(effector_colors,'black'),
+     labels = c("EC1 (Chromosome\nSegregation)", "EC2 (Golgi vesicle\nTransport)", "EC3 (Respiratory complex\nassembly)",'Non-effector genes')
+   ) +
   xlab("") +
@@
   theme_bw() +
-#   geom_signif(
-#     comparisons = list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
-#     annotation = c("*", "***", "ns"),
-#     y_position = c(115, 120, 130)
-#   ) +
+   geom_signif(
+     comparisons = comparisons_effectors[order(sapply(comparisons_effectors, function(x) x[1], simplify=TRUE), decreasing=TRUE)], #list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
+     annotation = c("*", "***", "ns"),
+     y_position = c(115, 120, 130)
+   ) +
   theme(
@@
   xlab("") +
-  #ggpubr::stat_compare_means(method = "kruskal.test") +
-#   scale_fill_manual(values = effector_colors,
-#   labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
+  ggpubr::stat_compare_means(method = "kruskal.test") +
+   scale_fill_manual(values = effector_colors,
+   labels = c("EC1 (Chromosome\nSegregation)", "EC2 (Golgi vesicle\nTransport)", "EC3 (Respiratory complex\nassembly)")) +
   ylab("Effectiveness (a.u.)") +
@@
 ggsave(glue("{figure_folder}/fig4a.png"),plot=eff_neighbor_degree_plot,width=3,height=3)
-ggsave(glue("{figure_folder}/fig4c.png"),plot=eff_deg_comp+theme(legend.position='none'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig4c.png"),plot=eff_deg_comp+theme(legend.position='right'),width=3,height=3)
 ggsave(glue("{figure_folder}/fig4d.png"),plot=eff_eff_comp+theme(legend.position='none'),width=3,height=3)

### 2021-10-16 notebooks/05-Rewired-network-sensors.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: percent
 #       format_version: '1.3'
-#       jupytext_version: 1.5.2
+#       jupytext_version: 1.12.0
 #   kernelspec:
 #     display_name: Python (enm)
 #     language: python
@@ -21,10 +21,21 @@ import pandas as pd
 import numpy as np
 import networkx as nx
 import matplotlib.pyplot as plt
-
-# %%
+from matplotlib.lines import Line2D
 from enm.Enm import Enm, rewire_network
 from enm.utils import *
+import pickle
+import random
+random.seed(4812)        # or any integer
+np.random.seed(4813)
+
+# %%
+# with open('../data/interim/pcc.pickle', 'rb') as f:
+#     enm_ee = pickle.load(f)
+
+# %%
+strain_ids =pd.read_csv('../data/interim/strain_ids.csv')
+
 
 # %%
 e = Enm('rew')
@@ -34,34 +45,18 @@ e.read_network('../data/interim/costanzo_pcc_ALL',sep=',')
 
 # %%
 gc_rew = rewire_network(e.graph_gc)
-
-# %%
-gc_rew
-
-# %%
 e_rew = Enm('rewired')
-
-# %%
 e_rew.G=gc_rew
-
-# %%
 e_rew.giant_component()
-
-# %%
 e_rew.gnm_analysis()
-
-# %%
-strain_ids =pd.read_csv('../data/interim/strain_ids.csv')
 e_rew.df = pd.merge(e_rew.df,strain_ids, left_on='orf_name',right_on='gene1')
-
-# %%
 e_rew.get_sensor_effector(True)
 
 # %%
-goea, geneid2name = create_goea(gaf='../data/raw/ontology/sgd.gaf', obo='../data/raw/ontology/go-basic.obo',background='../data/interim/go_background_list',
+goea, geneid2name,a = create_goea(gaf='../data/raw/ontology/sgd.gaf', obo='../data/raw/ontology/go-basic.obo',background='../data/interim/go_background_list',
                                sdg_info_tab='../data/raw/ontology/SGD_features.tab')
 
-# %% jupyter={"outputs_hidden": true}
+# %% tags=[] jupyter={"outputs_hidden": true}
 e_rew.analyze_components_biology(goea, geneid2name,True)
[…]

### 2021-11-16 notebooks/02-Figure2-051321.Rmd
updated supp figure notebooks

--- 2021-06-02 notebooks/02-Figure2-051321.Rmd
@@
 # Load packages
-```{r, message=FALSE,warning=FALSE}
+```{r message=FALSE, warning=FALSE}
 if (!require('tidyverse')) {
@@
 ```{r}
+# smake<-setClass("smake",slots=list(input="list"))
+# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
+# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
+# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
+```
+
+```{r tags=c()}
 #df_filename <-snakemake$input$df_filename
@@
 
+```{r}
+text_size = 15
+label_size = 17
+```
+
 # Figure2 A,B
@@
   xlab("Degree") +
-  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1) +
-  theme(strip.text.y = element_text(angle = 0)) +
+  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1,size=8) +
+  theme(strip.text.y = element_text(angle = 0),axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
   scale_y_continuous(labels = scales::label_scientific(digits = 1))
@@
   xlab("Degree") +
-  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1) +
-  theme(strip.text.y = element_text(angle = 0)) +
+  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1, size=8) +
+  theme(strip.text.y = element_text(angle = 0),axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
   scale_y_continuous(labels = scales::label_scientific(digits = 1))
@@
   labels = c("A", "B"),
-  ncol = 2
+  ncol = 2,label_size = 20
 )
@@
 #ggsave("reports/figures/paper_figures_0202_pcc_only/fig2.png", plot = deg_scatter_plots, width = 10, height = 10)
-print(cor.test(pcc_df$deg[pcc_df$deg<10],pcc_df$sens[pcc_df$deg<10],method='spearman',exact=FALSE))
+print(cor.test(pcc_df$deg[pcc_df$deg<10&pcc_df$group=='real'],pcc_df$sens[pcc_df$deg<10&pcc_df$group=='real'],method='spearman',exact=FALSE))
 ```
@@
 # Figure2 C,D,E
-```{r}
+```{r tags=c()}
 pcc_rewire_df <- pcc_df_random%>%group_by(random_id)%>%
@@
     eff_deg_pearson = cor.test(eff,deg)$estimate,
-    sens_deg_spearman = cor.test(sens,deg, method="spearman")$estimate
+    sens_deg_spearman = cor.test(sens,deg, method="spearman",exact=FALSE)$estimate
   )
@@
   theme_bw() +
-  theme(panel.spacing = unit(2, "lines")) +
+  theme(panel.spacing = unit(2, "lines"),axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
   scale_y_continuous(expand = c(0, 0))
@@
   theme_bw() +
-  theme(panel.spacing = unit(2, "lines"), legend.position = "bottom") +
+  theme(panel.spacing = unit(2, "lines"), legend.position = "bottom",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
   scale_color_discrete(labels = c("Random networks", "Genetic network")) +
@@
 
-pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
+pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size))) #+
 distr_plots <- plot_grid(pcc_degree_dens + theme(legend.position = ""),
@@
   ggdraw(p4 + theme(legend.position = "")),
-  labels = c("C", "D", "E"), nrow = 1
+  labels = c("C", "D", "E"), nrow = 1, rel_widths=c(0.3,0.35,0.35),label_size = 20
 )
@@
 pcc_eff_dens <-
-  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
+  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness (a.u.)") + theme(legend.position = "none",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
     coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
@@
 pcc_sensitivity_dens <-
-  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity (a.u.)") + theme(legend.position = "none")) #+
+  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity (a.u.)") + theme(legend.position = "none",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size))) #+
 #        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
@@
   #+theme(legend.position='none'),
-  labels = c("F", "G"), ncol = 2
+  labels = c("F", "G"), ncol = 2,label_size = 20
 )
@@
 if(snakemake@params['save']==TRUE){
-  figure_folder = "reports/figures/paper_figures_052521/"
+  figure_folder = "../reports/figures/paper_figures_052521/"
 combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
-ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=10,height=12)
+ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=12,height=12)
 }

### 2021-11-16 notebooks/03-Fig3abde_4acd-051821.Rmd
updated supp figure notebooks

@@
 # Load packages
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, tags=c()}
 #library(tidyverse)
@@
   sensor_connectivity_plot
+```
+
+```{r}
+(1/10001)<0.0001
 ```
@@
    ) +
+    scale_x_discrete(labels=c('EC1','EC2','EC3','Non-effector\ngenes'))+
   xlab("") +
@@
        axis.text.y=element_text(size=10),
-        axis.title.y=element_text(size=14),legend.title = element_blank(),  axis.text.x = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
+        axis.title.y=element_text(size=14),legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
 eff_deg_comp
@@
   ylab("Effectiveness (a.u.)") +
+    scale_x_discrete(labels=c('EC1','EC2','EC3','Non-effector\ngenes'))+
+
   theme_bw() +
@@
         axis.text.y=element_text(size=10),
-        axis.title.y=element_text(size=14),axis.text.x = element_blank(), legend.title = element_blank())
+        axis.title.y=element_text(size=14), legend.title = element_blank())
 eff_eff_comp
@@
 ```{r}
-if(snakemake@params['save']==TRUE){
+#if(snakemake@params['save']==TRUE){
   figure_folder = "../reports/figures/paper_figures_052521/"
@@
 ggsave(glue("{figure_folder}/fig4a.png"),plot=eff_neighbor_degree_plot,width=3,height=3)
-ggsave(glue("{figure_folder}/fig4c.png"),plot=eff_deg_comp+theme(legend.position='right'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig4c.png"),plot=eff_deg_comp+theme(legend.position='none'),width=3,height=3)
 ggsave(glue("{figure_folder}/fig4d.png"),plot=eff_eff_comp+theme(legend.position='none'),width=3,height=3)
@@
 ggsave(glue("{figure_folder}/fig3d_legend.pdf"),plot=legend_plot, width=10, height=2)
-}
+#}
 ```
+
+```{r}
+
+```

### 2021-11-16 notebooks/05-Rewired-network-sensors.py

@@ -1,3 +1,4 @@
+# -*- coding: utf-8 -*-
 # ---
 # jupyter:
 #   jupytext:
@@ -56,7 +57,7 @@ e_rew.get_sensor_effector(True)
 goea, geneid2name,a = create_goea(gaf='../data/raw/ontology/sgd.gaf', obo='../data/raw/ontology/go-basic.obo',background='../data/interim/go_background_list',
                                sdg_info_tab='../data/raw/ontology/SGD_features.tab')
 
-# %% tags=[] jupyter={"outputs_hidden": true}
+# %% tags=[]
 e_rew.analyze_components_biology(goea, geneid2name,True)
 e_rew.analyze_components_biology(goea, geneid2name,False)
 
@@ -125,8 +126,12 @@ legend_elements.extend(
     #                          markerfacecolor='#a6611a', markersize=0, linestyle="-")
     ]
 )
-lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(-0.5, -0.1),ncol=5)
+lgd = ax.legend(handles=legend_elements, fontsize=22,
+                loc='center right', bbox_to_anchor=(1.8, 0.5),ncol=1,
+               frameon=False)
 nx.draw_networkx_edges(nx.induced_subgraph(e_rew.graph_gc, sensors_pcc.orf_name.tolist()),pos=pos, edge_color='red', alpha=0.5)
+ax.axis('off')
+
 plt.savefig(f'../reports/figures/paper_figures_supp/figs1.png',bbox_inches='tight',dpi=150)
 
 # %% [markdown]
@@ -195,11 +200,20 @@ res2 = sensors_df_rew.groupby('level_0')['go_group'].nunique()
 idxx = np.argwhere(np.array(res)>0).reshape(1,-1)[0]
 idxx2 = np.argwhere(np.array(res2)>0).reshape(1,-1)[0]
 
+# %% [markdown]
+# There are 68 rewired networks (out of 500) with a sensor cluster
+
 # %%
 len(idxx)
 
+# %% [markdown]
+# This corresponds to 13.6% of rewired networks
+
 # %%
 len(idxx)/len(res)
+
+# %% [markdown]
+# While 25% of these are GO enriched, that corresponds to only 3.4% of 500 cases
 
 # %%
 len(idxx2)/len(res2)
[…]

### 2021-11-16 notebooks/02-Figure2-051321.Rmd
stage changes to figures

@@
 ```{r message=FALSE, warning=FALSE}
+if (!require('remotes')){
+install.packages('remotes', repos='http://cran.us.r-project.org')}
 if (!require('tidyverse')) {

### 2021-11-16 notebooks/01-Fig1bcd_3c_4b_5df-052421.py

@@ -7,7 +7,7 @@
 #       extension: .py
 #       format_name: percent
 #       format_version: '1.3'
-#       jupytext_version: 1.5.2
+#       jupytext_version: 1.12.0
 #   kernelspec:
 #     display_name: Python (enm)
 #     language: python
@@ -45,7 +45,7 @@ figure_folder = "reports/figures/paper_figures_052521"
 # # Read Enm pickle object
 
 # %%
-with open(snakemake.input.pickle_file_name,'rb') as f:
+with open('../data/interim/pcc.pickle','rb') as f:
     e_pcc = pickle.load(f)
 
 
@@ -102,7 +102,7 @@ if snakemake.params['save']:
 
 # %%
 e_pcc.figure_path=figure_folder
-e_pcc.heatmap_annotated( save_figure=snakemake.params['save'] , figure_name = 'fig1b_right')
+e_pcc.heatmap_annotated( save_figure=False , figure_name = 'fig1b_right')
 
 # %% [markdown]
 # # Figure 1C
@@ -154,6 +154,12 @@ estimates = np.fromiter(map(lambda x: run_permutation_test(pooled,z.size,y.size,
 diffCount = len(np.where(estimates >= delta)[0])
 pval_cc = ((float(diffCount)+1)/(float(numSamples)+1))
 pval_cc
+
+# %%
+delta
+
+# %%
+estimates
 
 # %%
 import seaborn as sns
@@ -276,7 +282,7 @@ import seaborn as sns
 sensor_colors = [mpl.colors.to_hex(i) for i in sns.color_palette('Set3')]
 
 # %%
-# change_go_group_names = snakemake.params['change_go_group_name']
+change_go_group_names = True#snakemake.params['change_go_group_name']
 # sensor_go_rename = {
 #   "cellular response to iron ion starvation":'Iron ion transport' ,
 # "mitochondria-nucleus signaling pathway":  "Mitochondria-nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle",
@@ -286,13 +292,11 @@ sensor_colors = [mpl.colors.to_hex(i) for i in sns.color_palette('Set3')]
 # }
 
 # %%
-sensors_pcc = pd.read_csv(snakemake.input.sensors_pcc)
+sensors_pcc = pd.read_csv('../data/interim/sensors_df.csv')
 # sensor_colors = ["#377EB8", "#4DAF4A", "#984EA3", "#FF7F00", "#FFFF33"]
[…]

### 2021-11-16 notebooks/06-Figs3s4.py

@@ -6,7 +6,7 @@
 #       extension: .py
 #       format_name: percent
 #       format_version: '1.3'
-#       jupytext_version: 1.5.2
+#       jupytext_version: 1.12.0
 #   kernelspec:
 #     display_name: Python (enm)
 #     language: python
@@ -20,68 +20,24 @@ import numpy as np
 import matplotlib.pyplot as plt
 from enm.utils import *
 
-# %% [markdown]
-# # Giant component size change
-
 # %%
-cpcc = pd.read_csv('../data/interim/costanzo_pcc_ALL')
-
-
-# %%
-def get_giant_component(G):
-    Gc = max([G.subgraph(c).copy() for c in nx.connected_components(G)], key=len)
-    return Gc
-
-
-# %%
-ne_ratio_list = []
-nv_ratio_list = []
-
-# %%
-thr_list =  [0.05,0.1,0.2,0.25,0.3,0.35,0.4]
-
-# %%
-for i in np.arange(0.2,0.75,0.05):
-    df = cpcc.loc[cpcc.pcc>=i]
-    nw = nx.from_pandas_edgelist(df,source='gene1',target='gene2')
-    nw_g = get_giant_component(nw)
-    n_e = len(nw_g.edges)
-    ne_ratio_list.append(n_e/len(nw.edges))
-    n_v = len(nw_g.nodes)
-    nv_ratio_list.append(n_v/len(nw.nodes))
-
-    print(f"{i} : ne = {n_e}, ne_ratio: {n_e/len(nw.edges)}, nv = {n_v}, nv_ratio = {n_v/len(nw.nodes)}")
-
-# %%
-xlab = "Pearson's Correlation Coefficient threshold"
-
-# %%
-fig, ax = plt.subplots(1,1,figsize=(8,8))
-ax.plot(np.arange(0.2,0.75,0.05),nv_ratio_list,'o-')
-ax.set_ylabel('Giant component size to network size')
-ax.set_xlabel(xlab)
-
-# %% [markdown]
-# # Effector and sensor clusters with GO enrichments
+thr_list = snakemake.params['thr_list']#[0.05,0.1,0.2,0.25,0.3,0.35,0.4]
 
 # %%
 sensor_df_names = [ ]
 
 # %%
-effector_dfs = get_result_dfs('effectors_df', thr_list)
[…]

### 2021-11-16 notebooks/03-Fig3abde_4acd-051821.Rmd

@@
 #library(tidyverse)
+if (!require('remotes')){
+install.packages('remotes', repos='http://cran.us.r-project.org')}
 if (!require('tidyverse')) {

### 2021-11-16 notebooks/07-Figs1.Rmd

---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.12.0
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r tags=c()}
Sys.setenv(TAR = "/bin/tar")

# Load packages
if (!require('remotes')){
install.packages('remotes', repos='http://cran.us.r-project.org')}
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}

plot_density_prs <-
    function
(
    df , x , xlab= 'Effectiveness (a.u.)', ylab='Density', coord_trans='log10', linesize = 1
)
{
    color_pal <- c('#00BFC4','#F8766D')
dens_plot <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= df%>%filter(group=='real'),
               aes(x={{x}} ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= df%>%filter(group=='random'),
               aes(x={{x}} ,y=..scaled..,fill=random_id, color=group),linetype='dashed',
               stat = 'density' ,show.legend=F)+#, binwidth = 0.1) + 
    geom_vline(data= df%>%filter(group=='real')%>%mutate(g = T),aes(xintercept = mean({{x}}), linetype='Real'),color=color_pal[1],size=linesize, show.legend=NA)+
    geom_vline(data= df%>%filter(group=='random')%>%mutate(g = F),aes(xintercept = mean({{x}}),linetype='Random', group=random_id),color=color_pal[2], size=linesize,show.legend=NA)+
    scale_linetype_manual(name = "Limits", labels = c("real", "random"), values = c("Real" = 3, "Random" = 3)) +
    guides(colour=guide_legend(override.aes = list(linetype=1)),
           linetype=guide_legend(override.aes=list(colour=color_pal)))+
    theme_bw()+
    ylab(ylab)+
    xlab(xlab)+
    coord_trans(x = coord_trans)+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
    scale_color_discrete(labels=c('Rewired\nnetworks','PSN'))+
theme(legend.text = element_text(margin = margin(b = 10)), panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
dens_plot
}
```

```{r}
# smake<-setClass("smake",slots=list(input="list"))
# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
```

```{r, tags=c()}
pcc_df_list <- list()

for(i in snakemake@params[['thr_list']]){
    pcc_df <- read_csv(paste0(snakemake@params[['folder_prefix']],'_',i,'/pcc_df.csv'))
    pcc_df_random <- read_csv(paste0(snakemake@params[['folder_prefix']],'_',i,'/pcc_df_random_10.csv'))%>%mutate(random_id=factor(random_id))
    pcc_df <- pcc_df %>%
      mutate(data = "pcc") %>%
      mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real") %>%
      bind_rows(
        pcc_df_random %>% mutate(data = "pcc") %>% mutate(sens_norm = sens / nrow(pcc_df), eff_norm = eff / nrow(pcc_df), group = "random")
      ) %>%
      mutate(group = fct_relevel(group, c("real", "random")))
    pcc_df_list[[as.character(i)]] <- pcc_df
}
```

```{r}
text_size = 15
label_size = 17
```

```{r}
pcc_eff_dens <-
  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness (a.u.)")
dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
pcc_eff_dens_list <- list()
pcc_sens_dens_list <- list()
for(i in as.character( snakemake@params[['thr_list']])){
   pcc_eff_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df_list[[i]], eff_norm, xlab = "Effectiveness (a.u.)") + theme(plot.title = element_text(size = 20),legend.position = "none",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
    ggtitle(paste0('PCC≥',i))+coord_trans(x = "log10", xlim = c(NA, NA)) +
    scale_x_continuous(
      breaks = scales::trans_breaks("log10", function(x) 10^x),
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    )) #+

    pcc_sensitivity_dens <-
      cowplot::ggdraw(plot_density_prs(pcc_df_list[[i]], sens_norm, xlab = "Sensitivity (a.u.)") +ggtitle(paste0('PCC≥',i))+ theme(plot.title = element_text(size = 20),legend.position = "none",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size))) #+
    pcc_eff_dens_list[[i]]<- pcc_eff_dens + theme(legend.position='none') 
    pcc_sens_dens_list[[i]]<- pcc_sensitivity_dens + theme(legend.position='none')
}

```

```{r}
eff_group <- plot_grid(plotlist=pcc_eff_dens_list)

```

```{r}
sens_group <- plot_grid(plotlist=pcc_sens_dens_list)

```

```{r, fig.height=12, fig.width=8}
options(repr.plot.width  = 8,
        repr.plot.height = 12)
plot_grid(eff_group, sens_group, ncol=1,labels = c('A','B'), label_size=20)
if(snakemake@params[['save']]==TRUE){

    ggsave('reports/figures/paper_figures_supp/figures1_comb.png',width= 8, height=12)
    }
```

### 2021-11-16 notebooks/09-Fig1b.Rmd

--- 2021-09-12 notebooks/06-Fig1b-091121.Rmd
@@
 #use_python("/home/oma21/miniconda3/envs/enm/bin/python")
-use_condaenv('enm')
-setwd('../')
-#source('enm/R/plot_density_prs.R')
-#source('enm/R/get.subclusters.dendrogram.R')
+#use_condaenv('enm')
+#setwd('../')
 library(RColorBrewer)
-col =brewer.pal(n=8,name='Set1')
-sensor_colors = col[1:4]
-effector_colors = col[5:8]
 ```
@@
 import pandas as pd
-import plotnine as p9
-import pickle 
 import os
-import re
-import itertools as itr
 from enm.Enm import Enm
@@
 import scipy.cluster.hierarchy as sch
-print(os.getcwd())
-with open(f'../data/interim/pcc.pickle','rb') as f:
+with open(f'data/interim/pcc.pickle','rb') as f:
     e_pcc = pickle.load(f)
@@
 prs_mat_cl_orig = prs_mat_cl
-# , optimal_ordering=True)
-#row_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl), method=method)
-# ,optimal_ordering=True)
-#col_linkage_cl = sch.linkage(sch.distance.pdist(prs_mat_cl.T), method=method)
-
 row_dist_orig = sch.distance.pdist((prs_mat),metric = metric)

### 2021-11-18 notebooks/02-Figure2-051321.Rmd
fixed getting input name from snakemake in notebooks

@@
 if(snakemake@params['save']==TRUE){
-  figure_folder = "../reports/figures/paper_figures_052521/"
+  figure_folder = "reports/figures/paper_figures_052521/"
 combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))

### 2021-11-18 notebooks/03-Fig3abde_4acd-051821.Rmd
fixed getting input name from snakemake in notebooks

@@
 #if(snakemake@params['save']==TRUE){
-  figure_folder = "../reports/figures/paper_figures_052521/"
+  figure_folder = "reports/figures/paper_figures_052521/"
 ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)

### 2021-11-18 notebooks/01-Fig1bcd_3c_4b_5df-052421.py

@@ -45,7 +45,7 @@ figure_folder = "reports/figures/paper_figures_052521"
 # # Read Enm pickle object
 
 # %%
-with open('../data/interim/pcc.pickle','rb') as f:
+with open(snakemake.input.pickle_file_name,'rb') as f:
     e_pcc = pickle.load(f)
 
 
@@ -292,7 +292,7 @@ change_go_group_names = True#snakemake.params['change_go_group_name']
 # }
 
 # %%
-sensors_pcc = pd.read_csv('../data/interim/sensors_df.csv')
+sensors_pcc = pd.read_csv(snakemake.input.sensors_pcc)
 # sensor_colors = ["#377EB8", "#4DAF4A", "#984EA3", "#FF7F00", "#FFFF33"]
 # if change_go_group_names:
 #    sensors_pcc['go_group']=sensors_pcc['go_group'].map(sensor_go_rename,na_action='ignore')
@@ -448,13 +448,13 @@ lgd = ax.legend(handles=antenna_legend,
                 loc = 'center',
                 bbox_to_anchor=(0., 0., 1, 1))
 # if snakemake.params['save']:
-fig.savefig(f'../reports/figures/paper_figures_052521//fig3f_legend.png',dpi=150,bbox_inches='tight')
+fig.savefig(f'{figure_folder}/fig3f_legend.png',dpi=150,bbox_inches='tight')
 
 # %% [markdown]
 # # Figure 4B
 
 # %%
-effector_pcc = pd.read_csv('../data/interim/effectors_df.csv')
+effector_pcc = pd.read_csv(snakemake.input.effector_pcc)
 #effector_colors = ["#A65628", "#F781BF", "#999999"]
 effector_order_orig = effector_pcc.groupby('go_group').eff.median().sort_values().index.tolist()
 effector_colors = ["#A65628", "#F781BF", "#999999",'blue','yellow','red']
@@ -521,121 +521,65 @@ lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center', bbox_to_ancho
 nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
 ax.axis('off')
 # if snakemake.params['save']:
-plt.savefig(f'../{figure_folder}/fig4b.png',bbox_inches='tight',dpi=150)
[…]

### 2021-11-18 notebooks/03-Fig3abde_4acd-051821.Rmd
fixed issues running snakemake

@@
 ```{r}
-sensor_neighbor_degree_plot <- pcc_df %>%
+#sensor_neighbor_degree_plot <- 
+pcc_df %>%
   mutate(is_sensor = factor(ifelse(sens > quantile(sens, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
-  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
-  geom_boxplot() +
-  theme_bw() +
-  ylab("Log(Average neighbor degree)") +
-  xlab("") +
-  stat_compare_means() +
-  scale_x_discrete(labels = c("Sensor", "Not Sensor"))
-  sensor_neighbor_degree_plot
+  group_by(is_sensor)%>%
+    summarise(mean = mean(neighbor_degree), median = median(neighbor_degree))
 
+```
+
+```{r}
+25.18/3.38
+```
+
+```{r}
+20.7/3
 ```

### 2021-11-18 notebooks/01-Fig1bcd_3c_4b_5df-052421.py

@@ -526,7 +526,7 @@ plt.savefig(f'{figure_folder}/fig4b.png',bbox_inches='tight',dpi=150)
 # %% [markdown]
 # # Figure 5D/F
 
-# %%
+# %% jupyter={"outputs_hidden": true} tags=[]
 #define source and target effector/sensor clusters
 
 eff_group = 'Chromosome segregation'
@@ -567,19 +567,20 @@ for itr, i in enumerate(sensor_order):
                                 markerfacecolor=sensor_colors[itr], markersize=12, linestyle="None")
         )
 
-for itr, i in enumerate(effector_order):
-    if i == eff_group:
-        orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
-        sub_list.extend(orf_names_to_plot)
 
-        nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
-                            node_color=effector_colors[itr],
-                            node_shape='s',edgecolors='black',
-                            linewidths=1)
-        nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, orf_names_to_plot), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
+orf_names_to_plot = effector_pcc.loc[effector_pcc.effector_cluster==0,'orf_name'].tolist()
+sub_list.extend(orf_names_to_plot)
+
+nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
+                    node_color=effector_colors[0],
+                    node_shape='s',edgecolors='black',
+                    linewidths=1)
+nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, orf_names_to_plot), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
 ax.set_facecolor('white')
 ax.axis('off')
 if snakemake.params['save']:
     plt.savefig(f'{figure_folder}/fig5d.png',bbox_inches='tight',dpi=150)
 
 nx.write_edgelist(nx.induced_subgraph(e_pcc.graph_gc,sub_list),f'{figure_folder}/path1.csv', delimiter=',',data=False)
+
+# %%

### 2021-11-18 scripts/pcc.py

@@ -15,7 +15,8 @@ print("calculating node positions")
 enm.spring_pos(seed=12)
 strain_ids = pd.read_csv(snakemake.input['strain_ids_file'])
 print("clustering prs matrix")
-enm.cluster_matrix(enm.prs_mat)
+if snakemake.params['cluster_matrix']:
+    enm.cluster_matrix(enm.prs_mat)
 neighbor_degree = []
 for i in enm.graph_gc.nodes:
     neighbor_degree.append(np.average([enm.df.loc[enm.df.orf_name==a,'deg'].values for a in nx.neighbors(enm.graph_gc,i)]))

### 2022-05-12 notebooks/23-FigureS6-S7.Rmd
figure S6-S7

--- 2021-11-18 notebooks/02-Figure2-051321.Rmd
@@
 # smake<-setClass("smake",slots=list(input="list"))
-# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
-# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
-# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
+# nw_type = 'coessentiality'
+# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv",
+#                                     "pcc_df"=glue('../data/interim/{nw_type}/{nw_type}_df_human.csv'),
+#                                     "pcc_df_random"=glue('../data/interim/{nw_type}/{nw_type}_df_random_500_human.csv')))
+
+```
+
+```{r}
+# smake<-setClass("smake",slots=list(input="list"))
+# nw_type = 'pombe'
+# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv",
+#                                     "pcc_df"=glue('../data/interim/{nw_type}/{nw_type}_df_corr.csv'),
+#                                     "pcc_df_random"=glue('../data/interim/{nw_type}/{nw_type}_df_random_500_corr.csv')))
+
 ```
@@
 
+```{r}
+combined_rewire_df %>% filter(type != "real")%>%summary()
+```
+
 # Figure2 G, F
@@
 ```{r}
-if(snakemake@params['save']==TRUE){
-  figure_folder = "reports/figures/paper_figures_052521/"
+#if(snakemake@params['save']==TRUE){
+  figure_folder = glue("../reports/figures/paper_figures_{nw_type}/")
 combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
 ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=12,height=12)
-}
+#}
 ```
+
+```{r}
+
+```

### 2022-05-13 notebooks/02-Figure2-051321.Rmd
hardcoded file paths for figure text size edits

@@
 ```{r}
-# smake<-setClass("smake",slots=list(input="list"))
-# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
-# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
-# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
+ smake<-setClass("smake",slots=list(input="list"))
+ snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim_bak_3/sensor_connectivity_df.csv", "pcc_df"='../data/interim_bak_3/pcc_df.csv',
+                                     "sensors_pcc"="../data/interim_bak_3/sensors_df.csv",'effector_pcc'='../data/interim_bak_3/effectors_df.csv',
+                                     "pcc_df_random" = "../data/interim_bak_3/pcc_df_random_100.csv",
+"rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
+"rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
+```
+
+```{r}
+read_csv(snakemake@input[['pcc_df_random']])
 ```
@@
 ```{r}
-text_size = 15
-label_size = 17
+text_size = 8
+label_size = 12
 ```
@@
   xlab("Degree") +
-  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1,size=8) +
+  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1,size=4) +
   theme(strip.text.y = element_text(angle = 0),axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
@@
   xlab("Degree") +
-  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1, size=8) +
+  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1, size=4) +
   theme(strip.text.y = element_text(angle = 0),axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
@@
 ```{r}
-if(snakemake@params['save']==TRUE){
-  figure_folder = "reports/figures/paper_figures_052521/"
+#if(snakemake@params['save']==TRUE){
+  figure_folder = "../reports/figures/paper_figures_051222/"
 combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
-ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=12,height=12)
-}
+ggsave(glue("{figure_folder}/fig2.pdf"),plot=combined_plot,width=6,height=6)
+#}
 ```
+
+```{r}
+
+```

### 2022-05-13 notebooks/03-Fig3abde_4acd-051821.Rmd
hardcoded file paths for figure text size edits

@@
 ```{r include=FALSE, eval=FALSE}
-# sessionInfo()
-# smake<-setClass("smake",slots=list(input="list"))
-# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
-# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
-# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
+#sessionInfo()
+smake<-setClass("smake",slots=list(input="list"))
+snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim_bak_3/sensor_connectivity_df.csv", "pcc_df"='../data/interim_bak_3/pcc_df.csv',"sensors_pcc"="../data/interim_bak_3/sensors_df.csv",'effector_pcc'='../data/interim_bak_3/effectors_df.csv',
+"rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim_bak_3/prs_ranked_goa_rows.csv",
+"rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim_bak_3/prs_ranked_goa_columns.csv"))
 ```
@@
 #sensor_neighbor_degree_plot <- 
-pcc_df %>%
-  mutate(is_sensor = factor(ifelse(sens > quantile(sens, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
-  group_by(is_sensor)%>%
-    summarise(mean = mean(neighbor_degree), median = median(neighbor_degree))
+sensor_neighbor_degree_plot <- pcc_df %>%
+  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real")%>%
+  mutate(is_sensor = factor(ifelse(sens_norm > quantile(sens_norm, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
+  ggplot(aes(x = is_sensor, y = log(neighbor_degree))) +
+  geom_boxplot() +
+  theme_bw() +
+    theme(axis.text=element_text(size=text_size),axis.title = element_text(size=label_size))+
+  ylab("Log(Average neighbor degree)") +
+  xlab("") +
+  stat_compare_means() +
+  scale_x_discrete(labels = c("Effector", "Not Effector"))
+sensor_neighbor_degree_plot
+# pcc_df %>%
+#   mutate(is_sensor = factor(ifelse(sens > quantile(sens, 0.99), TRUE, FALSE), levels = c(TRUE, FALSE))) %>%
+#   group_by(is_sensor)%>%
+#     summarise(mean = mean(neighbor_degree), median = median(neighbor_degree))
 
@@
 ```{r}
+text_size = 8
+label_size = 12
+```
+
+```{r}
 sensor_connectivity_plot <-
@@
   ylab("Density") +
-  xlab("% of between group edges\nto all edges") +
+  xlab("% of between group edges") +
   theme_bw() +
   scale_color_discrete(labels = c("Random sampled set", "Sensors")) +
-  theme(legend.position = "right") +
+  theme(legend.position = "right",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size) ) +
   scale_y_continuous(expand = c(0, 0))
@@
   theme(
-        axis.title.y=element_text(size=14),
-        axis.text.y=element_text(size=10),
+        axis.title.y=element_text(size=label_size),
+        axis.text.y=element_text(size=text_size),
         axis.text.x = element_text(size=7), 
@@
 ```{r}
+comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)]
+```
+
+```{r}
 comparisons <- str_split(sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]$Comparison,' - ',2)
@@
     comparisons = comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)],
-    annotation = c("***","*" , "*" ,  "***"), y_position = c(0.007, 0.005,0.0058, 0.0078),
+    annotation = c("*","***" , "*" ,  "***"), y_position = c(0.005,0.007,  0.0053, 0.0075),
                                            textsize = 3#, 0.008)
@@
   theme(
-        axis.title.y=element_text(size=14),
-        axis.text.y=element_text(size=10),
+        axis.title.y=element_text(size=label_size),
+        axis.text.y=element_text(size=text_size),
         axis.text.x = element_text(size=7),
-        legend.title = element_blank())+
-        ylim(NA, 0.008)
+        legend.title = element_blank())#+
+        #ylim(NA, 0.008)
 
@@
   theme_bw() +
+    theme(axis.text=element_text(size=text_size),axis.title = element_text(size=label_size))+
   ylab("Log(Average neighbor degree)") +
@@
   theme(
-       axis.text.y=element_text(size=10),
-        axis.title.y=element_text(size=14),legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
+       axis.text.y=element_text(size=text_size),
+        axis.title.y=element_text(size=label_size),legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
 eff_deg_comp
@@
   theme(
-        axis.text.y=element_text(size=10),
-        axis.title.y=element_text(size=14), legend.title = element_blank())
+        axis.text.y=element_text(size=text_size),
+        axis.title.y=element_text(size=label_size), legend.title = element_blank())
 eff_eff_comp
@@
 #if(snakemake@params['save']==TRUE){
-  figure_folder = "reports/figures/paper_figures_052521/"
-ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
-ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
-ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3.9,height=2.1)
-ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3.9,height=2.1)
+  figure_folder = "../reports/figures/paper_figures_051222/"
+ggsave(glue("{figure_folder}/fig3a.pdf"),plot=sensor_neighbor_degree_plot,width=2.1,height=)
+ggsave(glue("{figure_folder}/fig3b.pdf"),plot=sensor_connectivity_plot+theme(legend.position='none'),width=2.1,height=2.1)
+ggsave(glue("{figure_folder}/fig3d.pdf"),plot=sens_deg_comp+theme(legend.position='none'),width=3.2,height=2.1)
+ggsave(glue("{figure_folder}/fig3e.pdf"),plot=sens_sens_comp+theme(legend.position='none'),width=3.9,height=2.1)
 
-ggsave(glue("{figure_folder}/fig4a.png"),plot=eff_neighbor_degree_plot,width=3,height=3)
-ggsave(glue("{figure_folder}/fig4c.png"),plot=eff_deg_comp+theme(legend.position='none'),width=3,height=3)
-ggsave(glue("{figure_folder}/fig4d.png"),plot=eff_eff_comp+theme(legend.position='none'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig4a.pdf"),plot=eff_neighbor_degree_plot,width=3,height=3)
+ggsave(glue("{figure_folder}/fig4c.pdf"),plot=eff_deg_comp+theme(legend.position='none'),width=3,height=3)
+ggsave(glue("{figure_folder}/fig4d.pdf"),plot=eff_eff_comp+theme(legend.position='none'),width=3,height=3)
 
@@
 ```{r}
+ggsave(glue("{figure_folder}/fig3b_withlegend.pdf"),plot=sensor_connectivity_plot,width=2.1,height=2.1)
 
 ```
+
+```{r}
+ggsave(glue("{figure_folder}/fig3d.pdf"),plot=sens_deg_comp+theme(legend.position='none'),width=3.2,height=2.1)
+
+```
+
+```{r}
+ggsave(glue("{figure_folder}/fig3e.pdf"),plot=sens_sens_comp+theme(legend.position='none'),width=3.2,height=2.1)
+
+```
+
+```{r}
+
+```

### 2022-05-13 notebooks/01-Fig1bcd_3c_4b_5df-052421.py

@@ -39,13 +39,29 @@ from enm.utils import *
 
 # %%
 #os.chdir('../')
-figure_folder = "reports/figures/paper_figures_052521"
+figure_folder = "../reports/figures/paper_figures_051222"
+
+
+# %%
+class smake:
+    def __init__(self):
+        self.input = {}
+        self.output={}
+
+
+# %%
+snakemake = smake()
+
+# %%
+snakemake.input['pickle_file_name'] = '../data/interim_bak_3/pcc.pickle'
+snakemake.input['sensors_pcc'] = '../data/interim_bak_3/sensors_df.csv'
+snakemake.input['effector_pcc'] = '../data/interim_bak_3/effectors_df.csv'
 
 # %% [markdown]
 # # Read Enm pickle object
 
 # %%
-with open(snakemake.input.pickle_file_name,'rb') as f:
+with open(snakemake.input['pickle_file_name'],'rb') as f:
     e_pcc = pickle.load(f)
 
 
@@ -292,7 +308,7 @@ change_go_group_names = True#snakemake.params['change_go_group_name']
 # }
 
 # %%
-sensors_pcc = pd.read_csv(snakemake.input.sensors_pcc)
+sensors_pcc = pd.read_csv(snakemake.input['sensors_pcc'])
 # sensor_colors = ["#377EB8", "#4DAF4A", "#984EA3", "#FF7F00", "#FFFF33"]
 # if change_go_group_names:
 #    sensors_pcc['go_group']=sensors_pcc['go_group'].map(sensor_go_rename,na_action='ignore')
@@ -415,7 +431,7 @@ lgd = ax.legend(handles=legend_elements,
                 loc = 'center',
                 bbox_to_anchor=(0., 0., 1, 1))
 # if snakemake.params['save']:
-#     fig.savefig(f'{figure_folder}/fig3c_legend.png', dpi=150, pad_inches=0)#, bbox_inches='tight')
+fig.savefig(f'{figure_folder}/fig3c_legend.pdf', dpi=300, pad_inches=0)#, bbox_inches='tight')
 
 # %%
 antenna_legend = []
@@ -448,13 +464,13 @@ lgd = ax.legend(handles=antenna_legend,
                 loc = 'center',
                 bbox_to_anchor=(0., 0., 1, 1))
 # if snakemake.params['save']:
-fig.savefig(f'{figure_folder}/fig3f_legend.png',dpi=150,bbox_inches='tight')
[…]

### 2022-06-27 notebooks/02-Figure2-051321.Rmd
finalized figure text sizes

@@
 
-```{r}
-read_csv(snakemake@input[['pcc_df_random']])
-```
-
 ```{r tags=c()}
@@
   ggplot(aes(x = deg, y = eff_norm)) +
-  geom_point() +
+  geom_point(size=0.1) +
   #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
@@
   ggplot(aes(x = deg, y = sens_norm)) +
-  geom_point() +
+  geom_point(size=0.1) +
   #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
